### 2018-02-28 paper_own_docker/main.tex
Initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
\usepackage[options]{algorithm2e}                                     % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Attack Graph Generation for Micro-service
Architecture
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Stevica Bozhinoski$^{1}$ and Amjad Ibrahim$^{2}$% <-this % stops a space
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

\section{RELATED WORK}

\section{ARCHITECTURE}

\subsubsection{Breadth-first search}

We use a modification of the breadth first search algorithm to find the nodes and the edges.
\begin{algorithm}
	\SetAlgoLined
	\KwData{goal\_container, topology, container\_exploitability}
	\KwResult{nodes, edges}
	nodes, edges, queue, passed\_nodes = list(), dict\{\}, Queue(), []\;
	queue.put(goal\_container)\;

	nodes = get\_nodes()\;
	\While{! queue.isEmpty()}{
		ending\_node = queue.get()\;
		passed\_nodes[ending\_node] = True\;
		cont\_exp\_end = container\_exploitability[ending\_node]\;
		neighbours = topology[ending\_node]\;
	    \For{neighbour in neighbours}{
	    	\If{neighbour == "outside"}{

	    			edges.append(create\_edges())\;
	    			continue\;

	    		}
	        \If{! passed\_nodes[neighbour]}
	        {queue.put(neighbour)\;}
            \If{neighbour == goal\_container}{
            	continue\;}
            edges.append(create\_edges())
	    	}

	}

\caption{Breadth-first search algorithm for generating an attack graph.}
\end{algorithm}

The algorithm requires the goal container, the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the exploitable vulnerability.
Then into a while loop we iterate through every node, check its neighbours and add the edges. If the neighbour was not passed, then we add it to the queue. The algorithm terminates when the queue is empty.
\section{EXPERIMENTS}
\section{CONCLUSION}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{ACKNOWLEDGMENT}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{99}

\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.

\end{thebibliography}

\end{document}

### 2018-02-28 System/components/writer.py

@@ -1,0 +1,69 @@
+#!/usr/bin/env python
+"""This module is responsible for writing the outputs into files."""
+
+import os
+import json
+import yaml
+
+from components import reader
+
+def write_topology_file(list_services, example_folder_path=""):
+    """Writes list of services into a file."""
+
+    config = reader.read_config_file()
+    folder_name = os.path.basename(example_folder_path)
+    topology_writing_path = os.path.join(config["examples-results-path"],
+                                         folder_name,
+                                         "topology.json")
+
+    with open(topology_writing_path, "w") as topology:
+        json.dump(list_services, topology)
+
+def write_attack_graph(example_folder_path, graph):
+    """Writes the attack graph onto a dot file."""
+
+    config = reader.read_config_file()
+    folder_name = os.path.basename(example_folder_path)
+    attack_graph_path = os.path.join(config["examples-results-path"],
+                                     folder_name,
+                                     "attack_graph.dot")
+    graph.render(attack_graph_path)
+
+def write_topology_graph(example_folder_path, graph):
+    """Writes the topology graph onto a dot file."""
+
+    config = reader.read_config_file()
+    folder_name = os.path.basename(example_folder_path)
+    topology_graph_path = os.path.join(config["examples-results-path"],
+                                       folder_name,
+                                       "topology_graph.dot")
+    graph.render(topology_graph_path)
+def write_clarictl_config_file(clairctl_home, clairctl_config_dict):
+    """Writes the modified clairctl config file."""
+
+    with open(os.path.join(clairctl_home, "clairctl.yml"), "w") as outfile:
+        yaml.dump(clairctl_config_dict, outfile)
+
+def copy_vulnerability_file(clairctl_home, image_name, old_root_path, parent_folder):
+    """Copies the vulnerability file from clairctl to the local location."""
+
+    config = reader.read_config_file(old_root_path)
+    parent_folder = os.path.basename(parent_folder)
+
+    os.rename(os.path.join(clairctl_home,
+                           "docker-compose-data",
+                           "clairctl-reports",
+                           "json",
+                           "analysis-"+image_name+"-latest.json"),
+              os.path.join(old_root_path,
+                           config["examples-results-path"],
+                           parent_folder,
+                           image_name+"-vulnerabilities.json"))
+
+def create_folder(example_folder_path):
+    """Creates folder for storing the intermediate results of the examples."""
+
+    config = reader.read_config_file()
[…]

### 2018-04-30 paper_own_docker/main.tex
Updating .tex file with related work, and cleaning up the examples

@@
 \section{RELATED WORK}
+
+What makes us different to previous work:
+- To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
+- The paper(Automated Generation of Attack Graphs Using NVD) does not provide an example/ or clearly define the attack graph generation process.
+Their main focus is to evaluate attack rules.
+They dont use Clair as well.
+They do not offer any performance comparison between different topologies.
 

### 2018-04-30 System/examples/example/samba/src/ctdb/client/client_call.c

@@ -1,184 +1,0 @@
-/*
-   CTDB client code
-
-   Copyright (C) Amitay Isaacs  2015
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/network.h"
-#include "system/filesys.h"
-
-#include <talloc.h>
-#include <tevent.h>
-#include <tdb.h>
-
-#include "lib/util/tevent_unix.h"
-
-#include "common/reqid.h"
-#include "common/srvid.h"
-#include "common/comm.h"
-
-#include "protocol/protocol.h"
-#include "protocol/protocol_api.h"
-
-#include "client/client_private.h"
-#include "client/client.h"
-
-
-/*
- * Handle REQ_CALL and REPLY_CALL
- */
-
-struct ctdb_client_call_state {
-	struct ctdb_client_context *client;
-	uint32_t reqid;
-	struct ctdb_reply_call *reply;
-	struct tevent_req *req;
-};
-
-static int ctdb_client_call_state_destructor(
-	struct ctdb_client_call_state *state);
-static void ctdb_client_call_done(struct tevent_req *subreq);
-
-struct tevent_req *ctdb_client_call_send(TALLOC_CTX *mem_ctx,
-					 struct tevent_context *ev,
-					 struct ctdb_client_context *client,
-					 struct ctdb_req_call *request)
-{
-	struct ctdb_req_header h;
-	struct tevent_req *req, *subreq;
-	struct ctdb_client_call_state *state;
-	uint32_t reqid;
-	uint8_t *buf;
-	size_t datalen, buflen;
-	int ret;
-
-	req = tevent_req_create(mem_ctx, &state,
-				struct ctdb_client_call_state);
[…]

### 2018-04-30 System/examples/example/samba/src/ctdb/common/system_aix.c

@@ -1,395 +1,0 @@
-/* 
-   ctdb system specific code to manage raw sockets on aix
-
-   Copyright (C) Ronnie Sahlberg  2007
-   Copyright (C) Andrew Tridgell  2007
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-
-#include "replace.h"
-#include "system/network.h"
-#include "system/filesys.h"
-#include "system/wait.h"
-
-#include "lib/util/debug.h"
-#include "lib/util/blocking.h"
-
-#include "protocol/protocol.h"
-
-#include <netinet/if_ether.h>
-#include <netinet/ip6.h>
-#include <net/if_arp.h>
-#include <sys/ndd_var.h>
-#include <sys/kinfo.h>
-#include <pcap.h>
-
-#include "common/logging.h"
-#include "common/system.h"
-
-
-#if 0
-This function is no longer used and its code should be moved into
-send tcp packet   after that function has been enhanced to do ipv6 as well.
-
-/* This function is used to open a raw socket to send tickles from
- */
-int ctdb_sys_open_sending_socket(void)
-{
-	int s, ret;
-	uint32_t one = 1;
-
-	s = socket(AF_INET, SOCK_RAW, IPPROTO_RAW);
-	if (s == -1) {
-		DEBUG(DEBUG_CRIT,(" failed to open raw socket (%s)\n",
-			 strerror(errno)));
[…]

### 2018-04-30 System/examples/example/samba/src/ctdb/server/ctdb_update_record.c

@@ -1,369 +1,0 @@
-/* 
-   implementation of the update record control
-
-   Copyright (C) Andrew Tridgell  2007
-   Copyright (C) Ronnie Sahlberg  2007
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/network.h"
-#include "system/time.h"
-
-#include <talloc.h>
-#include <tevent.h>
-
-#include "lib/tdb_wrap/tdb_wrap.h"
-#include "lib/util/debug.h"
-#include "lib/util/samba_util.h"
-#include "lib/util/util_process.h"
-
-#include "ctdb_private.h"
-#include "ctdb_client.h"
-
-#include "common/system.h"
-#include "common/common.h"
-#include "common/logging.h"
-
-struct ctdb_persistent_write_state {
-	struct ctdb_db_context *ctdb_db;
-	struct ctdb_marshall_buffer *m;
-	struct ctdb_req_control_old *c;
-	uint32_t flags;
-};
-
-/* don't create/update records that does not exist locally */
-#define UPDATE_FLAGS_REPLACE_ONLY	1
-
-/*
-  called from a child process to write the data
- */
-static int ctdb_persistent_store(struct ctdb_persistent_write_state *state)
-{
-	int ret, i;
-	struct ctdb_rec_data_old *rec = NULL;
-	struct ctdb_marshall_buffer *m = state->m;
-
-	ret = tdb_transaction_start(state->ctdb_db->ltdb->tdb);
-	if (ret == -1) {
[…]

### 2018-04-30 System/examples/example/samba/src/ctdb/server/ctdbd.c

@@ -1,317 +1,0 @@
-/* 
-   standalone ctdb daemon
-
-   Copyright (C) Andrew Tridgell  2006
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/filesys.h"
-#include "system/time.h"
-#include "system/wait.h"
-#include "system/network.h"
-
-#include <popt.h>
-#include <talloc.h>
-/* Allow use of deprecated function tevent_loop_allow_nesting() */
-#define TEVENT_DEPRECATED
-#include <tevent.h>
-
-#include "lib/util/debug.h"
-#include "lib/util/samba_util.h"
-
-#include "ctdb_private.h"
-
-#include "common/reqid.h"
-#include "common/system.h"
-#include "common/cmdline.h"
-#include "common/common.h"
-#include "common/logging.h"
-
-static struct {
-	const char *nlist;
-	const char *transport;
-	const char *myaddress;
-	const char *public_address_list;
-	const char *event_script_dir;
-	const char *notification_script;
-	const char *logging;
-	const char *recovery_lock;
-	const char *db_dir;
-	const char *db_dir_persistent;
-	const char *db_dir_state;
-	const char *public_interface;
-	int         valgrinding;
-	int         nosetsched;
-	int         start_as_disabled;
-	int         start_as_stopped;
-	int         no_lmaster;
-	int         no_recmaster;
-	int	    script_log_level;
[…]

### 2018-04-30 System/examples/example/samba/src/ctdb/tests/eventscripts/05.system.monitor.018.sh

@@ -1,123 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "Check throttling of warnings"
-
-CTDB_MONITOR_MEMORY_USAGE="70:80"
-CTDB_MONITOR_SWAP_USAGE=""
-
-# Below threshold, nothing logged
-setup_memcheck 67 0
-ok_null
-simple_test
-
-setup_memcheck 71 0
-ok "WARNING: System memory utilization 71% >= threshold 70%"
-simple_test
-
-# 2nd time at same level, nothing logged
-setup_memcheck 71 0
-ok_null
-simple_test
-
-setup_memcheck 73 0
-ok "WARNING: System memory utilization 73% >= threshold 70%"
-simple_test
-
-# 2nd time at same level, nothing logged
-setup_memcheck 73 0
-ok_null
-simple_test
-
-setup_memcheck 79 0
-ok "WARNING: System memory utilization 79% >= threshold 70%"
-simple_test
-
-setup_memcheck 80 0
-required_result 1 <<EOF
-ERROR: System memory utilization 80% >= threshold 80%
-MemTotal:        3940712 kB
-MemFree:          225268 kB
-Buffers:          146120 kB
-Cached:          416754 kB
-SwapCached:        56016 kB
-Active:          2422104 kB
-Inactive:        1019928 kB
-Active(anon):    1917580 kB
-Inactive(anon):   523080 kB
-Active(file):     504524 kB
-Inactive(file):   496848 kB
-Unevictable:        4844 kB
-Mlocked:            4844 kB
-SwapTotal:       5857276 kB
-SwapFree:        5857276 kB
-...
-USER       PID %CPU %MEM    VSZ   RSS TTY      STAT START   TIME COMMAND
-root         2  0.0  0.0      0     0 ?        S    Aug28   0:00 [kthreadd]
-root         3  0.0  0.0      0     0 ?        S    Aug28   0:43  \_ [ksoftirqd/0]
-...
-root         1  0.0  0.0   2976   624 ?        Ss   Aug28   0:07 init [2]
-root       495  0.0  0.0   3888  1640 ?        Ss   Aug28   0:00 udevd --daemon
-...
-[MORE FAKE ps OUTPUT]
-EOF
-simple_test
-
-# Fall back into warning at same level as last warning... should log
-setup_memcheck 79 0
-ok "WARNING: System memory utilization 79% >= threshold 70%"
-simple_test
-
[…]

### 2018-04-30 System/examples/example/samba/src/ctdb/tests/eventscripts/10.interface.monitor.016.sh

@@ -1,18 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "Missing interface, CTDB_PARTIALLY_ONLINE_INTERFACES=yes, warn"
-
-setup_ctdb
-
-CTDB_PARTIALLY_ONLINE_INTERFACES="yes"
-
-iface=$(ctdb_get_1_interface)
-ip link delete "$iface"
-
-ok <<EOF
-ERROR: Monitored interface dev123 does not exist
-EOF
-
-simple_test

### 2018-04-30 System/examples/example/samba/src/ctdb/tests/eventscripts/11.natgw.015.sh

@@ -1,62 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "basic configuration, multiple transitions"
-
-setup_ctdb
-
-echo "*** Master node..."
-
-setup_ctdb_natgw <<EOF
-192.168.1.21 master
-192.168.1.22
-192.168.1.23
-192.168.1.24
-EOF
-
-ok_null
-simple_test_event "ipreallocated"
-
-ok "default via ${CTDB_NATGW_DEFAULT_GATEWAY} dev ethXXX  metric 10 "
-simple_test_command ip route show
-
-ok_natgw_master_ip_addr_show
-simple_test_command ip addr show "$CTDB_NATGW_PUBLIC_IFACE"
-
-echo "*** Slave node..."
-
-setup_ctdb_natgw <<EOF
-192.168.1.21
-192.168.1.22 master
-192.168.1.23
-192.168.1.24
-EOF
-
-ok "NAT gateway configuration has changed"
-simple_test_event "ipreallocated"
-
-ok "default via ${FAKE_CTDB_NATGW_MASTER} dev ethXXX  metric 10 "
-simple_test_command ip route show
-
-ok_natgw_slave_ip_addr_show
-simple_test_command ip addr show "$CTDB_NATGW_PUBLIC_IFACE"
-
-echo "*** Master node again..."
-
-setup_ctdb_natgw <<EOF
-192.168.1.21 master
-192.168.1.22
-192.168.1.23
-192.168.1.24
-EOF
-
-ok "NAT gateway configuration has changed"
-simple_test_event "ipreallocated"
-
-ok "default via ${CTDB_NATGW_DEFAULT_GATEWAY} dev ethXXX  metric 10 "
-simple_test_command ip route show
-
-ok_natgw_master_ip_addr_show
-simple_test_command ip addr show "$CTDB_NATGW_PUBLIC_IFACE"
-

### 2018-04-30 System/examples/example/samba/src/ctdb/tests/takeover/lcp2.009.sh

@@ -1,31 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "3 nodes, 3 healthy -> all disconnected"
-
-export CTDB_TEST_LOGLEVEL=0
-
-required_result <<EOF
-192.168.21.254 -1
-192.168.21.253 -1
-192.168.21.252 -1
-192.168.20.254 -1
-192.168.20.253 -1
-192.168.20.252 -1
-192.168.20.251 -1
-192.168.20.250 -1
-192.168.20.249 -1
-EOF
-
-simple_test 1,1,1 <<EOF
-192.168.20.249 0
-192.168.20.250 1
-192.168.20.251 2
-192.168.20.252 0
-192.168.20.253 1
-192.168.20.254 2
-192.168.21.252 0
-192.168.21.253 1
-192.168.21.254 2
-EOF

### 2018-04-30 System/examples/example/samba/src/examples/libsmbclient/teststatvfs.c

@@ -1,106 +1,0 @@
-#include <sys/types.h>
-#include <sys/statvfs.h>
-#include <stdio.h> 
-#include <unistd.h>
-#include <string.h> 
-#include <time.h> 
-#include <errno.h>
-#include <libsmbclient.h> 
-#include "get_auth_data_fn.h"
-
-
-int main(int argc, char * argv[]) 
-{ 
-    int             ret;
-    int             debug = 0;
-    char *          p;
-    char            path[2048];
-    struct statvfs  statvfsbuf;
-    
-    smbc_init(get_auth_data_fn, debug); 
-    
-    for (;;)
-    {
-        fprintf(stdout, "Path: ");
-        *path = '\0';
-	p = fgets(path, sizeof(path) - 1, stdin);
-	if (p == NULL) {
-		fprintf(stderr, "failed to read from stdin\n");
-		return 1;
-	}
-        if (strlen(path) == 0)
-        {
-            return 0;
-        }
-
-        p = path + strlen(path) - 1;
-        if (*p == '\n')
-        {
-            *p = '\0';
-        }
-    
-        ret = smbc_statvfs(path, &statvfsbuf);
-
-        if (ret < 0)
-        {
-            perror("fstatvfs");
-        }
-        else
-        {
-            printf("\n");
-            printf("Block Size: %lu\n", statvfsbuf.f_bsize);
-            printf("Fragment Size: %lu\n", statvfsbuf.f_frsize);
-            printf("Blocks: %llu\n",
-                   (unsigned long long) statvfsbuf.f_blocks);
-            printf("Free Blocks: %llu\n",
-                   (unsigned long long) statvfsbuf.f_bfree);
-            printf("Available Blocks: %llu\n",
-                   (unsigned long long) statvfsbuf.f_bavail);
-            printf("Files : %llu\n",
-                   (unsigned long long) statvfsbuf.f_files);
-            printf("Free Files: %llu\n",
-                   (unsigned long long) statvfsbuf.f_ffree);
-            printf("Available Files: %llu\n",
-                   (unsigned long long) statvfsbuf.f_favail);
-#ifdef HAVE_FSID_INT
-            printf("File System ID: %lu\n",
-                   (unsigned long) statvfsbuf.f_fsid);
-#endif
-            printf("\n");
-
-            printf("Flags: 0x%lx\n", statvfsbuf.f_flag);
-            printf("Extended Features: ");
-
-            if (statvfsbuf.f_flag & SMBC_VFS_FEATURE_NO_UNIXCIFS)
[…]

### 2018-04-30 System/examples/example/samba/src/libcli/smb/smb2cli_query_directory.c

@@ -1,210 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   smb2 lib
-   Copyright (C) Volker Lendecke 2011
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "system/network.h"
-#include "lib/util/tevent_ntstatus.h"
-#include "smb_common.h"
-#include "smbXcli_base.h"
-
-struct smb2cli_query_directory_state {
-	uint8_t fixed[32];
-	uint8_t dyn_pad[1];
-	struct iovec *recv_iov;
-	uint8_t *data;
-	uint32_t data_length;
-};
-
-static void smb2cli_query_directory_done(struct tevent_req *subreq);
-
-struct tevent_req *smb2cli_query_directory_send(TALLOC_CTX *mem_ctx,
-						struct tevent_context *ev,
-						struct smbXcli_conn *conn,
-						uint32_t timeout_msec,
-						struct smbXcli_session *session,
-						struct smbXcli_tcon *tcon,
-						uint8_t level,
-						uint8_t flags,
-						uint32_t file_index,
-						uint64_t fid_persistent,
-						uint64_t fid_volatile,
-						const char *mask,
-						uint32_t outbuf_len)
-{
-	struct tevent_req *req, *subreq;
-	struct smb2cli_query_directory_state *state;
-	uint8_t *fixed;
-	uint8_t *dyn;
-	size_t dyn_len;
-
-	req = tevent_req_create(mem_ctx, &state,
-				struct smb2cli_query_directory_state);
-	if (req == NULL) {
-		return NULL;
[…]

### 2018-04-30 System/examples/example/samba/src/libds/common/flags.h

@@ -1,286 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   User/Group specific flags
-
-   Copyright (C) Andrew Tridgell 2001-2003
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/* User flags for "userAccountControl" */
-#define UF_SCRIPT	 			0x00000001  /* NT or Lan Manager Login script must be executed */
-#define UF_ACCOUNTDISABLE			0x00000002
-#define UF_00000004				0x00000004
-#define UF_HOMEDIR_REQUIRED			0x00000008
-
-#define UF_LOCKOUT				0x00000010
-#define UF_PASSWD_NOTREQD			0x00000020
-#define UF_PASSWD_CANT_CHANGE			0x00000040
-#define UF_ENCRYPTED_TEXT_PASSWORD_ALLOWED	0x00000080
-
-#define UF_TEMP_DUPLICATE_ACCOUNT		0x00000100 /* Local user account in usrmgr */
-#define UF_NORMAL_ACCOUNT			0x00000200
-#define UF_00000400				0x00000400
-#define UF_INTERDOMAIN_TRUST_ACCOUNT		0x00000800
-
-#define UF_WORKSTATION_TRUST_ACCOUNT		0x00001000
-#define UF_SERVER_TRUST_ACCOUNT			0x00002000
[…]

### 2018-04-30 System/examples/example/samba/src/nsswitch/libwbclient/wbclient.c

@@ -1,333 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   Winbind client API
-
-   Copyright (C) Gerald (Jerry) Carter 2007
-   Copyright (C) Matthew Newton 2015
-
-
-   This library is free software; you can redistribute it and/or
-   modify it under the terms of the GNU Lesser General Public
-   License as published by the Free Software Foundation; either
-   version 3 of the License, or (at your option) any later version.
-
-   This library is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
-   Library General Public License for more details.
-
-   You should have received a copy of the GNU Lesser General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/* Required Headers */
-
-#include "replace.h"
-#include "libwbclient.h"
-
-/* From wb_common.c */
-
-struct winbindd_context;
-
-NSS_STATUS winbindd_request_response(struct winbindd_context *wbctx,
-				     int req_type,
-				     struct winbindd_request *request,
-				     struct winbindd_response *response);
-NSS_STATUS winbindd_priv_request_response(struct winbindd_context *wbctx,
-					  int req_type,
-					  struct winbindd_request *request,
-					  struct winbindd_response *response);
-struct winbindd_context *winbindd_ctx_create(void);
-void winbindd_ctx_free(struct winbindd_context *ctx);
-
-/* Global context used for non-Ctx functions */
-
-static struct wbcContext wbcGlobalCtx = {
-	.winbindd_ctx = NULL,
-	.pw_cache_size = 0,
-	.pw_cache_idx = 0,
-	.gr_cache_size = 0,
-	.gr_cache_idx = 0
-};
-
-/*
- result == NSS_STATUS_UNAVAIL: winbind not around
[…]

### 2018-04-30 System/examples/example/samba/src/nsswitch/tests/test_idmap_rid.sh

@@ -1,66 +1,0 @@
-#!/bin/sh
-#
-# Test id mapping with various SIDs and idmap_rid
-#
-
-if [ $# -lt 1 ]; then
-	echo Usage: $0 DOMAIN RANGE_START
-	exit 1
-fi
-
-DOMAIN="$1"
-RANGE_START="$2"
-
-wbinfo="$VALGRIND $BINDIR/wbinfo"
-failed=0
-
-. `dirname $0`/../../testprogs/blackbox/subunit.sh
-
-DOMAIN_SID=$($wbinfo -n "@$DOMAIN" | cut -f 1 -d " ")
-if [ $? -ne 0 ] ; then
-    echo "Could not find domain SID" | subunit_fail_test "test_idmap_rid"
-    exit 1
-fi
-
-# Find an unused uid and SID
-RID=66666
-MAX_RID=77777
-while true ; do
-    id $RID
-    if [ $? -ne 0 ] ; then
-	SID="$DOMAIN_SID-$RID"
-	$wbinfo -s $SID
-	if [ $? -ne 0 ] ; then
-	    break
-	fi
-    fi
-    RID=$(expr $RID + 1)
-    if [ $RID -eq $MAX_RID ] ; then
-	echo "Could not find free SID" | subunit_fail_test "test_idmap_rid"
-	exit 1
-    fi
-done
-
-#
-# Test 1: Using non-existing SID to check backend returns a mapping
-#
-
-EXPECTED_ID=$(expr $RID + $RANGE_START)
-out="$($wbinfo --sids-to-unix-ids=$SID)"
-echo "wbinfo returned: \"$out\", expecting \"$SID -> uid/gid $EXPECTED_ID\""
-test "$out" = "$SID -> uid/gid $EXPECTED_ID"
-ret=$?
-testit "Unknown RID from primary domain returns a mapping" test $ret -eq 0 || failed=$(expr $failed + 1)
-
-#
-# Test 2: Using bogus SID with bad domain part to check idmap backend does not generate a mapping
-#
-
-SID=S-1-5-21-1111-2222-3333-666
-out="$($wbinfo --sids-to-unix-ids=$SID)"
-echo "wbinfo returned: \"$out\", expecting \"$SID -> unmapped\""
-test "$out" = "$SID -> unmapped"
-ret=$?
-testit "Bogus SID returns unmapped" test $ret -eq 0 || failed=$(expr $failed + 1)
-
-exit $failed

### 2018-04-30 System/examples/example/samba/src/python/samba/dbchecker.py

@@ -1,2087 +1,0 @@
-# Samba4 AD database checker
-#
-# Copyright (C) Andrew Tridgell 2011
-# Copyright (C) Matthieu Patou <mat@matws.net> 2011
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-import ldb
-import samba
-import time
-from base64 import b64decode
-from samba import dsdb
-from samba import common
-from samba.dcerpc import misc
-from samba.dcerpc import drsuapi
-from samba.ndr import ndr_unpack, ndr_pack
-from samba.dcerpc import drsblobs
-from samba.common import dsdb_Dn
-from samba.dcerpc import security
-from samba.descriptor import get_wellknown_sds, get_diff_sds
-from samba.auth import system_session, admin_session
-from samba.netcmd import CommandError
-from samba.netcmd.fsmo import get_fsmo_roleowner
-
-
-class dbcheck(object):
-    """check a SAM database for errors"""
-
-    def __init__(self, samdb, samdb_schema=None, verbose=False, fix=False,
-                 yes=False, quiet=False, in_transaction=False,
-                 reset_well_known_acls=False):
-        self.samdb = samdb
-        self.dict_oid_name = None
-        self.samdb_schema = (samdb_schema or samdb)
-        self.verbose = verbose
-        self.fix = fix
-        self.yes = yes
-        self.quiet = quiet
-        self.remove_all_unknown_attributes = False
-        self.remove_all_empty_attributes = False
-        self.fix_all_normalisation = False
-        self.fix_all_duplicates = False
-        self.fix_all_DN_GUIDs = False
-        self.fix_all_binary_dn = False
-        self.remove_implausible_deleted_DN_links = False
-        self.remove_plausible_deleted_DN_links = False
-        self.fix_all_string_dn_component_mismatch = False
-        self.fix_all_GUID_dn_component_mismatch = False
[…]

### 2018-04-30 System/examples/example/samba/src/python/samba/samba3/__init__.py

@@ -1,408 +1,0 @@
-# Unix SMB/CIFS implementation.
-# Copyright (C) Jelmer Vernooij <jelmer@samba.org> 2007
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-"""Support for reading Samba 3 data files."""
-
-__docformat__ = "restructuredText"
-
-REGISTRY_VALUE_PREFIX = "SAMBA_REGVAL"
-REGISTRY_DB_VERSION = 1
-
-import os
-import struct
-import tdb
-
-import passdb
-import param as s3param
-
-
-def fetch_uint32(db, key):
-    try:
-        data = db[key]
-    except KeyError:
-        return None
-    assert len(data) == 4
-    return struct.unpack("<L", data)[0]
-
-
-def fetch_int32(db, key):
-    try:
-        data = db[key]
-    except KeyError:
-        return None
-    assert len(data) == 4
-    return struct.unpack("<l", data)[0]
-
-
-class DbDatabase(object):
-    """Simple Samba 3 TDB database reader."""
-    def __init__(self, file):
-        """Open a file.
-
-        :param file: Path of the file to open, appending .tdb or .ntdb.
-        """
-        self.db = tdb.Tdb(file + ".tdb", flags=os.O_RDONLY)
-        self._check_version()
-
-    def _check_version(self):
-        pass
-
-    def close(self):
-        """Close resources associated with this object."""
-        self.db.close()
-
-
-class Registry(DbDatabase):
-    """Simple read-only support for reading the Samba3 registry.
-
-    :note: This object uses the same syntax for registry key paths as
-        Samba 3. This particular format uses forward slashes for key path
-        separators and abbreviations for the predefined key names.
-        e.g.: HKLM/Software/Bar.
-    """
-    def __len__(self):
[…]

### 2018-04-30 System/examples/example/samba/src/source3/auth/auth_ntlmssp.c

@@ -1,230 +1,0 @@
-/* 
-   Unix SMB/Netbios implementation.
-   Version 3.0
-   handle NLTMSSP, server side
-
-   Copyright (C) Andrew Tridgell      2001
-   Copyright (C) Andrew Bartlett 2001-2005,2011
-   Copyright (C) Stefan Metzmacher 2005
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "auth.h"
-#include "libcli/security/security.h"
-
-NTSTATUS auth3_generate_session_info(struct auth4_context *auth_context,
-				     TALLOC_CTX *mem_ctx,
-				     void *server_returned_info,
-				     const char *original_user_name,
-				     uint32_t session_info_flags,
-				     struct auth_session_info **session_info)
-{
-	struct auth_user_info_dc *user_info = NULL;
-	struct auth_serversupplied_info *server_info = NULL;
-	NTSTATUS nt_status;
-
-	/*
-	 * This is a hack, some callers...
-	 *
-	 * Some callers pass auth_user_info_dc, the SCHANNEL and
-	 * NCALRPC_AS_SYSTEM gensec modules.
-	 *
-	 * While the reset passes auth3_check_password() returned.
-	 */
-	user_info = talloc_get_type(server_returned_info,
-				    struct auth_user_info_dc);
-	if (user_info != NULL) {
-		const struct dom_sid *sid;
-		int cmp;
-
-		/*
-		 * This should only be called from SCHANNEL or NCALRPC_AS_SYSTEM
-		 */
-		if (user_info->num_sids != 1) {
-			return NT_STATUS_INTERNAL_ERROR;
-		}
-		sid = &user_info->sids[PRIMARY_USER_SID_INDEX];
-
-		cmp = dom_sid_compare(sid, &global_sid_System);
-		if (cmp == 0) {
[…]

### 2018-04-30 System/examples/example/samba/src/source3/auth/server_info_sam.c

@@ -1,131 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Authentication utility functions
-   Copyright (C) Andrew Tridgell 1992-1998
-   Copyright (C) Andrew Bartlett 2001
-   Copyright (C) Jeremy Allison 2000-2001
-   Copyright (C) Rafal Szczesniak 2002
-   Copyright (C) Volker Lendecke 2006
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "auth.h"
-#include "nsswitch/winbind_client.h"
-#include "passdb.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_AUTH
-
-
-/***************************************************************************
- Is the incoming username our own machine account ?
- If so, the connection is almost certainly from winbindd.
-***************************************************************************/
-
-static bool is_our_machine_account(const char *username)
-{
-	bool ret;
-	char *truncname = NULL;
-	size_t ulen = strlen(username);
-
-	if (ulen == 0 || username[ulen-1] != '$') {
-		return false;
-	}
-	truncname = SMB_STRDUP(username);
-	if (!truncname) {
-		return false;
-	}
-	truncname[ulen-1] = '\0';
-	ret = strequal(truncname, lp_netbios_name());
-	SAFE_FREE(truncname);
-	return ret;
-}
-
-/***************************************************************************
- Make (and fill) a user_info struct from a struct samu
-***************************************************************************/
-
-NTSTATUS make_server_info_sam(TALLOC_CTX *mem_ctx,
-			      struct samu *sampass,
[…]

### 2018-04-30 System/examples/example/samba/src/source3/libads/ads_status.c

@@ -1,157 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   ads (active directory) utility library
-   Copyright (C) Andrew Tridgell 2001
-   Copyright (C) Remus Koos 2001
-   Copyright (C) Andrew Bartlett 2001
-   
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "smb_krb5.h"
-#include "system/gssapi.h"
-#include "smb_ldap.h"
-#include "libads/ads_status.h"
-
-/*
-  build a ADS_STATUS structure
-*/
-ADS_STATUS ads_build_error(enum ads_error_type etype, 
-			   int rc, int minor_status)
-{
-	ADS_STATUS ret;
-
-	if (etype == ENUM_ADS_ERROR_NT) {
-		DEBUG(0,("don't use ads_build_error with ENUM_ADS_ERROR_NT!\n"));
-		ret.err.rc = -1;
-		ret.error_type = ENUM_ADS_ERROR_SYSTEM;
-		ret.minor_status = 0;
-		return ret;	
-	}	
-		
-	ret.err.rc = rc;
-	ret.error_type = etype;		
-	ret.minor_status = minor_status;
-	return ret;
-}
-
-ADS_STATUS ads_build_nt_error(enum ads_error_type etype, 
-			   NTSTATUS nt_status)
-{
-	ADS_STATUS ret;
-
-	if (etype != ENUM_ADS_ERROR_NT) {
-		DEBUG(0,("don't use ads_build_nt_error without ENUM_ADS_ERROR_NT!\n"));
-		ret.err.rc = -1;
[…]

### 2018-04-30 System/examples/example/samba/src/source3/libsmb/libsmb_context.c

@@ -1,798 +1,0 @@
-/*
-   Unix SMB/Netbios implementation.
-   SMB client library implementation
-   Copyright (C) Andrew Tridgell 1998
-   Copyright (C) Richard Sharpe 2000, 2002
-   Copyright (C) John Terpstra 2000
-   Copyright (C) Tom Jansen (Ninja ISD) 2002
-   Copyright (C) Derrell Lipman 2003-2008
-   Copyright (C) Jeremy Allison 2007, 2008
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "libsmb/libsmb.h"
-#include "libsmbclient.h"
-#include "libsmb_internal.h"
-#include "secrets.h"
-#include "../libcli/smb/smbXcli_base.h"
-
-/*
- * Is the logging working / configfile read ?
- */
-static bool SMBC_initialized = false;
-static unsigned int initialized_ctx_count = 0;
-static void *initialized_ctx_count_mutex = NULL;
-
-/*
- * Do some module- and library-wide intializations
- */
-static void
-SMBC_module_init(void * punused)
-{
-    bool conf_loaded = False;
-    char *home = NULL;
-    TALLOC_CTX *frame = talloc_stackframe();
-
-    setup_logging("libsmbclient", DEBUG_STDOUT);
-
-    /* Here we would open the smb.conf file if needed ... */
-
-    home = getenv("HOME");
-    if (home) {
-        char *conf = NULL;
-        if (asprintf(&conf, "%s/.smb/smb.conf", home) > 0) {
-            if (lp_load_client(conf)) {
-                conf_loaded = True;
-            } else {
-                DEBUG(5, ("Could not load config file: %s\n",
-                          conf));
-            }
-            SAFE_FREE(conf);
-        }
-    }
-
-    if (!conf_loaded) {
-        /*
-         * Well, if that failed, try the get_dyn_CONFIGFILE
[…]

### 2018-04-30 System/examples/example/samba/src/source3/locking/brlock.c

@@ -1,2289 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   byte range locking code
-   Updated to handle range splits/merges.
-
-   Copyright (C) Andrew Tridgell 1992-2000
-   Copyright (C) Jeremy Allison 1992-2000
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/* This module implements a tdb based byte range locking service,
-   replacing the fcntl() based byte range locking previously
-   used. This allows us to provide the same semantics as NT */
-
-#include "includes.h"
-#include "system/filesys.h"
-#include "locking/proto.h"
-#include "smbd/globals.h"
-#include "dbwrap/dbwrap.h"
-#include "dbwrap/dbwrap_open.h"
-#include "serverid.h"
-#include "messages.h"
-#include "util_tdb.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_LOCKING
-
-#define ZERO_ZERO 0
-
-/* The open brlock.tdb database. */
-
-static struct db_context *brlock_db;
-
-struct byte_range_lock {
-	struct files_struct *fsp;
-	unsigned int num_locks;
-	bool modified;
-	uint32_t num_read_oplocks;
-	struct lock_struct *lock_data;
-	struct db_record *record;
-};
-
-/****************************************************************************
- Debug info at level 10 for lock struct.
-****************************************************************************/
-
-static void print_lock_struct(unsigned int i, const struct lock_struct *pls)
-{
-	struct server_id_buf tmp;
-
-	DEBUG(10,("[%u]: smblctx = %llu, tid = %u, pid = %s, ",
-			i,
-			(unsigned long long)pls->context.smblctx,
-			(unsigned int)pls->context.tid,
[…]

### 2018-04-30 System/examples/example/samba/src/source3/smbd/file_access.c

@@ -1,248 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Check access to files based on security descriptors.
-   Copyright (C) Jeremy Allison 2005-2006.
-   Copyright (C) Michael Adam 2007.
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "system/filesys.h"
-#include "../libcli/security/security.h"
-#include "../librpc/gen_ndr/ndr_security.h"
-#include "smbd/smbd.h"
-
-#undef  DBGC_CLASS
-#define DBGC_CLASS DBGC_ACLS
-
-/****************************************************************************
- Actually emulate the in-kernel access checking for delete access. We need
- this to successfully return ACCESS_DENIED on a file open for delete access.
-****************************************************************************/
-
-bool can_delete_file_in_directory(connection_struct *conn,
-				  const struct smb_filename *smb_fname)
-{
-	TALLOC_CTX *ctx = talloc_tos();
-	char *dname = NULL;
-	struct smb_filename *smb_fname_parent;
-	bool ret;
-
-	if (!CAN_WRITE(conn)) {
-		return False;
-	}
-
-	if (!lp_acl_check_permissions(SNUM(conn))) {
-		/* This option means don't check. */
-		return true;
-	}
-
-	/* Get the parent directory permission mask and owners. */
-	if (!parent_dirname(ctx, smb_fname->base_name, &dname, NULL)) {
-		return False;
-	}
-
-	smb_fname_parent = synthetic_smb_fname(ctx,
-				dname,
-				NULL,
-				NULL,
-				smb_fname->flags);
-	if (smb_fname_parent == NULL) {
[…]

### 2018-04-30 System/examples/example/samba/src/source3/smbd/globals.h

@@ -1,934 +1,0 @@
-/*
-   Unix SMB/Netbios implementation.
-   smbd globals
-   Copyright (C) Stefan Metzmacher 2009
-   Copyright (C) Jeremy Allison 2010
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "system/select.h"
-#include "librpc/gen_ndr/smbXsrv.h"
-#include "smbprofile.h"
-
-#ifdef USE_DMAPI
-struct smbd_dmapi_context;
-extern struct smbd_dmapi_context *dmapi_ctx;
-#endif
-
-/* how many write cache buffers have been allocated */
-extern unsigned int allocated_write_caches;
-
-/* A singleton cache to speed up searching by dev/inode. */
-struct fsp_singleton_cache {
-	files_struct *fsp;
-	struct file_id id;
-};
-
-extern const struct mangle_fns *mangle_fns;
-
-extern unsigned char *chartest;
-struct tdb_context;
-extern struct tdb_context *tdb_mangled_cache;
-
-/*
-  this determines how many characters are used from the original filename
-  in the 8.3 mangled name. A larger value leads to a weaker hash and more collisions.
-  The largest possible value is 6.
-*/
-extern unsigned mangle_prefix;
-
-struct msg_state;
-
-extern bool logged_ioctl_message;
-
-extern int trans_num;
-
-extern time_t last_smb_conf_reload_time;
-extern time_t last_printer_reload_time;
-extern pid_t background_lpq_updater_pid;
-
-/****************************************************************************
- structure to hold a linked list of queued messages.
- for processing.
[…]

### 2018-04-30 System/examples/example/samba/src/source3/utils/interact.c

@@ -1,135 +1,0 @@
-/*
- * Samba Unix/Linux SMB client library
- *
- * Copyright (C) Gregor Beck 2011
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program.  If not, see <http://www.gnu.org/licenses/>.
- */
-
-/**
- * @brief  Functions to interact with an user.
- * @author Gregor Beck <gb@sernet.de>
- * @date   Aug 2011
- *
- */
-
-#include "includes.h"
-#include "system/filesys.h"
-
-#include "interact.h"
-
-#include <termios.h>
-
-static const char* get_editor(void) {
-	static char editor[64] = {0};
-
-	if (editor[0] == '\0') {
-		const char *tmp = getenv("VISUAL");
-		if (tmp == NULL) {
-			tmp = getenv("EDITOR");
-		}
-		if (tmp == NULL) {
-			tmp = "vi";
-		}
-		snprintf(editor, sizeof(editor), "%s", tmp);
-	}
-
-	return editor;
-}
-
-int interact_prompt(const char* msg, const char* acc, char def) {
-	struct termios old_tio, new_tio;
-	int c;
-
-	tcgetattr(STDIN_FILENO, &old_tio);
-	new_tio=old_tio;
-	new_tio.c_lflag &=(~ICANON & ~ECHO);
-	tcsetattr(STDIN_FILENO, TCSANOW, &new_tio);
-
-	do {
-		d_printf("%s? [%c]\n", msg, def);
-		fflush(stdout);
-		c = getchar();
-		if (c == '\n') {
-			c = def;
-			break;
-		}
-		else if (strchr(acc, tolower(c)) != NULL) {
-			break;
-		}
-		d_printf("Invalid input '%c'\n", c);
-	} while(c != EOF);
[…]

### 2018-04-30 System/examples/example/samba/src/source3/utils/smbcquotas.c

@@ -1,762 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   QUOTA get/set utility
-
-   Copyright (C) Andrew Tridgell		2000
-   Copyright (C) Tim Potter			2000
-   Copyright (C) Jeremy Allison			2000
-   Copyright (C) Stefan (metze) Metzmacher	2003
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "popt_common.h"
-#include "rpc_client/cli_pipe.h"
-#include "../librpc/gen_ndr/ndr_lsa.h"
-#include "rpc_client/cli_lsarpc.h"
-#include "fake_file.h"
-#include "../libcli/security/security.h"
-#include "libsmb/libsmb.h"
-
-static char *server;
-
-/* numeric is set when the user wants numeric SIDs and ACEs rather
-   than going via LSA calls to resolve them */
-static bool numeric;
-static bool verbose;
-
-enum todo_values {NOOP_QUOTA=0,FS_QUOTA,USER_QUOTA,LIST_QUOTA,SET_QUOTA};
-enum exit_values {EXIT_OK, EXIT_FAILED, EXIT_PARSE_ERROR};
-
-static struct cli_state *cli_ipc;
-static struct rpc_pipe_client *global_pipe_hnd;
-static struct policy_handle pol;
-static bool got_policy_hnd;
-static struct user_auth_info *smbcquotas_auth_info;
-
[…]

### 2018-04-30 System/examples/example/samba/src/source3/utils/testparm.c

@@ -1,618 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   Test validity of smb.conf
-   Copyright (C) Karl Auer 1993, 1994-1998
-
-   Extensively modified by Andrew Tridgell, 1995
-   Converted to popt by Jelmer Vernooij (jelmer@nl.linux.org), 2002
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/*
- * Testbed for loadparm.c/params.c
- *
- * This module simply loads a specified configuration file and
- * if successful, dumps it's contents to stdout. Note that the
- * operation is performed with DEBUGLEVEL at 3.
- *
- * Useful for a quick 'syntax check' of a configuration file.
- *
- */
-
-#include "includes.h"
-#include "system/filesys.h"
-#include "popt_common.h"
-#include "lib/param/loadparm.h"
-
-/*******************************************************************
- Check if a directory exists.
-********************************************************************/
-
-static bool directory_exist_stat(const char *dname,SMB_STRUCT_STAT *st)
-{
-	SMB_STRUCT_STAT st2;
-	bool ret;
-
-	if (!st)
-		st = &st2;
-
-	if (sys_stat(dname, st, false) != 0)
-		return(False);
-
-	ret = S_ISDIR(st->st_ex_mode);
-	if(!ret)
-		errno = ENOTDIR;
-	return ret;
-}
-
-/***********************************************
- Here we do a set of 'hard coded' checks for bad
- configuration settings.
-************************************************/
-
[…]

### 2018-04-30 System/examples/example/samba/src/source4/client/cifsdd.c

@@ -1,630 +1,0 @@
-/*
-   CIFSDD - dd for SMB.
-   Main program, argument handling and block copying.
-
-   Copyright (C) James Peach 2005-2006
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "system/filesys.h"
-#include "auth/gensec/gensec.h"
-#include "lib/cmdline/popt_common.h"
-#include "libcli/resolve/resolve.h"
-#include "libcli/raw/libcliraw.h"
-#include "lib/events/events.h"
-
-#include "cifsdd.h"
-#include "param/param.h"
-
-const char * const PROGNAME = "cifsdd";
-
-#define SYNTAX_EXIT_CODE	 1	/* Invokation syntax or logic error. */
-#define EOM_EXIT_CODE		 9	/* Out of memory error. */
-#define FILESYS_EXIT_CODE	10	/* File manipulation error. */
-#define IOERROR_EXIT_CODE	11	/* Error during IO phase. */
-
-struct	dd_stats_record dd_stats;
-
-static int dd_sigint;
-static int dd_sigusr1;
-
-static void dd_handle_signal(int sig)
-{
-	switch (sig)
-	{
-		case SIGINT:
-			++dd_sigint;
-			break;
-		case SIGUSR1:
-			++dd_sigusr1;
-			break;
-		default:
-			break;
-	}
-}
-
-/* ------------------------------------------------------------------------- */
-/* Argument handling.							     */
[…]

### 2018-04-30 System/examples/example/samba/src/source4/heimdal/kdc/krb5tgs.c

@@ -1,2433 +1,0 @@
-/*
- * Copyright (c) 1997-2008 Kungliga Tekniska Högskolan
- * (Royal Institute of Technology, Stockholm, Sweden).
- * All rights reserved.
- *
- * Redistribution and use in source and binary forms, with or without
- * modification, are permitted provided that the following conditions
- * are met:
- *
- * 1. Redistributions of source code must retain the above copyright
- *    notice, this list of conditions and the following disclaimer.
- *
- * 2. Redistributions in binary form must reproduce the above copyright
- *    notice, this list of conditions and the following disclaimer in the
- *    documentation and/or other materials provided with the distribution.
- *
- * 3. Neither the name of the Institute nor the names of its contributors
- *    may be used to endorse or promote products derived from this software
- *    without specific prior written permission.
- *
- * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
- * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
- * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
- * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
- * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
- * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
- * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
- * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
- * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
- * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
- * SUCH DAMAGE.
- */
-
-#include "kdc_locl.h"
-
-/*
- * return the realm of a krbtgt-ticket or NULL
- */
-
-static Realm
[…]

### 2018-04-30 System/examples/example/samba/src/source4/kdc/mit-kdb/kdb_samba.c

@@ -1,185 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   Samba KDB plugin for MIT Kerberos
-
-   Copyright (c) 2010      Simo Sorce <idra@samba.org>.
-   Copyright (c) 2014      Andreas Schneider <asn@samba.org>
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-
-#include "system/kerberos.h"
-
-#include <profile.h>
-#include <kdb.h>
-
-#include "kdc/mit_samba.h"
-#include "kdb_samba.h"
-
-static krb5_error_code kdb_samba_init_library(void)
-{
-	return 0;
-}
-
-static krb5_error_code kdb_samba_fini_library(void)
-{
-	return 0;
-}
-
-static krb5_error_code kdb_samba_init_module(krb5_context context,
-					     char *conf_section,
-					     char **db_args,
-					     int mode)
-{
-	/* TODO mit_samba_context_init */
-	struct mit_samba_context *mit_ctx;
-	krb5_error_code code;
-	int rc;
-
-	rc = mit_samba_context_init(&mit_ctx);
-	if (rc != 0) {
-		return ENOMEM;
-	}
-
-
-	code = krb5_db_set_context(context, mit_ctx);
-
-	return code;
-}
-static krb5_error_code kdb_samba_fini_module(krb5_context context)
-{
-	struct mit_samba_context *mit_ctx;
-
-	mit_ctx = ks_get_context(context);
-	if (mit_ctx == NULL) {
-		return 0;
-	}
-
-	mit_samba_context_free(mit_ctx);
-
-	return 0;
-}
-
-static krb5_error_code kdb_samba_db_create(krb5_context context,
-					   char *conf_section,
-					   char **db_args)
-{
-	/* NOTE: used only by kadmin */
-	return KRB5_KDB_DBTYPE_NOSUP;
-}
-
[…]

### 2018-04-30 System/examples/example/samba/src/source4/rpc_server/drsuapi/dcesrv_drsuapi.c

@@ -1,1070 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-
-   endpoint server for the drsuapi pipe
-
-   Copyright (C) Stefan Metzmacher 2004
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2006
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "librpc/gen_ndr/ndr_drsuapi.h"
-#include "rpc_server/dcerpc_server.h"
-#include "rpc_server/common/common.h"
-#include "dsdb/samdb/samdb.h"
-#include "dsdb/common/util.h"
-#include "libcli/security/security.h"
-#include "libcli/security/session.h"
-#include "rpc_server/drsuapi/dcesrv_drsuapi.h"
-#include "auth/auth.h"
-#include "param/param.h"
-#include "lib/messaging/irpc.h"
-
-#define DRSUAPI_UNSUPPORTED(fname) do { \
-	DEBUG(1,(__location__ ": Unsupported DRS call %s\n", #fname)); \
-	if (DEBUGLVL(2)) NDR_PRINT_IN_DEBUG(fname, r); \
-	DCESRV_FAULT(DCERPC_FAULT_OP_RNG_ERROR); \
-} while (0)
-
-#define DCESRV_INTERFACE_DRSUAPI_BIND(call, iface) \
-	dcesrv_interface_drsuapi_bind(call, iface)
[…]

### 2018-04-30 System/examples/example/samba/src/source4/rpc_server/samr/dcesrv_samr.h

@@ -1,70 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   endpoint server for the samr pipe - definitions
-
-   Copyright (C) Andrew Tridgell 2004
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "param/param.h"
-#include "libds/common/roles.h"
-
-/*
-  this type allows us to distinguish handle types
-*/
-enum samr_handle {
-	SAMR_HANDLE_CONNECT,
-	SAMR_HANDLE_DOMAIN,
-	SAMR_HANDLE_USER,
-	SAMR_HANDLE_GROUP,
-	SAMR_HANDLE_ALIAS
-};
-
-
-/*
-  state asscoiated with a samr_Connect*() operation
-*/
-struct samr_connect_state {
-	struct ldb_context *sam_ctx;
-	uint32_t access_mask;
-};
-
-/*
-  state associated with a samr_OpenDomain() operation
-*/
-struct samr_domain_state {
-	struct samr_connect_state *connect_state;
-	void *sam_ctx;
-	uint32_t access_mask;
-	struct dom_sid *domain_sid;
-	const char *domain_name;
-	struct ldb_dn *domain_dn;
-	enum server_role role;
-	bool builtin;
-	struct loadparm_context *lp_ctx;
-};
-
-/*
-  state associated with a open account handle
-*/
-struct samr_account_state {
-	struct samr_domain_state *domain_state;
-	void *sam_ctx;
-	uint32_t access_mask;
-	struct dom_sid *account_sid;
-	const char *account_name;
-	struct ldb_dn *account_dn;
-};

### 2018-04-30 System/examples/example/samba/src/source4/smb_server/smb2/smb2_server.h

@@ -1,192 +1,0 @@
-/* 
-   Unix SMB2 implementation.
-   
-   Copyright (C) Stefan Metzmacher            2005
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/* the context for a single SMB2 request. This is passed to any request-context 
-   functions */
-struct smb2srv_request {
-	/* the smbsrv_connection needs a list of requests queued for send */
-	struct smb2srv_request *next, *prev;
-
-	/* the server_context contains all context specific to this SMB socket */
-	struct smbsrv_connection *smb_conn;
-
-	/* conn is only set for operations that have a valid TID */
-	struct smbsrv_tcon *tcon;
-
-	/* the session context is derived from the vuid */
-	struct smbsrv_session *session;
-
-#define SMB2SRV_REQ_CTRL_FLAG_NOT_REPLY (1<<0)
-	uint32_t control_flags;
-
-	/* the system time when the request arrived */
-	struct timeval request_time;
-
-	/* a pointer to the per request union smb_* io structure */
-	void *io_ptr;
-
-	/* the ntvfs_request */
-	struct ntvfs_request *ntvfs;
-
-	/* Now the SMB2 specific stuff */
-
-	/* the status the backend returned */
-	NTSTATUS status;
-
-	/* for matching request and reply */
-	uint64_t seqnum;
-
-	/* the id that can be used to cancel the request */
-	uint32_t pending_id;
-
[…]

### 2018-04-30 System/examples/example/samba/src/source4/torture/drs/python/repl_schema.py

@@ -1,352 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-#
-# Tests various schema replication scenarios
-#
-# Copyright (C) Kamen Mazdrashki <kamenim@samba.org> 2010
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-#
-# Usage:
-#  export DC1=dc1_dns_name
-#  export DC2=dc2_dns_name
-#  export SUBUNITRUN=$samba4srcdir/scripting/bin/subunitrun
-#  PYTHONPATH="$PYTHONPATH:$samba4srcdir/torture/drs/python" $SUBUNITRUN repl_schema -U"$DOMAIN/$DC_USERNAME"%"$DC_PASSWORD"
-#
-
-import time
-import random
-
-from ldb import (
-    ERR_NO_SUCH_OBJECT,
-    LdbError,
-    SCOPE_BASE,
-    Message,
-    FLAG_MOD_ADD,
-    FLAG_MOD_REPLACE,
-    )
-import ldb
-
-import drs_base
-from samba.dcerpc import drsuapi, misc
-from samba.drs_utils import drs_DsBind
-
-class DrsReplSchemaTestCase(drs_base.DrsBaseTestCase):
-
-    # prefix for all objects created
-    obj_prefix = None
-    # current Class or Attribute object id
-    obj_id = 0
-
-    def _ds_bind(self, server_name):
-        binding_str = "ncacn_ip_tcp:%s[seal]" % server_name
-
-        drs = drsuapi.drsuapi(binding_str, self.get_loadparm(), self.get_credentials())
-        (drs_handle, supported_extensions) = drs_DsBind(drs)
-        return (drs, drs_handle)
-
-    def _exop_req8(self, dest_dsa, invocation_id, nc_dn_str, exop,
-                   replica_flags=0, max_objects=0):
[…]

### 2018-04-30 System/examples/example/samba/src/source4/torture/local/fsrvp_state.c

@@ -1,492 +1,0 @@
-/*
-   Test suite for FSRVP server state
-
-   Copyright (C) David Disseldorp 2012-2015
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include <unistd.h>
-
-#include "librpc/gen_ndr/security.h"
-#include "lib/param/param.h"
-#include "lib/util/dlinklist.h"
-#include "libcli/resolve/resolve.h"
-#include "librpc/gen_ndr/ndr_fsrvp.h"
-#include "librpc/gen_ndr/ndr_fsrvp_c.h"
-#include "source3/rpc_server/fss/srv_fss_private.h"
-#include "torture/torture.h"
-#include "torture/local/proto.h"
-
-static bool test_fsrvp_state_empty(struct torture_context *tctx)
-{
-	NTSTATUS status;
-	struct fss_global fss_global;
-	struct stat sbuf;
-	char db_dir[] = "fsrvp_torture_XXXXXX";
-	char *db_path = talloc_asprintf(NULL, "%s/%s",
-					mkdtemp(db_dir), FSS_DB_NAME);
-
-	memset(&fss_global, 0, sizeof(fss_global));
-	fss_global.mem_ctx = talloc_new(NULL);
-	fss_global.db_path = db_path;
-
-	status = fss_state_store(fss_global.mem_ctx, fss_global.sc_sets,
-				 fss_global.sc_sets_count, fss_global.db_path);
-	torture_assert_ntstatus_ok(tctx, status,
-				   "failed to store empty fss state");
-
[…]

### 2018-04-30 System/examples/example/samba/src/source4/torture/raw/mux.c

@@ -1,342 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   basic raw test suite for multiplexing
-   Copyright (C) Andrew Tridgell 2003
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "system/filesys.h"
-#include "libcli/raw/libcliraw.h"
-#include "libcli/raw/raw_proto.h"
-#include "libcli/libcli.h"
-#include "torture/util.h"
-#include "torture/raw/proto.h"
-
-#define BASEDIR "\\test_mux"
-
-/*
-  test the delayed reply to a open that leads to a sharing violation
-*/
-static bool test_mux_open(struct torture_context *tctx, struct smbcli_state *cli, TALLOC_CTX *mem_ctx)
-{
-	union smb_open io;
-	NTSTATUS status;
-	int fnum1, fnum2;
-	bool ret = true;
-	struct smbcli_request *req1, *req2;
-	struct timeval tv;
-	double d;
-
-	torture_comment(tctx, "Testing multiplexed open/open/close\n");
-
-	torture_comment(tctx, "send first open\n");
-	io.generic.level = RAW_OPEN_NTCREATEX;
-	io.ntcreatex.in.root_fid.fnum = 0;
-	io.ntcreatex.in.flags = 0;
-	io.ntcreatex.in.access_mask = SEC_FILE_READ_DATA;
-	io.ntcreatex.in.create_options = 0;
-	io.ntcreatex.in.file_attr = FILE_ATTRIBUTE_NORMAL;
[…]

### 2018-04-30 System/examples/example/samba/src/source4/torture/smb2/smb2.c

@@ -1,184 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   SMB torture tester
-   Copyright (C) Jelmer Vernooij 2006
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "libcli/smb2/smb2.h"
-
-#include "torture/smbtorture.h"
-#include "torture/smb2/proto.h"
-#include "../lib/util/dlinklist.h"
-
-static bool wrap_simple_1smb2_test(struct torture_context *torture_ctx,
-				   struct torture_tcase *tcase,
-				   struct torture_test *test)
-{
-	bool (*fn) (struct torture_context *, struct smb2_tree *);
-	bool ret;
-	struct smb2_tree *tree1;
-	TALLOC_CTX *mem_ctx = talloc_new(torture_ctx);
-
-	if (!torture_smb2_connection(torture_ctx, &tree1)) {
-		torture_fail(torture_ctx,
-			    "Establishing SMB2 connection failed\n");
-		return false;
-	}
-
-	/*
-	 * This is a trick:
-	 * The test might close the connection. If we steal the tree context
-	 * before that and free the parent instead of tree directly, we avoid
-	 * a double free error.
-	 */
-	talloc_steal(mem_ctx, tree1);
-
-	fn = test->fn;
-
-	ret = fn(torture_ctx, tree1);
-
-	talloc_free(mem_ctx);
-
-	return ret;
-}
-
-struct torture_test *torture_suite_add_1smb2_test(struct torture_suite *suite,
-						  const char *name,
-						  bool (*run)(struct torture_context *,
-							      struct smb2_tree *))
-{
-	struct torture_test *test;
-	struct torture_tcase *tcase;
-
[…]

### 2018-04-30 System/examples/example/samba/src/testprogs/blackbox/test_export_keytab_heimdal.sh

@@ -1,103 +1,0 @@
-#!/bin/sh
-# Blackbox tests for kinit and kerberos integration with smbclient etc
-# Copyright (C) 2006-2007 Jelmer Vernooij <jelmer@samba.org>
-# Copyright (C) 2006-2008 Andrew Bartlett <abartlet@samba.org>
-
-if [ $# -lt 5 ]; then
-cat <<EOF
-Usage: test_extract_keytab.sh SERVER USERNAME REALM DOMAIN PREFIX SMBCLIENT
-EOF
-exit 1;
-fi
-
-SERVER=$1
-USERNAME=$2
-REALM=$3
-DOMAIN=$4
-PREFIX=$5
-smbclient=$6
-shift 6
-failed=0
-
-samba4bindir="$BINDIR"
-samba_tool="$samba4bindir/samba-tool"
-samba4ktutil="$BINDIR/samba4ktutil"
-newuser="$samba_tool user create"
-
-SERVER_FQDN="$SERVER.$(echo $REALM | tr '[:upper:]' '[:lower:]')"
-
-samba4kinit=kinit
-if test -x $BINDIR/samba4kinit; then
-	samba4kinit=$BINDIR/samba4kinit
-fi
-
-. `dirname $0`/subunit.sh
-. `dirname $0`/common_test_fns.inc
-
-test_keytab() {
-	testname="$1"
-	keytab="$2"
-	principal="$3"
-	expected_nkeys="$4"
-
-	echo "test: $testname"
-
-	NKEYS=$($VALGRIND $samba4ktutil $keytab | grep -i "$principal" | egrep -c "des|aes|arcfour")
-	status=$?
-	if [ x$status != x0 ]; then
-		echo "failure: $testname"
-		return $status
-	fi
-
-	if [ x$NKEYS != x$expected_nkeys ] ; then
-		echo "failure: $testname"
-		return 1
-	fi
-	echo "success: $testname"
-	return 0
-}
-
-USERPASS=testPaSS@01%
-unc="//$SERVER/tmp"
-
-testit "create user locally" $VALGRIND $newuser nettestuser $USERPASS $@ || failed=`expr $failed + 1`
-
-testit "dump keytab from domain" $VALGRIND $samba_tool domain exportkeytab $PREFIX/tmpkeytab $@ || failed=`expr $failed + 1`
-test_keytab "read keytab from domain" "$PREFIX/tmpkeytab" "$SERVER\\\$" 5
[…]

### 2018-04-30 System/examples/examplebig/samba/src/auth/credentials/tests/bind.py

@@ -1,142 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-# This is unit with tests for LDAP access checks
-
-import optparse
-import sys
-import base64
-import copy
-import time
-
-sys.path.insert(0, "bin/python")
-import samba
-from samba.tests.subunitrun import SubunitOptions, TestProgram
-
-import samba.getopt as options
-
-from ldb import SCOPE_BASE, SCOPE_SUBTREE
-
-from samba import gensec
-import samba.tests
-from samba.tests import delete_force
-
-parser = optparse.OptionParser("ldap [options] <host>")
-sambaopts = options.SambaOptions(parser)
-parser.add_option_group(sambaopts)
-
-# use command line creds if available
-credopts = options.CredentialsOptions(parser)
-parser.add_option_group(credopts)
-subunitopts = SubunitOptions(parser)
-parser.add_option_group(subunitopts)
-opts, args = parser.parse_args()
-
-if len(args) < 1:
-    parser.print_usage()
-    sys.exit(1)
-
-host = args[0]
-lp = sambaopts.get_loadparm()
-creds = credopts.get_credentials(lp)
-creds.set_gensec_features(creds.get_gensec_features() | gensec.FEATURE_SEAL)
-creds_machine = copy.deepcopy(creds)
-creds_user1 = copy.deepcopy(creds)
-creds_user2 = copy.deepcopy(creds)
-creds_user3 = copy.deepcopy(creds)
-
-class BindTests(samba.tests.TestCase):
-
-    info_dc = None
-
-    def setUp(self):
-        super(BindTests, self).setUp()
-        # fetch rootDSEs
-
-        self.ldb = samba.tests.connect_samdb(host, credentials=creds, lp=lp, ldap_only=True)
-
-        if self.info_dc is None:
-            res = self.ldb.search(base="", expression="", scope=SCOPE_BASE, attrs=["*"])
-            self.assertEquals(len(res), 1)
-            BindTests.info_dc = res[0]
-        # cache some of RootDSE props
-        self.schema_dn = self.info_dc["schemaNamingContext"][0]
-        self.domain_dn = self.info_dc["defaultNamingContext"][0]
-        self.config_dn = self.info_dc["configurationNamingContext"][0]
-        self.computer_dn = "CN=centos53,CN=Computers,%s" % self.domain_dn
-        self.password = "P@ssw0rd"
[…]

### 2018-04-30 System/examples/examplebig/samba/src/auth/ntlmssp/gensec_ntlmssp.c

@@ -1,246 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  Version 3.0
- *  NTLMSSP Signing routines
- *  Copyright (C) Luke Kenneth Casson Leighton 1996-2001
- *  Copyright (C) Andrew Bartlett <abartlet@samba.org> 2003-2005
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "auth/ntlmssp/ntlmssp.h"
-#include "auth/gensec/gensec.h"
-#include "auth/gensec/gensec_internal.h"
-#include "auth/ntlmssp/ntlmssp_private.h"
-
-NTSTATUS gensec_ntlmssp_magic(struct gensec_security *gensec_security,
-			      const DATA_BLOB *first_packet)
-{
-	if (ntlmssp_blob_matches_magic(first_packet)) {
-		return NT_STATUS_OK;
-	} else {
-		return NT_STATUS_INVALID_PARAMETER;
-	}
-}
-
-/**
- * Return the NTLMSSP master session key
- *
- * @param ntlmssp_state NTLMSSP State
- */
-
-NTSTATUS gensec_ntlmssp_session_key(struct gensec_security *gensec_security,
-				    TALLOC_CTX *mem_ctx,
-				    DATA_BLOB *session_key)
-{
-	struct gensec_ntlmssp_context *gensec_ntlmssp =
-		talloc_get_type_abort(gensec_security->private_data,
-				      struct gensec_ntlmssp_context);
-	struct ntlmssp_state *ntlmssp_state = gensec_ntlmssp->ntlmssp_state;
-
[…]

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/eventscripts/statd-callout.001.sh

@@ -1,15 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "single add-client"
-
-setup_ctdb
-
-FAKE_DATE_OUTPUT="1234565789"
-
-ok_null
-simple_test_event "add-client" "192.168.123.45"
-simple_test_event "update"
-
-check_ctdb_tdb_statd_state "192.168.123.45"

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/eventscripts/statd-callout.002.sh

@@ -1,16 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "2 x add-client, update"
-
-setup_ctdb
-
-FAKE_DATE_OUTPUT="1234565789"
-
-ok_null
-simple_test_event "add-client" "192.168.123.45"
-simple_test_event "add-client" "192.168.123.46"
-simple_test_event "update"
-
-check_ctdb_tdb_statd_state "192.168.123.45" "192.168.123.46"

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/simple/60_recoverd_missing_ip.sh

@@ -1,81 +1,0 @@
-#!/bin/bash
-
-test_info()
-{
-    cat <<EOF
-Verify that the recovery daemon handles unhosted IPs properly.
-
-This test does not do any network level checks to make sure the IP
-address is actually on an interface.  It just consults "ctdb ip".
-
-This is a variation of the "addip" test.
-EOF
-}
-
-. "${TEST_SCRIPTS_DIR}/integration.bash"
-
-ctdb_test_init "$@"
-
-set -e
-
-cluster_is_healthy
-
-# Reset configuration
-ctdb_restart_when_done
-
-select_test_node_and_ips
-
-echo "Running test against node $test_node and IP $test_ip"
-
-get_test_ip_mask_and_iface
-
-echo "Deleting IP $test_ip from all nodes"
-delete_ip_from_all_nodes $test_ip
-try_command_on_node -v $test_node $CTDB ipreallocate
-wait_until_ips_are_on_node ! $test_node $test_ip
-
-try_command_on_node -v all $CTDB ip
-
-my_exit_hook ()
-{
-    if [ -z "$TEST_LOCAL_DAEMONS" ] ; then
-	onnode -q all $CTDB enablescript "10.interface"
-    fi
-}
-
-ctdb_test_exit_hook_add my_exit_hook
-
-# This forces us to wait until the ipreallocated associated with the
-# delips is complete.
-try_command_on_node $test_node $CTDB sync
-
-# Wait for a monitor event.  Then the next steps are unlikely to occur
-# in the middle of a monitor event and will have the expected effect.
-wait_for_monitor_event $test_node
-
-if [ -z "$TEST_LOCAL_DAEMONS" ] ; then
-    # Stop monitor events from bringing up the link status of an interface
-    try_command_on_node $test_node $CTDB disablescript 10.interface
-fi
-
-echo "Marking interface $iface down on node $test_node"
-try_command_on_node $test_node $CTDB setifacelink $iface down
-
-echo "Adding IP $test_ip to node $test_node"
-try_command_on_node $test_node $CTDB addip $test_ip/$mask $iface
-try_command_on_node $test_node $CTDB ipreallocate
-
-echo "Wait long enough for IP verification to have taken place"
-sleep_for 15
-
-echo "Ensuring that IP ${test_ip} is not hosted on node ${test_node} when interface is down"
-if ips_are_on_node '!' $test_node $test_ip; then
[…]

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/src/message_ring.c

@@ -1,366 +1,0 @@
-/*
-   simple ctdb benchmark - send messages in a ring around cluster
-
-   Copyright (C) Amitay Isaacs  2015
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/network.h"
-
-#include "lib/util/time.h"
-#include "lib/util/tevent_unix.h"
-
-#include "client/client.h"
-#include "tests/src/test_options.h"
-#include "tests/src/cluster_wait.h"
-
-#define MSG_ID_BENCH	0
-
-struct message_ring_state {
-	struct tevent_context *ev;
-	struct ctdb_client_context *client;
-	int num_nodes;
-	int timelimit;
-	int interactive;
-	int msg_count;
-	int msg_plus, msg_minus;
-	struct timeval start_time;
-};
-
-static void message_ring_wait(struct tevent_req *subreq);
-static void message_ring_start(struct tevent_req *subreq);
-static void message_ring_each_second(struct tevent_req *subreq);
-static void message_ring_msg_sent(struct tevent_req *subreq);
-static void message_ring_msg_handler(uint64_t srvid, TDB_DATA data,
-				   void *private_data);
-static void message_ring_finish(struct tevent_req *subreq);
-
-static struct tevent_req *message_ring_send(TALLOC_CTX *mem_ctx,
-					    struct tevent_context *ev,
-					    struct ctdb_client_context *client,
-					    int num_nodes, int timelimit,
-					    int interactive)
-{
-	struct tevent_req *req, *subreq;
[…]

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/takeover/lcp2.003.sh

@@ -1,31 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "3 nodes, 1 -> all healthy"
-
-export CTDB_TEST_LOGLEVEL=0
-
-required_result <<EOF
-192.168.21.254 2
-192.168.21.253 0
-192.168.21.252 1
-192.168.20.254 2
-192.168.20.253 0
-192.168.20.252 1
-192.168.20.251 2
-192.168.20.250 0
-192.168.20.249 1
-EOF
-
-simple_test 0,0,0 <<EOF
-192.168.20.249 1
-192.168.20.250 1
-192.168.20.251 1
-192.168.20.252 1
-192.168.20.253 1
-192.168.20.254 1
-192.168.21.252 1
-192.168.21.253 1
-192.168.21.254 1
-EOF

### 2018-04-30 System/examples/examplebig/samba/src/ctdb/tests/tool/ctdb.setdbsticky.004.sh

@@ -1,33 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "set volatile read-only to read-only and sticky by name"
-
-setup_ctdbd <<EOF
-NODEMAP
-0       192.168.20.41   0x0     CURRENT RECMASTER
-1       192.168.20.42   0x0
-2       192.168.20.43   0x0
-
-DBMAP
-0x7a19d84d locking.tdb
-0x4e66c2b2 brlock.tdb READONLY
-0x4d2a432b g_lock.tdb
-0x7132c184 secrets.tdb PERSISTENT
-0x6cf2837d registry.tdb PERSISTENT 42
-EOF
-
-ok_null
-simple_test brlock.tdb
-
-ok <<EOF
-Number of databases:5
-dbid:0x7a19d84d name:locking.tdb path:/var/run/ctdb/DB_DIR/locking.tdb.0
-dbid:0x4e66c2b2 name:brlock.tdb path:/var/run/ctdb/DB_DIR/brlock.tdb.0 STICKY READONLY
-dbid:0x4d2a432b name:g_lock.tdb path:/var/run/ctdb/DB_DIR/g_lock.tdb.0
-dbid:0x7132c184 name:secrets.tdb path:/var/lib/ctdb/persistent/secrets.tdb.0 PERSISTENT
-dbid:0x6cf2837d name:registry.tdb path:/var/lib/ctdb/persistent/registry.tdb.0 PERSISTENT
-EOF
-
-simple_test_other getdbmap

### 2018-04-30 System/examples/examplebig/samba/src/dynconfig/dynconfig.h

@@ -1,58 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Copyright (C) 2001 by Martin Pool <mbp@samba.org>
-   Copyright (C) Jim McDonough (jmcd@us.ibm.com)  2003.
-
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-/**
- * @file dynconfig.h
- *
- * @brief Exported global configurations.
- **/
-
-#define DEFINE_DYN_CONFIG_PROTO(name)			\
-extern const char *dyn_##name;		 			\
-const char *get_dyn_##name(void);			\
-const char *set_dyn_##name(const char *newpath);	\
-bool is_default_dyn_##name(void);
-
-DEFINE_DYN_CONFIG_PROTO(SBINDIR)
-DEFINE_DYN_CONFIG_PROTO(BINDIR)
-DEFINE_DYN_CONFIG_PROTO(CONFIGFILE) /**< Location of smb.conf file. **/
-DEFINE_DYN_CONFIG_PROTO(LOGFILEBASE) /** Log file directory. **/
-DEFINE_DYN_CONFIG_PROTO(LMHOSTSFILE) /** Statically configured LanMan hosts. **/
-DEFINE_DYN_CONFIG_PROTO(CODEPAGEDIR)
-DEFINE_DYN_CONFIG_PROTO(LIBDIR)
-DEFINE_DYN_CONFIG_PROTO(MODULESDIR)
[…]

### 2018-04-30 System/examples/examplebig/samba/src/libcli/auth/spnego_proto.h

@@ -1,28 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   RFC2478 Compliant SPNEGO implementation
-
-   Copyright (C) Jim McDonough <jmcd@us.ibm.com>   2003
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-ssize_t spnego_read_data(TALLOC_CTX *mem_ctx, DATA_BLOB data, struct spnego_data *token);
-ssize_t spnego_write_data(TALLOC_CTX *mem_ctx, DATA_BLOB *blob, struct spnego_data *spnego);
-bool spnego_free_data(struct spnego_data *spnego);
-bool spnego_write_mech_types(TALLOC_CTX *mem_ctx,
-			     const char * const *mech_types,
-			     DATA_BLOB *blob);

### 2018-04-30 System/examples/examplebig/samba/src/libcli/named_pipe_auth/npa_tstream.h

@@ -1,130 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   Copyright (C) Stefan Metzmacher 2009
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#ifndef NPA_TSTREAM_H
-#define NPA_TSTREAM_H
-
-struct tevent_req;
-struct tevent_context;
-struct auth_session_info_transport;
-struct tsocket_address;
-
-struct tevent_req *tstream_npa_connect_send(TALLOC_CTX *mem_ctx,
-					    struct tevent_context *ev,
-					    const char *directory,
-					    const char *npipe,
-					    const struct tsocket_address *client,
-					    const char *client_name_in,
-					    const struct tsocket_address *server,
-					    const char *server_name,
-					    const struct auth_session_info_transport *session_info);
-int _tstream_npa_connect_recv(struct tevent_req *req,
-			      int *perrno,
-			      TALLOC_CTX *mem_ctx,
-			      struct tstream_context **stream,
-			      uint16_t *file_type,
-			      uint16_t *device_state,
-			      uint64_t *allocation_size,
-			      const char *location);
-#define tstream_npa_connect_recv(req, perrno, mem_ctx, stream, f, d, a) \
-	_tstream_npa_connect_recv(req, perrno, mem_ctx, stream, f, d, a, \
-				  __location__)
-
-int _tstream_npa_existing_socket(TALLOC_CTX *mem_ctx,
-				 int fd,
-				 uint16_t file_type,
-				 struct tstream_context **_stream,
-				 const char *location);
-#define tstream_npa_existing_socket(mem_ctx, fd, ft, stream) \
-	_tstream_npa_existing_socket(mem_ctx, fd, ft, stream, \
-				     __location__)
-
-
-/**
- * @brief Accepts a connection for authenticated named pipes
- *
- * @param[in]  mem_ctx          The memory context for the operation
- * @param[in]  ev               The tevent_context for the operation
[…]

### 2018-04-30 System/examples/examplebig/samba/src/libcli/security/security_token.c

@@ -1,151 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   security descriptor utility functions
-
-   Copyright (C) Andrew Tridgell 		2004
-   Copyright (C) Andrew Bartlett 		2010
-   Copyright (C) Stefan Metzmacher 		2005
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "libcli/security/security_token.h"
-#include "libcli/security/dom_sid.h"
-#include "libcli/security/privileges.h"
-
-/*
-  return a blank security token
-*/
-struct security_token *security_token_initialise(TALLOC_CTX *mem_ctx)
-{
-	struct security_token *st;
-
-	st = talloc_zero(mem_ctx, struct security_token);
-	if (!st) {
-		return NULL;
-	}
-
-	return st;
-}
-
-/****************************************************************************
- prints a struct security_token to debug output.
-****************************************************************************/
-void security_token_debug(int dbg_class, int dbg_lev, const struct security_token *token)
-{
-	TALLOC_CTX *mem_ctx;
-	uint32_t i;
-
-	if (!token) {
-		DEBUGC(dbg_class, dbg_lev, ("Security token: (NULL)\n"));
-		return;
-	}
-
-	mem_ctx = talloc_init("security_token_debug()");
-	if (!mem_ctx) {
-		return;
-	}
-
-	DEBUGC(dbg_class, dbg_lev, ("Security token SIDs (%lu):\n",
-				       (unsigned long)token->num_sids));
-	for (i = 0; i < token->num_sids; i++) {
-		DEBUGADDC(dbg_class, dbg_lev, ("  SID[%3lu]: %s\n", (unsigned long)i,
-			   dom_sid_string(mem_ctx, &token->sids[i])));
-	}
-
[…]

### 2018-04-30 System/examples/examplebig/samba/src/nsswitch/libwbclient/tests/wbclient.c

@@ -1,960 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   SMB torture tester
-   Copyright (C) Guenther Deschner 2009-2010
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "lib/replace/replace.h"
-#include "libcli/util/ntstatus.h"
-#include "libcli/util/werror.h"
-#include "lib/util/data_blob.h"
-#include "lib/util/time.h"
-#include "libcli/resolve/resolve.h"
-#include "nsswitch/libwbclient/wbclient.h"
-#include "torture/smbtorture.h"
-#include "torture/winbind/proto.h"
-#include "lib/util/util_net.h"
-#include "lib/util/charset/charset.h"
-#include "libcli/auth/libcli_auth.h"
-#include "lib/param/param.h"
-#include "lib/util/samba_util.h"
-#include "lib/crypto/arcfour.h"
-#include "auth/credentials/credentials.h"
-#include "lib/cmdline/popt_common.h"
-
-#define WBC_ERROR_EQUAL(x,y) (x == y)
-
-#define torture_assert_wbc_equal(torture_ctx, got, expected, cmt, cmt_arg)	\
-	do { wbcErr __got = got, __expected = expected; \
-	if (!WBC_ERROR_EQUAL(__got, __expected)) { \
-		torture_result(torture_ctx, TORTURE_FAIL, __location__": "#got" was %s, expected %s: " cmt, wbcErrorString(__got), wbcErrorString(__expected), cmt_arg); \
-		return false; \
-	} \
-	} while (0)
-
[…]

### 2018-04-30 System/examples/examplebig/samba/src/nsswitch/tests/test_wbinfo.sh

@@ -1,276 +1,0 @@
-#!/bin/sh
-# Blackbox test for wbinfo
-if [ $# -lt 4 ]; then
-cat <<EOF
-Usage: test_wbinfo.sh DOMAIN USERNAME PASSWORD TARGET
-EOF
-exit 1;
-fi
-
-DOMAIN=$1
-USERNAME=$2
-PASSWORD=$3
-TARGET=$4
-shift 4
-
-failed=0
-samba4bindir="$BINDIR"
-wbinfo="$VALGRIND $samba4bindir/wbinfo"
-
-. `dirname $0`/../../testprogs/blackbox/subunit.sh
-
-testfail() {
-	name="$1"
-	shift
-	cmdline="$*"
-	echo "test: $name"
-	$cmdline
-	status=$?
-        if [ x$status = x0 ]; then
-                echo "failure: $name"
-        else
-                echo "success: $name"
-        fi
-        return $status
-}
-
-knownfail() {
-        name="$1"
-        shift
-        cmdline="$*"
-        echo "test: $name"
-        $cmdline
-        status=$?
-        if [ x$status = x0 ]; then
-                echo "failure: $name [unexpected success]"
-				status=1
-        else
-                echo "knownfail: $name"
-				status=0
-        fi
-        return $status
-}
-
-# List users
-testit "wbinfo -u against $TARGET" $wbinfo -u || failed=`expr $failed + 1`
-# List groups
-testit "wbinfo -g against $TARGET" $wbinfo -g || failed=`expr $failed + 1`
-# Convert netbios name to IP
-# Does not work yet
-testit "wbinfo -N against $TARGET" $wbinfo -N $NETBIOSNAME || failed=`expr $failed + 1`
-# Convert IP to netbios name
-# Does not work yet
-testit "wbinfo -I against $TARGET" $wbinfo -I $SERVER_IP || failed=`expr $failed + 1`
-
-# Convert name to SID
-testit "wbinfo -n against $TARGET" $wbinfo -n "$DOMAIN/$USERNAME" || failed=`expr $failed + 1`
-admin_sid=`$wbinfo -n "$DOMAIN/$USERNAME" | cut -d " " -f1`
-echo "$DOMAIN/$USERNAME resolved to $admin_sid"
-
-testit "wbinfo -s $admin_sid against $TARGET" $wbinfo -s $admin_sid || failed=`expr $failed + 1`
[…]

### 2018-04-30 System/examples/examplebig/samba/src/python/samba/join.py

@@ -1,1334 +1,0 @@
-# python join code
-# Copyright Andrew Tridgell 2010
-# Copyright Andrew Bartlett 2010
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-"""Joining a domain."""
-
-from samba.auth import system_session
-from samba.samdb import SamDB
-from samba import gensec, Ldb, drs_utils, arcfour_encrypt, string_to_byte_array
-import ldb, samba, sys, uuid
-from samba.ndr import ndr_pack
-from samba.dcerpc import security, drsuapi, misc, nbt, lsa, drsblobs
-from samba.dsdb import DS_DOMAIN_FUNCTION_2003
-from samba.credentials import Credentials, DONT_USE_KERBEROS
-from samba.provision import secretsdb_self_join, provision, provision_fill, FILL_DRS, FILL_SUBDOMAIN
-from samba.provision.common import setup_path
-from samba.schema import Schema
-from samba import descriptor
-from samba.net import Net
-from samba.provision.sambadns import setup_bind9_dns
-from samba import read_and_sub_file
-from base64 import b64encode
-import logging
-import talloc
-import random
-import time
-
-class DCJoinException(Exception):
-
-    def __init__(self, msg):
-        super(DCJoinException, self).__init__("Can't join, error: %s" % msg)
-
-
-class dc_join(object):
-    """Perform a DC join."""
-
-    def __init__(ctx, logger=None, server=None, creds=None, lp=None, site=None,
-                 netbios_name=None, targetdir=None, domain=None,
-                 machinepass=None, use_ntvfs=False, dns_backend=None,
-                 promote_existing=False, clone_only=False):
-        ctx.clone_only=clone_only
-
-        ctx.logger = logger
-        ctx.creds = creds
-        ctx.lp = lp
[…]

### 2018-04-30 System/examples/examplebig/samba/src/python/samba/netcmd/ldapcmp.py

@@ -1,1000 +1,0 @@
-# Unix SMB/CIFS implementation.
-# A command to compare differences of objects and attributes between
-# two LDAP servers both running at the same time. It generally compares
-# one of the three pratitions DOMAIN, CONFIGURATION or SCHEMA. Users
-# that have to be provided sheould be able to read objects in any of the
-# above partitions.
-
-# Copyright (C) Zahari Zahariev <zahari.zahariev@postpath.com> 2009, 2010
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-import os
-import re
-import sys
-
-import samba
-import samba.getopt as options
-from samba import Ldb
-from samba.ndr import ndr_unpack
-from samba.dcerpc import security
-from ldb import SCOPE_SUBTREE, SCOPE_ONELEVEL, SCOPE_BASE, ERR_NO_SUCH_OBJECT, LdbError
-from samba.netcmd import (
-    Command,
-    CommandError,
-    Option,
-    )
-
-global summary
-summary = {}
-
-class LDAPBase(object):
-
-    def __init__(self, host, creds, lp,
-                 two=False, quiet=False, descriptor=False, sort_aces=False, verbose=False,
-                 view="section", base="", scope="SUB",
-                 outf=sys.stdout, errf=sys.stderr, skip_missing_dn=True):
-        ldb_options = []
-        samdb_url = host
-        if not "://" in host:
-            if os.path.isfile(host):
-                samdb_url = "tdb://%s" % host
-            else:
-                samdb_url = "ldap://%s" % host
-        # use 'paged_search' module when connecting remotely
-        if samdb_url.lower().startswith("ldap://"):
-            ldb_options = ["modules:paged_searches"]
-        self.outf = outf
-        self.errf = errf
-        self.ldb = Ldb(url=samdb_url,
-                       credentials=creds,
-                       lp=lp,
-                       options=ldb_options)
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/modules/nfs4_acls.c

@@ -1,1021 +1,0 @@
-/*
- * NFS4 ACL handling
- *
- * Copyright (C) Jim McDonough, 2006
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "smbd/smbd.h"
-#include "nfs4_acls.h"
-#include "librpc/gen_ndr/ndr_security.h"
-#include "../libcli/security/dom_sid.h"
-#include "../libcli/security/security.h"
-#include "dbwrap/dbwrap.h"
-#include "dbwrap/dbwrap_open.h"
-#include "system/filesys.h"
-#include "passdb/lookup_sid.h"
-#include "util_tdb.h"
-#include "lib/param/loadparm.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_ACLS
-
-#define SMBACL4_PARAM_TYPE_NAME "nfs4"
-
-extern const struct generic_mapping file_generic_mapping;
-
-struct SMB4ACE_T
-{
-	SMB_ACE4PROP_T	prop;
-	struct SMB4ACE_T *next;
-};
-
-struct SMB4ACL_T
-{
-	uint16_t controlflags;
-	uint32_t naces;
-	struct SMB4ACE_T	*first;
-	struct SMB4ACE_T	*last;
-};
-
-enum smbacl4_mode_enum {e_simple=0, e_special=1};
-enum smbacl4_acedup_enum {e_dontcare=0, e_reject=1, e_ignore=2, e_merge=3};
-
-typedef struct _smbacl4_vfs_params {
-	enum smbacl4_mode_enum mode;
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/modules/non_posix_acls.h

@@ -1,29 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Access Control List handling
-   Copyright (C) Andrew Bartlett 2012.
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-int non_posix_sys_acl_blob_get_file_helper(vfs_handle_struct *handle,
-					   const char *path_p,
-					   DATA_BLOB acl_as_blob,
-					   TALLOC_CTX *mem_ctx,
-					   DATA_BLOB *blob);
-int non_posix_sys_acl_blob_get_fd_helper(vfs_handle_struct *handle,
-					 files_struct *fsp,
-					 DATA_BLOB acl_as_blob,
-					 TALLOC_CTX *mem_ctx,
-					 DATA_BLOB *blob);

### 2018-04-30 System/examples/examplebig/samba/src/source3/modules/posixacl_xattr.h

@@ -1,44 +1,0 @@
-/*
-   Unix SMB/Netbios implementation.
-   VFS module to get and set posix acl through xattr
-   Copyright (c) 2013 Anand Avati <avati@redhat.com>
-   Copyright (c) 2016 Yan, Zheng <zyan@redhat.com>
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#ifndef __POSIXACL_XATTR_H__
-#define __POSIXACL_XATTR_H__
-
-SMB_ACL_T posixacl_xattr_acl_get_file(vfs_handle_struct *handle,
-				      const char *path_p,
-				      SMB_ACL_TYPE_T type,
-				      TALLOC_CTX *mem_ctx);
-
-SMB_ACL_T posixacl_xattr_acl_get_fd(vfs_handle_struct *handle,
-				    files_struct *fsp,
-				    TALLOC_CTX *mem_ctx);
-
-int posixacl_xattr_acl_set_file(vfs_handle_struct *handle,
-				const char *name,
-				SMB_ACL_TYPE_T type,
-				SMB_ACL_T theacl);
-
-int posixacl_xattr_acl_set_fd(vfs_handle_struct *handle,
-			      files_struct *fsp,
-			      SMB_ACL_T theacl);
-
-int posixacl_xattr_acl_delete_def_file(vfs_handle_struct *handle,
-				       const char *path);
-#endif

### 2018-04-30 System/examples/examplebig/samba/src/source3/modules/vfs_fake_dfq.c

@@ -1,182 +1,0 @@
-/*
- * Fake Disk-Free and Quota VFS module.  Implements passthrough operation
- * of all VFS calls, except for "disk free" and "get quota" which
- * are handled by reading a text file named ".dfq" in the current directory.
- *
- * This module is intended for testing purposes.
- *
- * Copyright (C) Uri Simchoni, 2016
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "smbd/smbd.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_VFS
-
-static int dfq_get_quota(struct vfs_handle_struct *handle, const char *path,
-			 enum SMB_QUOTA_TYPE qtype, unid_t id,
-			 SMB_DISK_QUOTA *qt);
-
-static uint64_t dfq_load_param(int snum, const char *path, const char *section,
-			       const char *param, uint64_t def_val)
-{
-	uint64_t ret;
-
-	char *option =
-	    talloc_asprintf(talloc_tos(), "%s/%s/%s", section, param, path);
-	if (option == NULL) {
-		return def_val;
-	}
-
-	ret = (uint64_t)lp_parm_ulonglong(snum, "fake_dfq", option,
-					  (unsigned long long)def_val);
-
-	TALLOC_FREE(option);
-
-	return ret;
-}
-
-static uint64_t dfq_disk_free(vfs_handle_struct *handle, const char *path,
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/modules/vfs_fileid.c

@@ -1,281 +1,0 @@
-/*
- * VFS module to alter the algorithm to calculate
- * the struct file_id used as key for the share mode
- * and byte range locking db's.
- *
- * Copyright (C) 2007, Stefan Metzmacher
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "smbd/smbd.h"
-#include "system/filesys.h"
-
-static int vfs_fileid_debug_level = DBGC_VFS;
-
-#undef DBGC_CLASS
-#define DBGC_CLASS vfs_fileid_debug_level
-
-struct fileid_mount_entry {
-	SMB_DEV_T device;
-	const char *mnt_fsname;
-	fsid_t fsid;
-	uint64_t devid;
-};
-
-struct fileid_handle_data {
-	uint64_t (*device_mapping_fn)(struct fileid_handle_data *data,
-				      SMB_DEV_T dev);
-	unsigned num_mount_entries;
-	struct fileid_mount_entry *mount_entries;
-};
-
-/* load all the mount entries from the mtab */
-static void fileid_load_mount_entries(struct fileid_handle_data *data)
-{
-	FILE *f;
-	struct mntent *m;
-
-	data->num_mount_entries = 0;
-	TALLOC_FREE(data->mount_entries);
-
-	f = setmntent("/etc/mtab", "r");
-	if (!f) return;
-
-	while ((m = getmntent(f))) {
-		struct stat st;
-		struct statfs sfs;
-		struct fileid_mount_entry *cur;
-
-		if (stat(m->mnt_dir, &st) != 0) continue;
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/rpc_client/rpc_transport.h

@@ -1,106 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  RPC client transport
- *  Copyright (C) Volker Lendecke 2009
- *  Copyright (C) Simo Sorce 2010
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#ifndef _RPC_CLIENT_RPC_TRANSPORT_H_
-#define _RPC_CLIENT_RPC_TRANSPORT_H_
-
-#include "librpc/rpc/dcerpc.h"
-
-/**
- * rpc_cli_transport defines a transport mechanism to ship rpc requests
- * asynchronously to a server and receive replies
- */
-
-struct rpc_cli_transport {
-
-	enum dcerpc_transport_t transport;
-
-	/**
-	 * Trigger an async read from the server. May return a short read.
-	 */
-	struct tevent_req *(*read_send)(TALLOC_CTX *mem_ctx,
-					struct tevent_context *ev,
-					uint8_t *data, size_t size,
-					void *priv);
-	/**
-	 * Get the result from the read_send operation.
-	 */
-	NTSTATUS (*read_recv)(struct tevent_req *req, ssize_t *preceived);
-
-	/**
-	 * Trigger an async write to the server. May return a short write.
-	 */
-	struct tevent_req *(*write_send)(TALLOC_CTX *mem_ctx,
-					 struct tevent_context *ev,
-					 const uint8_t *data, size_t size,
-					 void *priv);
-	/**
-	 * Get the result from the read_send operation.
-	 */
-	NTSTATUS (*write_recv)(struct tevent_req *req, ssize_t *psent);
-
-	/**
-	 * This is an optimization for the SMB transport. It models the
-	 * TransactNamedPipe API call: Send and receive data in one round
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/rpc_server/lsa/srv_lsa_nt.c

@@ -1,4628 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  RPC Pipe client / server routines
- *  Copyright (C) Andrew Tridgell              1992-1997,
- *  Copyright (C) Luke Kenneth Casson Leighton 1996-1997,
- *  Copyright (C) Paul Ashton                       1997,
- *  Copyright (C) Jeremy Allison                    2001, 2006.
- *  Copyright (C) Rafal Szczesniak                  2002,
- *  Copyright (C) Jim McDonough <jmcd@us.ibm.com>   2002,
- *  Copyright (C) Simo Sorce                        2003.
- *  Copyright (C) Gerald (Jerry) Carter             2005.
- *  Copyright (C) Volker Lendecke                   2005.
- *  Copyright (C) Guenther Deschner		    2008.
- *  Copyright (C) Andrew Bartlett		    2010.
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-/* This is the implementation of the lsa server code. */
-
-#include "includes.h"
-#include "ntdomain.h"
-#include "../librpc/gen_ndr/srv_lsa.h"
-#include "secrets.h"
-#include "../librpc/gen_ndr/netlogon.h"
-#include "rpc_client/init_lsa.h"
-#include "../libcli/security/security.h"
-#include "../libcli/security/dom_sid.h"
-#include "../librpc/gen_ndr/drsblobs.h"
-#include "../librpc/gen_ndr/ndr_drsblobs.h"
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/rpc_server/srv_access_check.c

@@ -1,164 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  RPC Pipe client / server routines
- *  Copyright (C) Andrew Tridgell                   1992-1997,
- *  Copyright (C) Luke Kenneth Casson Leighton      1996-1997,
- *  Copyright (C) Paul Ashton                       1997,
- *  Copyright (C) Marc Jacobsen			    1999,
- *  Copyright (C) Jeremy Allison                    2001-2008,
- *  Copyright (C) Jean François Micouleau           1998-2001,
- *  Copyright (C) Jim McDonough <jmcd@us.ibm.com>   2002,
- *  Copyright (C) Gerald (Jerry) Carter             2003-2004,
- *  Copyright (C) Simo Sorce                        2003.
- *  Copyright (C) Volker Lendecke		    2005.
- *  Copyright (C) Guenther Deschner		    2008.
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "system/passwd.h" /* uid_wrapper */
-#include "rpc_server/srv_access_check.h"
-#include "../libcli/security/security.h"
-#include "passdb/machine_sid.h"
-
-/*******************************************************************
- Checks if access to an object should be granted, and returns that
- level of access for further checks.
-
- If the user has either of needed_priv_1 or needed_priv_2 then they
- get the rights in rights_mask in addition to any calulated rights.
-
- This handles the unusual case where we need to allow two different
- privileges to obtain exactly the same rights, which occours only in
- SAMR.
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/script/tests/test_acl_xattr.sh

@@ -1,125 +1,0 @@
-#!/bin/sh
-
-# this tests acl_xattr config parameter "ignore system acl"
-
-if [ $# -lt 6 ]; then
-cat <<EOF
-Usage: $0 SERVER USERNAME PASSWORD PREFIX SMBCLIENT SMBCACLS
-EOF
-exit 1;
-fi
-
-SERVER="$1"
-USERNAME="$2"
-PASSWORD="$3"
-PREFIX="$4"
-SMBCLIENT="$5"
-SMBCACLS="$6"
-SMBCLIENT="$VALGRIND ${SMBCLIENT}"
-SMBCACLS="$VALGRIND ${SMBCACLS}"
-
-incdir=`dirname $0`/../../../testprogs/blackbox
-. $incdir/subunit.sh
-
-setup_remote_file() {
-    local share=$1
-    local fname="$share.$$"
-    local local_fname=$PREFIX/$fname
-    touch $local_fname
-    $SMBCLIENT //$SERVER/$share -U $USERNAME%$PASSWORD -c "rm $fname"
-    $SMBCLIENT //$SERVER/$share -U $USERNAME%$PASSWORD -c "ls" | grep "$fname" && exit 1
-    $SMBCLIENT //$SERVER/$share -U $USERNAME%$PASSWORD -c "lcd $PREFIX; put $fname" || exit 1
-}
-
-nt_affects_posix() {
-    local share=$1
-    local expected=$2
-    local b4
-    local af
-    local fname="$share.$$"
-    b4=$($SMBCLIENT //$SERVER/$share -U $USERNAME%$PASSWORD -c "getfacl $fname" 2>/dev/null) || exit 1
-    $SMBCACLS //$SERVER/$share $fname -U $USERNAME%$PASSWORD -a "ACL:$SERVER\force_user:ALLOWED/0x0/READ" 2>/dev/null || exit 1
-    af=$($SMBCLIENT //$SERVER/$share -U $USERNAME%$PASSWORD -c "getfacl $fname" 2>/dev/null) || exit 1
-    echo "before: $b4"
-    echo "after: $af"
-    if test "$expected" = "true" ; then
-        test "$b4" != "$af"
-    else
-        test "$b4" = "$af"
-    fi
-}
-
-nt_affects_chown() {
-    local share=$1
-    local b4_expected
-    local af_expected
-    local b4_actual
-    local af_actual
-    local fname="$share.$$"
-
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/smbd/error.c

@@ -1,167 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   error packet handling
-   Copyright (C) Andrew Tridgell 1992-1998
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "smbd/smbd.h"
-#include "smbd/globals.h"
-
-bool use_nt_status(void)
-{
-	return lp_nt_status_support() && (global_client_caps & CAP_STATUS32);
-}
-
-/****************************************************************************
- Create an error packet. Normally called using the ERROR() macro.
-
- Setting eclass and ecode to zero and status to a valid NT error will
- reply with an NT error if the client supports CAP_STATUS32, otherwise
- it maps to and returns a DOS error if the client doesn't support CAP_STATUS32.
- This is the normal mode of calling this function via reply_nterror(req, status).
-
- Setting eclass and ecode to non-zero and status to NT_STATUS_OK (0) will map
- from a DOS error to an NT error and reply with an NT error if the client
- supports CAP_STATUS32, otherwise it replies with the given DOS error.
- This mode is currently not used in the server.
-
- Setting both eclass, ecode and status to non-zero values allows a non-default
- mapping from NT error codes to DOS error codes, and will return one or the
- other depending on the client supporting CAP_STATUS32 or not. This is the
- path taken by calling reply_botherror(req, eclass, ecode, status);
-
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/smbd/smb2_break.c

@@ -1,508 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Core SMB2 server
-
-   Copyright (C) Stefan Metzmacher 2009
-   Copyright (C) Jeremy Allison 2010
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "smbd/smbd.h"
-#include "smbd/globals.h"
-#include "../libcli/smb/smb_common.h"
-#include "../lib/util/tevent_ntstatus.h"
-#include "locking/leases_db.h"
-
-static NTSTATUS smbd_smb2_request_process_lease_break(
-	struct smbd_smb2_request *req);
-
-static struct tevent_req *smbd_smb2_oplock_break_send(TALLOC_CTX *mem_ctx,
-						      struct tevent_context *ev,
-						      struct smbd_smb2_request *smb2req,
-						      struct files_struct *in_fsp,
-						      uint8_t in_oplock_level);
-static NTSTATUS smbd_smb2_oplock_break_recv(struct tevent_req *req,
-					    uint8_t *out_oplock_level);
-
-static void smbd_smb2_request_oplock_break_done(struct tevent_req *subreq);
-NTSTATUS smbd_smb2_request_process_break(struct smbd_smb2_request *req)
-{
-	NTSTATUS status;
-	const uint8_t *inbody;
-	uint8_t in_oplock_level;
-	uint64_t in_file_id_persistent;
-	uint64_t in_file_id_volatile;
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source3/utils/status_profile.c

@@ -1,363 +1,0 @@
-/*
- * Unix SMB/CIFS implementation.
- * status reporting
- * Copyright (C) Andrew Tridgell 1994-1998
- * Copyright (C) James Peach 2005-2006
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 3 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "smbprofile.h"
-#include "status_profile.h"
-
-static void profile_separator(const char * title)
-{
-    char line[79 + 1];
-    char * end;
-
-    snprintf(line, sizeof(line), "**** %s ", title);
-
-    for (end = line + strlen(line); end < &line[sizeof(line) -1]; ++end) {
-	    *end = '*';
-    }
-
-    line[sizeof(line) - 1] = '\0';
-    d_printf("%s\n", line);
-}
-
-/*******************************************************************
- dump the elements of the profile structure
-  ******************************************************************/
-bool status_profile_dump(bool verbose)
-{
-	struct profile_stats stats = {};
-
-	if (!profile_setup(NULL, True)) {
-		fprintf(stderr,"Failed to initialise profile memory\n");
-		return False;
-	}
-
-	smbprofile_collect(&stats);
-
-#define __PRINT_FIELD_LINE(name, _stats, field) do { \
-	d_printf("%-59s%20ju\n", \
-		 name "_" #field ":", \
-		 (uintmax_t)stats.values._stats.field); \
-} while(0);
-#define SMBPROFILE_STATS_START
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source4/dsdb/schema/schema_set.c

@@ -1,902 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   DSDB schema header
-
-   Copyright (C) Stefan Metzmacher <metze@samba.org> 2006-2007
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2006-2008
-   Copyright (C) Matthieu Patou <mat@matws.net> 2011
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-
-*/
-
-#include "includes.h"
-#include "lib/util/dlinklist.h"
-#include "dsdb/samdb/samdb.h"
-#include <ldb_module.h>
-#include "param/param.h"
-#include "librpc/ndr/libndr.h"
-#include "librpc/gen_ndr/ndr_misc.h"
-#include "lib/util/tsort.h"
-
-/* change this when we change something in our schema code that
- * requires a re-index of the database
- */
-#define SAMDB_INDEXING_VERSION "2"
-
-/*
-  override the name to attribute handler function
- */
-const struct ldb_schema_attribute *dsdb_attribute_handler_override(struct ldb_context *ldb,
-								   void *private_data,
-								   const char *name)
-{
-	struct dsdb_schema *schema = talloc_get_type_abort(private_data, struct dsdb_schema);
-	const struct dsdb_attribute *a = dsdb_attribute_by_lDAPDisplayName(schema, name);
-	if (a == NULL) {
-		/* this will fall back to ldb internal handling */
-		return NULL;
-	}
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source4/kdc/mit-kdb/kdb_samba.h

@@ -1,173 +1,0 @@
-/* -*- mode: c; c-basic-offset: 4; indent-tabs-mode: nil -*- */
-/*
- * plugins/kdb/samba/kdb_samba.h
- *
- * Copyright (c) 2009, Simo Sorce <idra@samba.org>
- * All Rights Reserved.
- *
- *   Export of this software from the United States of America may
- *   require a specific license from the United States Government.
- *   It is the responsibility of any person or organization contemplating
- *   export to obtain such a license before exporting.
- *
- * WITHIN THAT CONSTRAINT, permission to use, copy, modify, and
- * distribute this software and its documentation for any purpose and
- * without fee is hereby granted, provided that the above copyright
- * notice appear in all copies and that both that copyright notice and
- * this permission notice appear in supporting documentation, and that
- * the name of M.I.T. not be used in advertising or publicity pertaining
- * to distribution of the software without specific, written prior
- * permission.  Furthermore if you modify this software you must label
- * your software as modified software and not distribute it in such a
- * fashion that it might be confused with the original M.I.T. software.
- * M.I.T. makes no representations about the suitability of
- * this software for any purpose.  It is provided "as is" without express
- * or implied warranty.
- *
- */
-
-#ifndef _KDB_SAMBA_H_
-#define _KDB_SAMBA_H_
-
-#include <stdbool.h>
-
-#include <krb5/krb5.h>
-#include <krb5/plugin.h>
-
-#define PAC_LOGON_INFO 1
-
-#ifndef discard_const_p
-#if defined(__intptr_t_defined) || defined(HAVE_INTPTR_T)
-# define discard_const_p(type, ptr) ((type *)((intptr_t)(ptr)))
-#else
-# define discard_const_p(type, ptr) ((type *)(ptr))
-#endif
-#endif
-
-/* from kdb_samba_common.c */
-
-struct mit_samba_context *ks_get_context(krb5_context kcontext);
-
-void ks_free_krb5_db_entry(krb5_context context,
-			   krb5_db_entry *entry);
-
-bool ks_data_eq_string(krb5_data d, const char *s);
-
-krb5_data ks_make_data(void *data, unsigned int len);
-
-krb5_boolean ks_is_kadmin(krb5_context context,
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source4/rpc_server/lsa/lsa_init.c

@@ -1,292 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-
-   endpoint server for the lsarpc pipe
-
-   Copyright (C) Andrew Tridgell 2004
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2004-2007
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "rpc_server/lsa/lsa.h"
-
-/*
- * This matches a Windows 2012R2 dc in
- * a domain with function level 2012R2.
- */
-#define DCESRV_LSA_POLICY_SD_SDDL \
-	"O:BAG:SY" \
-	"D:" \
-	"(D;;0x00000800;;;AN)" \
-	"(A;;GA;;;BA)" \
-	"(A;;GX;;;WD)" \
-	"(A;;0x00000801;;;AN)" \
-	"(A;;0x00001000;;;LS)" \
-	"(A;;0x00001000;;;NS)" \
-	"(A;;0x00001000;;;IS)" \
-	"(A;;0x00000801;;;S-1-15-2-1)"
-
-static const struct generic_mapping dcesrv_lsa_policy_mapping = {
-	LSA_POLICY_READ,
-	LSA_POLICY_WRITE,
-	LSA_POLICY_EXECUTE,
-	LSA_POLICY_ALL_ACCESS
-};
-
-NTSTATUS dcesrv_lsa_get_policy_state(struct dcesrv_call_state *dce_call,
-				     TALLOC_CTX *mem_ctx,
-				     uint32_t access_desired,
-				     struct lsa_policy_state **_state)
-{
-	struct auth_session_info *session_info = dce_call->conn->auth_state.session_info;
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source4/torture/ndr/spoolss.c

@@ -1,1892 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   test suite for spoolss ndr operations
-
-   Copyright (C) Jelmer Vernooij 2007
-   Copyright (C) Guenther Deschner 2009-2011
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "torture/ndr/ndr.h"
-#include "librpc/gen_ndr/ndr_spoolss.h"
-#include "torture/ndr/proto.h"
-
-static const uint8_t openprinterex_req_data[] = {
-  0xf0, 0xa8, 0x39, 0x00, 0x09, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-  0x09, 0x00, 0x00, 0x00, 0x5c, 0x00, 0x5c, 0x00, 0x77, 0x00, 0x32, 0x00,
[…]

### 2018-04-30 System/examples/examplebig/samba/src/source4/torture/unix/whoami.c

@@ -1,419 +1,0 @@
-/*
-   Test the SMB_WHOAMI Unix extension.
-
-   Copyright (C) 2007 James Peach
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "libcli/libcli.h"
-#include "libcli/raw/raw_proto.h"
-#include "torture/torture.h"
-#include "torture/unix/proto.h"
-#include "lib/cmdline/popt_common.h"
-#include "auth/credentials/credentials.h"
-#include "param/param.h"
-#include "libcli/resolve/resolve.h"
-#include <ldb.h>
-#include "lib/util/util_ldb.h"
-#include "ldb_wrap.h"
-#include "dsdb/samdb/samdb.h"
-#include "../libcli/security/security.h"
-
-
-/* Size (in bytes) of the required fields in the SMBwhoami response. */
-#define WHOAMI_REQUIRED_SIZE	40
-
-/*
-   SMBWhoami - Query the user mapping performed by the server for the
-   connected tree. This is a subcommand of the TRANS2_QFSINFO.
-
-   Returns:
-       4 bytes unsigned -      mapping flags (smb_whoami_flags)
-       4 bytes unsigned -      flags mask
-
-       8 bytes unsigned -      primary UID
-       8 bytes unsigned -      primary GID
-       4 bytes unsigned -      number of supplementary GIDs
-       4 bytes unsigned -      number of SIDs
-       4 bytes unsigned -      SID list byte count
-       4 bytes -               pad / reserved (must be zero)
-
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/auth/ntlmssp/ntlmssp_server.c

@@ -1,1030 +1,0 @@
-/*
-   Unix SMB/Netbios implementation.
-   Version 3.0
-   handle NTLMSSP, server side
-
-   Copyright (C) Andrew Tridgell      2001
-   Copyright (C) Andrew Bartlett 2001-2010
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "lib/util/time_basic.h"
-#include "auth/ntlmssp/ntlmssp.h"
-#include "auth/ntlmssp/ntlmssp_private.h"
-#include "../librpc/gen_ndr/ndr_ntlmssp.h"
-#include "auth/ntlmssp/ntlmssp_ndr.h"
-#include "../libcli/auth/libcli_auth.h"
-#include "../lib/crypto/crypto.h"
-#include "auth/gensec/gensec.h"
-#include "auth/gensec/gensec_internal.h"
-#include "auth/common_auth.h"
-#include "param/param.h"
-#include "param/loadparm.h"
-#include "libcli/security/session.h"
-
-/**
- * Determine correct target name flags for reply, given server role
- * and negotiated flags
- *
- * @param ntlmssp_state NTLMSSP State
- * @param neg_flags The flags from the packet
- * @param chal_flags The flags to be set in the reply packet
- * @return The 'target name' string.
- */
-
-const char *ntlmssp_target_name(struct ntlmssp_state *ntlmssp_state,
-				uint32_t neg_flags, uint32_t *chal_flags)
-{
-	if (neg_flags & NTLMSSP_REQUEST_TARGET) {
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/buildtools/wafsamba/symbols.py

@@ -1,657 +1,0 @@
-# a waf tool to extract symbols from object files or libraries
-# using nm, producing a set of exposed defined/undefined symbols
-
-import os, re, subprocess
-import Utils, Build, Options, Logs
-from Logs import debug
-from samba_utils import TO_LIST, LOCAL_CACHE, get_tgt_list, os_path_relpath
-
-# these are the data structures used in symbols.py:
-#
-# bld.env.symbol_map : dictionary mapping public symbol names to list of
-#                      subsystem names where that symbol exists
-#
-# t.in_library       : list of libraries that t is in
-#
-# bld.env.public_symbols: set of public symbols for each subsystem
-# bld.env.used_symbols  : set of used symbols for each subsystem
-#
-# bld.env.syslib_symbols: dictionary mapping system library name to set of symbols
-#                         for that library
-# bld.env.library_dict  : dictionary mapping built library paths to subsystem names
-#
-# LOCAL_CACHE(bld, 'TARGET_TYPE') : dictionary mapping subsystem name to target type
-
-
-def symbols_extract(bld, objfiles, dynamic=False):
-    '''extract symbols from objfile, returning a dictionary containing
-       the set of undefined and public symbols for each file'''
-
-    ret = {}
-
-    # see if we can get some results from the nm cache
-    if not bld.env.nm_cache:
-        bld.env.nm_cache = {}
-
-    objfiles = set(objfiles).copy()
-
-    remaining = set()
-    for obj in objfiles:
-        if obj in bld.env.nm_cache:
-            ret[obj] = bld.env.nm_cache[obj].copy()
-        else:
-            remaining.add(obj)
-    objfiles = remaining
-
-    if len(objfiles) == 0:
-        return ret
-
-    cmd = ["nm"]
-    if dynamic:
-        # needed for some .so files
-        cmd.append("-D")
-    cmd.extend(list(objfiles))
-
-    nmpipe = subprocess.Popen(cmd, stdout=subprocess.PIPE).stdout
-    if len(objfiles) == 1:
-        filename = list(objfiles)[0]
-        ret[filename] = { "PUBLIC": set(), "UNDEFINED" : set()}
-
-    for line in nmpipe:
-        line = line.strip()
-        if line.endswith(':'):
-            filename = line[:-1]
-            ret[filename] = { "PUBLIC": set(), "UNDEFINED" : set() }
-            continue
-        cols = line.split(" ")
-        if cols == ['']:
-            continue
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/ctdb/client/ctdb_client.c

@@ -1,4616 +1,0 @@
-/* 
-   ctdb daemon code
-
-   Copyright (C) Andrew Tridgell  2007
-   Copyright (C) Ronnie Sahlberg  2007
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/network.h"
-#include "system/filesys.h"
-#include "system/locale.h"
-
-#include <talloc.h>
-#include <tevent.h>
-#include <tdb.h>
-
-#include "lib/tdb_wrap/tdb_wrap.h"
-#include "lib/util/dlinklist.h"
-#include "lib/util/time.h"
-#include "lib/util/debug.h"
-#include "lib/util/samba_util.h"
-
-#include "ctdb_private.h"
-#include "ctdb_client.h"
-
-#include "common/reqid.h"
-#include "common/system.h"
-#include "common/common.h"
-#include "common/logging.h"
-
-/*
-  allocate a packet for use in client<->daemon communication
- */
-struct ctdb_req_header *_ctdbd_allocate_pkt(struct ctdb_context *ctdb,
-					    TALLOC_CTX *mem_ctx, 
-					    enum ctdb_operation operation, 
-					    size_t length, size_t slength,
-					    const char *type)
-{
-	int size;
-	struct ctdb_req_header *hdr;
-
-	length = MAX(length, slength);
-	size = (length+(CTDB_DS_ALIGNMENT-1)) & ~(CTDB_DS_ALIGNMENT-1);
-
-	hdr = (struct ctdb_req_header *)talloc_zero_size(mem_ctx, size);
-	if (hdr == NULL) {
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/ctdb/server/ctdb_daemon.c

@@ -1,1879 +1,0 @@
-/* 
-   ctdb daemon code
-
-   Copyright (C) Andrew Tridgell  2006
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/network.h"
-#include "system/filesys.h"
-#include "system/wait.h"
-#include "system/time.h"
-
-#include <talloc.h>
-/* Allow use of deprecated function tevent_loop_allow_nesting() */
-#define TEVENT_DEPRECATED
-#include <tevent.h>
-#include <tdb.h>
-
-#include "lib/tdb_wrap/tdb_wrap.h"
-#include "lib/util/dlinklist.h"
-#include "lib/util/debug.h"
-#include "lib/util/samba_util.h"
-#include "lib/util/blocking.h"
-
-#include "ctdb_version.h"
-#include "ctdb_private.h"
-#include "ctdb_client.h"
-
-#include "common/rb_tree.h"
-#include "common/reqid.h"
-#include "common/system.h"
-#include "common/common.h"
-#include "common/logging.h"
-#include "common/pidfile.h"
-
-struct ctdb_client_pid_list {
-	struct ctdb_client_pid_list *next, *prev;
-	struct ctdb_context *ctdb;
-	pid_t pid;
-	struct ctdb_client *client;
-};
-
-const char *ctdbd_pidfile = NULL;
-static struct pidfile_context *ctdbd_pidfile_ctx = NULL;
-
-static void daemon_incoming_packet(void *, struct ctdb_req_header *);
-
-static void print_exit_message(void)
-{
-	if (debug_extra != NULL && debug_extra[0] != '\0') {
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/ctdb/server/ctdb_lock_helper.c

@@ -1,358 +1,0 @@
-/*
-   ctdb lock helper
-
-   Copyright (C) Amitay Isaacs  2013
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "replace.h"
-#include "system/filesys.h"
-#include "system/network.h"
-#include "system/wait.h"
-
-#include <talloc.h>
-#include <tevent.h>
-
-#include "lib/util/tevent_unix.h"
-
-#include "ctdb_private.h"
-
-#include "common/system.h"
-
-static char *progname = NULL;
-static bool realtime = true;
-
-struct lock_state {
-	struct tdb_context *tdb;
-	TDB_DATA key;
-};
-
-static void set_priority(void)
-{
-	const char *ptr;
-
-	ptr = getenv("CTDB_NOSETSCHED");
-	if (ptr != NULL) {
-		realtime = false;
-	}
-
-	if (! realtime) {
-		return;
-	}
-
-	realtime = set_scheduler();
-	if (! realtime) {
-		fprintf(stderr,
-			"%s: Unable to set real-time scheduler priority\n",
-			progname);
-	}
-}
-
-static void reset_priority(void)
-{
-	if (realtime) {
-		reset_scheduler();
-	}
-}
-
-static void send_result(int fd, char result)
-{
-	sys_write(fd, &result, 1);
-	if (result == 1) {
-		exit(1);
-	}
-}
-
-
-static void usage(void)
-{
-	fprintf(stderr, "\n");
-	fprintf(stderr, "Usage: %s <log-fd> <ctdbd-pid> <output-fd> RECORD <db-path> <db-flags> <db-key>\n",
-		progname);
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/ctdb/tests/simple/06_ctdb_getpid.sh

@@ -1,75 +1,0 @@
-#!/bin/bash
-
-test_info()
-{
-    cat <<EOF
-Verify that 'ctdb getpid' works as expected.
-
-Prerequisites:
-
-* An active CTDB cluster with at least 2 active nodes.
-
-Steps:
-
-1. Verify that the status on all of the ctdb nodes is 'OK'.
-2. Run 'ctdb getpid -n <number>' on the nodes to check the PID of the
-   ctdbd process.
-3. Verify that the output is valid.
-
-Expected results:
-
-* 'ctdb getpid' shows valid output.
-EOF
-}
-
-. "${TEST_SCRIPTS_DIR}/integration.bash"
-
-ctdb_test_init "$@"
-
-set -e
-
-cluster_is_healthy
-
-try_command_on_node 0 "$CTDB listnodes | wc -l"
-num_nodes="$out"
-echo "There are $num_nodes nodes..."
-
-# Call getpid a few different ways and make sure the answer is always the same.
-
-try_command_on_node -v 0 "onnode -q all $CTDB getpid"
-pids_onnode="$out"
-
-cmd=""
-n=0
-while [ $n -lt $num_nodes ] ; do
-    cmd="${cmd}${cmd:+; }$CTDB getpid -n $n"
-    n=$(($n + 1))
-done
-try_command_on_node -v 0 "( $cmd )"
-pids_getpid_n="$out"
-
-if [ "$pids_onnode" = "$pids_getpid_n" ] ; then
-    echo "They're the same... cool!"
-else
-    echo "Error: they differ."
-    testfailures=1
-fi
-
-echo "Checking each PID for validity"
-
-n=0
-while [ $n -lt $num_nodes ] ; do
-    read pid
-    try_command_on_node $n "ls -l /proc/${pid}/exe | sed -e 's@.*/@@'"
-    echo -n "Node ${n}, PID ${pid} looks to be running \"$out\" - "
-    if [ "$out" = "ctdbd" ] ; then
-	echo "GOOD!"
-    elif [ -n "$VALGRIND" -a "$out" = "memcheck" ] ; then
-	# We could check cmdline too if this isn't good enough.
-	echo "GOOD enough!"
-    else
-	echo "BAD!"
-	testfailures=1
-    fi
-    n=$(($n + 1))
-done <<<"$pids_onnode"

### 2018-04-30 System/examples/examplebigbig/samba/src/ctdb/tests/tool/ctdb.reloadnodes.003.sh

@@ -1,33 +1,0 @@
-#!/bin/sh
-
-. "${TEST_SCRIPTS_DIR}/unit.sh"
-
-define_test "3 nodes, missing file on 1"
-
-setup_nodes <<EOF
-192.168.20.41
-192.168.20.42
-192.168.20.43
-EOF
-
-setup_nodes 1 <<EOF
-192.168.20.41
-#192.168.20.42
-192.168.20.43
-EOF
-
-rm "$CTDB_NODES_1"
-
-setup_ctdbd <<EOF
-NODEMAP
-0       192.168.20.41   0x0     CURRENT RECMASTER
-1       192.168.20.42   0x0
-2       192.168.20.43   0x0
-EOF
-
-required_result 1 <<EOF
-Control GET_NODES_FILE failed, ret=-1
-ERROR: Failed to get nodes file from node 1
-EOF
-
-simple_test

### 2018-04-30 System/examples/examplebigbig/samba/src/libcli/auth/schannel_proto.h

@@ -1,31 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   dcerpc schannel operations
-
-   Copyright (C) Andrew Tridgell 2004
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2004-2005
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#ifndef _LIBCLI_AUTH_SCHANNEL_PROTO_H__
-#define _LIBCLI_AUTH_SCHANNEL_PROTO_H__
-
-struct schannel_state;
-
-struct db_context *open_schannel_session_store(TALLOC_CTX *mem_ctx,
-					       struct loadparm_context *lp_ctx);
-
-#endif

### 2018-04-30 System/examples/examplebigbig/samba/src/libcli/smb/read_smb.c

@@ -1,114 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Infrastructure for async SMB client requests
-   Copyright (C) Volker Lendecke 2008
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "system/network.h"
-#include "lib/async_req/async_sock.h"
-#include "read_smb.h"
-#include "lib/util/tevent_unix.h"
-#include "libcli/smb/smb_constants.h"
-
-/*
- * Read an smb packet asynchronously, discard keepalives
- */
-
-struct read_smb_state {
-	struct tevent_context *ev;
-	int fd;
-	uint8_t *buf;
-};
-
-static ssize_t read_smb_more(uint8_t *buf, size_t buflen, void *private_data);
-static void read_smb_done(struct tevent_req *subreq);
-
-struct tevent_req *read_smb_send(TALLOC_CTX *mem_ctx,
-				 struct tevent_context *ev,
-				 int fd)
-{
-	struct tevent_req *result, *subreq;
-	struct read_smb_state *state;
-
-	result = tevent_req_create(mem_ctx, &state, struct read_smb_state);
-	if (result == NULL) {
-		return NULL;
-	}
-	state->ev = ev;
-	state->fd = fd;
-
-	subreq = read_packet_send(state, ev, fd, 4, read_smb_more, NULL);
-	if (subreq == NULL) {
-		goto fail;
-	}
-	tevent_req_set_callback(subreq, read_smb_done, result);
-	return result;
- fail:
-	TALLOC_FREE(result);
-	return NULL;
-}
-
-static ssize_t read_smb_more(uint8_t *buf, size_t buflen, void *private_data)
-{
-	if (buflen > 4) {
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/libcli/smb/smbXcli_base.h

@@ -1,778 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Infrastructure for async SMB client requests
-   Copyright (C) Volker Lendecke 2008
-   Copyright (C) Stefan Metzmacher 2011
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#ifndef _SMBXCLI_BASE_H_
-#define _SMBXCLI_BASE_H_
-
-struct smbXcli_conn;
-struct smbXcli_session;
-struct smbXcli_tcon;
-struct smb_trans_enc_state;
-struct GUID;
-struct iovec;
-struct smb2_create_blobs;
-struct smb_create_returns;
-
-struct smbXcli_conn *smbXcli_conn_create(TALLOC_CTX *mem_ctx,
-					 int fd,
-					 const char *remote_name,
-					 enum smb_signing_setting signing_state,
-					 uint32_t smb1_capabilities,
-					 struct GUID *client_guid,
-					 uint32_t smb2_capabilities);
-
-bool smbXcli_conn_is_connected(struct smbXcli_conn *conn);
-void smbXcli_conn_disconnect(struct smbXcli_conn *conn, NTSTATUS status);
-
-bool smbXcli_conn_has_async_calls(struct smbXcli_conn *conn);
-
-bool smbXcli_conn_dfs_supported(struct smbXcli_conn *conn);
-
-enum protocol_types smbXcli_conn_protocol(struct smbXcli_conn *conn);
-bool smbXcli_conn_use_unicode(struct smbXcli_conn *conn);
-
-void smbXcli_conn_set_sockopt(struct smbXcli_conn *conn, const char *options);
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/librpc/ndr/ndr_dnsserver.c

@@ -1,100 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-
-   Manually parsed structures for DNSSERVER
-
-   Copyright (C) Amitay Isaacs 2011
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "librpc/gen_ndr/ndr_dnsp.h"
-#include "librpc/gen_ndr/ndr_dnsserver.h"
-
-/*
- * parsing DNS_RPC_RECORDS_ARRAY
- */
-
-enum ndr_err_code ndr_pull_DNS_RPC_RECORDS_ARRAY(struct ndr_pull *ndr,
-		int ndr_flags, struct DNS_RPC_RECORDS_ARRAY *rec)
-{
-	rec->count = 0;
-	rec->rec = talloc_array(ndr->current_mem_ctx, struct DNS_RPC_RECORDS, rec->count);
-	if (! rec->rec) {
-		return ndr_pull_error(ndr, NDR_ERR_ALLOC, "Failed to pull DNS_RPC_RECORDS_ARRAY");
-	}
-
-	while (ndr->offset < ndr->data_size) {
-		rec->rec = talloc_realloc(ndr->current_mem_ctx, rec->rec, struct DNS_RPC_RECORDS, rec->count+1);
-		if (! rec->rec) {
-			return ndr_pull_error(ndr, NDR_ERR_ALLOC, "Failed to pull DNS_RPC_RECORDS_ARRAY");
-		}
-		NDR_CHECK(ndr_pull_DNS_RPC_RECORDS(ndr, ndr_flags, &rec->rec[rec->count]));
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/python/samba/ndr.py

@@ -1,50 +1,0 @@
-# -*- coding: utf-8 -*-
-
-# Unix SMB/CIFS implementation.
-# Copyright © Jelmer Vernooij <jelmer@samba.org> 2008
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-
-"""Network Data Representation (NDR) marshalling and unmarshalling."""
-
-
-def ndr_pack(object):
-    """Pack a NDR object.
-
-    :param object: Object to pack
-    :return: String object with marshalled object.
-    """
-    ndr_pack = getattr(object, "__ndr_pack__", None)
-    if ndr_pack is None:
-        raise TypeError("%r is not a NDR object" % object)
-    return ndr_pack()
-
-
-def ndr_unpack(cls, data, allow_remaining=False):
-    """NDR unpack an object.
-
-    :param cls: Class of the object to unpack
-    :param data: Buffer to unpack
-    :param allow_remaining: allows remaining data at the end (default=False)
-    :return: Unpacked object
-    """
-    object = cls()
-    object.__ndr_unpack__(data, allow_remaining=allow_remaining)
-    return object
-
-
-def ndr_print(object):
-    return object.__ndr_print__()

### 2018-04-30 System/examples/examplebigbig/samba/src/python/samba/tests/samba_tool/user_check_password_script.py

@@ -1,97 +1,0 @@
-# Unix SMB/CIFS implementation.
-# Copyright (C) Sean Dague <sdague@linux.vnet.ibm.com> 2011
-# Copyright (C) Andrew Bartlett <abartlet@samba.org> 2016
-#
-# This program is free software; you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation; either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#
-
-import os
-import time
-import ldb
-from samba.tests.samba_tool.base import SambaToolCmdTest
-from samba import (
-        nttime2unix,
-        dsdb
-        )
-
-class UserCheckPwdTestCase(SambaToolCmdTest):
-    """Tests for samba-tool user subcommands"""
-    users = []
-    samdb = None
-
-    def setUp(self):
-        super(UserCheckPwdTestCase, self).setUp()
-        self.samdb = self.getSamDB("-H", "ldap://%s" % os.environ["DC_SERVER"],
-            "-U%s%%%s" % (os.environ["DC_USERNAME"], os.environ["DC_PASSWORD"]))
-        self.old_min_pwd_age = self.samdb.get_minPwdAge()
-        self.samdb.set_minPwdAge("0")
-
-    def tearDown(self):
-        super(UserCheckPwdTestCase, self).tearDown()
-        self.samdb.set_minPwdAge(self.old_min_pwd_age)
-
-    def test_checkpassword(self):
-        # Add
-        user = self._randomUser()
-        bad_password = os.environ["UNACCEPTABLE_PASSWORD"]
-        good_password = bad_password[:-1]
-
-        (result, out, err) = self.runsubcmd("user", "add", user["name"], bad_password,
-                                            "-H", "ldap://%s" % os.environ["DC_SERVER"],
-                                            "-U%s%%%s" % (os.environ["DC_USERNAME"], os.environ["DC_PASSWORD"]))
-        self.assertCmdFail(result, "Should fail adding a user with bad password.")
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/libads/ldap_utils.c

@@ -1,384 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-
-   Some Helpful wrappers on LDAP 
-
-   Copyright (C) Andrew Tridgell 2001
-   Copyright (C) Guenther Deschner 2006,2007
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "ads.h"
-#include "lib/param/loadparm.h"
-
-#ifdef HAVE_LDAP
-
-static ADS_STATUS ads_ranged_search_internal(ADS_STRUCT *ads,
-					     TALLOC_CTX *mem_ctx,
-					     int scope,
-					     const char *base,
-					     const char *filter,
-					     const char **attrs,
-					     void *args,
-					     const char *range_attr,
-					     char ***strings,
-					     size_t *num_strings,
-					     uint32_t *first_usn,
-					     int *num_retries,
-					     bool *more_values);
-
-/*
-  a wrapper around ldap_search_s that retries depending on the error code
-  this is supposed to catch dropped connections and auto-reconnect
-*/
-static ADS_STATUS ads_do_search_retry_internal(ADS_STRUCT *ads, const char *bind_path, int scope, 
-					       const char *expr,
-					       const char **attrs, void *args,
-					       LDAPMessage **res)
-{
-	ADS_STATUS status = ADS_SUCCESS;
-	int count = 3;
-	char *bp;
-
-	*res = NULL;
-
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/nmbd/nmbd_winsproxy.c

@@ -1,233 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   NBT netbios routines and daemon - version 2
-
-   Copyright (C) Jeremy Allison 1994-1998
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-   
-*/
-
-#include "includes.h"
-#include "nmbd/nmbd.h"
-
-/****************************************************************************
-Function called when the name lookup succeeded.
-****************************************************************************/
-
-static void wins_proxy_name_query_request_success( struct subnet_record *subrec,
-                        struct userdata_struct *userdata,
-                        struct nmb_name *nmbname, struct in_addr ip, struct res_rec *rrec)
-{
-	unstring name;
-	struct packet_struct *original_packet;
-	struct subnet_record *orig_broadcast_subnet;
-	struct name_record *namerec = NULL;
-	uint16_t nb_flags;
-	int num_ips;
-	int i;
-	int ttl = 3600; /* By default one hour in the cache. */
-	struct in_addr *iplist;
-
-	/* Extract the original packet and the original broadcast subnet from
-			the userdata. */
-
-	memcpy( (char *)&orig_broadcast_subnet, userdata->data, sizeof(struct subnet_record *) );
-	memcpy( (char *)&original_packet, &userdata->data[sizeof(struct subnet_record *)],
-			sizeof(struct packet_struct *) );
-
-	if (rrec) {
-		nb_flags = get_nb_flags( rrec->rdata );
-		num_ips = rrec->rdlength / 6;
-	} else {
-		nb_flags = 0;
-		num_ips = 0;
-	}
-
-	if(num_ips == 0) {
-		DEBUG(0,("wins_proxy_name_query_request_success: Invalid number of IP records (0) \
-returned for name %s.\n", nmb_namestr(nmbname) ));
-		return;
-	}
-
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/registry/reg_api_util.c

@@ -1,247 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  Virtual Windows Registry Layer
- *  Copyright (C) Volker Lendecke 2006
- *  Copyright (C) Michael Adam 2007-2010
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-/*
- * Higher level utility functions on top of reg_api.c
- */
-
-#include "includes.h"
-#include "registry.h"
-#include "reg_api.h"
-#include "reg_api_util.h"
-#include "libcli/registry/util_reg.h"
-
-/**
- * Utility function to open a complete registry path including the hive prefix.
- */
-WERROR reg_open_path(TALLOC_CTX *mem_ctx, const char *orig_path,
-		     uint32_t desired_access, const struct security_token *token,
-		     struct registry_key **pkey)
-{
-	struct registry_key *hive, *key;
-	char *path, *p;
-	WERROR err;
-
-	if (!(path = SMB_STRDUP(orig_path))) {
-		return WERR_NOMEM;
-	}
-
-	p = strchr(path, '\\');
-
-	if ((p == NULL) || (p[1] == '\0')) {
-		/*
-		 * No key behind the hive, just return the hive
-		 */
-
-		err = reg_openhive(mem_ctx, path, desired_access, token,
-				   &hive);
-		if (!W_ERROR_IS_OK(err)) {
-			SAFE_FREE(path);
-			return err;
-		}
-		SAFE_FREE(path);
-		*pkey = hive;
-		return WERR_OK;
-	}
-
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/registry/reg_parse_prs.c

@@ -1,445 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   Samba memory buffer functions
-   Copyright (C) Andrew Tridgell              1992-1997
-   Copyright (C) Luke Kenneth Casson Leighton 1996-1997
-   Copyright (C) Jeremy Allison               1999
-   Copyright (C) Andrew Bartlett              2003.
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "reg_parse_prs.h"
-#include "rpc_dce.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_RPC_PARSE
-
-/*******************************************************************
- Debug output for parsing info
-
- XXXX side-effect of this function is to increase the debug depth XXXX.
-
-********************************************************************/
-
-void prs_debug(prs_struct *ps, int depth, const char *desc, const char *fn_name)
-{
-	DEBUG(5+depth, ("%s%06x %s %s\n", tab_depth(5+depth,depth), ps->data_offset, fn_name, desc));
-}
-
-/**
- * Initialise an expandable parse structure.
- *
- * @param size Initial buffer size.  If >0, a new buffer will be
- * created with talloc().
- *
- * @return False if allocation fails, otherwise True.
- **/
-
-bool prs_init(prs_struct *ps, uint32_t size, TALLOC_CTX *ctx, bool io)
-{
-	ZERO_STRUCTP(ps);
-	ps->io = io;
-	ps->bigendian_data = RPC_LITTLE_ENDIAN;
-	ps->align = RPC_PARSE_ALIGN;
-	ps->is_dynamic = False;
-	ps->data_offset = 0;
-	ps->buffer_size = 0;
-	ps->data_p = NULL;
-	ps->mem_ctx = ctx;
-
-	if (size != 0) {
-		ps->buffer_size = size;
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/rpc_server/dssetup/srv_dssetup_nt.c

@@ -1,227 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *  RPC Pipe client / server routines
- *  Copyright (C) Andrew Tridgell               1992-1997.
- *  Copyright (C) Luke Kenneth Casson Leighton  1996-1997.
- *  Copyright (C) Paul Ashton                        1997.
- *  Copyright (C) Jeremy Allison                     2001.
- *  Copyright (C) Gerald Carter                      2002.
- *  Copyright (C) Guenther Deschner                  2008.
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "ntdomain.h"
-#include "../librpc/gen_ndr/srv_dssetup.h"
-#include "secrets.h"
-
-#undef DBGC_CLASS
-#define DBGC_CLASS DBGC_RPC_SRV
-
-/********************************************************************
- Fill in a dssetup_DsRolePrimaryDomInfoBasic structure
- ********************************************************************/
-
-static WERROR fill_dsrole_dominfo_basic(TALLOC_CTX *ctx,
-					struct dssetup_DsRolePrimaryDomInfoBasic **info)
-{
-	struct dssetup_DsRolePrimaryDomInfoBasic *basic = NULL;
-	char *dnsdomain = NULL;
-
-	DEBUG(10,("fill_dsrole_dominfo_basic: enter\n"));
-
-	basic = talloc_zero(ctx, struct dssetup_DsRolePrimaryDomInfoBasic);
-	if (!basic) {
-		DEBUG(0,("fill_dsrole_dominfo_basic: out of memory\n"));
-		return WERR_NOMEM;
-	}
-
-	switch (lp_server_role()) {
-		case ROLE_STANDALONE:
-			basic->role = DS_ROLE_STANDALONE_SERVER;
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/rpc_server/rpc_ep_register.c

@@ -1,277 +1,0 @@
-/*
- *  Unix SMB/CIFS implementation.
- *
- *  RPC Endpoint Registration
- *
- *  Copyright (c) 2011      Andreas Schneider <asn@samba.org>
- *
- *  This program is free software; you can redistribute it and/or modify
- *  it under the terms of the GNU General Public License as published by
- *  the Free Software Foundation; either version 3 of the License, or
- *  (at your option) any later version.
- *
- *  This program is distributed in the hope that it will be useful,
- *  but WITHOUT ANY WARRANTY; without even the implied warranty of
- *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- *  GNU General Public License for more details.
- *
- *  You should have received a copy of the GNU General Public License
- *  along with this program; if not, see <http://www.gnu.org/licenses/>.
- */
-
-#include "includes.h"
-#include "ntdomain.h"
-
-#include "../librpc/gen_ndr/ndr_epmapper_c.h"
-
-#include "librpc/rpc/dcerpc_ep.h"
-#include "rpc_server/rpc_ep_register.h"
-
-static void rpc_ep_register_loop(struct tevent_req *subreq);
-static NTSTATUS rpc_ep_try_register(TALLOC_CTX *mem_ctx,
-				    struct tevent_context *ev_ctx,
-				    struct messaging_context *msg_ctx,
-				    const struct ndr_interface_table *iface,
-				    const struct dcerpc_binding_vector *v,
-				    struct dcerpc_binding_handle **pbh);
-
-struct rpc_ep_register_state {
-	struct dcerpc_binding_handle *h;
-
-	struct tevent_context *ev_ctx;
-	struct messaging_context *msg_ctx;
-
-	const struct ndr_interface_table *iface;
-	const struct dcerpc_binding_vector *vector;
-
-	uint32_t wait_time;
-};
-
-NTSTATUS rpc_ep_register(struct tevent_context *ev_ctx,
-			 struct messaging_context *msg_ctx,
-			 const struct ndr_interface_table *iface,
-			 const struct dcerpc_binding_vector *v)
-{
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/rpcclient/cmd_drsuapi.c

@@ -1,594 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   RPC pipe client
-
-   Copyright (C) Guenther Deschner 2008
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "rpcclient.h"
-#include "../librpc/gen_ndr/ndr_drsuapi_c.h"
-
-static WERROR cracknames(struct rpc_pipe_client *cli,
-			 TALLOC_CTX *mem_ctx,
-			 struct policy_handle *bind_handle,
-			 enum drsuapi_DsNameFormat format_offered,
-			 enum drsuapi_DsNameFormat format_desired,
-			 int argc,
-			 const char **argv,
-			 union drsuapi_DsNameCtr *ctr)
-{
-	NTSTATUS status;
-	WERROR werr;
-	int i;
-	uint32_t level = 1;
-	union drsuapi_DsNameRequest req;
-	uint32_t level_out;
-	struct drsuapi_DsNameString *names;
-	struct dcerpc_binding_handle *b = cli->binding_handle;
-
-	names = talloc_zero_array(mem_ctx, struct drsuapi_DsNameString, argc);
-	W_ERROR_HAVE_NO_MEMORY(names);
-
-	for (i=0; i<argc; i++) {
-		names[i].str = argv[i];
-	}
-
-	req.req1.codepage	= 1252; /* german */
-	req.req1.language	= 0x00000407; /* german */
-	req.req1.count		= argc;
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/script/tests/test_net_rpc_join.sh

@@ -1,25 +1,0 @@
-#!/bin/sh
-
-if [ $# -lt 4 ]; then
-cat <<EOF
-Usage: test_net_rpc_join.sh  USERNAME PASSWORD SERVER PREFIX
-EOF
-exit 1;
-fi
-
-USERNAME="$1"
-PASSWORD="$2"
-SERVER="$3"
-PREFIX="$4"
-shift 4
-ADDARGS="$*"
-
-incdir=`dirname $0`/../../../testprogs/blackbox
-. $incdir/subunit.sh
-mkdir -p $PREFIX/private
-testit "net_rpc_join" $VALGRIND $BINDIR/net rpc join -S $SERVER --option=netbiosname=netrpcjointest --option=domainlogons=yes --option=privatedir=$PREFIX/private -U$USERNAME%$PASSWORD $ADDARGS || failed=`expr $failed + 1`
-testit "net_rpc_testjoin" $VALGRIND $BINDIR/net rpc testjoin -S $SERVER --option=netbiosname=netrpcjointest --option=domainlogons=yes --option=privatedir=$PREFIX/private $ADDARGS || failed=`expr $failed + 1`
-testit "net_rpc_changetrustpw" $VALGRIND $BINDIR/net rpc changetrustpw -S $SERVER --option=netbiosname=netrpcjointest --option=domainlogons=yes --option=privatedir=$PREFIX/private $ADDARGS || failed=`expr $failed + 1`
-testit "net_rpc_testjoin2" $VALGRIND $BINDIR/net rpc testjoin -S $SERVER --option=netbiosname=netrpcjointest --option=domainlogons=yes --option=privatedir=$PREFIX/private $ADDARGS || failed=`expr $failed + 1`
-
-testok $0 $failed

### 2018-04-30 System/examples/examplebigbig/samba/src/source3/smbd/srvstr.c

@@ -1,118 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   server specific string routines
-   Copyright (C) Andrew Tridgell 2001
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2003
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "smbd/smbd.h"
-#include "smbd/globals.h"
-
-/* Make sure we can't write a string past the end of the buffer */
-
-NTSTATUS srvstr_push_fn(const char *base_ptr, uint16_t smb_flags2, void *dest,
-		      const char *src, int dest_len, int flags, size_t *ret_len)
-{
-	size_t len;
-	int saved_errno;
-	NTSTATUS status;
-
-	if (dest_len < 0) {
-		return NT_STATUS_INVALID_PARAMETER;
-	}
-
-	saved_errno = errno;
-	errno = 0;
-
-	/* 'normal' push into size-specified buffer */
-	len = push_string_base(base_ptr, smb_flags2, dest, src,
-				dest_len, flags);
-
-	if (errno != 0) {
-		/*
-		 * Special case E2BIG, EILSEQ, EINVAL
-		 * as they mean conversion errors here,
-		 * but we don't generically map them as
-		 * they can mean different things in
-		 * generic filesystem calls (such as
-		 * read xattrs).
-		 */
-		if (errno == E2BIG || errno == EILSEQ || errno == EINVAL) {
-			status = NT_STATUS_ILLEGAL_CHARACTER;
-		} else {
-			status = map_nt_error_from_unix_common(errno);
-			/*
-			 * Paranoia - Filter out STATUS_MORE_ENTRIES.
-			 * I don't think we can get this but it has a
-			 * specific meaning to the client.
-			 */
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/dsdb/repl/drepl_notify.c

@@ -1,481 +1,0 @@
-/* 
-   Unix SMB/CIFS mplementation.
-
-   DSDB replication service periodic notification handling
-   
-   Copyright (C) Andrew Tridgell 2009
-   based on drepl_periodic
-    
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-   
-*/
-
-#include "includes.h"
-#include "lib/events/events.h"
-#include "dsdb/samdb/samdb.h"
-#include "auth/auth.h"
-#include "smbd/service.h"
-#include "dsdb/repl/drepl_service.h"
-#include <ldb_errors.h>
-#include "../lib/util/dlinklist.h"
-#include "librpc/gen_ndr/ndr_misc.h"
-#include "librpc/gen_ndr/ndr_drsuapi.h"
-#include "librpc/gen_ndr/ndr_drsblobs.h"
-#include "libcli/composite/composite.h"
-#include "../lib/util/tevent_ntstatus.h"
-
-
-struct dreplsrv_op_notify_state {
-	struct tevent_context *ev;
-	struct dreplsrv_notify_operation *op;
-	void *ndr_struct_ptr;
-};
-
-static void dreplsrv_op_notify_connect_done(struct tevent_req *subreq);
-
-/*
-  start the ReplicaSync async call
- */
-static struct tevent_req *dreplsrv_op_notify_send(TALLOC_CTX *mem_ctx,
-						  struct tevent_context *ev,
-						  struct dreplsrv_notify_operation *op)
-{
-	struct tevent_req *req;
-	struct dreplsrv_op_notify_state *state;
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/dsdb/tests/python/sam.py

@@ -1,3609 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-# This is a port of the original in testprogs/ejs/ldap.js
-
-import optparse
-import sys
-import os
-import time
-
-sys.path.insert(0, "bin/python")
-import samba
-from samba.tests.subunitrun import SubunitOptions, TestProgram
-
-import samba.getopt as options
-
-from samba.auth import system_session
-from ldb import SCOPE_BASE, LdbError
-from ldb import ERR_NO_SUCH_OBJECT, ERR_ATTRIBUTE_OR_VALUE_EXISTS
-from ldb import ERR_ENTRY_ALREADY_EXISTS, ERR_UNWILLING_TO_PERFORM
-from ldb import ERR_OTHER, ERR_NO_SUCH_ATTRIBUTE
-from ldb import ERR_OBJECT_CLASS_VIOLATION
-from ldb import ERR_CONSTRAINT_VIOLATION
-from ldb import ERR_UNDEFINED_ATTRIBUTE_TYPE
-from ldb import ERR_INSUFFICIENT_ACCESS_RIGHTS
-from ldb import Message, MessageElement, Dn
-from ldb import FLAG_MOD_ADD, FLAG_MOD_REPLACE, FLAG_MOD_DELETE
-from samba.samdb import SamDB
-from samba.dsdb import (UF_NORMAL_ACCOUNT, UF_ACCOUNTDISABLE,
-    UF_WORKSTATION_TRUST_ACCOUNT, UF_SERVER_TRUST_ACCOUNT,
-    UF_PARTIAL_SECRETS_ACCOUNT, UF_TEMP_DUPLICATE_ACCOUNT,
-    UF_INTERDOMAIN_TRUST_ACCOUNT, UF_SMARTCARD_REQUIRED,
-    UF_PASSWD_NOTREQD, UF_LOCKOUT, UF_PASSWORD_EXPIRED, ATYPE_NORMAL_ACCOUNT,
-    GTYPE_SECURITY_BUILTIN_LOCAL_GROUP, GTYPE_SECURITY_DOMAIN_LOCAL_GROUP,
-    GTYPE_SECURITY_GLOBAL_GROUP, GTYPE_SECURITY_UNIVERSAL_GROUP,
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/libcli/ldap/ldap_client.h

@@ -1,149 +1,0 @@
-/* 
-   Unix SMB/CIFS Implementation.
-
-   ldap client side header
-
-   Copyright (C) Andrew Tridgell 2005
-    
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-
-#include "system/network.h" /* for struct iovec */
-#include "libcli/ldap/libcli_ldap.h"
-
-enum ldap_request_state { LDAP_REQUEST_SEND=1, LDAP_REQUEST_PENDING=2, LDAP_REQUEST_DONE=3, LDAP_REQUEST_ERROR=4 };
-
-/* this is the handle that the caller gets when an async ldap message
-   is sent */
-struct ldap_request {
-	struct ldap_request *next, *prev;
-	struct ldap_connection *conn;
-
-	enum ldap_request_tag type;
-	int messageid;
-	enum ldap_request_state state;
-
-	int num_replies;
-	struct ldap_message **replies;
-
-	NTSTATUS status;
-	DATA_BLOB data;
-	struct iovec write_iov;
-
-	struct {
-		void (*fn)(struct ldap_request *);
-		void *private_data;
-	} async;
-
-	struct tevent_timer *time_event;
-};
-
-
-/* main context for a ldap client connection */
-struct ldap_connection {
-	struct {
-		struct tstream_context *raw;
-		struct tstream_context *tls;
-		struct tstream_context *sasl;
-		struct tstream_context *active;
-
-		struct tevent_queue *send_queue;
-		struct tevent_req *recv_subreq;
-	} sockets;
-
-	struct loadparm_context *lp_ctx;
-
-	char *host;
-	uint16_t port;
-	bool ldaps;
-
-	const char *auth_dn;
-	const char *simple_pw;
-
-	struct {
-		char *url;
-		int max_retries;
-		int retries;
-		time_t previous;
-	} reconnect;
-
-	struct {
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/libcli/smb2/cancel.c

@@ -1,45 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-
-   SMB2 client notify calls
-
-   Copyright (C) Stefan Metzmacher 2006
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include <tevent.h>
-#include "libcli/raw/libcliraw.h"
-#include "libcli/smb2/smb2.h"
-#include "libcli/smb2/smb2_calls.h"
-
-/*
-  send a cancel request
-*/
-NTSTATUS smb2_cancel(struct smb2_request *r)
-{
-	bool ok;
-
-	if (r->subreq == NULL) {
-		return NT_STATUS_OK;
-	}
-
-	ok = tevent_req_cancel(r->subreq);
-	if (!ok) {
-		return NT_STATUS_INTERNAL_ERROR;
-	}
-
-	return NT_STATUS_OK;
-}

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/librpc/rpc/pyrpc.h

@@ -1,67 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   Samba utility functions
-   Copyright (C) Jelmer Vernooij <jelmer@samba.org> 2008
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#ifndef _PYRPC_H_
-#define _PYRPC_H_
-
-#include "libcli/util/pyerrors.h"
-
-#ifndef Py_TYPE /* Py_TYPE is only available on Python > 2.6 */
-#define Py_TYPE(ob)             (((PyObject*)(ob))->ob_type)
-#endif
-
-#define PY_CHECK_TYPE(type, var, fail) \
-	if (!PyObject_TypeCheck(var, type)) {\
-		PyErr_Format(PyExc_TypeError, __location__ ": Expected type '%s' for '%s' of type '%s'", (type)->tp_name, #var, Py_TYPE(var)->tp_name); \
-		fail; \
-	}
-
-#define dom_sid0_Type dom_sid_Type
-#define dom_sid2_Type dom_sid_Type
-#define dom_sid28_Type dom_sid_Type
-#define dom_sid0_Check dom_sid_Check
-#define dom_sid2_Check dom_sid_Check
-#define dom_sid28_Check dom_sid_Check
-
-typedef struct {
-	PyObject_HEAD
-	TALLOC_CTX *mem_ctx;
-	struct dcerpc_pipe *pipe;
-	struct dcerpc_binding_handle *binding_handle;
-} dcerpc_InterfaceObject;
-
-
-/*
-  these prototypes should be generated by the python pidl backend, but
-  aren't yet. They are needed when one module that has python access
-  is accessed by another module
- */
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/nbt_server/query.c

@@ -1,102 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-
-   answer name queries
-
-   Copyright (C) Andrew Tridgell	2005
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "../lib/util/dlinklist.h"
-#include "system/network.h"
-#include "nbt_server/nbt_server.h"
-#include "nbt_server/wins/winsserver.h"
-#include "smbd/service_task.h"
-#include "librpc/gen_ndr/ndr_nbt.h"
-#include "lib/socket/socket.h"
-#include "param/param.h"
-
-/*
-  answer a name query
-*/
-void nbtd_request_query(struct nbt_name_socket *nbtsock, 
-			struct nbt_name_packet *packet, 
-			struct socket_address *src)
-{
-	struct nbtd_iface_name *iname;
-	struct nbt_name *name;
-	struct nbtd_interface *iface = talloc_get_type(nbtsock->incoming.private_data,
-						       struct nbtd_interface);
-
-	/* see if its a node status query */
-	if (packet->qdcount == 1 &&
-	    packet->questions[0].question_type == NBT_QTYPE_STATUS) {
-		nbtd_query_status(nbtsock, packet, src);
-		return;
-	}
-
-	NBTD_ASSERT_PACKET(packet, src, packet->qdcount == 1);
-	NBTD_ASSERT_PACKET(packet, src, 
-			   packet->questions[0].question_type == NBT_QTYPE_NETBIOS);
-	NBTD_ASSERT_PACKET(packet, src, 
-			   packet->questions[0].question_class == NBT_QCLASS_IP);
-
-	/* see if we have the requested name on this interface */
-	name = &packet->questions[0].name;
-
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/torture/rpc/lsa_lookup.c

@@ -1,424 +1,0 @@
-/* 
-   Unix SMB/CIFS implementation.
-   test suite for lsa rpc lookup operations
-
-   Copyright (C) Volker Lendecke 2006
-   
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-   
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-   
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "torture/rpc/torture_rpc.h"
-#include "librpc/gen_ndr/ndr_lsa_c.h"
-#include "libcli/security/security.h"
-
-static bool open_policy(struct torture_context *tctx,
-			struct dcerpc_binding_handle *b,
-			struct policy_handle **handle)
-{
-	struct lsa_ObjectAttribute attr;
-	struct lsa_QosInfo qos;
-	struct lsa_OpenPolicy2 r;
-
-	*handle = talloc(tctx, struct policy_handle);
-	if (!*handle) {
-		return false;
-	}
-
-	qos.len = 0;
-	qos.impersonation_level = 2;
-	qos.context_mode = 1;
-	qos.effective_only = 0;
-
-	attr.len = 0;
-	attr.root_dir = NULL;
-	attr.object_name = NULL;
-	attr.attributes = 0;
-	attr.sec_desc = NULL;
-	attr.sec_qos = &qos;
-
-	r.in.system_name = "\\";
-	r.in.attr = &attr;
-	r.in.access_mask = SEC_FLAG_MAXIMUM_ALLOWED;
-	r.out.handle = *handle;
-
-	torture_assert_ntstatus_ok(tctx, dcerpc_lsa_OpenPolicy2_r(b, tctx, &r),
-		"OpenPolicy2 failed");
[…]

### 2018-04-30 System/examples/examplebigbig/samba/src/source4/torture/winbind/winbind.c

@@ -1,317 +1,0 @@
-/*
-   Unix SMB/CIFS implementation.
-   SMB torture tester
-   Copyright (C) Stefan Metzmacher 2007
-   Copyright (C) Andrew Bartlett <abartlet@samba.org> 2012
-   Copyright (C) Christof Schmit <christof.schmitt@us.ibm.com> 2012
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 3 of the License, or
-   (at your option) any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-
-#include "includes.h"
-#include "torture/smbtorture.h"
-#include "torture/winbind/proto.h"
-#include "auth/auth.h"
-#include "auth/auth_sam_reply.h"
-#include "auth/gensec/gensec.h"
-#include "system/kerberos.h"
-#include "auth/kerberos/kerberos.h"
-#include "auth/credentials/credentials.h"
-#include "param/param.h"
-#include "lib/cmdline/popt_common.h"
-#include "auth/kerberos/pac_utils.h"
-#include "wbclient.h"
-
-struct pac_data {
-	DATA_BLOB pac_blob;
-};
-
-/* A helper function which avoids touching the local databases to
- * generate the session info, as we just want to verify the PAC
- * details, not the full local token */
-static NTSTATUS test_generate_session_info_pac(struct auth4_context *auth_ctx,
-					       TALLOC_CTX *mem_ctx,
-					       struct smb_krb5_context *smb_krb5_context,
-					       DATA_BLOB *pac_blob,
-					       const char *principal_name,
-					       const struct tsocket_address *remote_address,
-					       uint32_t session_info_flags,
-					       struct auth_session_info **session_info)
-{
[…]

### 2018-06-22 paper_own_docker/main.tex
500 and 1000 scalability test examples added, scalability and characteristics performance table also added.

--- 2018-02-28 paper_own_docker/main.tex
@@
 
-\author{Stevica Bozhinoski$^{1}$ and Amjad Ibrahim$^{2}$% <-this % stops a space
+\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
 }
@@
 \begin{abstract}
+Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
+This advantage has resulted in a rapid increase in usage of microservices in recent years.
+Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
+Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
 
@@
 
+Attack graphs are a popular way of examining security aspects of network.
+They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
+An attack graph depicts the actions that an attacker uses in order to reach his goal.
+
+We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
+
 \section{RELATED WORK}
+
+Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
+There the attacker performs multiple steps to achieve his goal, i.e.
+gaining privileges of the goal container.
+Some works use model checkers with goal property(Sheyner reference).
+They However model checkers as a disadvantage have a state explosion.(Ingols reference)
+
+Others use breath first search algorithm. (Ingols reference)  They model the
+
+Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
+
+Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
+To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
+ They dont use Clair as well. They do not offer any performance comparison between different topologies.
 
@@
 
-\subsubsection{Breadth-first search}
+In this section, we examine the architecture of our attack graph generator.
+We first present a brief overview of the main concepts.
+Next, we have a look at the preprocessing step.
+Lastly we have look into the main algorithm for generating the attack graph.
 
-We use a modification of the breadth first search algorithm to find the nodes and the edges.
+\subsubsection{Main concepts}
+
+Preconditions are conditions that have to be fulfilled in order for the attack to take place. Postconditions are the result of a successful attack and the privileges acquired.
+
+Atomic attack is one step or edge in the attack graph. A state is the container with its privilege level.
+
+We model the privileges into a hierarchy.
+The priviliges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
+VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been infected.
+Since VOS are on some hosts, they have lower level of hierarchy.
+
+<INSERT IMAGE PRIVILEGES>
+
+<INSERT IMAGE EXAMPLE>
+
+<INSERT IMAGE ATTACK GRAPH>
+
+\subsubsection{Preprocessing}
+In our preprocessing step, we use Clair in order to generate the vulnerabilities for a given container.
+Clair provides the CVE-ID, description and attack vector.
+Attack vector is an entity that descriptes which conditions and effects are connected to this vulnerability.
+Clairctl is a wrapper that we use in order to analyze a docker image.
+
+Additionaly, we parse the attack vectors from the vulnerability database to generate attack rules. We use rules annotated
+
+docker-compose.yml is used for extraction of the topology of the system. The containers that have published ports are connected to the outside.
+Some containers have privileged access. That means that an attacker with access to these containers, has also access to the docker daemon. This can be done by us
+
+This results in a list of container vulnerabilities with their preconditions and postconditions.
+\subsubsection{Breadth-First Search}
+
+After the preprocessing step is done, the vulnerabilties are parsed and their pre- and postconditions are extracted, together with the topology are feed into the Bradth-First Search algorithm(BFS).
+Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
+
+Some properties of BFS:
+
+Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
+
+Termination - monotonicity properties
+- complexity
+time complexity O(|N| + |E|) where |N| is the number of nodes and |E| is the number of edges in the attack graph.
+memory complexity
+We use a modification of the breadth first search algorithm to find the nodes and the edges of the attack graph.
 \begin{algorithm}
 	\SetAlgoLined
-	\KwData{goal\_container, topology, container\_exploitability}
+	\KwData{topology, container\_exploitability,
+	privileged\_access}
 	\KwResult{nodes, edges}
@@
 
-The algorithm requires the goal container, the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph.
+The algorithm requires the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
 The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the exploitable vulnerability.
@@
 The algorithm terminates when the queue is empty.
+
 \section{EXPERIMENTS}
+
+In this section, we will conduct few experiments in order to test the scalability of our system with different number of containers and links between them.
+
+Throughout the experiments, the biggest time bottleneck is the preprocessing step, and the graph drawing step.
+However these steps are with linear complexity because the container files are analyzied only once.
+The attack graph generation less time than the preprocessing step.
+
+The following experiments were perfomed.
+We used the Samba(reference) and Phpmailer(reference) examples which were taken from .
+Where we artificially made clique of 1, 5, 20, 50 and 100 containers to test the scalability of the system.
+Each of them has a lot of vulnerabilities.
+
+We also performed testing on a real example- atsea sample shop app(reference). The system is composed of the containers app, database, payment_gateway and reverse_proxy.
+
+\begin{table*}[t]
+\begin{center}
+	\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
+		\hline
+		Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+
+		No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
+
+		No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
+
+		No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
+
+	    No. of edges in topology & 8 & 44 & 464 & 2654 & 10304 & 251504 & 1003004 \\
+
+		No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
+
+		No. edges in attack graph & 4 & 12 & 42 & 102 & 202 & 1002 & 2002 \\
+
+		Topology parsing time & 0.0053 & 0.0093 & 0.0250 & 0.0672 & 0.1112 & 0.7047 & 2.1485 \\
+
+		Attack Graph Generation time & 16.3807 & 16.9825 & 16.0742 & 18.0513 & 21.3882 & 78.6452 & 245.4832 \\
+
+		Breadth-First Search time & 0.0016 & 0.0099 & 0.0931 & 0.5109 & 2.0188 & 54.5766 & 212.2954 \\
+
+		Total time & 17.5676 & 18.2907 & 17.3227 & 19.3901 & 22.7405 & 81.0005 & 249.2042 \\ 
+		\hline
+	\end{tabular}
+\end{center}
+
+\caption{Table with graph characteristics(no.
+of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components(topology parser, attack graph generator and Breadth-first Search) of example graphs containing Phpmailer and Samba.
+Phpmailer has 181, while Samba has 367 vulnerabilities.
+The times are given in seconds.
+The topology time is the time required to generate the graph topology.
+The attack graph generation time includes both  the breath first search and filtering and processing of the vulnerabilities which has a linear time.
+The Breadth-First Search has a complexity O(V + E) where V is the number of nodes represented by the number of containers and E is a tuple of the container, the neighboring container and the vulnerabilities of the neighboring container.
+The total time contains the topology parsing, the attack graph generation and some minor processes.
+However, the total time does not include the vulnerability analysis by Clair.
+Evaluation of Clair can depend on multiple factors and it is not in the scope of this analysis.}
+
+\end{table*}[t]
+
 \section{CONCLUSION}
+
+\section{FUTURE WORK}
 
@@
 
+\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
+
+\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
+
+\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
+National vulnerability database version 2.2 (2010),
+http://nvd.nist.gov/
+
+\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
+"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
+ACSAC'06.
+22nd Annual.
+IEEE, 2006.
+
+\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
+
+\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
+
+\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
 \end{thebibliography}

### 2018-07-04 paper_own_docker/main.tex
Added new example and tests. The scalability tests are now averaged.

@@
 We used the Samba(reference) and Phpmailer(reference) examples which were taken from .
-Where we artificially made clique of 1, 5, 20, 50 and 100 containers to test the scalability of the system.
-Each of them has a lot of vulnerabilities.
+Where we artificially made clique of 1, 5, 20, 50, 100, 500 and 1000 containers to test the scalability of the system.
+The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
+
+On the table(Table I) we can see the results of our experiments.
+In each of the experiments the number of Phpcontainer is constant, while the number of Samba containers is increasing in a clique fashion.
+There are also two artifitial containers("outside" that represents the outside world from where the attacker can attack and the "docker host", i.e.
+the docker daemon where the containers are present).
+Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
+The number of edges of the topology graph is: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
+For example_5, the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clicque edges(5*6/2=15).
 
@@
 
-	    No. of edges in topology & 8 & 44 & 464 & 2654 & 10304 & 251504 & 1003004 \\
+	    No. of edges in topology & 4 & 22 & 232 & 1327 & 5152 & 125752 & 501502 \\
 
@@
 
-		Topology parsing time & 0.0053 & 0.0093 & 0.0250 & 0.0672 & 0.1112 & 0.7047 & 2.1485 \\
+		Topology parsing time & 0.0052 & 0.0096 & 0.0257 & 0.0638 & 0.1185 & 0.8763 & 1.8723 \\
 
-		Attack Graph Generation time & 16.3807 & 16.9825 & 16.0742 & 18.0513 & 21.3882 & 78.6452 & 245.4832 \\
+		Vulnerabilities preprocessing time & 14.7317 & 15.1778 & 15.5593 & 17.1801 & 16.6612 & 23.8188 & 28.1352 \\
 
-		Breadth-First Search time & 0.0016 & 0.0099 & 0.0931 & 0.5109 & 2.0188 & 54.5766 & 212.2954 \\
+		Breadth-First Search time & 0.0017 & 0.0106 & 0.1043 & 0.6128 & 2.1841 & 55.1850 & 193.2329 \\
 
-		Total time & 17.5676 & 18.2907 & 17.3227 & 19.3901 & 22.7405 & 81.0005 & 249.2042 \\ 
+		Total time & 14.7387 & 15.1981 & 15.6895 & 17.8567 & 18.9638 & 79.8802 & 223.2404 \\ 
 		\hline
@@
 \caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components(topology parser, attack graph generator and Breadth-first Search) of example graphs containing Phpmailer and Samba.
-Phpmailer has 181, while Samba has 367 vulnerabilities.
+of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
+The examples are composed of two containers: Phpmailer and Samba.
+The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
+The topology time is the time required to generate the graph topology.
+The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
+The Breath-First Search is the main component that generates the attack graph.
+All of the components are executed five times for each of the examples and their final time is averaged.
 The times are given in seconds.
-The topology time is the time required to generate the graph topology.
-The attack graph generation time includes both  the breath first search and filtering and processing of the vulnerabilities which has a linear time.
-The Breadth-First Search has a complexity O(V + E) where V is the number of nodes represented by the number of containers and E is a tuple of the container, the neighboring container and the vulnerabilities of the neighboring container.
 The total time contains the topology parsing, the attack graph generation and some minor processes.
 However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is not in the scope of this analysis.}
+Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
 

### 2018-07-27 paper_own_docker/main.tex
Paper update. The Proposed method section is updated and the text is reorganized. An image has been added and the algorithm pseudocode has been changed.

@@
                                                           % paper
-
+\usepackage{graphicx}
+\graphicspath{ {./images/} }
 \IEEEoverridecommandlockouts                              % This command is only
@@
 
-\section{ARCHITECTURE}
+\section{PROPOSED METHOD}
 
-In this section, we examine the architecture of our attack graph generator.
-We first present a brief overview of the main concepts.
-Next, we have a look at the preprocessing step.
-Lastly we have look into the main algorithm for generating the attack graph.
+In this section, we first have a look at docker and attack graph terminology.
+We then present an overview of our proposed system with its components and at the end describe each of these components in more detail.
 
-\subsubsection{Main concepts}
+In Docker, distinction is being made between the terms image, container and service.
+Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
+A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
+In our work we treat these terms equally, since we are doing a statical attack graph analysis.
 
-Preconditions are conditions that have to be fulfilled in order for the attack to take place. Postconditions are the result of a successful attack and the privileges acquired.
+In this work we model an attack graph as a sequence of atomic attacks.
+Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or a completely new component with a new privilege.
+A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
+For example, let us suppose that an attacker wants to have access to a database of a certain website.
+In order to reach the database, he has to pass other containers between them/ He does that by finding a vulnerability to exploit and give access to the container's neighbors.After a successful exploitation of a chain of intermediate containers, he finally has access to the database and its functions.
+Eventhough attack graphs model the attacker scenario, they are of crucial importance in computer security.
+A system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
 
-Atomic attack is one step or edge in the attack graph. A state is the container with its privilege level.
+\begin{figure*}
+	\includegraphics[width=\textwidth]{AttackGraphSystem}
+	\caption{Our Attack Graph System.
+The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
+The arrows describe the flow of the system and the files are the intermediate products.}
+	\label{AttackGraphSystem}
+\end{figure*}
 
+Atomic attacks are the fundamental building blocks in our attack graph.
+A single atomic attack represents a successful vulnerability exploitation.
+A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute the attack graph.
+For an atomic attack to be executed, two constraints are imposed.
+First, the containers have to be connected to each other, so that physical access can be ensured.
+Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
 We model the privileges into a hierarchy.
-The priviliges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
+The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
 VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been infected.
@@
 
-<INSERT IMAGE PRIVILEGES>
+Furthermore, in order for an atomic attack to be performed, a certain precondition has to be met.
+Preconditions are privilege levels that are required so that a vulnerability can be exploited.
+When an atomic attack is successfully executed, a postcondition is obtained.
+Postconditions are privileges acquired as a result of a successful attack.
+Both the Pre- and Postconditions are transformed from pre- and postcondition rules which are collected by experts.
+
+Nodes in our attack graph model are composed as a combination of (docker image and privilege level), while edges are a connection between node pairs with a vulnerability as a descriptor.
+Once an attacker exploits a given vulnerability, he gains the privileges for the new container and an edge is added to the attack graph.
+
+Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
+\ref{AttackGraphSystem}).
+The Topology Parser reads the underlying topology of the system and converts it to a more machine readable format, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser from the topology and vulnerabilities files generates the attack graph.
+
+<INSERT IMAGE PRIVILEGES><REF new paper>
 
@@
 
-\subsubsection{Preprocessing}
-In our preprocessing step, we use Clair in order to generate the vulnerabilities for a given container.
-Clair provides the CVE-ID, description and attack vector.
-Attack vector is an entity that descriptes which conditions and effects are connected to this vulnerability.
-Clairctl is a wrapper that we use in order to analyze a docker image.
+In the following subsections, we first look into the required technical system specifications, we then describe each of the parsers in more detail and at the end examine the characteristics of the Breath-First Search used by the Attack Graph Parser.
 
-Additionaly, we parse the attack vectors from the vulnerability database to generate attack rules. We use rules annotated
+\subsubsection{Technical Details}
+Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
 
-docker-compose.yml is used for extraction of the topology of the system. The containers that have published ports are connected to the outside.
+We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
+However, please note that the main algorithm is easily extendable  to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
+
+\subsubsection{Topology Parser}
+The topology of Docker containers can be described in either runtime, or by using Docker Compose.
+In our case, since we are doing static attack graph analysis, we use Docker Compose.
+Docker Compose provides us with a docker-compose.yml which is used for extraction of the topology of the system.
+Even docker-compose.yml are different, based on the version.
+For example older versions use the deprecated keyword link, while newer ones use exclusively networks.
+In this work, we use the keyword networks as a statement that a connection between two containers exists.
+
+However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world. The containers that have published ports are connected to the outside.
+
 Some containers have privileged access. That means that an attacker with access to these containers, has also access to the docker daemon. This can be done by us
 
-This results in a list of container vulnerabilities with their preconditions and postconditions.
+\subsubsection{Vulnerability Parser}
+In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
+Clair provides CVE-ID, description and attack vector for each vulnerability.
+Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
+The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
+However, Clair does not provide with an easy to use interface to analyze a docker image.
+As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
+
+\subsubsection{Attack Graph Parser}
+After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
+
+We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
+In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
+When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
+If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
+If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
 \subsubsection{Breadth-First Search}
 
-After the preprocessing step is done, the vulnerabilties are parsed and their pre- and postconditions are extracted, together with the topology are feed into the Bradth-First Search algorithm(BFS).
+After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
+Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
 Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
+Pseudocode of our modified Breath First Search is given on (Figure.)
 
-Some properties of BFS:
-
-Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
-
-Termination - monotonicity properties
-- complexity
-time complexity O(|N| + |E|) where |N| is the number of nodes and |E| is the number of edges in the attack graph.
-memory complexity
-We use a modification of the breadth first search algorithm to find the nodes and the edges of the attack graph.
 \begin{algorithm}
 	\SetAlgoLined
-	\KwData{topology, container\_exploitability,
-	privileged\_access}
+	\KwData{topology, cont\_expl,
+	priv\_acc}
 	\KwResult{nodes, edges}
-	nodes, edges, queue, passed\_nodes = list(), dict\{\}, Queue(), []\;
-	queue.put(goal\_container)\;
+	nodes, edges, passed\_nodes = [], [], [] \\
+	queue = Queue() \\
+	queue.put("outside" + "ADMIN") \\
 
-	nodes = get\_nodes()\;
 	\While{! queue.isEmpty()}{
-		ending\_node = queue.get()\;
-		passed\_nodes[ending\_node] = True\;
-		cont\_exp\_end = container\_exploitability[ending\_node]\;
-		neighbours = topology[ending\_node]\;
-	    \For{neighbour in neighbours}{
-	    	\If{neighbour == "outside"}{
-
-	    			edges.append(create\_edges())\;
-	    			continue\;
-
+		curr\_node = queue.get() \\
+		curr\_cont = get\_cont(curr\_node) \\
+		curr\_priv = get\_priv(curr\_node) \\
+		neighbours = topology[curr\_cont] \\
+	    \For{neigh in neighbours}{
+	    	\If{curr\_cont == docker\_host}
+	    	{
+	    		end = neigh + "ADMIN" \\
+	    		create\_edge(curr\_node, end) \\
 	    		}
-	        \If{! passed\_nodes[neighbour]}
-	        {queue.put(neighbour)\;}
-            \If{neighbour == goal\_container}{
-            	continue\;}
-            edges.append(create\_edges())
+	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
+	        { 	
+	        	end = neigh + "ADMIN" \\
+	        	create\_edge(curr\_node, end) \\
+	        	queue.put(end) \\
+	        	passed\_nodes.add(end)    	
 	        	}
-
+            \If{neigh != outside and neigh != docker\_host}{
+            	precond = cont\_expl[neigh][precond] \\
+            	postcond = cont\_expl[neigh][postcond] \\
+            	\For{vul in vuls}{
+            		\If{$curr_priv > precond[vul]$}{	
+            	end = neigh + post\_cond[vul]\\
+            	create\_edge(curr\_node, end\_node)\\
+            	\If{end\_node not in passed\_nodes}{
+            		queue.put(end\_node)\\
+            		passed\_nodes.add(end\_node)
+            		}}
+            	}
+                }
+	    	}
+	    nodes = update\_nodes()\\
+	    edges = update\_edges() \\
 	}
@@
 The algorithm requires the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the exploitable vulnerability.
-Then into a while loop we iterate through every node, check its neighbours and add the edges.
-If the neighbour was not passed, then we add it to the queue.
+The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
+Then into a while loop we iterate through every node, check its neighbors and add the edges.
+If the neighbor was not passed, then we add it to the queue.
 The algorithm terminates when the queue is empty.
 
-\section{EXPERIMENTS}
+Breath First Search is characterized by the following properties:
+
+\begin{itemize}
+ \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
+ \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
+ \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
+\end{itemize}
+\section{EVALUATION}
 
@@
 The number of edges of the topology graph is: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example_5, the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clicque edges(5*6/2=15).
+For example\_5, the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clicque edges(5*6/2=15).
 
-We also performed testing on a real example- atsea sample shop app(reference). The system is composed of the containers app, database, payment_gateway and reverse_proxy.
+We also performed testing on a real example- atsea sample shop app(reference). The system is composed of the containers app, database, payment\_gateway and reverse\_proxy.
+
+\begin{table*}[t]
+	\begin{center}
+		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
+			\hline
+			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
+
+			Netflix OSS & Combination of containers provided from Netflix.
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
+
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
+
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
+
+			PHPMailer and Samba & An artificial example created from two separate containers.
+We use an augmented version for the scalability tests.
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
+			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
+
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
+
+\end{table*}[t]
 
@@
 
-		No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
+		No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & n\\
 
-	    No. of edges in topology & 4 & 22 & 232 & 1327 & 5152 & 125752 & 501502 \\
+	    No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & n \\
 
-		No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
+		No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & n \\
 
-		No. edges in attack graph & 4 & 12 & 42 & 102 & 202 & 1002 & 2002 \\
+		No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & n \\
 
-		Topology parsing time & 0.0052 & 0.0096 & 0.0257 & 0.0638 & 0.1185 & 0.8763 & 1.8723 \\
+		Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & n \\
 
-		Vulnerabilities preprocessing time & 14.7317 & 15.1778 & 15.5593 & 17.1801 & 16.6612 & 23.8188 & 28.1352 \\
+		Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & n \\
 
-		Breadth-First Search time & 0.0017 & 0.0106 & 0.1043 & 0.6128 & 2.1841 & 55.1850 & 193.2329 \\
+		Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & n \\
 
-		Total time & 14.7387 & 15.1981 & 15.6895 & 17.8567 & 18.9638 & 79.8802 & 223.2404 \\ 
+		Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & n \\ 
 		\hline

### 2018-08-02 paper_own_docker/main.tex
Proposed method section is complete. two images are added and Evaluation section is begun.

@@
 
-In this section, we first have a look at docker and attack graph terminology.
-We then present an overview of our proposed system with its components and at the end describe each of these components in more detail.
+In this section we first have a look at Docker and attack graph terminology.
+We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
 
@@
 A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a statical attack graph analysis.
+In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
 
 In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or a completely new component with a new privilege.
+Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
 A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
 For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between them/ He does that by finding a vulnerability to exploit and give access to the container's neighbors.After a successful exploitation of a chain of intermediate containers, he finally has access to the database and its functions.
-Eventhough attack graphs model the attacker scenario, they are of crucial importance in computer security.
-A system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
+In order to reach the database, he has to pass other containers between him and the database.
+He does that by finding a vulnerability to exploit and give access to the container's neighbors.
+After a successful exploitation of a chain of intermediate containers, he finally has access to the database and its functions.
+Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
+For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
 
@@
 
-Atomic attacks are the fundamental building blocks in our attack graph.
+Atomic attacks are fundamental building blocks in our attack graph.
 A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute the attack graph.
+A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
 For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected to each other, so that physical access can be ensured.
+First, the containers have to be connected between each other, so that physical access can be ensured.
 Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
@@
 VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been infected.
-Since VOS are on some hosts, they have lower level of hierarchy.
+Since VOS are on some hosts, they are in the lower level of hierarchy.
 
@@
 Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules which are collected by experts.
+Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
+We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
 
-Nodes in our attack graph model are composed as a combination of (docker image and privilege level), while edges are a connection between node pairs with a vulnerability as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privileges for the new container and an edge is added to the attack graph.
+Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
+Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
+
+In order to show how the attack graph generation works in practice, we present a small example.
+The example is taken from the Netflix OSS Github repository.
+Displayed on figure \ref{TopologyGraph} is the topology of the example.
+The topology consists of "Outside" node, "Docker daemon" and the a subset of the containers.
+On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
+An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
+Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
+Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
+It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
+Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
 
@@
 \ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it to a more machine readable format, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser from the topology and vulnerabilities files generates the attack graph.
+The Topology Parser reads the underlying topology of the system and converts it into a more machine readable format, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
 
-<INSERT IMAGE PRIVILEGES><REF new paper>
+\begin{figure}
+	\includegraphics[]{Topology_graph}
+	\caption{Example topology graph.
+The topology graph is a subset of a real topology graph from the Netflix OSS example.
+Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
+	\label{TopologyGraph}
+\end{figure}
 
-<INSERT IMAGE EXAMPLE>
+\begin{figure}
+	\includegraphics[]{Attack_graph}
+	\caption{Example resulting attack graph.
+This attack graph is a subset of a real attack graph from the Netflix OSS example.
+Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
+	\label{AttackGraph}
+\end{figure}
 
-<INSERT IMAGE ATTACK GRAPH>
-
-In the following subsections, we first look into the required technical system specifications, we then describe each of the parsers in more detail and at the end examine the characteristics of the Breath-First Search used by the Attack Graph Parser.
+In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
 
@@
 \subsubsection{Topology Parser}
-The topology of Docker containers can be described in either runtime, or by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose.
-Docker Compose provides us with a docker-compose.yml which is used for extraction of the topology of the system.
-Even docker-compose.yml are different, based on the version.
-For example older versions use the deprecated keyword link, while newer ones use exclusively networks.
-In this work, we use the keyword networks as a statement that a connection between two containers exists.
+The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
+In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
+Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
+However different version of docker-compose.yml, use different syntax.
+For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
+In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
 
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world. The containers that have published ports are connected to the outside.
+However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
+This is usually done using publishing ports.
+This is the case in both computer networks, as well as in microservice architectures.
 
-Some containers have privileged access. That means that an attacker with access to these containers, has also access to the docker daemon. This can be done by us
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair provides CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-However, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given on (Figure.)
+Another thing that we take into account is the privileged access.
+Some containers require certain privileges over the docker daemon in order to function properly.
+In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
+An attacker with access to these containers, has also access to the docker daemon.
+And once he has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
 
@@
 \caption{Breadth-first search algorithm for generating an attack graph.}
+\label{BFSalgorithm}
 \end{algorithm}
+
+\begin{table*}[t]
+	\begin{center}
+		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
+			\hline
+			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+
+			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
+
+			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
+
+			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
+
+			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
+
+			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
+
+			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
+
+			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
+
+			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
+
+			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
+
+			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{Table with graph characteristics(no.
+of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
+The examples are composed of two containers: Phpmailer and Samba.
+The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
+The topology time is the time required to generate the graph topology.
+The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
+The Breath-First Search is the main component that generates the attack graph.
+All of the components are executed five times for each of the examples and their final time is averaged.
+The times are given in seconds.
+The total time contains the topology parsing, the attack graph generation and some minor processes.
+However, the total time does not include the vulnerability analysis by Clair.
+Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
+
+	\label{table_scalability}
+\end{table*}[t]
+
+\subsubsection{Vulnerability Parser}
+In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
+Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
+Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
+The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
+Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
+As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
+
+\subsubsection{Attack Graph Parser}
+After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
+
+We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
+In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
+When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
+If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
+If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
+
+\subsubsection{Breadth-First Search}
+
+After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
+Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
+Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
+Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
 
@@
 The algorithm terminates when the queue is empty.
-
-Breath First Search is characterized by the following properties:
+It is characterized by the following properties:
 
@@
 \end{itemize}
+
 \section{EVALUATION}
 
-In this section, we will conduct few experiments in order to test the scalability of our system with different number of containers and links between them.
+An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
+(some references and description with statistics).
+In this section, we first have a look at how others evaluate their proposed systems.
+We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
 
-Throughout the experiments, the biggest time bottleneck is the preprocessing step, and the graph drawing step.
-However these steps are with linear complexity because the container files are analyzied only once.
-The attack graph generation less time than the preprocessing step.
-
-The following experiments were perfomed.
-We used the Samba(reference) and Phpmailer(reference) examples which were taken from .
-Where we artificially made clique of 1, 5, 20, 50, 100, 500 and 1000 containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On the table(Table I) we can see the results of our experiments.
-In each of the experiments the number of Phpcontainer is constant, while the number of Samba containers is increasing in a clique fashion.
-There are also two artifitial containers("outside" that represents the outside world from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clicque edges(5*6/2=15).
-
-We also performed testing on a real example- atsea sample shop app(reference). The system is composed of the containers app, database, payment\_gateway and reverse\_proxy.
+Evaluation of a given system is a usually required part, when evaluating a given program.
+Extensive scalability study is not available.
+Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
+All of these components contribute to the execution time.
+Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
+In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
 
@@
 	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
+	\label{table_technologies}
 
@@
 
-\begin{table*}[t]
-\begin{center}
-	\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-		\hline
-		Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+For each example describe their setup and their results.
 
-		No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
+Seyner, the attack graph has 5948 nodes and 68364 edges.
+The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
+They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
 
-		No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
+Ingols tested on a network of 250 hosts.
+He also tested on a simulated network of 50000 hosts in under 4 minutes.
+(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
 
-		No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & n\\
+Amman does not provide with scalability methods.
 
-	    No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & n \\
+Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
 
-		No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & n \\
+In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
+We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
+The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
 
-		No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & n \\
+On Table \ref{table_scalability} we can see the results of our experiments.
+In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
+This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
+In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
+the docker daemon where the containers are present).
+Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
+The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
+For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
 
-		Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & n \\
+Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
+However these steps are with the number of containers because the container files are analyzed only once.
+The attack graph generation less time than the preprocessing step.
+Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
+For the previous example with example\_100, needed 6.5 seconds.
 
-		Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & n \\
+We also performed tests on some real examples as described on table.
+These examples are different from the synthetic ones presented above, since they contain less containers.
+Also they are in a more linear fashion.
+For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
 
-		Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & n \\
+ We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
+These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
+Short summary of them is given on the table \ref{table_technologies}.
+We want to show that we can generalize our approach for different types of technologies.
 
-		Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & n \\ 
-		\hline
-	\end{tabular}
-\end{center}
-
-\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-\end{table*}[t]
+Characteristics of the Attack Graph Generator.
+ - stopping criteria (When all edges are traversed)
+ - BFS is guaranteed to traverse all of the edges 
+ - monothonicity no edge is visited more than once.
+ - all of the vulnerabilities per edge are checked
+ - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
 

### 2018-08-04 paper_own_docker/main.tex
Some modifications in the text of the main section of the paper.

@@
 He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of a chain of intermediate containers, he finally has access to the database and its functions.
+After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
 Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
@@
 The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been infected.
-Since VOS are on some hosts, they are in the lower level of hierarchy.
+VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
+Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
 
-Furthermore, in order for an atomic attack to be performed, a certain precondition has to be met.
+Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
 Preconditions are privilege levels that are required so that a vulnerability can be exploited.
@@
 Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" and the a subset of the containers.
+The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
 On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
@@
 \ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into a more machine readable format, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
+The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
 
@@
 
-Another thing that we take into account is the privileged access.
+Another consideration that we take into account is the privileged access.
 Some containers require certain privileges over the docker daemon in order to function properly.
@@
 An attacker with access to these containers, has also access to the docker daemon.
-And once he has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
+Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
 
@@
 
-\begin{table*}[t]
+\begin{table*}
 	\begin{center}
@@
 	\label{table_scalability}
-\end{table*}[t]
+\end{table*}
 
@@
 
-The algorithm requires the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
+The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
 The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges.
+Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
 If the neighbor was not passed, then we add it to the queue.
 The algorithm terminates when the queue is empty.
-It is characterized by the following properties:
+Furthermore BFS is characterized by the following properties:
 

### 2018-08-10 paper_own_docker/main.tex
Sections related work and evaluation are done. Minor mistakes corrected in proposed method and references added.

@@
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[options]{algorithm2e}                                     % if you need a4paper
+\usepackage[]{algorithm2e}                                     % if you need a4paper
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
@@
 
+ Statistics. They do not offer any performance comparison between different topologies.
+
 We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
@@
 
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
-There the attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of the goal container.
-Some works use model checkers with goal property(Sheyner reference).
-They However model checkers as a disadvantage have a state explosion.(Ingols reference)
+Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the Internet.
+In these networks an attacker performs multiple steps to achieve his goal, i.e.
+gaining privileges of a specific host.
+Attack graphs help in analyzing this behavior.
+Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
+Tools that generate vulnerabilities of specific host are available.
+However previous works have state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
+Therefore, some teams have working in constructing systems that generate attack graphs automatically by using different approaches.
 
-Others use breath first search algorithm. (Ingols reference)  They model the
+One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
+A collection of these counter examples form an attack graph.
+They state that model checkers satisfy a monotonicity property in order to ensure termination.
+However model checkers have a computational disadvantage.
+In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed.
+Amman et al.
+extends this work with some simplifications and more efficient storage.\cite{amman}
 
-Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
+Ou et al.
+use logical attack graph\cite{ou} and Ingols\cite{ingols} et al.
+use breath first search algorithm in order to tackle the scalability issue.
+Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes.
+They use breath first search technique for generating the attack graph.
+This approach provides faster results in comparison to using model checkers.
+An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
 
-Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
-To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- They dont use Clair as well. They do not offer any performance comparison between different topologies.
+Aksu et al.
+builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks.\cite{aksu} They define a specific test of pre- and postcondition rules and test their correctness.
+In their evaluation, they use machine learning approach.
+
+Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers.
+Therefore we extend the work from Ingols\cite{ingols} and Aksu\cite{aksu} in conjuction to Clair OS to generate attack graphs for microservice architectures.
+Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
+Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
 
@@
 We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
 
@@
 \end{figure*}
+
+In Docker, distinction is being made between the terms image, container and service.
+Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production.
+A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
+In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.\cite{docker}
+
+In this work we model an attack graph as a sequence of atomic attacks.
+Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
+A goal of an attacker would be to perform multiple atomic attacks to reach the desired goal container.
+For example, let us suppose that an attacker wants to have access to a database of a certain website.
+In order to reach the database, he has to pass other containers between him and the database.
+He does that by finding a vulnerability to exploit and gives access to the container's neighbors.
+After a successful exploitation of multiple intermediate containers, he finally has access to the database and its content.
+Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
+For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
 
@@
 VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
+Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.\cite{aksu}
 
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
+Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured.
 Preconditions are privilege levels that are required so that a vulnerability can be exploited.
@@
 Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
+We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated.\cite{aksu}
 
@@
 In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Displayed on figure \ref{TopologyGraph} is the topology of the example.
+The example is taken from the Netflix OSS Github repository.\cite{netflixoss} Displayed on figure \ref{TopologyGraph} is the topology of the example.
 The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
@@
 \subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
+Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair\cite{clair} and Clairctl\cite{clairctl} for vulnerabilities generation.
 
@@
 Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different version of docker-compose.yml, use different syntax.
+However different versions of docker-compose.yml, use different syntax.
 For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
@@
 	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
+of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulnerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
 The examples are composed of two containers: Phpmailer and Samba.
@@
 In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
+Clair is a vulnerability scanner that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
 Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
@@
 
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
+Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
 In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
+When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
+If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
+If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.
+This results in a list of container vulnerabilities with their preconditions and postconditions.
 
@@
 Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
+Breadth-First Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
 Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
 
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
+The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph. 
 The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
-If the neighbor was not passed, then we add it to the queue.
+Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
+If the neighbor was not passed, then it is added to the queue.
 The algorithm terminates when the queue is empty.
@@
 
-An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
-(some references and description with statistics).
-In this section, we first have a look at how others evaluate their proposed systems.
-We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
+In real-world microservice architectures, many containers are interconnected to each other.
+This raises the need for a scalable attack graph system.
+In this section, we first have a look at how others evaluate their systems.
+We then conduct few experiments in order to test the scalability of our system with different number of containers, and connections in both artificial and real networks.
+All of the experiments were performed on a Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
 
-Evaluation of a given system is a usually required part, when evaluating a given program.
-Extensive scalability study is not available.
-Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time.
-Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
-In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
+Extensive scalability study of attack graph generators  is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
+Characteristics that usually vary in this sort of evaluation are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
+All of these components contribute to the execution time of a given algorithm.
+Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
+In our case we compare our system to existing work by treating every container as a computer, and any physical connection between two computers as a connection between two containers.
 
-\begin{table*}[t]
+\begin{table*}
 	\begin{center}
-		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
+		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{15mm}|p{45mm}| } 
 			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
+			Name & Description & Technology stack & No. Containers & No. vuln. & Attack Graph generation time & Github link \\\hline
 
 			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & 0.5120 sec.
+& https://github.com/Oreste-Luci/netflix-oss-example \\\hline
 
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & 0.2761 sec. & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
 
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
+			JavaEE demo & An application for browsing movies along with other related functions.
+& Java EE application, React, Tomcat EE & 2 & 149 & 0.2613 sec.
+& https://github.com/dockersamples/javaee-demo \\\hline
 
@@
 We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & 0.2570 sec.
+& https://github.com/opsxcq/exploit-CVE-2016-10033
 			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
@@
 
-\end{table*}[t]
+\end{table*}
 
-For each example describe their setup and their results.
+Seyner in his work tests the system in both a small and extended examples.\cite{sheyner} The attack graph in the larger example has 5948 nodes and 68364 edges.
+The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
+Sheyner claims that the performance bottleneck is inside the graph generation procedure.
 
-Seyner, the attack graph has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
+Ingols tested his system on a network of 250 hosts.
+He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes.\cite{ingols} Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
+In addition to this, missing explanation of how the hosts are connected, does not make it directly comparable to our method.
 
-Ingols tested on a network of 250 hosts.
-He also tested on a simulated network of 50000 hosts in under 4 minutes.
-(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
+Ou provides some more extended study where he tests his system on more examples.\cite{ou}  He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds.
+He also provides an evaluation where he MulVAL clearly outperforms the Sheyner's system.
 
-Amman does not provide with scalability methods.
-
-Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
-
-In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
+In our scalability experiments we use Samba\cite{samba} and Phpmailer\cite{phpmailer} containers which were taken from their respective Github repositories.
 We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
@@
 On Table \ref{table_scalability} we can see the results of our experiments.
-In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
+In each of these experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
+This increase is done in a fully connected fashion, a node of each additional container is connected to every existing container.
 In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
@@
 
-Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
-However these steps are with the number of containers because the container files are analyzed only once.
-The attack graph generation less time than the preprocessing step.
-Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
-For the previous example with example\_100, needed 6.5 seconds.
+Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step.
+However this step increases in linear fashion because the container files are analyzed only once by Clair.
+The attack graph generation for the smaller examples is considerably less than the preprocessing time.
+Starting from example\_500, we can notice sharp increase in BDF execution time to 165 seconds.
+For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
 
-We also performed tests on some real examples as described on table.
-These examples are different from the synthetic ones presented above, since they contain less containers.
-Also they are in a more linear fashion.
-For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
-
- We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
-Short summary of them is given on the table \ref{table_technologies}.
-We want to show that we can generalize our approach for different types of technologies.
-
-Characteristics of the Attack Graph Generator.
- - stopping criteria (When all edges are traversed)
- - BFS is guaranteed to traverse all of the edges 
- - monothonicity no edge is visited more than once.
- - all of the vulnerabilities per edge are checked
- - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
+We also performed tests on some real examples as described on table \ref{table_technologies} and extend our system to different types of technologies, number of containers and vulnerabilities.
+The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
+These examples are different from the synthetic ones presented above, since they contain less and different containers.
+They are connected in a more linear fashion in contrast to the full connection provided in the previous example.
+For example, in order for an attacker to reach a database, he needs to gain suitable privilege levels of multiple intermediate containers in several steps.
 
@@
 
-\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
+\bibitem{docker} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
 
-\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
+\bibitem{clair}  CoreOS Clair. https://github.com/coreos/clair
 
-\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
+\bibitem{clairctl}  Clairctl. https://github.com/jgsqware/clairctl
 
-\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
+\bibitem{nvd}  Computer Security Division of National Institute of Standards and Technology.
 National vulnerability database version 2.2 (2010),
@@
 
-\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
+\bibitem{ingols}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
 "Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
@@
 
-\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
+\bibitem{aksu}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
 
-\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
+\bibitem{sheyner}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
 
-\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
+\bibitem{netspa}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
+
+\bibitem{amman}  Ritchey, Ronald W., and Paul Ammann. "Using model checking to analyze network vulnerabilities." Security and Privacy, 2000. S\&P 2000. Proceedings. 2000 IEEE Symposium on. IEEE, 2000.
+
+\bibitem{ou}  Ou, Xinming, Wayne F.
+Boyer, and Miles A.
+McQueen.
+"A scalable approach to attack graph generation." Proceedings of the 13th ACM conference on Computer and communications security.
+ACM, 2006.
+
+\bibitem{samba} https://github.com/opsxcq/exploit-CVE-2017-7494
+
+\bibitem{phpmailer} https://github.com/opsxcq/exploit-CVE-2016-10033
+
+\bibitem{netflixoss} https://github.com/Oreste-Luci/netflix-oss-example
 \end{thebibliography}

### 2018-08-29 paper_own_docker/main.tex
Some first notes

@@
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[]{algorithm2e}                                     % if you need a4paper
+\usepackage[]{algorithm2e}      
+\usepackage{xcolor} 
+\newcommand\todo[1]{\textcolor{red}{#1}}                                     % if you need a4paper
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
@@
                                                           % use the \thanks command
+
 \overrideIEEEmargins
@@
 
+\todo{We need to use the format of the conference, i added a folder ACM that contains it, please use it. And split the sections into different latex files using, so that we don't run into merges }
+
 Attack graphs are a popular way of examining security aspects of network.
@@
 
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the Internet.
-In these networks an attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of a specific host.
+Previous work has dealt with attack graph generation, mainly in computer networks \todo{please cite them}, where multiple machines are connected to each other and the Internet.
+In these networks an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
 Attack graphs help in analyzing this behavior.
-Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
+Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process\todo{elaborate a bit why; scalability, expertise, completeness..
+}.
 Tools that generate vulnerabilities of specific host are available.
-However previous works have state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
-Therefore, some teams have working in constructing systems that generate attack graphs automatically by using different approaches.
+However previous works have state that these tools alone are not enough to analyze the vulnerability \todo{mention why coz they can be connected ..} of an entire network and that these tools in addition to network topology could solve this issue.
+Therefore, some teams have been  working on developing systems that generate attack graphs automatically by using different approaches.
 
-One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
+One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} \todo{space citation then the dot, e.g., property [5].}Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
 A collection of these counter examples form an attack graph.
@@
 use breath first search algorithm in order to tackle the scalability issue.
-Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes.
+Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes\todo{please rephrase this sentence to clarify it what is redundanccy full, define MP}.
 They use breath first search technique for generating the attack graph.
@@
 Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-
+\todo{in general good story line, some language work is needed later-on}
 \section{PROPOSED METHOD}
@@
 
+\todo{it is early to put this image here, also long caption, image quality should be enhanced}
 \begin{figure*}

### 2018-08-31 paper_own_docker/chapters/abstract.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-04 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[options]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
-
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
-
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
-
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
 Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
@@
 Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
-
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
-
-\section{RELATED WORK}
-
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
-There the attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of the goal container.
-Some works use model checkers with goal property(Sheyner reference).
-They However model checkers as a disadvantage have a state explosion.(Ingols reference)
-
-Others use breath first search algorithm. (Ingols reference)  They model the
-
-Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
-
-Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
-To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- They dont use Clair as well. They do not offer any performance comparison between different topologies.
-
-\section{PROPOSED METHOD}
-
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
-
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different version of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-	priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-	    \For{neigh in neighbours}{
-	    	\If{curr\_cont == docker\_host}
-	    	{
-	    		end = neigh + "ADMIN" \\
-	    		create\_edge(curr\_node, end) \\
-	    		}
-	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
-	        { 	
-	        	end = neigh + "ADMIN" \\
-	        	create\_edge(curr\_node, end) \\
-	        	queue.put(end) \\
-	        	passed\_nodes.add(end)    	
-	        	}
-            \If{neigh != outside and neigh != docker\_host}{
-            	precond = cont\_expl[neigh][precond] \\
-            	postcond = cont\_expl[neigh][postcond] \\
-            	\For{vul in vuls}{
-            		\If{$curr_priv > precond[vul]$}{	
-            	end = neigh + post\_cond[vul]\\
-            	create\_edge(curr\_node, end\_node)\\
-            	\If{end\_node not in passed\_nodes}{
-            		queue.put(end\_node)\\
-            		passed\_nodes.add(end\_node)
-            		}}
-            	}
-                }
-	    	}
-	    nodes = update\_nodes()\\
-	    edges = update\_edges() \\
-	}
-
-\caption{Breadth-first search algorithm for generating an attack graph.}
-\label{BFSalgorithm}
-\end{algorithm}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-			\hline
-			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-	\label{table_scalability}
-\end{table*}
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
-If the neighbor was not passed, then we add it to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-\begin{itemize}
- \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
- \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
- \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-\end{itemize}
-
-\section{EVALUATION}
-
-An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
-(some references and description with statistics).
-In this section, we first have a look at how others evaluate their proposed systems.
-We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
-
-Evaluation of a given system is a usually required part, when evaluating a given program.
-Extensive scalability study is not available.
-Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time.
-Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
-In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
-
-\begin{table*}[t]
-	\begin{center}
-		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}[t]
-
-For each example describe their setup and their results.
-
-Seyner, the attack graph has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
-
-Ingols tested on a network of 250 hosts.
-He also tested on a simulated network of 50000 hosts in under 4 minutes.
-(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
-
-Amman does not provide with scalability methods.
-
-Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
-
-In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On Table \ref{table_scalability} we can see the results of our experiments.
-In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
-
-Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
-However these steps are with the number of containers because the container files are analyzed only once.
-The attack graph generation less time than the preprocessing step.
-Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
-For the previous example with example\_100, needed 6.5 seconds.
-
-We also performed tests on some real examples as described on table.
-These examples are different from the synthetic ones presented above, since they contain less containers.
-Also they are in a more linear fashion.
-For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
-
- We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
-Short summary of them is given on the table \ref{table_technologies}.
-We want to show that we can generalize our approach for different types of technologies.
-
-Characteristics of the Attack Graph Generator.
- - stopping criteria (When all edges are traversed)
- - BFS is guaranteed to traverse all of the edges 
- - monothonicity no edge is visited more than once.
- - all of the vulnerabilities per edge are checked
- - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-\end{thebibliography}
-
-\end{document}

### 2018-08-31 paper_own_docker/chapters/background.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

\section{BACKGROUND}

\subsection{Attack Graphs}
\subsection{Microservice Architectures}

### 2018-08-31 paper_own_docker/chapters/evaluation.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-10 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
-
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
-
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
-
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
-
- Statistics. They do not offer any performance comparison between different topologies.
-
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
-
-\section{RELATED WORK}
-
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the Internet.
-In these networks an attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of a specific host.
-Attack graphs help in analyzing this behavior.
-Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
-Tools that generate vulnerabilities of specific host are available.
-However previous works have state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
-Therefore, some teams have working in constructing systems that generate attack graphs automatically by using different approaches.
-
-One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
-A collection of these counter examples form an attack graph.
-They state that model checkers satisfy a monotonicity property in order to ensure termination.
-However model checkers have a computational disadvantage.
-In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed.
-Amman et al.
-extends this work with some simplifications and more efficient storage.\cite{amman}
-
-Ou et al.
-use logical attack graph\cite{ou} and Ingols\cite{ingols} et al.
-use breath first search algorithm in order to tackle the scalability issue.
-Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes.
-They use breath first search technique for generating the attack graph.
-This approach provides faster results in comparison to using model checkers.
-An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
-
-Aksu et al.
-builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks.\cite{aksu} They define a specific test of pre- and postcondition rules and test their correctness.
-In their evaluation, they use machine learning approach.
-
-Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers.
-Therefore we extend the work from Ingols\cite{ingols} and Aksu\cite{aksu} in conjuction to Clair OS to generate attack graphs for microservice architectures.
-Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
-Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-
-\section{PROPOSED METHOD}
-
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.\cite{docker}
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to reach the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and gives access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its content.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
-
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.\cite{aksu}
-
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated.\cite{aksu}
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.\cite{netflixoss} Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair\cite{clair} and Clairctl\cite{clairctl} for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different versions of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-	priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-	    \For{neigh in neighbours}{
-	    	\If{curr\_cont == docker\_host}
-	    	{
-	    		end = neigh + "ADMIN" \\
-	    		create\_edge(curr\_node, end) \\
-	    		}
-	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
-	        { 	
-	        	end = neigh + "ADMIN" \\
-	        	create\_edge(curr\_node, end) \\
-	        	queue.put(end) \\
-	        	passed\_nodes.add(end)    	
-	        	}
-            \If{neigh != outside and neigh != docker\_host}{
-            	precond = cont\_expl[neigh][precond] \\
-            	postcond = cont\_expl[neigh][postcond] \\
-            	\For{vul in vuls}{
-            		\If{$curr_priv > precond[vul]$}{	
-            	end = neigh + post\_cond[vul]\\
-            	create\_edge(curr\_node, end\_node)\\
-            	\If{end\_node not in passed\_nodes}{
-            		queue.put(end\_node)\\
-            		passed\_nodes.add(end\_node)
-            		}}
-            	}
-                }
-	    	}
-	    nodes = update\_nodes()\\
-	    edges = update\_edges() \\
-	}
-
-\caption{Breadth-first search algorithm for generating an attack graph.}
-\label{BFSalgorithm}
-\end{algorithm}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-			\hline
-			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulnerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-	\label{table_scalability}
-\end{table*}
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a vulnerability scanner that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.
-This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-First Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
-If the neighbor was not passed, then it is added to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-\begin{itemize}
- \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
- \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
- \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-\end{itemize}
-
 \section{EVALUATION}
@@
 
-Seyner in his work tests the system in both a small and extended examples.\cite{sheyner} The attack graph in the larger example has 5948 nodes and 68364 edges.
+Seyner in his work tests the system in both a small and extended examples \cite{sheyner2002automated}.
+The attack graph in the larger example has 5948 nodes and 68364 edges.
 The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
@@
 Ingols tested his system on a network of 250 hosts.
-He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes.\cite{ingols} Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
+He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
+Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
 In addition to this, missing explanation of how the hosts are connected, does not make it directly comparable to our method.
 
-Ou provides some more extended study where he tests his system on more examples.\cite{ou}  He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
+Ou provides some more extended study where he tests his system on more examples \cite{ou2006scalable}.
+He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
 The performance of the system for 1000 fully connected nodes takes more than 1000 seconds.
@@
 
-In our scalability experiments we use Samba\cite{samba} and Phpmailer\cite{phpmailer} containers which were taken from their respective Github repositories.
+In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
 We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
@@
 For example, in order for an attacker to reach a database, he needs to gain suitable privilege levels of multiple intermediate containers in several steps.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{docker} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{clair}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{clairctl}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{nvd}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{ingols}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{aksu}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{sheyner}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{netspa}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-
-\bibitem{amman}  Ritchey, Ronald W., and Paul Ammann. "Using model checking to analyze network vulnerabilities." Security and Privacy, 2000. S\&P 2000. Proceedings. 2000 IEEE Symposium on. IEEE, 2000.
-
-\bibitem{ou}  Ou, Xinming, Wayne F.
-Boyer, and Miles A.
-McQueen.
-"A scalable approach to attack graph generation." Proceedings of the 13th ACM conference on Computer and communications security.
-ACM, 2006.
-
-\bibitem{samba} https://github.com/opsxcq/exploit-CVE-2017-7494
-
-\bibitem{phpmailer} https://github.com/opsxcq/exploit-CVE-2016-10033
-
-\bibitem{netflixoss} https://github.com/Oreste-Luci/netflix-oss-example
-\end{thebibliography}
-
-\end{document}

### 2018-08-31 paper_own_docker/chapters/introduction.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-04 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[options]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
-
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
-
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
-
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{INTRODUCTION}
+%\todo{We need to use the format of the conference, i added a folder ACM that contains it, please use it. And split the sections into different latex files using, so that we don't run into merges }
 
@@
 
+ Statistics. They do not offer any performance comparison between different topologies.
+
 We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
-
-\section{RELATED WORK}
-
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
-There the attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of the goal container.
-Some works use model checkers with goal property(Sheyner reference).
-They However model checkers as a disadvantage have a state explosion.(Ingols reference)
-
-Others use breath first search algorithm. (Ingols reference)  They model the
-
-Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
-
-Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
-To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- They dont use Clair as well. They do not offer any performance comparison between different topologies.
-
-\section{PROPOSED METHOD}
-
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
-
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different version of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-	priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-	    \For{neigh in neighbours}{
-	    	\If{curr\_cont == docker\_host}
-	    	{
-	    		end = neigh + "ADMIN" \\
-	    		create\_edge(curr\_node, end) \\
-	    		}
-	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
-	        { 	
-	        	end = neigh + "ADMIN" \\
-	        	create\_edge(curr\_node, end) \\
-	        	queue.put(end) \\
-	        	passed\_nodes.add(end)    	
-	        	}
-            \If{neigh != outside and neigh != docker\_host}{
-            	precond = cont\_expl[neigh][precond] \\
-            	postcond = cont\_expl[neigh][postcond] \\
-            	\For{vul in vuls}{
-            		\If{$curr_priv > precond[vul]$}{	
-            	end = neigh + post\_cond[vul]\\
-            	create\_edge(curr\_node, end\_node)\\
-            	\If{end\_node not in passed\_nodes}{
-            		queue.put(end\_node)\\
-            		passed\_nodes.add(end\_node)
-            		}}
-            	}
-                }
-	    	}
-	    nodes = update\_nodes()\\
-	    edges = update\_edges() \\
-	}
-
-\caption{Breadth-first search algorithm for generating an attack graph.}
-\label{BFSalgorithm}
-\end{algorithm}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-			\hline
-			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-	\label{table_scalability}
-\end{table*}
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
-If the neighbor was not passed, then we add it to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-\begin{itemize}
- \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
- \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
- \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-\end{itemize}
-
-\section{EVALUATION}
-
-An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
-(some references and description with statistics).
-In this section, we first have a look at how others evaluate their proposed systems.
-We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
-
-Evaluation of a given system is a usually required part, when evaluating a given program.
-Extensive scalability study is not available.
-Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time.
-Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
-In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
-
-\begin{table*}[t]
-	\begin{center}
-		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}[t]
-
-For each example describe their setup and their results.
-
-Seyner, the attack graph has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
-
-Ingols tested on a network of 250 hosts.
-He also tested on a simulated network of 50000 hosts in under 4 minutes.
-(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
-
-Amman does not provide with scalability methods.
-
-Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
-
-In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On Table \ref{table_scalability} we can see the results of our experiments.
-In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
-
-Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
-However these steps are with the number of containers because the container files are analyzed only once.
-The attack graph generation less time than the preprocessing step.
-Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
-For the previous example with example\_100, needed 6.5 seconds.
-
-We also performed tests on some real examples as described on table.
-These examples are different from the synthetic ones presented above, since they contain less containers.
-Also they are in a more linear fashion.
-For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
-
- We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
-Short summary of them is given on the table \ref{table_technologies}.
-We want to show that we can generalize our approach for different types of technologies.
-
-Characteristics of the Attack Graph Generator.
- - stopping criteria (When all edges are traversed)
- - BFS is guaranteed to traverse all of the edges 
- - monothonicity no edge is visited more than once.
- - all of the vulnerabilities per edge are checked
- - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-\end{thebibliography}
-
-\end{document}

### 2018-08-31 paper_own_docker/chapters/method.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-10 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
-
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
-
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
-
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
-
- Statistics. They do not offer any performance comparison between different topologies.
-
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
-
-\section{RELATED WORK}
-
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the Internet.
-In these networks an attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of a specific host.
-Attack graphs help in analyzing this behavior.
-Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
-Tools that generate vulnerabilities of specific host are available.
-However previous works have state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
-Therefore, some teams have working in constructing systems that generate attack graphs automatically by using different approaches.
-
-One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
-A collection of these counter examples form an attack graph.
-They state that model checkers satisfy a monotonicity property in order to ensure termination.
-However model checkers have a computational disadvantage.
-In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed.
-Amman et al.
-extends this work with some simplifications and more efficient storage.\cite{amman}
-
-Ou et al.
-use logical attack graph\cite{ou} and Ingols\cite{ingols} et al.
-use breath first search algorithm in order to tackle the scalability issue.
-Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes.
-They use breath first search technique for generating the attack graph.
-This approach provides faster results in comparison to using model checkers.
-An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
-
-Aksu et al.
-builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks.\cite{aksu} They define a specific test of pre- and postcondition rules and test their correctness.
-In their evaluation, they use machine learning approach.
-
-Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers.
-Therefore we extend the work from Ingols\cite{ingols} and Aksu\cite{aksu} in conjuction to Clair OS to generate attack graphs for microservice architectures.
-Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
-Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-
-\section{PROPOSED METHOD}
-
+\section{METHOD}
 In this section we first have a look at Docker and attack graph terminology.
@@
 
+%\todo{it is early to put this image here, also long caption, image quality should be enhanced}
 \begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
+	\includegraphics[width=\textwidth]{./images/AttackGraphSystem}
 	\caption{Our Attack Graph System.
@@
 A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.\cite{docker}
+In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis \cite{merkel2014docker}.
 
@@
 VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.\cite{aksu}
+Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
 
@@
 Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated.\cite{aksu}
+We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated \cite{aksu2018automated}.
 
@@
 \begin{figure}
-	\includegraphics[]{Topology_graph}
+	\includegraphics[]{./images/Topology_graph}
 	\caption{Example topology graph.
@@
 \begin{figure}
-	\includegraphics[]{Attack_graph}
+	\includegraphics[]{./images/Attack_graph}
 	\caption{Example resulting attack graph.
@@
 \subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair\cite{clair} and Clairctl\cite{clairctl} for vulnerabilities generation.
+Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
 
@@
 Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
+The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
 Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
@@
 	\end{itemize}
-
-\section{EVALUATION}
-
-In real-world microservice architectures, many containers are interconnected to each other.
-This raises the need for a scalable attack graph system.
-In this section, we first have a look at how others evaluate their systems.
-We then conduct few experiments in order to test the scalability of our system with different number of containers, and connections in both artificial and real networks.
-All of the experiments were performed on a Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
-
-Extensive scalability study of attack graph generators  is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
-Characteristics that usually vary in this sort of evaluation are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time of a given algorithm.
-Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
-In our case we compare our system to existing work by treating every container as a computer, and any physical connection between two computers as a connection between two containers.
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{15mm}|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Attack Graph generation time & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & 0.5120 sec.
-& https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & 0.2761 sec. & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions.
-& Java EE application, React, Tomcat EE & 2 & 149 & 0.2613 sec.
-& https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & 0.2570 sec.
-& https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}
-
-Seyner in his work tests the system in both a small and extended examples.\cite{sheyner} The attack graph in the larger example has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-Sheyner claims that the performance bottleneck is inside the graph generation procedure.
-
-Ingols tested his system on a network of 250 hosts.
-He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes.\cite{ingols} Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
-In addition to this, missing explanation of how the hosts are connected, does not make it directly comparable to our method.
-
-Ou provides some more extended study where he tests his system on more examples.\cite{ou}  He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds.
-He also provides an evaluation where he MulVAL clearly outperforms the Sheyner's system.
-
-In our scalability experiments we use Samba\cite{samba} and Phpmailer\cite{phpmailer} containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On Table \ref{table_scalability} we can see the results of our experiments.
-In each of these experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a fully connected fashion, a node of each additional container is connected to every existing container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
-
-Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step.
-However this step increases in linear fashion because the container files are analyzed only once by Clair.
-The attack graph generation for the smaller examples is considerably less than the preprocessing time.
-Starting from example\_500, we can notice sharp increase in BDF execution time to 165 seconds.
-For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
-
-We also performed tests on some real examples as described on table \ref{table_technologies} and extend our system to different types of technologies, number of containers and vulnerabilities.
-The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These examples are different from the synthetic ones presented above, since they contain less and different containers.
-They are connected in a more linear fashion in contrast to the full connection provided in the previous example.
-For example, in order for an attacker to reach a database, he needs to gain suitable privilege levels of multiple intermediate containers in several steps.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{docker} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{clair}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{clairctl}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{nvd}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{ingols}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{aksu}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{sheyner}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{netspa}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-
-\bibitem{amman}  Ritchey, Ronald W., and Paul Ammann. "Using model checking to analyze network vulnerabilities." Security and Privacy, 2000. S\&P 2000. Proceedings. 2000 IEEE Symposium on. IEEE, 2000.
-
-\bibitem{ou}  Ou, Xinming, Wayne F.
-Boyer, and Miles A.
-McQueen.
-"A scalable approach to attack graph generation." Proceedings of the 13th ACM conference on Computer and communications security.
-ACM, 2006.
-
-\bibitem{samba} https://github.com/opsxcq/exploit-CVE-2017-7494
-
-\bibitem{phpmailer} https://github.com/opsxcq/exploit-CVE-2016-10033
-
-\bibitem{netflixoss} https://github.com/Oreste-Luci/netflix-oss-example
-\end{thebibliography}
-
-\end{document}

### 2018-08-31 paper_own_docker/chapters/related_work.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-04 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
+\section{RELATED WORK}
+Previous work has dealt with attack graph generation, mainly in computer networks 
+%\todo{please cite them}
+, where multiple machines are connected to each other and the Internet.
+In these networks an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
+Attack graphs help in analyzing this behavior.
+Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process
+%\todo{elaborate a bit why; scalability, expertise, completeness.. }
+. Tools that generate vulnerabilities of specific host are available. However previous works have state that these tools alone are not enough to analyze the vulnerability 
+%\todo{mention why coz they can be connected ..} 
+of an entire network and that these tools in addition to network topology could solve this issue.
+Therefore, some teams have been  working on developing systems that generate attack graphs automatically by using different approaches.
 
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[options]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
+One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols2006practical} %\todo{space citation then the dot, e.g., property [5].}
 
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
+Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
+A collection of these counter examples form an attack graph.
+They state that model checkers satisfy a monotonicity property in order to ensure termination.
+However model checkers have a computational disadvantage.
+In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed.
+Amman et al.
+extends this work with some simplifications and more efficient storage \cite{ritchey2000using}.
 
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
+Ou et al.
+use logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al.
+use breath first search algorithm in order to tackle the scalability issue.
+Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes
+%\todo{please rephrase this sentence to clarify it what is redundanccy full, define MP}
+.
+They use breath first search technique for generating the attack graph.
+This approach provides faster results in comparison to using model checkers.
+An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
 
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
+Aksu et al.
+builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks \cite{aksu2018automated}.
+They define a specific test of pre- and postcondition rules and test their correctness.
+In their evaluation, they use machine learning approach.
 
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
-
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
-
-\section{RELATED WORK}
-
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
-There the attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of the goal container.
-Some works use model checkers with goal property(Sheyner reference).
-They However model checkers as a disadvantage have a state explosion.(Ingols reference)
-
-Others use breath first search algorithm. (Ingols reference)  They model the
-
-Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
-
-Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
-To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- They dont use Clair as well. They do not offer any performance comparison between different topologies.
-
-\section{PROPOSED METHOD}
-
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
-
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different version of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-	priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-	    \For{neigh in neighbours}{
-	    	\If{curr\_cont == docker\_host}
-	    	{
-	    		end = neigh + "ADMIN" \\
-	    		create\_edge(curr\_node, end) \\
-	    		}
-	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
-	        { 	
-	        	end = neigh + "ADMIN" \\
-	        	create\_edge(curr\_node, end) \\
-	        	queue.put(end) \\
-	        	passed\_nodes.add(end)    	
-	        	}
-            \If{neigh != outside and neigh != docker\_host}{
-            	precond = cont\_expl[neigh][precond] \\
-            	postcond = cont\_expl[neigh][postcond] \\
-            	\For{vul in vuls}{
-            		\If{$curr_priv > precond[vul]$}{	
-            	end = neigh + post\_cond[vul]\\
-            	create\_edge(curr\_node, end\_node)\\
-            	\If{end\_node not in passed\_nodes}{
-            		queue.put(end\_node)\\
-            		passed\_nodes.add(end\_node)
-            		}}
-            	}
-                }
-	    	}
-	    nodes = update\_nodes()\\
-	    edges = update\_edges() \\
-	}
-
-\caption{Breadth-first search algorithm for generating an attack graph.}
-\label{BFSalgorithm}
-\end{algorithm}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-			\hline
-			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-	\label{table_scalability}
-\end{table*}
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
-If the neighbor was not passed, then we add it to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-\begin{itemize}
- \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
- \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
- \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-\end{itemize}
-
-\section{EVALUATION}
-
-An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
-(some references and description with statistics).
-In this section, we first have a look at how others evaluate their proposed systems.
-We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
-
-Evaluation of a given system is a usually required part, when evaluating a given program.
-Extensive scalability study is not available.
-Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time.
-Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
-In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
-
-\begin{table*}[t]
-	\begin{center}
-		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}[t]
-
-For each example describe their setup and their results.
-
-Seyner, the attack graph has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
-
-Ingols tested on a network of 250 hosts.
-He also tested on a simulated network of 50000 hosts in under 4 minutes.
-(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
-
-Amman does not provide with scalability methods.
-
-Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
-
-In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On Table \ref{table_scalability} we can see the results of our experiments.
-In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
-
-Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
-However these steps are with the number of containers because the container files are analyzed only once.
-The attack graph generation less time than the preprocessing step.
-Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
-For the previous example with example\_100, needed 6.5 seconds.
-
-We also performed tests on some real examples as described on table.
-These examples are different from the synthetic ones presented above, since they contain less containers.
-Also they are in a more linear fashion.
-For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
-
- We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
-Short summary of them is given on the table \ref{table_technologies}.
-We want to show that we can generalize our approach for different types of technologies.
-
-Characteristics of the Attack Graph Generator.
- - stopping criteria (When all edges are traversed)
- - BFS is guaranteed to traverse all of the edges 
- - monothonicity no edge is visited more than once.
- - all of the vulnerabilities per edge are checked
- - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-\end{thebibliography}
-
-\end{document}
+Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers.
+Therefore we extend the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjuction to Clair OS to generate attack graphs for microservice architectures.
+Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
+Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
+%\todo{in general good story line, some language work is needed later-on}

### 2018-08-31 paper_own_docker/main.tex
Paper migrated to new ACM style. Chapters are additionaly subdivided.

--- 2018-08-04 paper_own_docker/main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
+\documentclass[sigconf]{acmart}
 
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-\usepackage[options]{algorithm2e}                                     % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
+\usepackage{booktabs} % For formal tables
+\usepackage[]{algorithm2e}
 
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
 
-\title{\LARGE \bf
-Attack Graph Generation for Micro-service
-Architecture
-}
+% DOI
+\acmDOI{xx.xxx/xxx_x}
 
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
+% ISBN
+\acmISBN{978-1-4503-5933-7/19/04}
 
-\author{Stevica Bozhinoski$^{1}$, Amjad Ibrahim$^{2}$ and Prof. Dr. Alexander Pretschner$^{3}$% <-this % stops a space
-}
+%Conference
+\acmConference[SAC'19]{ACM SAC Conference}{April 8-12, 2019}{Limassol, Cyprus} 
+\acmYear{2019}
+\copyrightyear{2019}
+
+\acmArticle{4}
+\acmPrice{15.00}
+
+% These commands are optional
+%\acmBooktitle{Transactions of the ACM Woodstock conference}
+%\editor{Jennifer B. Sartor}
+%\editor{Theo D'Hondt}
+%\editor{Wolfgang De Meuter}
 
 \begin{document}
+\title{Attack Graph Generation for Micro-service
+	Architecture}
+\titlenote{Produces the permission block, and
+  copyright information}
+\subtitle{Extended Abstract}
+\subtitlenote{The full version of the author's guide is available as
+  \texttt{acmart.pdf} document}
 
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
+\author{Amjad Ibrahim}
+\affiliation{\institution{Technical University of Munich}}
+\email{amjad.ibrahim@tum.de}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Stevica Bozhinoski}
+\affiliation{\institution{Technical University of Munich}}
+\email{stevica.bozhinoski@tum.de}
+
+\author{Prof. Dr. Alexander Pretschner}
+\affiliation{\institution{Technical University of Munich}}
+\email{alexander.pretschner@tum.de}
+
+% The default list of authors is too long for headers}
+\renewcommand{\shortauthors}{B. Trovato et al.}
+
 \begin{abstract}
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
+
+\input{./chapters/abstract}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>10010520.10010553.10010562</concept_id>
+  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010575.10010755</concept_id>
+  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010553.10010554</concept_id>
+  <concept_desc>Computer systems organization~Robotics</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10003033.10003083.10003095</concept_id>
+  <concept_desc>Networks~Network reliability</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>  
+\end{CCSXML}
 
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
 
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
+\keywords{Attack Graph Generaton, Computer Security, Microservices}
 
-\section{RELATED WORK}
+\maketitle
+\input{./chapters/introduction}
+\input{./chapters/background}
+\input{./chapters/method}
+\input{./chapters/evaluation}
+\input{./chapters/related_work}
+\input{./chapters/conclusion}
+\input{./chapters/future_work}
 
-Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet.
-There the attacker performs multiple steps to achieve his goal, i.e.
-gaining privileges of the goal container.
-Some works use model checkers with goal property(Sheyner reference).
-They However model checkers as a disadvantage have a state explosion.(Ingols reference)
-
-Others use breath first search algorithm. (Ingols reference)  They model the
-
-Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.
-
-Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).
-To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- They dont use Clair as well. They do not offer any performance comparison between different topologies.
-
-\section{PROPOSED METHOD}
-
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and give access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.
-
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different version of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-	priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-	    \For{neigh in neighbours}{
-	    	\If{curr\_cont == docker\_host}
-	    	{
-	    		end = neigh + "ADMIN" \\
-	    		create\_edge(curr\_node, end) \\
-	    		}
-	        \If{neigh == docker\_host and priv\_acc[curr\_cont]}
-	        { 	
-	        	end = neigh + "ADMIN" \\
-	        	create\_edge(curr\_node, end) \\
-	        	queue.put(end) \\
-	        	passed\_nodes.add(end)    	
-	        	}
-            \If{neigh != outside and neigh != docker\_host}{
-            	precond = cont\_expl[neigh][precond] \\
-            	postcond = cont\_expl[neigh][postcond] \\
-            	\For{vul in vuls}{
-            		\If{$curr_priv > precond[vul]$}{	
-            	end = neigh + post\_cond[vul]\\
-            	create\_edge(curr\_node, end\_node)\\
-            	\If{end\_node not in passed\_nodes}{
-            		queue.put(end\_node)\\
-            		passed\_nodes.add(end\_node)
-            		}}
-            	}
-                }
-	    	}
-	    nodes = update\_nodes()\\
-	    edges = update\_edges() \\
-	}
-
-\caption{Breadth-first search algorithm for generating an attack graph.}
-\label{BFSalgorithm}
-\end{algorithm}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-			\hline
-			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-			No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-			No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-			No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-			No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-			No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-			Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-			Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-			Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-			Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-	\label{table_scalability}
-\end{table*}
-
-\subsubsection{Vulnerability Parser}
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-\subsubsection{Attack Graph Parser}
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule.
-If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-\subsubsection{Breadth-First Search}
-
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied.
-If the neighbor was not passed, then we add it to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-\begin{itemize}
- \item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
- \item Termination: This follows from its monotonicity property. Each edge is traversed only once.
- \item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-\end{itemize}
-
-\section{EVALUATION}
-
-An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other.
-(some references and description with statistics).
-In this section, we first have a look at how others evaluate their proposed systems.
-We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.
-
-Evaluation of a given system is a usually required part, when evaluating a given program.
-Extensive scalability study is not available.
-Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
-All of these components contribute to the execution time.
-Even though the notion of attack graph vary, we hope to reach a comprehensive comparison.
-In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.
-
-\begin{table*}[t]
-	\begin{center}
-		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}[t]
-
-For each example describe their setup and their results.
-
-Seyner, the attack graph has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.
-
-Ingols tested on a network of 250 hosts.
-He also tested on a simulated network of 50000 hosts in under 4 minutes.
-(reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.
-
-Amman does not provide with scalability methods.
-
-Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.
-
-In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-
-On Table \ref{table_scalability} we can see the results of our experiments.
-In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a clique fashion, a node of each additional container is connected to every existing container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
-
-Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step.
-However these steps are with the number of containers because the container files are analyzed only once.
-The attack graph generation less time than the preprocessing step.
-Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds.
-For the previous example with example\_100, needed 6.5 seconds.
-
-We also performed tests on some real examples as described on table.
-These examples are different from the synthetic ones presented above, since they contain less containers.
-Also they are in a more linear fashion.
-For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.
-
- We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These systems are composed of different kind of technologies, different number of containers and vulnerabilities.
-Short summary of them is given on the table \ref{table_technologies}.
-We want to show that we can generalize our approach for different types of technologies.
-
-Characteristics of the Attack Graph Generator.
- - stopping criteria (When all edges are traversed)
- - BFS is guaranteed to traverse all of the edges 
- - monothonicity no edge is visited more than once.
- - all of the vulnerabilities per edge are checked
- - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.
-
-\section{CONCLUSION}
-
-\section{FUTURE WORK}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{ACKNOWLEDGMENT}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{thebibliography}{99}
-
-\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.
-
-\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair
-
-\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl
-
-\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
-National vulnerability database version 2.2 (2010),
-http://nvd.nist.gov/
-
-\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski.
-"Practical attack graph generation for network defense." Computer Security Applications Conference, 2006.
-ACSAC'06.
-22nd Annual.
-IEEE, 2006.
-
-\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.
-
-\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.
-
-\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
-\end{thebibliography}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{sample-bibliography}
 

### 2018-09-01 paper_own_docker/chapters/background.tex
Background section is divided into two separate files.
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

@@
 
-\subsection{Attack Graphs}
-\subsection{Microservice Architectures}
+In this section we start by formally defining attack graphs and their characteristics (Subsection \ref{chap:attack_graphs}).
+Afterwards we look into microservices, their advantages in comparison to monolithic systems and conclude with their security implications (Subsection \ref{chap:microservices}).
+
+\input{./chapters/background_attack_graphs}
+\input{./chapters/background_microservices}

### 2018-09-01 paper_own_docker/chapters/background_attack_graphs.tex
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

--- 2018-08-31 paper_own_docker/chapters/method.tex
@@
-\section{METHOD}
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
-
-%\todo{it is early to put this image here, also long caption, image quality should be enhanced}
-\begin{figure*}
-	\includegraphics[width=\textwidth]{./images/AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure*}
-
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis \cite{merkel2014docker}.
-
+\subsection{Attack Graphs}
+\label{chap:attack_graphs}
 In this work we model an attack graph as a sequence of atomic attacks.
@@
 
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
-
 Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured.
@@
 Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
-We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated \cite{aksu2018automated}.
 
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
-
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.\cite{netflixoss} Displayed on figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
-
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
-
-\begin{figure}
-	\includegraphics[]{./images/Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[]{./images/Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
-
-\subsubsection{Technical Details}
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
-
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
-
-\subsubsection{Topology Parser}
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
-However different versions of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
-
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
-
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
-
-\begin{algorithm}
-	\SetAlgoLined
-	\KwData{topology, cont\_expl,
-		priv\_acc}
-	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
-
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
-		curr\_cont = get\_cont(curr\_node) \\
-		curr\_priv = get\_priv(curr\_node) \\
-		neighbours = topology[curr\_cont] \\
-		\For{neigh in neighbours}{
-			\If{curr\_cont == docker\_host}
-			{
-				end = neigh + "ADMIN" \\
-				create\_edge(curr\_node, end) \\
-			}
-			\If{neigh == docker\_host and priv\_acc[curr\_cont]}
-			{ 	
-				end = neigh + "ADMIN" \\
-				create\_edge(curr\_node, end) \\
-				queue.put(end) \\
-				passed\_nodes.add(end)    	
-			}
-			\If{neigh != outside and neigh != docker\_host}{
-				precond = cont\_expl[neigh][precond] \\
-				postcond = cont\_expl[neigh][postcond] \\
-				\For{vul in vuls}{
-					\If{$curr_priv > precond[vul]$}{	
-						end = neigh + post\_cond[vul]\\
-						create\_edge(curr\_node, end\_node)\\
-						\If{end\_node not in passed\_nodes}{
-							queue.put(end\_node)\\
-							passed\_nodes.add(end\_node)
-						}}
-					}
-				}
-			}
-			nodes = update\_nodes()\\
-			edges = update\_edges() \\
-		}
-
-		\caption{Breadth-first search algorithm for generating an attack graph.}
-		\label{BFSalgorithm}
-	\end{algorithm}
-
-	\begin{table*}
-		\begin{center}
-			\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-				\hline
-				Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
-
-				No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-				No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-				No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-				No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-				No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-				No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-				Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-				Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-				Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-				Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-				\hline
-			\end{tabular}
-		\end{center}
-
-		\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulnerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-		\label{table_scalability}
-	\end{table*}
-
-	\subsubsection{Vulnerability Parser}
-	In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a vulnerability scanner that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
-
-	\subsubsection{Attack Graph Parser}
-	After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
-	Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.
-This results in a list of container vulnerabilities with their preconditions and postconditions.
-
-	\subsubsection{Breadth-First Search}
-
-	After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-	Breadth-First Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
-	The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph. 
-	The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-	Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
-If the neighbor was not passed, then it is added to the queue.
-The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
-
-	\begin{itemize}
-		\item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
-		\item Termination: This follows from its monotonicity property. Each edge is traversed only once.
-		\item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
-	\end{itemize}
+- mention monotonicity

### 2018-09-01 paper_own_docker/chapters/background_microservices.tex
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

\subsection{Microservices}
\label{chap:microservices}
mention Service Oriented Architecture \cite{ahmadvand2016requirements} \cite{papazoglou2003service} (cite Amjads paper and original paper), difference to monolithic systems. Wide attack surface.
- Formalize microservices. 
- Provide definition from literature
- When people started using them and why

- Vulnerability scanner definitions

### 2018-09-01 paper_own_docker/chapters/evaluation.tex
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

@@
 \section{EVALUATION}
+
+\begin{table*}
+	\begin{center}
+		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{60mm}| } 
+			\hline
+			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
+
+			Netflix OSS & Combination of containers provided from Netflix.
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
+
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 &  https://github.com/dockersamples/atsea-sample-shop-app \\\hline
+
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 &  https://github.com/dockersamples/javaee-demo \\\hline
+
+			PHPMailer and Samba & An artificial example created from two separate containers.
+We use an augmented version for the scalability tests.
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  https://github.com/opsxcq/exploit-CVE-2016-10033
+			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
+
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{Microservice architecture examples analyzed by the attack graph generator.}
+	\label{table_technologies}
+
+\end{table*}
 
@@
 In our case we compare our system to existing work by treating every container as a computer, and any physical connection between two computers as a connection between two containers.
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{15mm}|p{45mm}| } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Attack Graph generation time & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & 0.5120 sec.
-& https://github.com/Oreste-Luci/netflix-oss-example \\\hline
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & 0.2761 sec. & https://github.com/dockersamples/atsea-sample-shop-app \\\hline
-
-			JavaEE demo & An application for browsing movies along with other related functions.
-& Java EE application, React, Tomcat EE & 2 & 149 & 0.2613 sec.
-& https://github.com/dockersamples/javaee-demo \\\hline
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & 0.2570 sec.
-& https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{List of randomly selected examples that were analyzed with our attack graph generation system.}
-	\label{table_technologies}
-
-\end{table*}
 
@@
 The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
+
+\begin{table*}
+	\begin{center}
+		\begin{tabular}{ |c|c|c|c|c|c| } 
+			\hline
+			Statistics & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+
+			No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 \\
+
+			No. of Samba containers & 20 & 50 & 100 & 500 & 1000 \\
+
+			No. of nodes in topology & 23 & 53 & 103 & 503 & 1003\\
+
+			No. of edges in topology & 253 & 1378 & 5253 & 126253 & 502503 \\
+
+			No. nodes in attack graph & 43 & 103 & 203 & 1003 & 2003 \\
+
+			No. edges in attack graph & 863 & 5153 & 20303 & 501503 & 2003003 \\
+
+			Topology parsing time & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
+
+			Vulnerabilities preprocessing time & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
+
+			Breadth-First Search time & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
+
+			Total time & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{Table with number of topology and attack graph elements and executing times of the main attack graph generator components. The times are given in seconds.}
+
+	\label{table_scalability}
+\end{table*}
+The examples are composed of two containers: Phpmailer and Samba.
+The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
+The topology time is the time required to generate the graph topology.
+The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
+The Breath-First Search is the main component that generates the attack graph.
+All of the components are executed five times for each of the examples and their final time is averaged.
+The times are given in seconds.
+The total time contains the topology parsing, the attack graph generation and some minor processes.
+However, the total time does not include the vulnerability analysis by Clair.
+Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.
 

### 2018-09-01 paper_own_docker/chapters/introduction.tex
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

@@
 \section{INTRODUCTION}
-%\todo{We need to use the format of the conference, i added a folder ACM that contains it, please use it. And split the sections into different latex files using, so that we don't run into merges }
 
@@
 
-We first have a look into the work of other( Section 2), then present the architecure of our system(Section 3), test the scalability(Section 4) and at the end provide a conclusion(Section 5) and future work(Section 6).
+We first have a look into the work of other (Section 2), then present the architecure of our system (Section 3), test the scalability (Section 4) and at the end provide a conclusion (Section 5) and future work (Section 6).

### 2018-09-01 paper_own_docker/chapters/method.tex
Subsections referenced in each section, Tables modified(long caption reduced, few fields removed), some references added.

@@
 \section{METHOD}
-In this section we first have a look at Docker and attack graph terminology.
-We then present an overview of our proposed system with its components, provide a small example and at the end describe each of the components in more detail.
+In this section we first have a look at how existing work of attack graph generation maps for computer networks maps into the microservices environment (Subsection \ref{chap:mapping}) and provide a small example.
+We then mentioned the third party tools used in this work and present an overview of our proposed system with its components (Topology Parser (Subsection \ref{chap:topology_p}), Vulnerabilities Parser (Subsection \ref{chap:vulnerability_p}) and Attack Graph Parser (Subsection \ref{chap:attack_graph_p}) with the Breath-First Search graph traversal algorithm (Subsection \ref{chap:bfs})).
 
@@
 
+\subsection{Mapping attack graphs from network to microservice perspective}
+\label{chap:mapping}
 In Docker, distinction is being made between the terms image, container and service.
@@
 
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to reach the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and gives access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its content.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
+Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
 
@@
 
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
 We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated \cite{aksu2018automated}.
@@
 
-\subsubsection{Technical Details}
+\subsection{Technical Details}
+\label{chap:technical}
+
 Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
@@
 
-\subsubsection{Topology Parser}
+\subsection{Topology Parser}
+\label{chap:topology_p}
+
 The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
@@
 
-	\begin{table*}
-		\begin{center}
-			\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
-				\hline
-				Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+\subsection{Vulnerability Parser}
+\label{chap:vulnerability_p}
 
-				No. of Phpmailer containers & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
-
-				No. of Samba containers & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
-
-				No. of nodes in topology & 4 & 8 & 23 & 53 & 103 & 503 & 1003\\
-
-				No. of edges in topology & 6 & 28 & 253 & 1378 & 5253 & 126253 & 502503 \\
-
-				No. nodes in attack graph & 5 & 13 & 43 & 103 & 203 & 1003 & 2003 \\
-
-				No. edges in attack graph & 8 & 68 & 863 & 5153 & 20303 & 501503 & 2003003 \\
-
-				Topology parsing time & 0.0082 & 0.0094 & 0.02879 & 0.0563 & 0.1241 & 0.7184 & 2.3664 \\
-
-				Vulnerabilities preprocessing time & 0.2551 & 0.2840 & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
-
-				Breadth-First Search time & 0.0019 & 0.0209 & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
-
-				Total time & 0.2654 & 0.3144 & 0.8429 & 2.6216 & 8.3417 & 173.0781 & 784.9843 \\ 
-				\hline
-			\end{tabular}
-		\end{center}
-
-		\caption{Table with graph characteristics(no.
-of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulnerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process).
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}
-
-		\label{table_scalability}
-	\end{table*}
-
-	\subsubsection{Vulnerability Parser}
 In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
@@
 
-	\subsubsection{Attack Graph Parser}
+\subsection{Attack Graph Parser}
+
 After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
@@
 When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
+If more than one rule matches, we take the one with the highest privilege level for the preconditions an\label{chap:attack_graph_p}d the lowest privilege level for the postconditions.
 If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.
@@
 \subsubsection{Breadth-First Search}
+\label{chap:bfs}
 

### 2018-09-02 paper_own_docker/chapters/background_attack_graphs.tex
Corrections in Method and Evaluation text

@@
 \label{chap:attack_graphs}
+
+Atomic attacks are fundamental building blocks in our attack graph.
+A single atomic attack represents a successful vulnerability exploitation.
+A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
+For an atomic attack to be executed, two constraints are imposed.
+First, the containers have to be connected between each other, so that physical access can be ensured.
+Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
+Describe different attack graphs?
+
 In this work we model an attack graph as a sequence of atomic attacks.

### 2018-09-02 paper_own_docker/chapters/background_microservices.tex
Corrections in Method and Evaluation text

@@
 \label{chap:microservices}
-mention Service Oriented Architecture \cite{ahmadvand2016requirements} \cite{papazoglou2003service} (cite Amjads paper and original paper), difference to monolithic systems. Wide attack surface.
+
+As a typical real world software grows bigger, there is an every growing need to decompose it an organizied structure to promote scaling, reusability and readability.
+A software application whose modules cannot be executed independently is called a monolith.
+It is caracterized by tight coupling, vertical scaling and strong dependence.
+Service Oriented Architecture addresses these issues.
+Service Oriented Architecture is a paradigm in which components provide services that are used by other components through a networking protocol.
+\cite{papazoglou2003service} However in a typical SOA, the services are monolithic and a new concept is required.
+\cite{ahmadvand2016requirements}
+In microservices paradigm, multiple services are split into very basic units and they are task oriented.
+According to , a microservice is a cohesive, independent process interacting via messages.
+There microservicies constitute a distributed architecture called a microservice architecture.
+Microservice architectures provide us with the benefits of having more heterogenious technologies, cheaper scalling, resilience, organizational alignment, and composability among other things \cite{newman2015building}.
+However they add additional complexity and have a wider attack surface, since a lot of services need to communicate with each other.
+They promote service reuse through third party software.
+Data needs to be transferred and stored securely .
+
 - Formalize microservices. 

### 2018-09-02 paper_own_docker/chapters/evaluation.tex
Corrections in Method and Evaluation text

@@
 
-In real-world microservice architectures, many containers are interconnected to each other.
-This raises the need for a scalable attack graph system.
-In this section, we first have a look at how others evaluate their systems.
-We then conduct few experiments in order to test the scalability of our system with different number of containers, and connections in both artificial and real networks.
+Real-world microservice architectures are composed of many containers that run different technologies with various degrees of connectivity between each other.
+This raises the need for a robust and scalable attack graph system.
+In Subsection \ref{chap:heterogenious_systems}, we first show different microservice architectures on which our system was tested on.
+We then have a look at how others evaluate their systems.
+Finally in Subsection \ref{chap:scalability_eval} we conduct few experiments in order to test the scalability of our system with different number of containers and connectivity.
 All of the experiments were performed on a Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
 
+\subsection{Heterogenious microservice systems evaluation}
+\label{chap:heterogenious_systems}
+Modern microservice architectures use an abundance of different technologies, number of containers, various connectivity and number of vulnerabilities.
+Therefore it is of immense importance to show that the attack graph generator works in such heterogenious scenarios.
+In order to do this we ran our system on some real and slightly modified Github examples as described on Table \ref{table_technologies} composed of different types of technologies, number of containers and vulnerabilities.
+The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
+NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses Spring Cloud, Netflix Ribbon, Netflix Eureka etc.
+Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and that uses Spring Boot, React, NGINX and PostgreSQL.
+JavaEE demo is a sample application for browsing movies that is composed of only 2 containers and uses JavaEE, React and Tomcat EE.
+We ran the attack graph generator and checked for correctness of the resulting attack graph based on domain knowledge.
+After running the attack graph generator, the structure of the resulting attack graphs (especially in the Netflix case) was quite linear.
+This linearity is because each container is connected to few other containers to reduce unnecessary communication and increase encapsulation.
+So based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
+Additionally we noted that the running time of our system for each of these examples was short, and additional tests to test the scalability were needed.
+Phpmailer and Samba is an artificial example that we use and extend in the following subsection to perform these scalability tests.
+
+\subsection{Scalability evaluation}
+\label{chap:scalability_eval}
 Extensive scalability study of attack graph generators  is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
-Characteristics that usually vary in this sort of evaluation are the number of nodes, their interconnectedness and the amount of vulnerabilities per container.
+Parameters that usually vary in this sort of evaluation are the number of nodes, their connectivity and the amount of vulnerabilities per container.
 All of these components contribute to the execution time of a given algorithm.
 Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
-In our case we compare our system to existing work by treating every container as a computer, and any physical connection between two computers as a connection between two containers.
+In this case we compare our system to existing work by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
+In the following text, we first look at three works and their scalability evaluation results.
+After this comparison, we present the scalability results of our system.
 
@@
 He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds.
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
 He also provides an evaluation where he MulVAL clearly outperforms the Sheyner's system.
-
-In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
-We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
 
@@
 
-			Vulnerabilities preprocessing time & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
+			Vulnerability preprocessing time & 0.5377 & 0.9128 & 1.6648 & 6.9961 & 15.0639 \\
 
@@
 
-	\caption{Table with number of topology and attack graph elements and executing times of the main attack graph generator components. The times are given in seconds.}
+	\caption{Scalability experiments with the graph characteristics and execution times. The times are given in seconds.}
 
@@
 \end{table*}
-The examples are composed of two containers: Phpmailer and Samba.
-The Phpmailer container has 181, while the Samba container has 367 vulnerabilities.
-The topology time is the time required to generate the graph topology.
-The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search is the main component that generates the attack graph.
+
+In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
+We extended this example and artificially made fully connected topologies of 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
+The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
+In our tests, we report the total execution time as well as its components times: Topology parsing time, Vulnerability preprocessing time and Breath-First Search time.
+The total time contains the topology parsing, the attack graph generation and some minor utility processes.
+The Topology parsing time is the time required to generate the graph topology.
+The Vulnerability preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
+The Breath-First Search time is the time needed for Breadth-First Search to traverse the topology and  generate the attack graph after the previous steps are done.
 All of the components are executed five times for each of the examples and their final time is averaged.
 The times are given in seconds.
-The total time contains the topology parsing, the attack graph generation and some minor processes.
 However, the total time does not include the vulnerability analysis by Clair.
@@
 
-On Table \ref{table_scalability} we can see the results of our experiments.
+Table \ref{table_scalability} shows the results of our experiments.
 In each of these experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a fully connected fashion, a node of each additional container is connected to every existing container.
+This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
 In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are present).
+the docker daemon where the containers are hosted).
 Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
@@
 For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
-
-We also performed tests on some real examples as described on table \ref{table_technologies} and extend our system to different types of technologies, number of containers and vulnerabilities.
-The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-These examples are different from the synthetic ones presented above, since they contain less and different containers.
-They are connected in a more linear fashion in contrast to the full connection provided in the previous example.
-For example, in order for an attacker to reach a database, he needs to gain suitable privilege levels of multiple intermediate containers in several steps.

### 2018-09-02 paper_own_docker/chapters/method.tex
Corrections in Method and Evaluation text

@@
 \section{METHOD}
-In this section we first have a look at how existing work of attack graph generation maps for computer networks maps into the microservices environment (Subsection \ref{chap:mapping}) and provide a small example.
-We then mentioned the third party tools used in this work and present an overview of our proposed system with its components (Topology Parser (Subsection \ref{chap:topology_p}), Vulnerabilities Parser (Subsection \ref{chap:vulnerability_p}) and Attack Graph Parser (Subsection \ref{chap:attack_graph_p}) with the Breath-First Search graph traversal algorithm (Subsection \ref{chap:bfs})).
+Up to this point we formally defined what attack graph is.
+In this section we first look at how the existing components of attack graph generation for computer networks map into a microservice environment  and provide a small example (Subsection \ref{chap:mapping}).
+We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-First Search graph traversal algorithm in Subsection \ref{chap:bfs}.
 
 %\todo{it is early to put this image here, also long caption, image quality should be enhanced}
-\begin{figure*}
-	\includegraphics[width=\textwidth]{./images/AttackGraphSystem}
+\begin{figure}
+	\includegraphics[scale=0.9]{./images/AttackGraphSystem}
 	\caption{Our Attack Graph System.
@@
 	\label{AttackGraphSystem}
-\end{figure*}
+\end{figure}
 
@@
 \label{chap:mapping}
+
+In our work, we try to translate already existing attack graph generation work from computer networks into the microservices ecosystem.
+In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
+In this subsection we start first by shortly introducing a famous microservice framework(Docker) and some of its terminology.
+We then modify the attack graph concepts mentioned above for our use-case(nodes, edges, privilege levels, pre- and postconditions).
+At the end we see how this translation works in practice by demonstrating a small example.
+
+Docker is one of the most popular and used microservice frameworks currently available.
 In Docker, distinction is being made between the terms image, container and service.
 Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis \cite{merkel2014docker}.
+A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs  \cite{merkel2014docker}.
+In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
 
-Both the Pre- and Postconditions are transformed from pre- and postcondition rules.
+As mentioned above, nodes and edges are the basic building blocks of an attack graph.
+Nodes in our attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
+In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
+Once an attacker exploits this vulnerability, he gains the privilege of the target container as a postcondition and an edge is added to the attack graph.
+Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
+The pre- and postcondition rules use the fields defined by NVD, as well as ocrcurence of specific keywords from the CVEs descriptions.
 
-Atomic attacks are fundamental building blocks in our attack graph.
-A single atomic attack represents a successful vulnerability exploitation.
-A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph.
-For an atomic attack to be executed, two constraints are imposed.
-First, the containers have to be connected between each other, so that physical access can be ensured.
-Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level.
+Privileges play a central role in this attack graph generation.
 We model the privileges into a hierarchy.
 The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised.
+VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
+On the other side OS means that the host machine has been compromised.
 Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
-
-We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated \cite{aksu2018automated}.
-
-Nodes in our attack graph model are represented as a combination of a docker image and its respective privilege level, while edges are a connection between node pairs with the vulnerability that is being exploited as a descriptor.
-Once an attacker exploits a given vulnerability, he gains the privilege of the new container and an edge is added to the attack graph.
+None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.
 
 In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.\cite{netflixoss} Displayed on figure \ref{TopologyGraph} is the topology of the example.
+The example is taken from the Netflix OSS Github repository \cite{netflixoss}.
+Displayed on Figure \ref{TopologyGraph} is the topology of the example.
 The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On figure \ref{AttackGraph}, we can see a part of the resulting attack graph.
-An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege.
-Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege.
+On Figure \ref{AttackGraph} we can see a part of the resulting attack graph.
+Parts of the both graphs has been intentionally omitted to reduce complexity.
+An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability and gain USER privilege.
+Then with this USER privilege it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege.
+Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 and gain ADMIN privilege.
 It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.
+Another path would be to exploit the CVE-20108-1124 vulnerability while have only USER privilege on Zuul to gain directly ADMIN privileges and then attack the Eureka container.
+Our attack graph generator shows both paths, since it is of an interest to see every possible route in which a container can be compromised.
 
@@
 However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done using publishing ports.
+This is usually done by using publishing ports.
 This is the case in both computer networks, as well as in microservice architectures.
@@
 The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image.
+Unfortunately Clair does not provide with an ready to use interface to analyze a docker image.
 As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
@@
 After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-
 Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
@@
 Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
-
 The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph.
-The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
+The algorithm first initializes the nodes, edges, queue and the passed nodes.
+Afterwards it generates the nodes which are a combination of the image name and the privilege level.
 Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.

### 2018-09-03 paper_own_docker/chapters/background.tex
Background text updated and new references added.

--- 2018-08-31 paper_own_docker/chapters/background.tex
@@
 
-\subsection{Attack Graphs}
-\subsection{Microservice Architectures}
+In this section we start by introducing the concept of microservices, their benefits and security implications (Subsection \ref{chap:microservices}).
+Afterwards we look into vulnerability scanners as tools to generate vulnerabilities of a single host (Subsection \ref{chap:vulnerability_scanners}).
+At the end we introduce and formally describe attack graphs as methods to disagnose security weakness of a given system composed of multiple hosts (Subsection \ref{chap:attack_graphs}).
+
+\input{./chapters/background_microservices}
+\input{./chapters/vulnerability_scanners}
+\input{./chapters/background_attack_graphs}

### 2018-09-03 paper_own_docker/chapters/background_microservices.tex
Background text updated and new references added.

--- 2018-09-01 paper_own_docker/chapters/background_microservices.tex
@@
 \label{chap:microservices}
-mention Service Oriented Architecture \cite{ahmadvand2016requirements} \cite{papazoglou2003service} (cite Amjads paper and original paper), difference to monolithic systems. Wide attack surface.
-- Formalize microservices. 
-- Provide definition from literature
-- When people started using them and why
 
-- Vulnerability scanner definitions
+As real world software grows bigger, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.
+A software application whose modules cannot be executed independently is called a monolith.
+Monoliths are characterized by tight coupling, vertical scaling and strong dependence.
+Service Oriented Architecture(SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
+However in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
+In microservices paradigm, multiple services are split into very basic units which are task oriented.
+According to Dragoni et al.
+a microservice is a cohesive, independent process interacting via messages.
+There microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
+Microservice architectures provide us with the advantage of having more heterogenious technologies, cheaper scaling, resilience, organizational alignment, and composability among other benefits \cite{newman2015building}.
+However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third party software increases.

### 2018-09-04 paper_own_docker/chapters/background.tex
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

--- 2018-08-31 paper_own_docker/chapters/background.tex
@@
 
-\subsection{Attack Graphs}
-\subsection{Microservice Architectures}
+In this section, we start by introducing the concept of microservices, their benefits and security implications (Subsection \ref{chap:microservices}).
+Afterward, we look into vulnerability scanners as tools that generate vulnerabilities for a single host (Subsection \ref{chap:vulnerability_scanners}).
+In the end, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts (Subsection \ref{chap:attack_graphs}).
+
+\input{./chapters/background_microservices}
+\input{./chapters/vulnerability_scanners}
+\input{./chapters/background_attack_graphs}

### 2018-09-04 paper_own_docker/chapters/background_attack_graphs.tex
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

--- 2018-09-01 paper_own_docker/chapters/background_attack_graphs.tex
@@
 \label{chap:attack_graphs}
-In this work we model an attack graph as a sequence of atomic attacks.
-Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege.
-A goal of an attacker would be to perform multiple atomic attacks to reach the desired goal container.
-For example, let us suppose that an attacker wants to have access to a database of a certain website.
-In order to reach the database, he has to pass other containers between him and the database.
-He does that by finding a vulnerability to exploit and gives access to the container's neighbors.
-After a successful exploitation of multiple intermediate containers, he finally has access to the database and its content.
-Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security.
-For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.
 
-Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured.
-Preconditions are privilege levels that are required so that a vulnerability can be exploited.
-When an atomic attack is successfully executed, a postcondition is obtained.
-Postconditions are privileges acquired as a result of a successful attack.
+The definition of attack graphs may vary but it is essentially a directed graph that consists of nodes and edges with various representations.
+In this subsection, we first look at a few examples of how others define attacks graphs and at the end present the model of an attack graph that we use in this work.
 
-- mention monotonicity
+Seyner et al.
+define an attack graph as a tuple of states, transitions between the states, initial state and success states.
+An initial state represents the state from where the attacker starts the attack and through a chain of atomic attacks tries to reach one of the success states \cite{sheyner2002automated}.
+
+Ou et al.
+introduce the notion of a logical attack graph.
+A logical attack graph is a bipartite directed graph that consists of two kinds of nodes: fact nodes and derivation nodes.
+Each fact node is labeled with a logical statement in the form of a predicate applied to its arguments, while each derivation node is labeled with an interaction rule that is used for the derivation step.
+The edges in the graph represent the "depends on" relation \cite{ou2006scalable}.
+
+Ingols et al.
+make a distinction between full, predictive and multiple-prerequisite (MP) attack graphs.
+Full graph is a directed acyclic graph that consists of nodes that represent hosts and edges that represent vulnerability instances.
+Predictive attack graphs use the same representation as full attack graphs with the only difference lying in the constraint of when the edges are added to the attack graph.
+These graphs are generally smaller than full graphs.
+MP attack is an attack graph with as contentless edges and three node type: state nodes, vulnerability instance nodes and prerequisite nodes \cite{ingols2006practical}.
+
+In our work we define attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
+\cite{ingols2006practical}.
+As an expansion to this model, a node represents a state of a host with its current privilege.
+An edge represents a successful transition between two such hosts.
+We can think of an edge as a successful vulnerability exploitation which is initiated from a host with a required privilege to another or the same host with the newly gained privilege as a result of the vulnerability exploitation.

### 2018-09-04 paper_own_docker/chapters/background_microservices.tex
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

--- 2018-09-01 paper_own_docker/chapters/background_microservices.tex
@@
 \label{chap:microservices}
-mention Service Oriented Architecture \cite{ahmadvand2016requirements} \cite{papazoglou2003service} (cite Amjads paper and original paper), difference to monolithic systems. Wide attack surface.
-- Formalize microservices. 
-- Provide definition from literature
-- When people started using them and why
 
-- Vulnerability scanner definitions
+As real-world software increases in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.
+A software application whose modules cannot be executed independently is called a monolith.
+Monoliths are characterized by tight coupling, vertical scaling and strong dependence.
+Service Oriented Architecture(SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
+However, in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
+In the microservices paradigm, multiple services are split into very basic units which are task oriented.
+According to Dragoni et al.
+a microservice is a cohesive, independent process interacting via messages.
+These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
+Microservice architectures provide us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability among other benefits \cite{newman2015building}.
+However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.

### 2018-09-04 paper_own_docker/chapters/evaluation.tex
Background text updated and new references added.
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

@@
 We then have a look at how others evaluate their systems.
-Finally in Subsection \ref{chap:scalability_eval} we conduct few experiments in order to test the scalability of our system with different number of containers and connectivity.
-All of the experiments were performed on a Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
+Finally in Subsection \ref{chap:scalability_eval} we conduct a few experiments in order to test the scalability of our system with a different number of containers and connectivity.
+All of the experiments were performed on an Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
 
@@
 Modern microservice architectures use an abundance of different technologies, number of containers, various connectivity and number of vulnerabilities.
-Therefore it is of immense importance to show that the attack graph generator works in such heterogenious scenarios.
-In order to do this we ran our system on some real and slightly modified Github examples as described on Table \ref{table_technologies} composed of different types of technologies, number of containers and vulnerabilities.
-The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
+Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
+In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} composed of different types of technologies, number of containers and vulnerabilities.
+The examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
 NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses Spring Cloud, Netflix Ribbon, Netflix Eureka etc.
 Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and that uses Spring Boot, React, NGINX and PostgreSQL.
-JavaEE demo is a sample application for browsing movies that is composed of only 2 containers and uses JavaEE, React and Tomcat EE.
+JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
 We ran the attack graph generator and checked for correctness of the resulting attack graph based on domain knowledge.
-After running the attack graph generator, the structure of the resulting attack graphs (especially in the Netflix case) was quite linear.
-This linearity is because each container is connected to few other containers to reduce unnecessary communication and increase encapsulation.
-So based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
-Additionally we noted that the running time of our system for each of these examples was short, and additional tests to test the scalability were needed.
-Phpmailer and Samba is an artificial example that we use and extend in the following subsection to perform these scalability tests.
-
-\subsection{Scalability evaluation}
-\label{chap:scalability_eval}
-Extensive scalability study of attack graph generators  is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
-Parameters that usually vary in this sort of evaluation are the number of nodes, their connectivity and the amount of vulnerabilities per container.
-All of these components contribute to the execution time of a given algorithm.
-Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
-In this case we compare our system to existing work by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
-In the following text, we first look at three works and their scalability evaluation results.
-After this comparison, we present the scalability results of our system.
-
-Seyner in his work tests the system in both a small and extended examples \cite{sheyner2002automated}.
-The attack graph in the larger example has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-Sheyner claims that the performance bottleneck is inside the graph generation procedure.
-
-Ingols tested his system on a network of 250 hosts.
-He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
-Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
-In addition to this, missing explanation of how the hosts are connected, does not make it directly comparable to our method.
-
-Ou provides some more extended study where he tests his system on more examples \cite{ou2006scalable}.
-He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
-He also provides an evaluation where he MulVAL clearly outperforms the Sheyner's system.
+After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo was small as expected with few nodes and edges.
+However, the structure of the resulting attack graphs in the Netflix case was quite linear.
+This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
+Therefore based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
+Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed.
+The Phpmailer \cite{phpmailer} and Samba \cite{samba} system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
 
@@
 
+\subsection{Scalability evaluation}
+\label{chap:scalability_eval}
+Extensive scalability study of attack graph generators is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
+Parameters that usually vary in this sort of evaluation are the number of nodes, their connectivity and the number of vulnerabilities per container.
+All of these components contribute to the execution time of a given algorithm.
+Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
+In this case, we compare our system to existing work by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
+In the following text, we first look at three works and their scalability evaluation results.
+After this comparison, we present the scalability results of our system.
+
+Sheyner et al.
+test their system in both small and extended examples.
+The attack graph in the larger example has 5948 nodes and 68364 edges.
+The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
+The authors claim that the performance bottleneck is inside the graph generation procedure \cite{sheyner2002automated}.
+
+Ingols et al.
+tested their system on a network of 250 hosts.
+He afterward continued his study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
+Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
+In addition to this, missing an explanation of how the hosts are connected, does not make it directly comparable to our method.
+
+Ou et al.
+provide some more extended study where they test their system(MulVAL) on more examples.
+They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
+The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system \cite{ou2006scalable}.
+
 In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
@@
 The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-In our tests, we report the total execution time as well as its components times: Topology parsing time, Vulnerability preprocessing time and Breath-First Search time.
+In our tests, we report the total execution time as well as its components times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
 The total time contains the topology parsing, the attack graph generation and some minor utility processes.
@@
 The Vulnerability preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-First Search time is the time needed for Breadth-First Search to traverse the topology and  generate the attack graph after the previous steps are done.
+The Breath-first Search time is the time needed for Breadth-first Search to traverse the topology and generate the attack graph after the previous steps are done.
 All of the components are executed five times for each of the examples and their final time is averaged.
@@
 Table \ref{table_scalability} shows the results of our experiments.
-In each of these experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
+In each of these experiments, the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
 This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
@@
 Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2.
+The number of edges of the topology graph is a combination of 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and a clique of the Phpmailer and Samba containers n*(n+1)/2.
 For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
@@
 Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step.
-However this step increases in linear fashion because the container files are analyzed only once by Clair.
+However, this step increases in a linear fashion because the container files are analyzed only once by Clair.
 The attack graph generation for the smaller examples is considerably less than the preprocessing time.
-Starting from example\_500, we can notice sharp increase in BDF execution time to 165 seconds.
+Starting from example\_500, we can notice a sharp increase in BDF execution time to 165 seconds.
 For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.

### 2018-09-04 paper_own_docker/chapters/method.tex
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

@@
 \section{METHOD}
-Up to this point we formally defined what attack graph is.
-In this section we first look at how the existing components of attack graph generation for computer networks map into a microservice environment  and provide a small example (Subsection \ref{chap:mapping}).
-We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-First Search graph traversal algorithm in Subsection \ref{chap:bfs}.
+Up to this point, we formally defined what an attack graph is.
+In this section, we first look at how the existing components of attack graph generation for computer networks map into a microservice environment and provide a small example (Subsection \ref{chap:mapping}).
+We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
 
@@
 In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
-In this subsection we start first by shortly introducing a famous microservice framework(Docker) and some of its terminology.
+In this subsection, we start first by shortly introducing a famous microservice framework(Docker) and some of its terminology.
 We then modify the attack graph concepts mentioned above for our use-case(nodes, edges, privilege levels, pre- and postconditions).
-At the end we see how this translation works in practice by demonstrating a small example.
+In the end, we see how this translation works in practice by demonstrating a small example.
 
 Docker is one of the most popular and used microservice frameworks currently available.
-In Docker, distinction is being made between the terms image, container and service.
-Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs  \cite{merkel2014docker}.
-In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
+In Docker, a distinction is being made between the terms image, container and service.
+An image is an executable package that includes everything needed to run an application, a container is a runtime instance of an image and service represents a container in production.
+A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs  \cite{merkel2014docker}.
+In our work, we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
 
 As mentioned above, nodes and edges are the basic building blocks of an attack graph.
-Nodes in our attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
+Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
 In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
@@
 Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
-The pre- and postcondition rules use the fields defined by NVD, as well as ocrcurence of specific keywords from the CVEs descriptions.
+The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.
 
 Privileges play a central role in this attack graph generation.
-We model the privileges into a hierarchy.
-The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
+We model the privileges in a hierarchy.
+The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
 VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-On the other side OS means that the host machine has been compromised.
+On the other side, The keyword OS means that the host machine has been compromised.
 Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
@@
 The example is taken from the Netflix OSS Github repository \cite{netflixoss}.
-Displayed on Figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes.
-On Figure \ref{AttackGraph} we can see a part of the resulting attack graph.
-Parts of the both graphs has been intentionally omitted to reduce complexity.
+Displayed in Figure \ref{TopologyGraph} is the topology of the example.
+The topology consists of "Outside" node, "Docker daemon" node and a subset of other nodes.
+In Figure \ref{AttackGraph} we can see a part of the resulting attack graph.
+Parts of both graphs have been intentionally omitted to reduce complexity.
 An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability and gain USER privilege.
-Then with this USER privilege it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege.
+Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege.
 Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 and gain ADMIN privilege.
@@
 Another path would be to exploit the CVE-20108-1124 vulnerability while have only USER privilege on Zuul to gain directly ADMIN privileges and then attack the Eureka container.
-Our attack graph generator shows both paths, since it is of an interest to see every possible route in which a container can be compromised.
+Our attack graph generator shows both paths since it is of an interest to see every possible route in which a container can be compromised.
 
@@
 
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-First Search graph transversal algorithm.
+In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-first Search graph transversal algorithm.
 
@@
 
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
+Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
+The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
 
@@
 
-The topology of Docker containers can be described at either runtime, or statically by using Docker Compose.
+The topology of Docker containers can be described at either runtime or statically by using Docker Compose.
 In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
@@
 However different versions of docker-compose.yml, use different syntax.
-For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
+For example, older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
 In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
@@
 Some containers require certain privileges over the docker daemon in order to function properly.
-In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file .
-An attacker with access to these containers, has also access to the docker daemon.
-Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.
+In docker, this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
+An attacker with access to these containers has also access to the Docker daemon.
+Once the attacker has access to the docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
 
@@
 
-		\caption{Breadth-first search algorithm for generating an attack graph.}
+		\caption{Breadth-first Search algorithm for generating an attack graph.}
 		\label{BFSalgorithm}
@@
 In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a vulnerability scanner that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability.
-Attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
+Clair is a vulnerability scanner that inspects a docker image and generates its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability \cite{clair}.
+An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
 The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
-Unfortunately Clair does not provide with an ready to use interface to analyze a docker image.
-As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.
+Unfortunately, Clair does not provide with a ready to use interface to analyze a docker image.
+As a result, we use Clairctl \cite{clairctl} in order to analyze a complete docker image.
 
 \subsection{Attack Graph Parser}
+\label{chap:attack_graph_p}
 
@@
 When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-If more than one rule matches, we take the one with the highest privilege level for the preconditions an\label{chap:attack_graph_p}d the lowest privilege level for the postconditions.
-If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.
+If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
+If no rule matches, we take None as a precondition and ADMIN(OS) as a postcondition.
 This results in a list of container vulnerabilities with their preconditions and postconditions.
 
-\subsubsection{Breadth-First Search}
+\subsubsection{Breadth-first Search}
 \label{chap:bfs}
@@
 After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
-Breadth-First Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph.
-Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.
+Together with the topology, they are feed into the Breadth-first Search algorithm (BFS).
+Breadth-first Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before diving deeper into the graph.
+Pseudocode of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
 The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph.
 The algorithm first initializes the nodes, edges, queue and the passed nodes.
-Afterwards it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
+Afterward, it generates the nodes which are a combination of the image name and the privilege level.
+Then into a while loop, it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
 If the neighbor was not passed, then it is added to the queue.
 The algorithm terminates when the queue is empty.
-Furthermore BFS is characterized by the following properties:
+Furthermore, BFS is characterized by the following properties:
 
 \begin{itemize}
-		\item Completeness: Breadth First Search is complete i.e. if there is a solution, breadth-first search will find it regardless of the kind of graph.
+	\item Completeness: Breadth-first Search is complete i.e. if there is a solution, Breadth-first search will find it regardless of the kind of graph.
 	\item Termination: This follows from its monotonicity property. Each edge is traversed only once.

### 2018-09-04 paper_own_docker/chapters/related_work.tex
Attack graphs subsection and related work redone, some references added and text mostly corrected with help of correctify

@@
 \section{RELATED WORK}
-Previous work has dealt with attack graph generation, mainly in computer networks 
-%\todo{please cite them}
-, where multiple machines are connected to each other and the Internet.
-In these networks an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
+Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.
+In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
 Attack graphs help in analyzing this behavior.
-Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process
-%\todo{elaborate a bit why; scalability, expertise, completeness.. }
-. Tools that generate vulnerabilities of specific host are available. However previous works have state that these tools alone are not enough to analyze the vulnerability 
-%\todo{mention why coz they can be connected ..} 
-of an entire network and that these tools in addition to network topology could solve this issue.
+Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
+Tools that generate vulnerabilities of a specific host are available \cite{clair, artz2002netspa, farmer1990cops}.
+However previous works state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
+This outcome is because different hosts are connected together and influence the outcome of an attack.
 Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
 
-One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols2006practical} %\todo{space citation then the dot, e.g., property [5].}
-
-Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example.
-A collection of these counter examples form an attack graph.
+One of the earlier works in attack graph generation was done by Sheyner et al.
+by using model checkers with goal property \cite{sheyner2002automated}.
+Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counterexample.
+A collection of these counterexamples form an attack graph.
 They state that model checkers satisfy a monotonicity property in order to ensure termination.
-However model checkers have a computational disadvantage.
-In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed.
+However, model checkers have a computational disadvantage.
+In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges \cite{sheyner2002automated}.
+As a result of this, more scalable approach was needed.
 Amman et al.
-extends this work with some simplifications and more efficient storage \cite{ritchey2000using}.
-
+extend this work with some simplifications and more efficient storage \cite{ritchey2000using}.
 Ou et al.
 use logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al.
-use breath first search algorithm in order to tackle the scalability issue.
-Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes
-%\todo{please rephrase this sentence to clarify it what is redundanccy full, define MP}
-.
-They use breath first search technique for generating the attack graph.
+use Breadth-first search algorithm in order to tackle the scalability issue.
+Ingols et al.
+discuss the redundancy Full and Predictive graphs and model an attack graph as an MP graph with contentless edges and 3 types of nodes.
+They use Breath-first search technique for generating the attack graph.
 This approach provides faster results in comparison to using model checkers.
 An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
+Aksu et al.
+build on top of Ingols's system and evaluate a set of rule pre- and postconditions in generating attacks.
+They define a specific test of pre- and postcondition rules and test their correctness.
+In their evaluation, they use a machine learning approach \cite{aksu2018automated}.
 
-Aksu et al.
-builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks \cite{aksu2018automated}.
-They define a specific test of pre- and postcondition rules and test their correctness.
-In their evaluation, they use machine learning approach.
-
-Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers.
-Therefore we extend the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjuction to Clair OS to generate attack graphs for microservice architectures.
+Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and a lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}.
+To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for Docker containers.
 Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
 Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-%\todo{in general good story line, some language work is needed later-on}
+Therefore we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction to Clair OS \cite{clair} to generate attack graphs for microservice architectures.

### 2018-09-04 paper_own_docker/chapters/abstract.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
+Therefore, in the following paper, we present a novel Breath-first Search (BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.

### 2018-09-04 paper_own_docker/chapters/background.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

--- 2018-09-01 paper_own_docker/chapters/background.tex
@@
 \section{BACKGROUND}
+\label{chap:background}
 
-In this section we start by formally defining attack graphs and their characteristics (Subsection \ref{chap:attack_graphs}).
-Afterwards we look into microservices, their advantages in comparison to monolithic systems and conclude with their security implications (Subsection \ref{chap:microservices}).
+We first start by introducing the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
+Afterward in Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools that generate vulnerabilities for a single host .
+In the end in Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
 
+\input{./chapters/background_microservices}
+\input{./chapters/vulnerability_scanners}
 \input{./chapters/background_attack_graphs}
-\input{./chapters/background_microservices}

### 2018-09-04 paper_own_docker/chapters/background_microservices.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 Monoliths are characterized by tight coupling, vertical scaling and strong dependence.
-Service Oriented Architecture(SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
+Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
 However, in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.

### 2018-09-04 paper_own_docker/chapters/evaluation.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 \section{EVALUATION}
+\label{chap:eval}
 
@@
 	\begin{center}
-		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{60mm}| } 
+		\begin{tabular}{ p{20mm}p{25mm}p{20mm}p{10mm}cp{60mm} } 
 			\hline
@@
 			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\
 
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 &  https://github.com/dockersamples/atsea-sample-shop-app \\\hline
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 &  https://github.com/dockersamples/atsea-sample-shop-app \\
 
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 &  https://github.com/dockersamples/javaee-demo \\\hline
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 &  https://github.com/dockersamples/javaee-demo \\
 
@@
 & PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline
+			https://github.com/opsxcq/exploit-CVE-2017-7494 \\
 
@@
 	\begin{center}
-		\begin{tabular}{ |c|c|c|c|c|c| } 
+		\begin{tabular}{ cccccc } 
 			\hline
-			Statistics & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\
+			Statistics & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\ \hline
 
@@
 \label{chap:scalability_eval}
+
 Extensive scalability study of attack graph generators is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
@@
 tested their system on a network of 250 hosts.
-He afterward continued his study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
+They afterward continued the study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
 Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
@@
 The Topology parsing time is the time required to generate the graph topology.
-The Vulnerability preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions.
+The Vulnerability preprocessing time is the time needed to convert the vulnerabilities into sets of pre- and postconditions.
 The Breath-first Search time is the time needed for Breadth-first Search to traverse the topology and generate the attack graph after the previous steps are done.
@@
 This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
-In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are hosted).
+In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
+the docker daemon where the containers are hosted.
 Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a combination of 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and a clique of the Phpmailer and Samba containers n*(n+1)/2.
-For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).
+The number of edges of the topology graph is a combination of one edge ("outside"-"Phpmailer"), n edges ("docker host" to all of the containers) and n*(n+1)/2 edges of between Phpmailer and Samba containers.
+For example\_20, the number of containers is 23 (one Phpmailer, one "outside", one "docker host" and 20 Samba containers) the number of edges in the topology graph would be 253: one outside edge, 21 docker host edges (one toward Phpmailer and 20 toward the Samba containers) and 231 between-container edges (21*22/2=231).
 

### 2018-09-04 paper_own_docker/chapters/introduction.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyse a system connection and detect the most vulnerable parts of the system.
+They help security analysts to carefully analyze a system connection and detect the most vulnerable parts of the system.
 An attack graph depicts the actions that an attacker uses in order to reach his goal.
 
-Statistics. They do not offer any performance comparison between different topologies.
+Statistics. 
+https://banyanops.com/blog/analyzing-docker-hub/
+https://blog.acolyer.org/2017/04/03/a-study-of-security-vulnerabilities-on-docker-hub/
+http://dance.csc.ncsu.edu/papers/codaspy17.pdf \cite{shu2017study}
 
-We first have a look into the work of other (Section 2), then present the architecure of our system (Section 3), test the scalability (Section 4) and at the end provide a conclusion (Section 5) and future work (Section 6).
+They do not offer any performance comparison between different topologies.
+
+In this work, we first get familiar with the basic attack graph and microservice terminology in Section \ref{chap:background}, then present the architecture of our system in Section \ref{chap:method}, perform evaluation in Section \ref{chap:eval} and at the end present what others did in the area in section \ref{chap:related_work}, a conclusion in Section \ref{chap:conclusion} and future work directions in Section \ref{chap:future_work}.

### 2018-09-04 paper_own_docker/chapters/method.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 \section{METHOD}
+\label{chap:method}
+
 Up to this point, we formally defined what an attack graph is.
-In this section, we first look at how the existing components of attack graph generation for computer networks map into a microservice environment and provide a small example (Subsection \ref{chap:mapping}).
+Here, we first look at how the existing components of attack graph generation for computer networks map into a microservice environment and provide a small example in Subsection \ref{chap:mapping}.
 We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
-
-%\todo{it is early to put this image here, also long caption, image quality should be enhanced}
-\begin{figure}
-	\includegraphics[scale=0.9]{./images/AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
-	\label{AttackGraphSystem}
-\end{figure}
 
@@
 In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
-In this subsection, we start first by shortly introducing a famous microservice framework(Docker) and some of its terminology.
-We then modify the attack graph concepts mentioned above for our use-case(nodes, edges, privilege levels, pre- and postconditions).
+In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology.
+We then modify the attack graph concepts mentioned above for our use-case (nodes, edges, privilege levels, pre- and postconditions).
 In the end, we see how this translation works in practice by demonstrating a small example.
@@
 In our work, we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
+
+\begin{figure}
+	\includegraphics[]{./images/Topology_graph}
+	\caption{Example topology graph.
+The topology graph is a subset of a real topology graph from the Netflix OSS example.
+Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
+	\label{TopologyGraph}
+\end{figure}
 
@@
 
+\begin{figure}
+	\includegraphics[]{./images/Attack_graph}
+	\caption{Example resulting attack graph.
+This attack graph is a subset of a real attack graph from the Netflix OSS example.
+Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
+	\label{AttackGraph}
+\end{figure}
+
 In order to show how the attack graph generation works in practice, we present a small example.
@@
 
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig.
-\ref{AttackGraphSystem}).
+Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser (Figure \ref{AttackGraphSystem}).
 The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
 
-\begin{figure}
-	\includegraphics[]{./images/Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
+In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-first Search graph transversal algorithm.
 
 \begin{figure}
-	\includegraphics[]{./images/Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
+	\includegraphics[scale=0.9]{./images/AttackGraphSystem}
+	\caption{Our Attack Graph System.
+The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
+The arrows describe the flow of the system and the files are the intermediate products.}
+	\label{AttackGraphSystem}
 \end{figure}
-
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-first Search graph transversal algorithm.
 
@@
 We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if the appropriate Topology and Vulnerability parsers are provided and conform to the input of the attack graph generator.
+However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if needed.
+In this case appropriate Topology and Vulnerability parsers need to be provided and they need conform to the input of the attack graph generator.
 
@@
 Some containers require certain privileges over the docker daemon in order to function properly.
-In docker, this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
+In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
 An attacker with access to these containers has also access to the Docker daemon.
-Once the attacker has access to the docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
+Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
 
@@
 In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a vulnerability scanner that inspects a docker image and generates its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability \cite{clair}.
+Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability \cite{clair}.
 An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete).
+The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
 Unfortunately, Clair does not provide with a ready to use interface to analyze a docker image.

### 2018-09-04 paper_own_docker/chapters/related_work.tex
Added docker vulnerability statistics links, removed horizonal rules from tables to conform with ACM style and some minor text corrections.

@@
 \section{RELATED WORK}
+\label{chap:related_work}
+
 Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.

### 2018-09-14 paper_own_docker/chapters/abstract.tex
TODOs

--- 2018-08-31 paper_own_docker/chapters/abstract.tex
@@
-Microservices, in contrast to monolithic systems, provide an architecture that is modular and easily scalable.
-This advantage has resulted in a rapid increase in usage of microservices in recent years.
-Despite their rapid increase in popularity, there is a lack of work that focuses of their security aspect.
-Therefore, in the following paper, we present a novel Breath-First Search(BFS) based method for attack graph generation and security analysis of microservice architectures using Docker and Clair.
+Microservices are increasingly dominating the field of service systems, among their many characterstics, practices are technology heterogeneity and reuse and network interfaces.
+Therefore, with the increase of utilizing third-party components, the potential vulanrabilities existing in a microservice-based system increase.
+Based on components dependency, these vulnerabilities lead to exposing critical assets of such systems.
+Similar problems have been tackled in computer networks communities.
+In this paper, we propose the utilization of attack graphs as a part of the automated development infrastructure used in microservices-based systems.
+To that end, we relate microservices to network nodes, and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks.
+We present a complete solution that can be easily embeded into the continuous delivery systems, and show with real-world use cases its efficiency and scalability.
+%Breath-first Search (BFS) based method for attack graph generation and security analysis of microservice architectures using Docker

### 2018-09-14 paper_own_docker/chapters/background_microservices.tex
TODOs

@@
 
+\textbf{TODO} add a brief histroy of ms\\
+\textbf{TODO} at the end introduce container based 
 As real-world software increases in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.

### 2018-09-14 paper_own_docker/chapters/introduction.tex
TODOs

@@
 \section{INTRODUCTION}
+
+%intro about the new paradiagm of mirocservices its benefits and new oppurnties, maybe its utilization in secuirty/ safety critical systems
+Microservices, as a new approach to manage the complexity of modern applications, are increasingly adopted in real-world systems. The new architectural style 
+follows the Unix fundamental principles  of decomposing systems into small programs \cite{Unix ideas [115]:} that each fulfills only one cohesive task and can work together using universal interfaces.
+Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{[Microservices.
+Martin Fowler(2015)]}.
+The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{}.
+However, clearly, other qualities like the network utilization, and the security are negatively affected \cite{ahmadvand2016requirements}.
+Balancing the trades-off among these factors derive the decision of using microservices in industry.
+That said, a non exhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
+This shift is  motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts.
+We see microservice-based systems in domains of video streaming, social networks, logistics, internet of things \cite{internet}, and smart cities \cite{smartcity}.
+
+% the new tools or eco system of this style, especially container based deployment...
+the benefits of it and the challanges brought by it, like open source utilization and scurity overhead brought by networks and docker security issues.
+Microservices have popularized two main concepts in the software engineering community.
+The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in lightweight containers.
+As a result the systems are deployed as networks of communicating micorservices.
+Each microservice achieves an independent task.
+% threat modeling as a way to systmatically analyze threats...
+its benefits and obstecales, ag as an example especially for newtorked systems...
+the mapping between container based and network applications...
+and the progress there.
+
+% the problem: summing it up and the solution
+% the potentisl benefit in the scope of devops practices and automation (automation should be mentioned before)
+% contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
+% structure
 

### 2018-09-14 paper_own_docker/chapters/method.tex
TODOs

@@
 
+\textbf{TODO} add this image to fig 2 in the same figure and have them as subfigures\\
 \begin{figure}
@@
 As mentioned above, nodes and edges are the basic building blocks of an attack graph.
-Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
+Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels\textbf{TODO}  explain this, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
 In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
@@
 
+\textbf{TODO} explain here why VOS we dont have virtual machines say that we are adapting those to the images\\
 Privileges play a central role in this attack graph generation.
@@
 
+\subsubsection{Example}
+\textbf{TODO}  explain the example usage what is the system and what is ZUUL and give an example of one of the CVE briefly.\\
 In order to show how the attack graph generation works in practice, we present a small example.

### 2018-09-15 paper_own_docker/chapters/evaluation.tex
notes on the mthod and evaluation

@@
 \label{chap:eval}
-
+\textbf{TODO} increase width of description and stack, reduce the links and use latex url for them
 \begin{table*}
@@
 
-Real-world microservice architectures are composed of many containers that run different technologies with various degrees of connectivity between each other.
+Real-world microservice systems are composed of many containers that run different technologies with various degrees of connectivity among each other.
 This raises the need for a robust and scalable attack graph system.
@@
 We then have a look at how others evaluate their systems.
-Finally in Subsection \ref{chap:scalability_eval} we conduct a few experiments in order to test the scalability of our system with a different number of containers and connectivity.
+Finally in Subsection \ref{chap:scalability_eval} we conduct experiments in order to test the scalability of our system with a different number of containers and connectivity.
 All of the experiments were performed on an Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
 
-\subsection{Heterogenious microservice systems evaluation}
+\subsection{Use Cases}
 \label{chap:heterogenious_systems}
@@
 Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} composed of different types of technologies, number of containers and vulnerabilities.
+In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} \textbf{TODO: say how did we find these use cases}.
 The examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
@@
 We ran the attack graph generator and checked for correctness of the resulting attack graph based on domain knowledge.
-After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo was small as expected with few nodes and edges.
+After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
 However, the structure of the resulting attack graphs in the Netflix case was quite linear.
@@
 The Phpmailer \cite{phpmailer} and Samba \cite{samba} system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
+\textbf{TODO explain the result of correctness, what did you find out i.e., they are correct to our knowledge maybe show one example of an attack graph generated, also explain more the linearity thing}
 
@@
 In this case, we compare our system to existing work by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
-In the following text, we first look at three works and their scalability evaluation results.
+In the following, we first look at three works and their scalability evaluation results.
 After this comparison, we present the scalability results of our system.
@@
 provide some more extended study where they test their system(MulVAL) on more examples.
-They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts.
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
-The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system \cite{ou2006scalable}.
+They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.% The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system \cite{ou2006scalable}.
 
@@
 For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
+\textbf{TODO so what is the main finding, add a paragraph to compare the results to the numbers you mentioned earlier.}

### 2018-09-15 paper_own_docker/chapters/introduction.tex
notes on the mthod and evaluation

@@
 the benefits of it and the challanges brought by it, like open source utilization and scurity overhead brought by networks and docker security issues.
-Microservices have popularized two main concepts in the software engineering community.
-The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in lightweight containers.
-As a result the systems are deployed as networks of communicating micorservices.
-Each microservice achieves an independent task.
+The utilization of microservices have popularized two main concepts in the software engineering community.
+The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{bibid}.
+As a result, the systems are deployed as networks of communicating micorservices.
+For their lightweight and operating-system level virtualization \cite{what is the container hype}, the containerization frameworks like \textit{Docker} \cite{bibid}, are a high performance alternative to hypervisors \cite{nw}.
+The second often-used concept in the domain of microservices development is DevOps \cite{bibid}.
+DevOps enable practices in which full automation of the deployment process is achieved.
+In the course of this, end-to-end automated packaging and deployment  is a vital part of microservices development.
+In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements}.
+The increasing communication end-points among the microservices \cite{ahmadvand2016requirements}, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and container isolation.
+
+ In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordysurvey}.
+Following the Devops mentality, we propose an automated method that can be integrated into continuous delivery systems to generate attack graphs.
+
 % threat modeling as a way to systmatically analyze threats...
@@
 and the progress there.
+
+Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.
+In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
+Attack graphs help in analyzing this behavior.
+Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process.
+Tools that generate vulnerabilities of a specific host are available \cite{clair, artz2002netspa, farmer1990cops}.
+However previous works state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue.
+This outcome is because different hosts are connected together and influence the outcome of an attack.
+Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
 

### 2018-09-15 paper_own_docker/chapters/method.tex
notes on the mthod and evaluation

@@
 
+\subsection{Attack Graph Generation for Docker Networks}
+\label{chap:technical}
 Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser (Figure \ref{AttackGraphSystem}).
@@
 
+\textbf{TODO} why do we have an edge between topology file and vul parser\\
 \begin{figure}
@@
 
-\subsection{Technical Details}
-\label{chap:technical}
-
 Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
-The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
-
+The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities scanning.
+\textbf{TODO} explain docker compose \\
 We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
@@
 In this case appropriate Topology and Vulnerability parsers need to be provided and they need conform to the input of the attack graph generator.
-
-\subsection{Topology Parser}
+\textbf{TODO} need to rewrite the previous paragraph \\
+\subsubsection{Topology Parser}
 \label{chap:topology_p}
-
+\textbf{TODO} explain a topology at the beginning.\\
 The topology of Docker containers can be described at either runtime or statically by using Docker Compose.
 In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
+Docker Compose provides a docker-compose.yml file which is used for extraction of the topology of the system.
 However different versions of docker-compose.yml, use different syntax.
@@
 Some containers require certain privileges over the docker daemon in order to function properly.
-In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
+\textbf{TODO} explain why would people do that with an example maybe \\In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
 An attacker with access to these containers has also access to the Docker daemon.
@@
 
-\subsection{Vulnerability Parser}
+\subsubsection{Vulnerability Parser}
 \label{chap:vulnerability_p}
@@
 
-\subsection{Attack Graph Parser}
+\subsubsection{Attack Graph Generator}
 \label{chap:attack_graph_p}
@@
 
-\subsubsection{Breadth-first Search}
+\paragraph{Breadth-first Search}
 \label{chap:bfs}
@@
 	\item Completeness: Breadth-first Search is complete i.e. if there is a solution, Breadth-first search will find it regardless of the kind of graph.
-	\item Termination: This follows from its monotonicity property. Each edge is traversed only once.
+	\item Termination: This follows from its monotonicity property. Each edge is traversed only once.\textbf{TODO} explain monotonicity and cite something\\
 	\item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.

### 2018-09-17 paper_own_docker/chapters/evaluation.tex
Todos in method and evaluation done

@@
 \label{chap:eval}
-\textbf{TODO} increase width of description and stack, reduce the links and use latex url for them
+
 \begin{table*}
 	\begin{center}
-		\begin{tabular}{ p{20mm}p{25mm}p{20mm}p{10mm}cp{60mm} } 
+		\begin{tabular}{ p{20mm}p{35mm}p{35mm}p{10mm}cp{35mm} } 
 			\hline
@@
 			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
 
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 &  https://github.com/dockersamples/atsea-sample-shop-app \\
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & \url{https://github.com/dockersamples/atsea-sample-shop-app} \\
 
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 &  https://github.com/dockersamples/javaee-demo \\
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & \url{https://github.com/dockersamples/javaee-demo} \\
 
@@
 We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  https://github.com/opsxcq/exploit-CVE-2016-10033
-			https://github.com/opsxcq/exploit-CVE-2017-7494 \\
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  \url{https://github.com/opsxcq/exploit-CVE-2016-10033}
+			\url{https://github.com/opsxcq/exploit-CVE-2017-7494} \\
 
@@
 Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} \textbf{TODO: say how did we find these use cases}.
-The examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
+In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties(topologies, technologies, vulnerabilities) and coming from different usage domains.
+We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or few containers, which made this search challenging.
+The resulting examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
 NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses Spring Cloud, Netflix Ribbon, Netflix Eureka etc.
@@
 JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
-We ran the attack graph generator and checked for correctness of the resulting attack graph based on domain knowledge.
+We ran the attack graph generator and verified the resulting attack graphs manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
+\cite{aksu2018automated} are correct.
 After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
@@
 Therefore based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
+All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property.
 Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed.
@@
 They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.% The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system \cite{ou2006scalable}.
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute \cite{ou2006scalable}.
+% The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system .
 
@@
 For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
-\textbf{TODO so what is the main finding, add a paragraph to compare the results to the numbers you mentioned earlier.}
+
+The total time of the attack graph generation procedure for 1000 fully connected hosts (784 seconds) outperforms Ou's results (1000 seconds).
+In the Sheyners's extended example(4 hosts, 8 atomic attacks and multiple vulnerabilites) the attack graph took 2 hours to create.
+Our attack graph procedure even for the bigger number of hosts(1000) shows faster attack graph generation time.
+It however performs worse than Ingols, but that is attributed to the usage of MP attack graph which is different from ours.
+From the results we can see that Breath-first Search can be used to generate attack graphs for increasing number of services and denser connectivity in microservices architectures.

### 2018-09-17 paper_own_docker/chapters/method.tex
Todos in method and evaluation done

--- 2018-09-04 paper_own_docker/chapters/method.tex
@@
 \label{chap:method}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=.6\linewidth]{./images/Topology_graph}
+		\caption{}
+		\label{TopologyGraph}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=.6\linewidth]{./images/Attack_graph}
+		\caption{}
+		\label{AttackGraph}
+	\end{subfigure}
+
+	\caption[Two numerical solutions]{(a) Example topology graph where each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.
+(b) Example resulting attack graph, where nodes correspond to a pair of container plus privilege, while edges are atomic attacks.
+The topology and attack graphs are a subset of the real topology and attack graphs from the Netflix OSS example.}
+\end{figure}
 
@@
 
-\begin{figure}
-	\includegraphics[]{./images/Topology_graph}
-	\caption{Example topology graph.
-The topology graph is a subset of a real topology graph from the Netflix OSS example.
-Each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.}
-	\label{TopologyGraph}
-\end{figure}
+Privileges play a central role in this attack graph generation.
+We model the privileges in a hierarchy.
+The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
+VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
+However in our case, unlike hosts connected in a computer networks, these privileges are adapted to images and not virtual machines.
+On the other side, The keyword OS means that the host machine has been compromised.
+Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
+None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.
 
@@
 Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
+The starting node of an edge denotes the container from which the attack is performed and the privilege level that an attacker needs to have to exploit a given vulnerability.
+The end node of an edge is the container which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation.
 In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
@@
 
-Privileges play a central role in this attack graph generation.
-We model the privileges in a hierarchy.
-The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-On the other side, The keyword OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
-None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.
-
-\begin{figure}
-	\includegraphics[]{./images/Attack_graph}
-	\caption{Example resulting attack graph.
-This attack graph is a subset of a real attack graph from the Netflix OSS example.
-Nodes correspond to a pair of container plus privilege, while edges are atomic attacks.}
-	\label{AttackGraph}
-\end{figure}
+\subsubsection{Example}
 
 In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository \cite{netflixoss}.
-Displayed in Figure \ref{TopologyGraph} is the topology of the example.
-The topology consists of "Outside" node, "Docker daemon" node and a subset of other nodes.
+The example is taken from the Netflix OSS Github repository.
+Netflix OSS example is a Spring Cloud based microservices architecture that enables Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
+Displayed in Figure \ref{TopologyGraph} is a subset of the example topology.
+The topology consists of "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
+According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resiliency, security, and more \cite{netflixzuul}, while Eureka is a REST (Representational State Transfer) based service that is primarily used in the AWS cloud for locating services for the purpose of load balancing and failover of middle-tier servers \cite{netflixeureka}.
 In Figure \ref{AttackGraph} we can see a part of the resulting attack graph.
 Parts of both graphs have been intentionally omitted to reduce complexity.
-An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability and gain USER privilege.
-Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 and gain ADMIN privilege.
+An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gain USER privilege.
+Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain ADMIN privilege.
+Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 via another crafted image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2017-7600}} and gain ADMIN privilege.
 It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to exploit the CVE-20108-1124 vulnerability while have only USER privilege on Zuul to gain directly ADMIN privileges and then attack the Eureka container.
+Another path would be to exploit the CVE-2018-1124 vulnerability via creating entries in procfs by starting processes, which could result in crashes or arbitrary code execution\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2018-1124}}.
+This vulnerability can be exploited by having only USER privilege on Zuul to gain directly ADMIN privileges of the Eureka container.
 Our attack graph generator shows both paths since it is of an interest to see every possible route in which a container can be compromised.
 
+\subsection{Attack Graph Generation for Docker Networks}
+\label{chap:technical}
 Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser (Figure \ref{AttackGraphSystem}).
@@
 
-\subsection{Technical Details}
-\label{chap:technical}
+Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
+Docker Compose is a tool for defining and running multi-container Docker applications \cite{dockercompose}.
+It provides a static configuration file that specifies the system containers, networks, ports etc.
+The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities scanning.
 
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
-The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities generation.
+We developed this system to be used with a specific version of Docker and Docker-Compose.
+This modular structure could however be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing the Vulnerability and Topology Parsers with custom ones and making sure that their outputs conform to the input of the Attack Graph Parser.
 
-We developed this system to be used exclusively with a specific version of Docker and Docker-Compose.
-However, please note that the main algorithm is easily extendable to accommodate other microservice architectures if needed.
-In this case appropriate Topology and Vulnerability parsers need to be provided and they need conform to the input of the attack graph generator.
-
-\subsection{Topology Parser}
+\textbf{TODO} need to rewrite the previous paragraph \\
+\subsubsection{Topology Parser}
 \label{chap:topology_p}
 
+In order to generate an attack graph of a given system, we require an arrangement of its components and connections described by a system topology.
 The topology of Docker containers can be described at either runtime or statically by using Docker Compose.
 In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
-Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system.
+Docker Compose provides a docker-compose.yml file which is used for extraction of the topology of the system.
 However different versions of docker-compose.yml, use different syntax.
@@
 Some containers require certain privileges over the docker daemon in order to function properly.
+For example a user may want to run some hardware (web-cam \cite{webcam}) or some applications that demand higher privilege levels (Libvirt \cite{libvirt}) from Docker.
 In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
@@
 	\item Completeness: Breadth-first Search is complete i.e. if there is a solution, Breadth-first search will find it regardless of the kind of graph.
-	\item Termination: This follows from its monotonicity property. Each edge is traversed only once.
+	\item Termination: This follows from the monotonicity property. Monotonicity is ensured if it is assumed that an attacker will
+	never need to relinquish a state \cite{ingols2006practical, ou2006scalable, ammann2002scalable}. In this implementation, each edge is traversed only once, making sure that monotonicity is preserved.
 	\item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.

### 2018-09-18 paper_own_docker/chapters/background.tex
Todos in the background and minor changes in method and evaluation done

@@
 We first start by introducing the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
-Afterward in Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools that generate vulnerabilities for a single host .
-In the end in Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
+Afterward in Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools that generate vulnerabilities for a single host.
+At the end in Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
 

### 2018-09-18 paper_own_docker/chapters/background_attack_graphs.tex
TODOs
Todos in the background and minor changes in method and evaluation done

@@
 
+Attack graphs are a popular way of examining network security weaknesses.
+They help security analysts to carefully analyze a given system and detect its vulnerable parts.
 The definition of attack graphs may vary but it is essentially a directed graph that consists of nodes and edges with various representations.
@@
 Each fact node is labeled with a logical statement in the form of a predicate applied to its arguments, while each derivation node is labeled with an interaction rule that is used for the derivation step.
-The edges in the graph represent the "depends on" relation \cite{ou2006scalable}.
+The edges in the graph represent a "depends on" relation \cite{ou2006scalable}.
 

### 2018-09-18 paper_own_docker/chapters/background_microservices.tex
Todos in the background and minor changes in method and evaluation done

--- 2018-09-04 paper_own_docker/chapters/background_microservices.tex
@@
 Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
-However, in a typical SOA, the services are monolithic which gives rise to microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
+However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
+The novel term "microservices" was first introduced in 2011 at an architectural workshop in order to bridge a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
 In the microservices paradigm, multiple services are split into very basic units which are task oriented.
@@
 However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.
+While microservices are an architectural principle, container technology has emerged in cloud computing to provide a lightweight virtualization mechanism.
+This technology enables microservices to be packaged and orchestrated through the Cloud \cite{pahl2016microservices}.

### 2018-09-18 paper_own_docker/chapters/evaluation.tex
Todos in the background and minor changes in method and evaluation done

@@
 \label{chap:eval}
-
-\begin{table*}
-	\begin{center}
-		\begin{tabular}{ p{20mm}p{35mm}p{35mm}p{10mm}cp{35mm} } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & \url{https://github.com/dockersamples/atsea-sample-shop-app} \\
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & \url{https://github.com/dockersamples/javaee-demo} \\
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  \url{https://github.com/opsxcq/exploit-CVE-2016-10033}
-			\url{https://github.com/opsxcq/exploit-CVE-2017-7494} \\
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Microservice architecture examples analyzed by the attack graph generator.}
-	\label{table_technologies}
-
-\end{table*}
 
@@
 \label{chap:heterogenious_systems}
+
 Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities.
 Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies} Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties(topologies, technologies, vulnerabilities) and coming from different usage domains.
-We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or few containers, which made this search challenging.
+In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies}.
+Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties(topologies, technologies, vulnerabilities) and coming from different usage domains.
+We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging.
 The resulting examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
@@
 JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
-We ran the attack graph generator and verified the resulting attack graphs manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
+We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
 \cite{aksu2018automated} are correct.
 After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
-However, the structure of the resulting attack graphs in the Netflix case was quite linear.
+The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks.
 This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
@@
 The Phpmailer \cite{phpmailer} and Samba \cite{samba} system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
-\textbf{TODO explain the result of correctness, what did you find out i.e., they are correct to our knowledge maybe show one example of an attack graph generated, also explain more the linearity thing}
 
@@
 The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute \cite{ou2006scalable}.
-% The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system .
+% The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system.
 
@@
 The total time of the attack graph generation procedure for 1000 fully connected hosts (784 seconds) outperforms Ou's results (1000 seconds).
-In the Sheyners's extended example(4 hosts, 8 atomic attacks and multiple vulnerabilites) the attack graph took 2 hours to create.
+In the Sheyners's extended example(4 hosts, 8 atomic attacks and multiple vulnerabilities) the attack graph took 2 hours to create.
 Our attack graph procedure even for the bigger number of hosts(1000) shows faster attack graph generation time.
-It however performs worse than Ingols, but that is attributed to the usage of MP attack graph which is different from ours.
-From the results we can see that Breath-first Search can be used to generate attack graphs for increasing number of services and denser connectivity in microservices architectures.
+It, however, performs worse than the generator from Ingols et al., but that is attributed to the usage of MP attack graph which is different from ours.
+From the aforementioned results, we can see that Breath-first Search can be used to generate attack graphs for an increasing number of services and denser connectivity in microservices architectures.

### 2018-09-18 paper_own_docker/chapters/method.tex
Todos in the background and minor changes in method and evaluation done

@@
 VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-However in our case, unlike hosts connected in a computer networks, these privileges are adapted to images and not virtual machines.
+However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines.
 On the other side, The keyword OS means that the host machine has been compromised.
@@
 The example is taken from the Netflix OSS Github repository.
-Netflix OSS example is a Spring Cloud based microservices architecture that enables Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
+Netflix OSS example is a Spring Cloud-based microservices architecture that enables Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
 Displayed in Figure \ref{TopologyGraph} is a subset of the example topology.
@@
 We developed this system to be used with a specific version of Docker and Docker-Compose.
-This modular structure could however be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing the Vulnerability and Topology Parsers with custom ones and making sure that their outputs conform to the input of the Attack Graph Parser.
+This modular structure could, however, be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing the Vulnerability and Topology Parsers with custom ones and making sure that their outputs conform to the input of the Attack Graph Parser.
 
-\textbf{TODO} need to rewrite the previous paragraph \\
 \subsubsection{Topology Parser}
@@
 The topology of Docker containers can be described at either runtime or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning.
+In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool.
 Docker Compose provides a docker-compose.yml file which is used for extraction of the topology of the system.
@@
 Some containers require certain privileges over the docker daemon in order to function properly.
-For example a user may want to run some hardware (web-cam \cite{webcam}) or some applications that demand higher privilege levels (Libvirt \cite{libvirt}) from Docker.
+For example, a user may want to run some hardware (web-cam \cite{webcam}) or some applications that demand higher privilege levels (Libvirt \cite{libvirt}) from Docker.
 In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
@@
 
+\begin{table*}[t]
+	\begin{center}
+		\begin{tabular}{ p{20mm}p{35mm}p{35mm}p{10mm}cp{35mm} } 
+			\hline
+			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
+
+			Netflix OSS & Combination of containers provided from Netflix.
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
+
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & \url{https://github.com/dockersamples/atsea-sample-shop-app} \\
+
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & \url{https://github.com/dockersamples/javaee-demo} \\
+
+			PHPMailer and Samba & An artificial example created from two separate containers.
+We use an augmented version for the scalability tests.
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  \url{https://github.com/opsxcq/exploit-CVE-2016-10033}
+			\url{https://github.com/opsxcq/exploit-CVE-2017-7494} \\
+
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{Microservice architecture examples analyzed by the attack graph generator.}
+	\label{table_technologies}
+
+\end{table*}
+
 \begin{itemize}
 	\item Completeness: Breadth-first Search is complete i.e. if there is a solution, Breadth-first search will find it regardless of the kind of graph.
-	\item Termination: This follows from the monotonicity property. Monotonicity is ensured if it is assumed that an attacker will
-	never need to relinquish a state \cite{ingols2006practical, ou2006scalable, ammann2002scalable}. In this implementation, each edge is traversed only once, making sure that monotonicity is preserved.
+	\item Termination: This follows from the monotonicity property.
+Monotonicity is ensured if it is assumed that an attacker will never need to relinquish a state \cite{ingols2006practical, ou2006scalable, ammann2002scalable}.
+In this implementation, each edge is traversed only once, making sure that monotonicity is preserved.
 	\item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.

### 2018-09-18 paper_own_docker/chapters/conclusion.tex
intro draft

\section{CONCLUSIONS AND FUTURE WORK}
\label{chap:conclusion}

### 2018-09-18 paper_own_docker/chapters/introduction.tex
intro draft

--- 2018-09-14 paper_own_docker/chapters/introduction.tex
@@
 the benefits of it and the challanges brought by it, like open source utilization and scurity overhead brought by networks and docker security issues.
-Microservices have popularized two main concepts in the software engineering community.
-The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in lightweight containers.
-As a result the systems are deployed as networks of communicating micorservices.
-Each microservice achieves an independent task.
+The utilization of microservices have popularized two main concepts in the software engineering community.
+The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{bibid}.
+As a result, the systems are deployed as networks of communicating micorservices.
+For their lightweight and operating-system level virtualization \cite{what is the container hype}, the containerization frameworks like \textit{Docker} \cite{bibid}, are a high performance alternative to hypervisors \cite{nw}.
+The second often-used concept in the domain of microservices development is DevOps \cite{bibid}.
+DevOps enable practices in which full automation of the deployment process is achieved.
+In the course of this, end-to-end automated packaging and deployment  is a vital part of microservices development.
+In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements}.
+The increasing communication end-points among the microservices \cite{ahmadvand2016requirements}, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley}.
+In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordy2014dag}.
+Following the DevOps mentality, we propose an automated method that can be integrated into continuous delivery systems to generate attack graphs.
+
 % threat modeling as a way to systmatically analyze threats...
@@
 
+Security threat models are widely used to assess threats facing a system \cite{kordy2014dag}.
+Not only are they appealing to the practitioners as they provide a visual presentation of possible attack paths on a system, but also to scientists, since they are well formalized (syntax and semantics \cite{mauw2005foundations,jha2002two}).
+Such formalism enables quantitative and qualitative analysis of the risk, cost, and likelihood of the attacks, which affect the defense strategy.
+In computer networks, attack graphs \cite{sheyner2002automated,ou2006scalable} are the dominant threat model to inspect the security aspects of a network.
+They help analysts to carefully analyze a system connections and detect the most vulnerable parts of the system.
+An attack graph depicts the actions that an attacker uses in order to reach their goal.
+Normally, experts (e.g., red teams) manually construct attack graphs.
+The manual process is time-consuming, error-prone and does not address the complexity of modern infrastructure.
+%Within the last 15 years, there have been some proposals of approaches [e.g., 5-9] to automate the generation of attack graphs and attack trees in the domain of network security.
+
 % the problem: summing it up and the solution
@@
 % contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
+Previous work has dealt with automated  attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated,  sheyner2003tools, ou2006scalable}.
+In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.
+Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}.
+However these tools alone are not sufficient to analyze the security of an entire network, and the possible composition of multiple vulnerability exploitation as an attack path \cite{sheyner2002automated}.
+
+To the best of our knowledge, an automated attack graph generation for microservice architectures was not tackled by any previous work.
+To that end, in this paper we extend the advancement made in the computer networks field to the domain of microservices.
+Therefore the contribution of this paper is as follows.
+\begin{itemize}
+\item We propose attack graphs as a new artifact of the continuous delivery systems.
+We present an approach, based on methods from computer networks, to automatically generate attack graphs for microservice-based architectures that are deployed as containers.
+\item We present the technical details of an extensible tool that implements our approach. The tool is available for use at\footnote{}.
+\item An empirical evaluation of the efficiency of our tool in generating attack graphs of real-world systems.
+\end{itemize}
+
 % structure
 
-Attack graphs are a popular way of examining security aspects of network.
-They help security analysts to carefully analyze a system connection and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach his goal.
-
-Statistics. 
-https://banyanops.com/blog/analyzing-docker-hub/
-https://blog.acolyer.org/2017/04/03/a-study-of-security-vulnerabilities-on-docker-hub/
-http://dance.csc.ncsu.edu/papers/codaspy17.pdf \cite{shu2017study}
-
-They do not offer any performance comparison between different topologies.
-
-In this work, we first get familiar with the basic attack graph and microservice terminology in Section \ref{chap:background}, then present the architecture of our system in Section \ref{chap:method}, perform evaluation in Section \ref{chap:eval} and at the end present what others did in the area in section \ref{chap:related_work}, a conclusion in Section \ref{chap:conclusion} and future work directions in Section \ref{chap:future_work}.
+The structure of this paper is as follows.
+We introduce the preliminaries needed for this paper in Section \ref{chap:background}.
+We, then, present our approach in Section \ref{chap:method}, and its evaluation in Section \ref{chap:eval}.
+We discuss related work in Section \ref{chap:related_work}.
+Lastly, conclusions and future work are discussed in Section \ref{chap:conclusion}.

### 2018-09-18 paper_own_docker/chapters/conclusion.tex
intro refrences and conclusions

@@
 \label{chap:conclusion}
+
+Microservices are a promising architectural style that advocate practitioners to build systems as a group of connected small services.
+Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns.
+In this paper, we proposed to use automated attack graph generation as part of the practices of developing microservice-based architectures.
+Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services.
+The manual constriction of attack graphs is an error-prone, resource consuming activity, hence, automating this construction does not only guarantee efficient construction but also complies with the spirit of DevOps practices.
+We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big mircroservice-based systems.
+
+As a future work, we plan to extend this work to support more frameworks that are used in microservices systems.
+We also plan to study the possible analysis of the resulting attack graphs for purposes of attack detection, and post-postmortem forensics investigations.

### 2018-09-18 paper_own_docker/chapters/introduction.tex
intro refrences and conclusions

@@
 Microservices, as a new approach to manage the complexity of modern applications, are increasingly adopted in real-world systems. The new architectural style 
-follows the Unix fundamental principles  of decomposing systems into small programs \cite{Unix ideas [115]:} that each fulfills only one cohesive task and can work together using universal interfaces.
-Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{[Microservices.
-Martin Fowler(2015)]}.
-The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{}.
+follows the foundational principle of Unix  that decomposes systems into small programs \cite{wolff2016microservices} that each fulfills only one cohesive task and can work together using universal interfaces.
+Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{microservicesfrowler}.
+The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{newman2015building}.
 However, clearly, other qualities like the network utilization, and the security are negatively affected \cite{ahmadvand2016requirements}.
@@
 This shift is  motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts.
-We see microservice-based systems in domains of video streaming, social networks, logistics, internet of things \cite{internet}, and smart cities \cite{smartcity}.
+We see microservice-based systems in domains of video streaming, social networks, logistics, Internet of things \cite{butzin2016microservices}, smart cities \cite{krylovskiy2015designing}, and security-critical systems \cite{fetzer2016building}.
 
@@
 The utilization of microservices have popularized two main concepts in the software engineering community.
-The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{bibid}.
+The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{jaramillo2016leveraging}.
 As a result, the systems are deployed as networks of communicating micorservices.
-For their lightweight and operating-system level virtualization \cite{what is the container hype}, the containerization frameworks like \textit{Docker} \cite{bibid}, are a high performance alternative to hypervisors \cite{nw}.
-The second often-used concept in the domain of microservices development is DevOps \cite{bibid}.
+For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative to hypervisors \cite{kratzke2017microservices}.
+The second often-used concept in the domain of microservices development is DevOps \cite{cerny2018contextual}.
 DevOps enable practices in which full automation of the deployment process is achieved.
@@
 In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements}.
-The increasing communication end-points among the microservices \cite{ahmadvand2016requirements}, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley}.
+The increasing communication end-points among the microservices \cite{ahmadvand2016requirements}, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley,bui2015analysis}.
 In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordy2014dag}.

### 2018-09-18 paper_own_docker/chapters/conclusion.tex
fixes here and there

@@
 
-Microservices are a promising architectural style that advocate practitioners to build systems as a group of connected small services.
+Microservices are a promising architectural style that advocate practitioners to build systems as a group of small connected  services.
 Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns.
@@
 The manual constriction of attack graphs is an error-prone, resource consuming activity, hence, automating this construction does not only guarantee efficient construction but also complies with the spirit of DevOps practices.
-We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big mircroservice-based systems.
+We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.
 

### 2018-09-18 paper_own_docker/chapters/abstract.tex
checks here and there

@@
-Microservices are increasingly dominating the field of service systems, among their many characterstics, practices are technology heterogeneity and reuse and network interfaces.
-Therefore, with the increase of utilizing third-party components, the potential vulanrabilities existing in a microservice-based system increase.
+Microservices are increasingly dominating the field of service systems, among their many characteristics, practices are technology heterogeneity and reuse and network interfaces.
+Therefore, with the increase of utilizing third-party components, the potential vulnerabilities existing in a microservice-based system increase.
 Based on components dependency, these vulnerabilities lead to exposing critical assets of such systems.
@@
 In this paper, we propose the utilization of attack graphs as a part of the automated development infrastructure used in microservices-based systems.
-To that end, we relate microservices to network nodes, and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks.
-We present a complete solution that can be easily embeded into the continuous delivery systems, and show with real-world use cases its efficiency and scalability.
+To that end, we relate microservices to network nodes and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks.
+We present a complete solution that can be easily embedded into the continuous delivery systems, and show with real-world use cases its efficiency and scalability.
 %Breath-first Search (BFS) based method for attack graph generation and security analysis of microservice architectures using Docker

### 2018-09-18 paper_own_docker/chapters/introduction.tex
checks here and there

@@
 %intro about the new paradiagm of mirocservices its benefits and new oppurnties, maybe its utilization in secuirty/ safety critical systems
-Microservices, as a new approach to manage the complexity of modern applications, are increasingly adopted in real-world systems. The new architectural style 
-follows the foundational principle of Unix  that decomposes systems into small programs \cite{wolff2016microservices} that each fulfills only one cohesive task and can work together using universal interfaces.
+Microservices, a recent approach to manage the complexity of modern applications, are increasingly adopted in real-world systems.
+The new architectural style follows the foundational principle of Unix that decomposes systems into small programs \cite{wolff2016microservices} that each fulfills only one cohesive task and can work together using universal interfaces.
 Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{microservicesfrowler}.
 The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{newman2015building}.
-However, clearly, other qualities like the network utilization, and the security are negatively affected \cite{ahmadvand2016requirements}.
-Balancing the trades-off among these factors derive the decision of using microservices in industry.
-That said, a non exhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
+However, other qualities like the network utilization and the security are negatively affected \cite{ahmadvand2016requirements}.
+Balancing the trade-off among these factors derive the decision of using microservices in industry.
+That said, a nonexhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
 This shift is motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts.
@@
 the benefits of it and the challanges brought by it, like open source utilization and scurity overhead brought by networks and docker security issues.
-The utilization of microservices have popularized two main concepts in the software engineering community.
+The utilization of microservices has popularized two main concepts in the software engineering community.
 The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{jaramillo2016leveraging}.
-As a result, the systems are deployed as networks of communicating micorservices.
+As a result, the systems are deployed as networks of communicating microservices.
 For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative to hypervisors \cite{kratzke2017microservices}.
@@
 In computer networks, attack graphs \cite{sheyner2002automated,ou2006scalable} are the dominant threat model to inspect the security aspects of a network.
-They help analysts to carefully analyze a system connections and detect the most vulnerable parts of the system.
+They help analysts to carefully analyze system connections and detect the most vulnerable parts of the system.
 An attack graph depicts the actions that an attacker uses in order to reach their goal.
-Normally, experts (e.g., red teams) manually construct attack graphs.
+Typically, experts (e.g., red teams) manually construct attack graphs.
 The manual process is time-consuming, error-prone and does not address the complexity of modern infrastructure.
@@
 % contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
-Previous work has dealt with automated  attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated,  sheyner2003tools, ou2006scalable}.
+Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated,  sheyner2003tools, ou2006scalable}.
 In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.
 Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}.
-However these tools alone are not sufficient to analyze the security of an entire network, and the possible composition of multiple vulnerability exploitation as an attack path \cite{sheyner2002automated}.
+However these tools alone are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
 
 To the best of our knowledge, an automated attack graph generation for microservice architectures was not tackled by any previous work.
-To that end, in this paper we extend the advancement made in the computer networks field to the domain of microservices.
+To that end, in this paper, we extend the advancement made in the computer networks field to the domain of microservices.
 Therefore the contribution of this paper is as follows.

### 2018-09-19 paper_own_docker/chapters/method.tex
one small run on the first sections of the method

@@
 \label{chap:method}
+We already defined an attack graph.
+We, now, look at how the existing components of attack graph generation for computer networks map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}.
+We then, in Subsection \ref{chap:technical}, present the tools that we use to achieve this mapping and present an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
 
-\begin{figure}
+\subsection{From Network Nodes to Microservices}
+\label{chap:mapping}
+% abit reptative 
+In our work, we adapt already existing attack graph generation methods from computer networks to the microservices ecosystem.
+In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
+In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology.
+We then modify the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}: nodes, edges, privilege levels, pre- and postconditions to match our use-case.
+We illustrate the whole idea  by demonstrating a small example.
+
+Docker is one of the most popular and used containerization frameworks currently available.
+In Docker, a distinction is being made between the terms \textit{image}, \textit{container} and \textit{service}.
+An \textit{image} is an executable package that includes everything needed to run an application, a \textit{container} is a runtime instance of an image, and a \textit{service} represents a container in production.
+A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}.
+In our work, we construct attack graphs by statically analyzing the topology of the containers, hence, we treat these terms equally.
+
+Privileges play a central role in the generation if attack graphs.
+Traditionally, the privileges are modeled as a hierarchy that varies in the access type (\textit{User, Admin}), and the access scope (Virtual machine VOS, host machine OS).
+The exhaustive list of privileges, that are used in this paper, are: \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}.
+VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
+However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines.
+On the other side, the keyword OS means that the  host machine can be controlled by a user who has this privilege.
+Since VOS are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
+None means that no privilege is obtained, User means only a subset of user level privileges are available, while Admin grants control over the whole system.
+
+\textbf{TODO this paragraph is very hard to follow.
+it is very important, i tried a bit with it but please try to re-phrase..
+what is starting node and the end node of the edge and how to decide to add an edge.
+Maybe try to rephrase by saying between a two connected images we add a node if .......}\\
+As mentioned earlier, \textit{nodes} and \textit{edges} are the basic building blocks of an attack graph.
+\textit{Nodes} are represented as a combination of docker images and their respective compromise level (presented as the privilege granted to the attacker), while edges are connections between images represented by the vulnerabilities that are being exploited as descriptors.
+The starting node of an edge denotes the image from which the attack is performed and the required privilege level to exploit a given vulnerability.
+The end node of an edge is the image which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation.
+In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
+Once attackers exploits this vulnerability, they gain the privilege of the target container as a postcondition and an edge is added to the attack graph.
+Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
+The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.
+
+\subsubsection{Example}
+
+\textbf{TODO shorten all the captions, they should be one line, and add all the description to the text. this goes to all the figures and table..}\\
+\begin{figure*}[!h]
 	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{\columnwidth}
 		\centering
-		\includegraphics[width=.6\linewidth]{./images/Topology_graph}
+		\includegraphics[width=.5\linewidth]{./images/Topology_graph}
 		\caption{}
@@
 	\end{subfigure}
-
-	\begin{subfigure}[b]{0.5\textwidth}
+	\hfill
+	\begin{subfigure}[b]{\columnwidth}
 		\centering
-		\includegraphics[width=.6\linewidth]{./images/Attack_graph}
+		\includegraphics[width=.5\linewidth]{./images/Attack_graph}
 		\caption{}
@@
 The topology and attack graphs are a subset of the real topology and attack graphs from the Netflix OSS example.}
-\end{figure}
-
-Up to this point, we formally defined what an attack graph is.
-Here, we first look at how the existing components of attack graph generation for computer networks map into a microservice environment and provide a small example in Subsection \ref{chap:mapping}.
-We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
-
-\subsection{Mapping attack graphs from network to microservice perspective}
-\label{chap:mapping}
-
-In our work, we try to translate already existing attack graph generation work from computer networks into the microservices ecosystem.
-In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
-In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology.
-We then modify the attack graph concepts mentioned above for our use-case (nodes, edges, privilege levels, pre- and postconditions).
-In the end, we see how this translation works in practice by demonstrating a small example.
-
-Docker is one of the most popular and used microservice frameworks currently available.
-In Docker, a distinction is being made between the terms image, container and service.
-An image is an executable package that includes everything needed to run an application, a container is a runtime instance of an image and service represents a container in production.
-A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}.
-In our work, we treat these terms equally, since we are doing a static and not runtime attack graph analysis.
-
-Privileges play a central role in this attack graph generation.
-We model the privileges in a hierarchy.
-The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin).
-VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines.
-On the other side, The keyword OS means that the host machine has been compromised.
-Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
-None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.
-
-As mentioned above, nodes and edges are the basic building blocks of an attack graph.
-Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors.
-The starting node of an edge denotes the container from which the attack is performed and the privilege level that an attacker needs to have to exploit a given vulnerability.
-The end node of an edge is the container which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation.
-In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
-Once an attacker exploits this vulnerability, he gains the privilege of the target container as a postcondition and an edge is added to the attack graph.
-Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
-The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.
-
-\subsubsection{Example}
+\end{figure*}
 

### 2018-09-20 paper_own_docker/chapters/method.tex
TODOs done

@@
 
-\textbf{TODO this paragraph is very hard to follow.
-it is very important, i tried a bit with it but please try to re-phrase..
-what is starting node and the end node of the edge and how to decide to add an edge.
-Maybe try to rephrase by saying between a two connected images we add a node if .......}\\
 As mentioned earlier, \textit{nodes} and \textit{edges} are the basic building blocks of an attack graph.
-\textit{Nodes} are represented as a combination of docker images and their respective compromise level (presented as the privilege granted to the attacker), while edges are connections between images represented by the vulnerabilities that are being exploited as descriptors.
-The starting node of an edge denotes the image from which the attack is performed and the required privilege level to exploit a given vulnerability.
-The end node of an edge is the image which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation.
-In order for an attacker to exploit a given vulnerability, certain preconditions have to be met.
-Once attackers exploits this vulnerability, they gain the privilege of the target container as a postcondition and an edge is added to the attack graph.
+\textit{Nodes} are represented as a combination of docker images and their respective compromise levels (presented as privileges granted to the attacker), while directed edges represent attacks from start nodes (images with their current privileges) to end nodes (exploitable adjacent images with gained privileges).
+In addition, vulnerabilities that could be exploited in the end nodes serve as edge descriptors.
+
+In order for an attacker to exploit a given vulnerability, certain preconditions in the start node have to be met.
+Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a postcondition and a directed edge is added between them.
 Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
@@
 
-	\caption[Two numerical solutions]{(a) Example topology graph where each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers.
-(b) Example resulting attack graph, where nodes correspond to a pair of container plus privilege, while edges are atomic attacks.
-The topology and attack graphs are a subset of the real topology and attack graphs from the Netflix OSS example.}
+	\caption[Two numerical solutions]{Reduced Netflix OSS example (a) Example topology graph  (b) Example resulting attack graph}
 \end{figure*}
@@
 Netflix OSS example is a Spring Cloud-based microservices architecture that enables Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
-Displayed in Figure \ref{TopologyGraph} is a subset of the example topology.
+Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge denotes a connection between two containers.
 The topology consists of "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
 According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resiliency, security, and more \cite{netflixzuul}, while Eureka is a REST (Representational State Transfer) based service that is primarily used in the AWS cloud for locating services for the purpose of load balancing and failover of middle-tier servers \cite{netflixeureka}.
-In Figure \ref{AttackGraph} we can see a part of the resulting attack graph.
+In Figure \ref{AttackGraph} we can see a part of the resulting attack graph, where a node corresponds to a pair of container plus its privilege, while an edge represents an atomic attack.
 Parts of both graphs have been intentionally omitted to reduce complexity.
@@
 \label{chap:technical}
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser (Figure \ref{AttackGraphSystem}).
+ Figure \ref{AttackGraphSystem} gives an overview of the attack graph generator system.
+In the figure, the rectangles denote the main components of the system, while the arrows describe the flow of the system and the files are the intermediate products.
+Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser.
 The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
@@
 	\includegraphics[scale=0.9]{./images/AttackGraphSystem}
-	\caption{Our Attack Graph System.
-The rectangles denote the main components of the system: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The arrows describe the flow of the system and the files are the intermediate products.}
+	\caption{Overview of the Attack Graph Generator System}
 	\label{AttackGraphSystem}
@@
 
-	\caption{Breadth-first Search algorithm for generating an attack graph.}
+	\caption{BFS algorithm for attack graph generation}
 	\label{BFSalgorithm}
@@
 
-	\caption{Microservice architecture examples analyzed by the attack graph generator.}
+	\caption{Microservice architecture examples analyzed by the attack graph generator}
 	\label{table_technologies}

### 2018-09-20 paper_own_docker/chapters/evaluation.tex
TODOS in the method

@@
 The Phpmailer \cite{phpmailer} and Samba \cite{samba} system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
+\begin{table*}[t]
+	\begin{center}
+		\begin{tabular}{ p{20mm}p{35mm}p{35mm}p{10mm}cp{35mm} } 
+			\hline
+			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
 
+			Netflix OSS & Combination of containers provided from Netflix.
+& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
+
+			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & \url{https://github.com/dockersamples/atsea-sample-shop-app} \\
+
+			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & \url{https://github.com/dockersamples/javaee-demo} \\
+
+			PHPMailer and Samba & An artificial example created from two separate containers.
+We use an augmented version for the scalability tests.
+& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  \url{https://github.com/opsxcq/exploit-CVE-2016-10033}
+			\url{https://github.com/opsxcq/exploit-CVE-2017-7494} \\
+
+			\hline
+		\end{tabular}
+	\end{center}
+
+	\caption{Microservice architecture examples analyzed by the attack graph generator}
+	\label{table_technologies}
+
+\end{table*}
 \begin{table*}

### 2018-09-20 paper_own_docker/chapters/method.tex
remove TODO
TODOS in the method

@@
 In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
-In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology.
+In this subsection, we start first by shortly introducing a famous framework (Docker) and some of its terminology.
 We then modify the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}: nodes, edges, privilege levels, pre- and postconditions to match our use-case.
@@
 Privileges play a central role in the generation if attack graphs.
-Traditionally, the privileges are modeled as a hierarchy that varies in the access type (\textit{User, Admin}), and the access scope (Virtual machine VOS, host machine OS).
+Traditionally, the privileges are modeled as a hierarchy that varies in the access level (\textit{User, Admin}), and the access scope (virtual machine VOS, host machine OS).
 The exhaustive list of privileges, that are used in this paper, are: \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}.
 VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines.
-On the other side, the keyword OS means that the  host machine can be controlled by a user who has this privilege.
-Since VOS are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}.
-None means that no privilege is obtained, User means only a subset of user level privileges are available, while Admin grants control over the whole system.
+However in our case, unlike hosts connected in a computer network, these privileges refer to images and not virtual machines.
+On the other side, the keyword \textit{OS} means that the  host machine can be controlled by a user who has this privilege.
+Since \textit{VOS} are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of the hierarchy \cite{aksu2018automated}.
+\textit{None} means that no privilege is obtained, \textit{User} means only a subset of user level privileges are granted, and \textit{Admin} grants control over the whole system.
 
-As mentioned earlier, \textit{nodes} and \textit{edges} are the basic building blocks of an attack graph.
-\textit{Nodes} are represented as a combination of docker images and their respective compromise levels (presented as privileges granted to the attacker), while directed edges represent attacks from start nodes (images with their current privileges) to end nodes (exploitable adjacent images with gained privileges).
-In addition, vulnerabilities that could be exploited in the end nodes serve as edge descriptors.
+As mentioned earlier, the \textit{nodes} and the \textit{edges} are the basic building blocks of an attack graph.
+A \textit{node} represents  a combination of a docker image and its respective compromise levels (expressed as privileges obtained by the attacker).
+A directed \textit{edge} between two nodes represents an attack step from one node (a compromised image with a certain privilege gained by the attacker) to another node (adjacent exploitable image with the gained privileges).
+Each edge is typed with the vulnerability (CVE) that could be exploited in the end node.
 
-In order for an attacker to exploit a given vulnerability, certain preconditions in the start node have to be met.
-Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a postcondition and a directed edge is added between them.
+In order for attackers to exploit a given vulnerability, they need to have certain \textit{preconditions}, i.e, the minimum privileges needed to exploit \cite{aksu2018automated}.
+Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a \textit{postcondition} and a directed edge is added between them.
 Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
@@
 
-\textbf{TODO shorten all the captions, they should be one line, and add all the description to the text. this goes to all the figures and table..}\\
 \begin{figure*}[!h]
@@
 The example is taken from the Netflix OSS Github repository.
-Netflix OSS example is a Spring Cloud-based microservices architecture that enables Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
-Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge denotes a connection between two containers.
-The topology consists of "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
-According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resiliency, security, and more \cite{netflixzuul}, while Eureka is a REST (Representational State Transfer) based service that is primarily used in the AWS cloud for locating services for the purpose of load balancing and failover of middle-tier servers \cite{netflixeureka}.
-In Figure \ref{AttackGraph} we can see a part of the resulting attack graph, where a node corresponds to a pair of container plus its privilege, while an edge represents an atomic attack.
+Netflix OSS example is a Spring Cloud-based microservices architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
+Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge is a connection between two containers, if one calls the other.
+The topology consists of an "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
+According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resiliency, and security functionalities.
+Eureka is a REST (Representational State Transfer) based service that is primarily used in the cloud for locating services for the purpose of load balancing and fail-over of middle-tier servers.
+In Figure \ref{AttackGraph} we can see a part of the corresponding attack graph, where a node is a pair of the image and its privilege, while an edge represents an atomic attack.
 Parts of both graphs have been intentionally omitted to reduce complexity.
 An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gain USER privilege.
-Then with this USER privilege, it can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain ADMIN privilege.
+With this USER privilege, an attacker can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain ADMIN privilege.
 Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 via another crafted image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2017-7600}} and gain ADMIN privilege.
@@
 \label{chap:technical}
- Figure \ref{AttackGraphSystem} gives an overview of the attack graph generator system.
+
+ Figure \ref{AttackGraphSystem} gives an overview of the attack graph generator.
 In the figure, the rectangles denote the main components of the system, while the arrows describe the flow of the system and the files are the intermediate products.
-Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser.
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
+Our attack graph generator is composed of three main components: \textit{Topology Parser, Vulnerability Parser and Attack Graph Generator}.
+The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Generator, the Vulnerability Parser scans the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
+In the following subsections, we first have a look into the system requirements, then describe each component in more details.
 
-In the following subsections, we first have a look into the system requirements, then describe each of the parsers in more detail and finally examine the characteristics of the Breath-first Search graph transversal algorithm.
+The generator is developed and tested for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
+Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of a multi-container applications.
+It provides a static configuration file that specifies the system containers, networks, and ports.
+Clair and ClairCtl \footnote{\url{https://github.com/coreos/clair}}  are used for vulnerabilities scanning.
+The generator is written in Python 3.6.
+Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing.
 
+\textbf{TODO rename the attack graph parser in the box to Attack graph Generator}
 \begin{figure}
@@
 
-Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
-Docker Compose is a tool for defining and running multi-container Docker applications \cite{dockercompose}.
-It provides a static configuration file that specifies the system containers, networks, ports etc.
-The code is written in Python 3.6, and we use Clair \cite{clair} and Clairctl \cite{clairctl} for vulnerabilities scanning.
-
-We developed this system to be used with a specific version of Docker and Docker-Compose.
-This modular structure could, however, be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing the Vulnerability and Topology Parsers with custom ones and making sure that their outputs conform to the input of the Attack Graph Parser.
-
 \subsubsection{Topology Parser}
@@
 
-In order to generate an attack graph of a given system, we require an arrangement of its components and connections described by a system topology.
-The topology of Docker containers can be described at either runtime or statically by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool.
-Docker Compose provides a docker-compose.yml file which is used for extraction of the topology of the system.
+In order to generate an attack graph of a given system, we require an arrangement of its components and connections described as a system topology.
+The topology of Docker containers can be described either at  runtime or at design time by using Docker Compose.
+In our case, since we are doing static attack graph analysis, we use Docker Compose to extract the topology.
+Docker Compose provides a  file (docker-compose.yml) which is used for describes the orchestration of the services.
 However different versions of docker-compose.yml, use different syntax.
-For example, older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers.
-In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.
+For example, older versions use the deprecated keyword "\textit{link}", while newer ones use exclusively "\textit{networks}", to denote a connection between two images.
+In this work, we use the keyword "\textit{networks}" as an indicator that a connection between two images exists.
 
-However, in the majority of cases, in order for an application to be useful, it has to communicate with the outside world.
-This is usually done by using publishing ports.
+In the majority of cases, for an application to be useful, it communicates with the outside world, i.e, it has end points that can be used by the outer network.
+In Docker, this is usually done by using publishing ports.
 This is the case in both computer networks, as well as in microservice architectures.
 
-Another consideration that we take into account is the privileged access.
-Some containers require certain privileges over the docker daemon in order to function properly.
-For example, a user may want to run some hardware (web-cam \cite{webcam}) or some applications that demand higher privilege levels (Libvirt \cite{libvirt}) from Docker.
+Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}} \cite{libvirt}.
+Some containers obtain certain privileges that grant them control over the docker daemon in order to function properly.
+For example, a user may want to run some hardware (e.g., web-cam) or some applications that demand higher privilege levels  from Docker.
 In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
@@
 Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
+
+\subsubsection{Vulnerability Parser}
+\label{chap:vulnerability_p}
+
+In the preprocessing step, we use Clair to generate the vulnerabilities of a given image.
+Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing \textit{CVE-ID}, a description and attack vector for each vulnerability.
+An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
+We collect the fields in the attack vector which are,  as described by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
+Unfortunately, Clair does not provide a command line interface to analyze a docker image.
+We use another tool, i.e.,  Clairctl  to analyze a complete docker image.
 
@@
 
-\subsubsection{Vulnerability Parser}
-\label{chap:vulnerability_p}
-
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given container.
-Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability \cite{clair}.
-An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-The fields in the attack vector as described by the National Vulnerability Database(NVD) \cite{booth2013national} are: Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
-Unfortunately, Clair does not provide with a ready to use interface to analyze a docker image.
-As a result, we use Clairctl \cite{clairctl} in order to analyze a complete docker image.
-
 \subsubsection{Attack Graph Generator}
@@
 
-After the topology file is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions.
+After the topology  is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
+Here, we first pre-process the vulnerabilities and convert them into sets of pre- and postconditions.
 In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
@@
 This results in a list of container vulnerabilities with their preconditions and postconditions.
+\textbf{TODO give an example of the attack rule and refer to the source of these rules}
 
@@
 After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into the Breadth-first Search algorithm (BFS).
+Together with the topology, they are feed into a Breadth-first Search algorithm (BFS).
 Breadth-first Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before diving deeper into the graph.
-Pseudocode of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph.
+A pseudo-code of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
+The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph \textbf{TODO please explain what is cont expl, priv acc and refer to them in the text}.
 The algorithm first initializes the nodes, edges, queue and the passed nodes.
@@
 The algorithm terminates when the queue is empty.
-Furthermore, BFS is characterized by the following properties:
-
-\begin{table*}[t]
-	\begin{center}
-		\begin{tabular}{ p{20mm}p{35mm}p{35mm}p{10mm}cp{35mm} } 
-			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
-
-			Netflix OSS & Combination of containers provided from Netflix.
-& Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
-
-			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & \url{https://github.com/dockersamples/atsea-sample-shop-app} \\
-
-			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & \url{https://github.com/dockersamples/javaee-demo} \\
-
-			PHPMailer and Samba & An artificial example created from two separate containers.
-We use an augmented version for the scalability tests.
-& PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 &  \url{https://github.com/opsxcq/exploit-CVE-2016-10033}
-			\url{https://github.com/opsxcq/exploit-CVE-2017-7494} \\
-
-			\hline
-		\end{tabular}
-	\end{center}
-
-	\caption{Microservice architecture examples analyzed by the attack graph generator}
-	\label{table_technologies}
-
-\end{table*}
+Furthermore, BFS is characterized by the following properties.
+\textbf{TODO: add line numbers to the algo and refer to those numbers in the text.}
 
@@
 In this implementation, each edge is traversed only once, making sure that monotonicity is preserved.
-	\item Time Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
+	\item  Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
 \end{itemize}

### 2018-09-20 paper_own_docker/chapters/abstract.tex
fixes here and there

@@
-Microservices are increasingly dominating the field of service systems, among their many characteristics, practices are technology heterogeneity and reuse and network interfaces.
-Therefore, with the increase of utilizing third-party components, the potential vulnerabilities existing in a microservice-based system increase.
-Based on components dependency, these vulnerabilities lead to exposing critical assets of such systems.
+Microservices are increasingly dominating the field of service systems, among their many characteristics are technology heterogeneity, communicating small services, and automated deployment.
+Therefore, with the increase of utilizing third-party components distributed as images, the potential vulnerabilities existing in a microservice-based system increase.
+Based on components dependency, these vulnerabilities may lead to exposing critical assets of systems.
 Similar problems have been tackled in computer networks communities.
-In this paper, we propose the utilization of attack graphs as a part of the automated development infrastructure used in microservices-based systems.
+In this paper, we propose the utilization of attack graphs as a part of the continuous delivery infrastructure used in microservices-based systems.
 To that end, we relate microservices to network nodes and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks.

### 2018-09-20 paper_own_docker/chapters/background.tex
fixes here and there

@@
 
-We first start by introducing the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
-Afterward in Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools that generate vulnerabilities for a single host.
-At the end in Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
+We start by introducing the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
+In Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools to scan a single host for vulnerabilities.
+In Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
 

### 2018-09-20 paper_own_docker/chapters/background_attack_graphs.tex
fixes here and there

--- 2018-09-04 paper_own_docker/chapters/background_attack_graphs.tex
@@
 
+Attack graphs \cite{sheyner2002automated} are a popular way of examining network security weaknesses.
+They help analysts to carefully analyze a given system and detect its vulnerable parts.
 The definition of attack graphs may vary but it is essentially a directed graph that consists of nodes and edges with various representations.
@@
 An initial state represents the state from where the attacker starts the attack and through a chain of atomic attacks tries to reach one of the success states \cite{sheyner2002automated}.
-
 Ou et al.
@@
 Each fact node is labeled with a logical statement in the form of a predicate applied to its arguments, while each derivation node is labeled with an interaction rule that is used for the derivation step.
-The edges in the graph represent the "depends on" relation \cite{ou2006scalable}.
-
+The edges in the graph represent a "depends on" relation \cite{ou2006scalable}.
 Ingols et al.
@@
 
-In our work we define attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
+In this paper, we define attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
 \cite{ingols2006practical}.

### 2018-09-20 paper_own_docker/chapters/background_microservices.tex
fixes here and there

@@
 
-As real-world software increases in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.
+As real-world software grows in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.
 A software application whose modules cannot be executed independently is called a monolith.
-Monoliths are characterized by tight coupling, vertical scaling and strong dependence.
+Monolithic systems  are characterized by tight coupling, vertical scaling and strong dependence \cite{microservicesfrowler}.
 Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
 However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
-The novel term "microservices" was first introduced in 2011 at an architectural workshop in order to bridge a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
+The novel term "microservices" was first introduced in 2011 at an architectural workshop in order to propose a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
 In the microservices paradigm, multiple services are split into very basic units which are task oriented.
@@
 a microservice is a cohesive, independent process interacting via messages.
-These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
-Microservice architectures provide us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability among other benefits \cite{newman2015building}.
+These microservices constitute as a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
+Microservice architectures benefit us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability \cite{newman2015building}.
 However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.

### 2018-09-20 paper_own_docker/chapters/evaluation.tex
fixes here and there

@@
 Real-world microservice systems are composed of many containers that run different technologies with various degrees of connectivity among each other.
-This raises the need for a robust and scalable attack graph system.
+This raises the need for a robust and scalable attack graph generator.
 In Subsection \ref{chap:heterogenious_systems}, we first show different microservice architectures on which our system was tested on.
@@
 \label{chap:heterogenious_systems}
-
-Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities.
-Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-In order to do this, we tested our system on some real and slightly modified Github examples as described in Table \ref{table_technologies}.
-Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties(topologies, technologies, vulnerabilities) and coming from different usage domains.
-We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging.
-The resulting examples are as follows: NetflixOSS \cite{netflixoss}, Atsea Sample Shop App \cite{atsea} and JavaEE demo \cite{java}.
-NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses Spring Cloud, Netflix Ribbon, Netflix Eureka etc.
-Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and that uses Spring Boot, React, NGINX and PostgreSQL.
-JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
-We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
-\cite{aksu2018automated} are correct.
-After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
-The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks.
-This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
-Therefore based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
-All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property.
-Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed.
-The Phpmailer \cite{phpmailer} and Samba \cite{samba} system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
 \begin{table*}[t]
@@
 \end{table*}
+
+Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities.
+Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
+In order to do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}.
+Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains.
+We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging.
+The resulting examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
+NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses many tools like Spring Cloud, Netflix Ribbon, and Netflix Eureka.
+Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL.
+JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
+We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
+\cite{aksu2018automated} are \textit{correct}.
+After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
+The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks.
+This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
+Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
+All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property.
+Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed.
+The Phpmailer and Samba  system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
+
+\subsection{Scalability evaluation}
+\label{chap:scalability_eval}
+
 \begin{table*}
@@
 
-	\caption{Scalability experiments with the graph characteristics and execution times. The times are given in seconds.}
+	\caption{Scalability results with the graph characteristics and execution times in seconds.}
 
@@
 \end{table*}
-
-\subsection{Scalability evaluation}
-\label{chap:scalability_eval}
-
 Extensive scalability study of attack graph generators is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
@@
 All of these components contribute to the execution time of a given algorithm.
-Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods.
-In this case, we compare our system to existing work by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
+Even though the definitions of an attack graph differ, we hope to reach a comprehensive comparison with current methods.
+In this case, we compare our system to existing work in computer networks by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
 In the following, we first look at three works and their scalability evaluation results.
@@
 Sheyner et al.
-test their system in both small and extended examples.
+\cite{sheyner2002automated} test their system in both small and extended examples.
 The attack graph in the larger example has 5948 nodes and 68364 edges.
 The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-The authors claim that the performance bottleneck is inside the graph generation procedure \cite{sheyner2002automated}.
-
+The authors claim that the performance bottleneck is inside the graph generation procedure.
 Ingols et al.
-tested their system on a network of 250 hosts.
-They afterward continued the study on a simulated network of 50000 hosts in under 4 minutes \cite{ingols2006practical}.
+\cite{ingols2006practical} tested their system on a network of 250 hosts.
+They afterward continued the study on a simulated network of 50000 hosts in under 4 minutes.
 Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
 In addition to this, missing an explanation of how the hosts are connected, does not make it directly comparable to our method.
-
 Ou et al.
-provide some more extended study where they test their system(MulVAL) on more examples.
+\cite{ou2006scalable} provide some more extended study where they test their system (MulVAL) on more examples.
 They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute \cite{ou2006scalable}.
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute .
 % The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system.
@@
 In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
-We extended this example and artificially made fully connected topologies of 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system.
-The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.
-In our tests, we report the total execution time as well as its components times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
+We extended this example and artificially made fully connected topologies of \textit{20, 50, 100, 500 and 1000} Samba containers to test the scalability of the system.
+The Phpmailer container has \textit{181} vulnerabilities, while the Samba container has \textit{367} vulnerabilities detected by Clair.
+In our tests, we report the total execution time as well as partial components times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
 The total time contains the topology parsing, the attack graph generation and some minor utility processes.
@@
 This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
-In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e.
-the docker daemon where the containers are hosted.
+In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e., the docker daemon where the containers are hosted.
 Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
@@
 
-The total time of the attack graph generation procedure for 1000 fully connected hosts (784 seconds) outperforms Ou's results (1000 seconds).
+The total time of the attack graph generation procedure for 1000 fully connected hosts (784 seconds) outperforms results from OurOu et al.
+\cite{ou2006scalable}, i.e., 1000 seconds.
 In the Sheyners's extended example(4 hosts, 8 atomic attacks and multiple vulnerabilities) the attack graph took 2 hours to create.
@@
 It, however, performs worse than the generator from Ingols et al., but that is attributed to the usage of MP attack graph which is different from ours.
-From the aforementioned results, we can see that Breath-first Search can be used to generate attack graphs for an increasing number of services and denser connectivity in microservices architectures.
+From the aforementioned results, we can see that Breath-first Search can be used efficiently to generate attack graphs for an increasing number of services and denser connectivity in microservices architectures.

### 2018-09-20 paper_own_docker/chapters/introduction.tex
fixes here and there

@@
 Microservices, a recent approach to manage the complexity of modern applications, are increasingly adopted in real-world systems.
-The new architectural style follows the foundational principle of Unix that decomposes systems into small programs \cite{wolff2016microservices} that each fulfills only one cohesive task and can work together using universal interfaces.
+The new architectural style follows the foundational principle of Unix that decomposes systems into small programs \cite{wolff2016microservices}, each fulfills only one cohesive task and can work together using universal interfaces.
 Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{microservicesfrowler}.
 The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{newman2015building}.
-However, other qualities like the network utilization and the security are negatively affected \cite{ahmadvand2016requirements}.
+However, other qualities like the network utilization and the security can be negatively affected \cite{ahmadvand2016requirements}.
 Balancing the trade-off among these factors derive the decision of using microservices in industry.
-That said, a nonexhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
+That said, a none-exhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
 This shift is motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts.
@@
 As a result, the systems are deployed as networks of communicating microservices.
-For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative to hypervisors \cite{kratzke2017microservices}.
-The second often-used concept in the domain of microservices development is DevOps \cite{cerny2018contextual}.
-DevOps enable practices in which full automation of the deployment process is achieved.
+For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative of hypervisors \cite{kratzke2017microservices}.
+The second often-used concept in the domain of microservices development is \textit{DevOps} \cite{cerny2018contextual}.
+\textit{DevOps} enable practices in which full automation of the deployment process is achieved.
 In the course of this, end-to-end automated packaging and deployment is a vital part of microservices development.
-In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements}.
-The increasing communication end-points among the microservices \cite{ahmadvand2016requirements}, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley,bui2015analysis}.
+In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements} arise.
+These concerns are motivated by the increasing communication end-points among the microservices, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley,bui2015analysis}.
 In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordy2014dag}.
@@
 They help analysts to carefully analyze system connections and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker uses in order to reach their goal.
+An attack graph depicts the actions that an attacker may use to reach their goal.
 Typically, experts (e.g., red teams) manually construct attack graphs.
@@
 In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.
-Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}.
-However these tools alone are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
+Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
 

### 2018-09-20 paper_own_docker/chapters/method.tex
fixes here and there

@@
 We already defined an attack graph.
-We, now, look at how the existing components of attack graph generation for computer networks map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}.
-We then, in Subsection \ref{chap:technical}, present the tools that we use to achieve this mapping and present an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
+Now, we look at how the existing components of attack graph generation for a computer network map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}.
+Then, in Subsection \ref{chap:technical}, we present the tools that we use to achieve this mapping and present an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Generator Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
 

### 2018-09-20 paper_own_docker/chapters/related_work.tex
notes on the mthod and evaluation
fixes here and there

@@
 Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.
-In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
+%In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
 Attack graphs help in analyzing this behavior.
@@
 Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
-
 One of the earlier works in attack graph generation was done by Sheyner et al.
@@
 Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-Therefore we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction to Clair OS \cite{clair} to generate attack graphs for microservice architectures.
+Therefore we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction to Clair OS  to generate attack graphs for microservice architectures.

### 2018-09-21 paper_own_docker/chapters/method.tex
An example precondition rule added, figure changed and the algorithm now has numbers and they are referenced in the text.

@@
 Our attack graph generator is composed of three main components: \textit{Topology Parser, Vulnerability Parser and Attack Graph Generator}.
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Generator, the Vulnerability Parser scans the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.
+The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Generator, the Vulnerability Parser scans the vulnerabilities for each of the images and the Attack Graph Generator generates the attack graph from the topology and vulnerabilities files.
 In the following subsections, we first have a look into the system requirements, then describe each component in more details.
@@
 
-\textbf{TODO rename the attack graph parser in the box to Attack graph Generator}
 \begin{figure}
@@
 	\KwResult{nodes, edges}
-	nodes, edges, passed\_nodes = [], [], [] \\
-	queue = Queue() \\
-	queue.put("outside" + "ADMIN") \\
+	nodes, edges, passed\_nodes = [], [], [] \\ \label{alg:init_1}
+	queue = Queue() \\ \label{alg:init_2}
+	queue.put("outside" + "ADMIN") \\ \label{alg:attackNodeInit}
 
-	\While{! queue.isEmpty()}{
-		curr\_node = queue.get() \\
+	\While{! queue.isEmpty()}{ \label{alg:while}
+		curr\_node = queue.get() \\ \label{alg:get_node}
 		curr\_cont = get\_cont(curr\_node) \\
@@
 		neighbours = topology[curr\_cont] \\
-		\For{neigh in neighbours}{
+		\For{neigh in neighbours}{ \label{alg:neigh}
 			\If{curr\_cont == docker\_host}
@@
 				end = neigh + "ADMIN" \\
-				create\_edge(curr\_node, end) \\
+				create\_edge(curr\_node, end) \\ \label{alg:daemonEdge}
 			}
@@
 				end = neigh + "ADMIN" \\
-				create\_edge(curr\_node, end) \\
+				create\_edge(curr\_node, end) \\ \label{alg:privEdge}
 				queue.put(end) \\
@@
 						end = neigh + post\_cond[vul]\\
-						create\_edge(curr\_node, end\_node)\\
+						create\_edge(curr\_node, end\_node)\\ \label{alg:addEdge}
 						\If{end\_node not in passed\_nodes}{
-							queue.put(end\_node)\\
+							queue.put(end\_node)\\ \label{alg:putQueue}
 							passed\_nodes.add(end\_node)
@@
 When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
+An example precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the Impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}.
 If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
@@
 This results in a list of container vulnerabilities with their preconditions and postconditions.
-\textbf{TODO give an example of the attack rule and refer to the source of these rules}
 
@@
 A pseudo-code of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
-The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph \textbf{TODO please explain what is cont expl, priv acc and refer to them in the text}.
-The algorithm first initializes the nodes, edges, queue and the passed nodes.
-Afterward, it generates the nodes which are a combination of the image name and the privilege level.
-Then into a while loop, it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied.
-If the neighbor was not passed, then it is added to the queue.
-The algorithm terminates when the queue is empty.
+The algorithm requires a topology, a dictionary of the exploitable vulnerabilities and a list of nodes with privileged access as an input and the output is made up of nodes and edges that make the attack graph.
+Topology (Subsection \ref{chap:topology_p}) contains the information about the connectivity between the containers, cont\_expl (Subsections \ref{chap:vulnerability_p} and \ref{chap:attack_graph_p}) contains information regarding which vulnerabilities can be attacked (with their pre- and postconditions) and priv\_acc (Subsection \ref{chap:topology_p}) is the array of nodes that have high (ADMIN) permissions to the docker daemon.
+The algorithm first initializes the nodes, edges, queue and the passed nodes (Lines \ref{alg:init_1}, \ref{alg:init_2}).
+Afterward, it generates the attacker node (line \ref{alg:attackNodeInit}) from where the attack starts.
+The attacker node is a combination of the image name ("Outside") and the privilege level (ADMIN).
+Then into a while loop (Line \ref{alg:while}), it iterates through every node (Line \ref{alg:get_node}), checks its neighbors (Line \ref{alg:neigh}) and adds the edges if the conditions are satisfied (Lines \ref{alg:daemonEdge}, \ref{alg:privEdge}, \ref{alg:addEdge}).
+If the neighbor was not passed, then it is added to the queue (Line \ref{alg:putQueue}).
+The algorithm terminates when the queue is empty (Line \ref{alg:while}).
 Furthermore, BFS is characterized by the following properties.
-\textbf{TODO: add line numbers to the algo and refer to those numbers in the text.}
 

### 2018-09-23 paper_own_docker/chapters/evaluation.tex
reductions

@@
 JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
-We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
+We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
 \cite{aksu2018automated} are \textit{correct}.

### 2018-09-23 paper_own_docker/chapters/introduction.tex
reductions

@@
 % contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
-Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated,  sheyner2003tools, ou2006scalable}.
+Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated, ou2006scalable}.
 In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.

### 2018-09-23 paper_own_docker/chapters/method.tex
reductions

@@
 
-Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}} \cite{libvirt}.
+Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}}.
 Some containers obtain certain privileges that grant them control over the docker daemon in order to function properly.

### 2018-09-23 paper_own_docker/main.tex
Todos in method and evaluation done
intro draft
fixes here and there
checks here and there
An example precondition rule added, figure changed and the algorithm now has numbers and they are referenced in the text.
reductions

@@
 \usepackage{booktabs} % For formal tables
-\usepackage[]{algorithm2e}
-
+\usepackage[linesnumbered]{algorithm2e} 
+\usepackage{subcaption}
 % Copyright
@@
 %\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
 
@@
 \acmDOI{xx.xxx/xxx_x}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
 
@@
 
+\def\anonymous{}
 \begin{document}
-\title{Attack Graph Generation for Micro-service
+\title{Attack Graph Generation for Microservice
 	Architecture}
-\titlenote{Produces the permission block, and
-  copyright information}
-\subtitle{Extended Abstract}
-\subtitlenote{The full version of the author's guide is available as
-  \texttt{acmart.pdf} document}
 
+\ifdefined\anonymous
+\author{Anonymized  author(s)}
+\else
 \author{Amjad Ibrahim}
@@
 
-\author{Prof. Dr. Alexander Pretschner}
+\author{Alexander Pretschner}
 \affiliation{\institution{Technical University of Munich}}
@@
 % The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{B. Trovato et al.}
+\renewcommand{\shortauthors}{A. Ibrahim et al.}
+\fi
 
@@
 %
+\iffalse
 \begin{CCSXML}
@@
 \ccsdesc[100]{Networks~Network reliability}
+\fi
 
-\keywords{Attack Graph Generaton, Computer Security, Microservices}
+\keywords{Attack Graph Generaton, Microservices, Containers}
 
@@
 \input{./chapters/conclusion}
-\input{./chapters/future_work}
-
 \bibliographystyle{ACM-Reference-Format}

### 2018-09-23 paper_own_docker/chapters/method.tex
reductions

@@
 In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
-In this subsection, we start first by shortly introducing a famous framework (Docker) and some of its terminology.
-We then modify the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}: nodes, edges, privilege levels, pre- and postconditions to match our use-case.
+In this subsection, we start first by introducing the Docker framework and its terminology.
+We then discuss the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}:  that fit our use-case.
 We illustrate the whole idea  by demonstrating a small example.
@@
 
-Privileges play a central role in the generation if attack graphs.
+Privileges play a central role in the generation of attack graphs.
 Traditionally, the privileges are modeled as a hierarchy that varies in the access level (\textit{User, Admin}), and the access scope (virtual machine VOS, host machine OS).
@@
 VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
-However in our case, unlike hosts connected in a computer network, these privileges refer to images and not virtual machines.
+However in our case, unlike hosts in a network, these privileges refer to images and not virtual machines.
 On the other side, the keyword \textit{OS} means that the  host machine can be controlled by a user who has this privilege.
@@
 The example is taken from the Netflix OSS Github repository.
-Netflix OSS example is a Spring Cloud-based microservices architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon) \cite{netflixoss, springcloudnetflix}.
+Netflix OSS example is a Spring Cloud-based microservices architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon).
 Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge is a connection between two containers, if one calls the other.

### 2018-09-24 paper_own_docker/chapters/background_attack_graphs.tex
fixes

@@
 Attack graphs \cite{sheyner2002automated} are a popular way of examining network security weaknesses.
-They help analysts to carefully analyze a given system and detect its vulnerable parts.
-The definition of attack graphs may vary but it is essentially a directed graph that consists of nodes and edges with various representations.
-In this subsection, we first look at a few examples of how others define attacks graphs and at the end present the model of an attack graph that we use in this work.
+They help analysts to analyze a given system and detect its vulnerable parts carefully.
+The definition of attack graphs may vary, but it is essentially a directed graph that consists of nodes and edges with various representations.
 
@@
 
-In this paper, we define attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
+In this paper, we define an attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
 \cite{ingols2006practical}.
@@
 We can think of an edge as a successful vulnerability exploitation which is initiated from a host with a required privilege to another or the same host with the newly gained privilege as a result of the vulnerability exploitation.
+To the best of our knowledge, attack graphs are used for networks but not microservices, potentially because there is no tool support.

### 2018-09-24 paper_own_docker/chapters/background_microservices.tex
fixes

@@
 
-As real-world software grows in size, there is an ever growing need to decompose it into an organized structure to promote scaling, reuse and readability.
+As real-world software grows in size, there is an ever-increasing need to decompose it into an organized structure to promote scaling, reuse, and readability.
 A software application whose modules cannot be executed independently is called a monolith.
@@
 Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
-However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices in order to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
-The novel term "microservices" was first introduced in 2011 at an architectural workshop in order to propose a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
+However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices  to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
+The novel term "microservices" was first introduced in 2011 at an architectural workshop to propose a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
 In the microservices paradigm, multiple services are split into very basic units which are task oriented.
@@
 a microservice is a cohesive, independent process interacting via messages.
-These microservices constitute as a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
+These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
 Microservice architectures benefit us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability \cite{newman2015building}.
-However, they add an additional complexity and have a wider attack surface as the need of many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.
+However, they add additional complexity and have a wider attack surface as the need for many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.
 While microservices are an architectural principle, container technology has emerged in cloud computing to provide a lightweight virtualization mechanism.

### 2018-09-24 paper_own_docker/chapters/evaluation.tex
fixes

@@
 This raises the need for a robust and scalable attack graph generator.
-In Subsection \ref{chap:heterogenious_systems}, we first show different microservice architectures on which our system was tested on.
+In Subsection \ref{chap:heterogenious_systems}, we first our use-cases.
 We then have a look at how others evaluate their systems.
-Finally in Subsection \ref{chap:scalability_eval} we conduct experiments in order to test the scalability of our system with a different number of containers and connectivity.
+Finally, in Subsection \ref{chap:scalability_eval}, we conduct experiments to test the scalability of our system with a different number of containers and connectivity.
 All of the experiments were performed on an Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
@@
 			\hline
-			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline
+			Name & Description & Technology Stack & No. Containers & No. vuln. & Github link \\\hline
 
-			Netflix OSS & Combination of containers provided from Netflix.
+			Netflix OSS & Combination of containers provided by Netflix.
 & Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & \url{https://github.com/Oreste-Luci/netflix-oss-example} \\
@@
 
-Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities.
+Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity, and number of vulnerabilities.
 Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-In order to do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}.
-Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains.
+To do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}.
+We intended to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains.
 We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging.
@@
 NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses many tools like Spring Cloud, Netflix Ribbon, and Netflix Eureka.
-Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL.
+Atsea Sample Shop App is an e-commerce sample web application consisting  of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL.
 JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
@@
 This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
-Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container.
+Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps to reach the target container.
 All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property.
@@
 \end{table*}
-Extensive scalability study of attack graph generators is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis.
+Extensive scalability study of attack graph generators is rare in current literature, and many parameters contribute to the complexity of a comprehensive analysis.
 Parameters that usually vary in this sort of evaluation are the number of nodes, their connectivity and the number of vulnerabilities per container.
@@
 They afterward continued the study on a simulated network of 50000 hosts in under 4 minutes.
-Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours.
+Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple-Prerequisite graph, which is different from ours.
 In addition to this, missing an explanation of how the hosts are connected, does not make it directly comparable to our method.
@@
 They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute .
+The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
 % The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system.
 
-In our scalability experiments we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers which were taken from their respective Github repositories.
-We extended this example and artificially made fully connected topologies of \textit{20, 50, 100, 500 and 1000} Samba containers to test the scalability of the system.
-The Phpmailer container has \textit{181} vulnerabilities, while the Samba container has \textit{367} vulnerabilities detected by Clair.
-In our tests, we report the total execution time as well as partial components times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
+In our scalability experiments, we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers.
+We extended this example and artificially created fully connected topologies of \textit{20, 50, 100, 500 and 1000} Samba containers to test the scalability of the system.
+The Phpmailer container has \textit{181} vulnerabilities, while the Samba container has \textit{367} vulnerabilities reported by Clair.
+In our tests, we measure the total execution time as well as partial times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
 The total time contains the topology parsing, the attack graph generation and some minor utility processes.
@@
 However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.
+Evaluation of Clair is not in the scope of this analysis.
 
@@
 This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
-In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e., the docker daemon where the containers are hosted.
+In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e., the Docker daemon where the containers are hosted.
 Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
 The number of edges of the topology graph is a combination of one edge ("outside"-"Phpmailer"), n edges ("docker host" to all of the containers) and n*(n+1)/2 edges of between Phpmailer and Samba containers.
-For example\_20, the number of containers is 23 (one Phpmailer, one "outside", one "docker host" and 20 Samba containers) the number of edges in the topology graph would be 253: one outside edge, 21 docker host edges (one toward Phpmailer and 20 toward the Samba containers) and 231 between-container edges (21*22/2=231).
+For example\_20, the number of containers is 23 (one Phpmailer, one "outside", one "docker host" and 20 Samba containers) the number of edges in the topology graph would be 253: one outside edge, 21 Docker host edges (one toward Phpmailer and 20 toward the Samba containers) and 231 between-container edges (21*22/2=231).
 
 Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step.
-However, this step increases in a linear fashion because the container files are analyzed only once by Clair.
+However, this step increases linearly because the container files are analyzed only once by Clair.
 The attack graph generation for the smaller examples is considerably less than the preprocessing time.
-Starting from example\_500, we can notice a sharp increase in BDF execution time to 165 seconds.
-For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.
+Starting from example\_500, we can notice a sharp increase in execution time to 165 seconds.
+For the previous example with example\_100, the attack graph was generated in  6.5 seconds.
 
@@
 It, however, performs worse than the generator from Ingols et al., but that is attributed to the usage of MP attack graph which is different from ours.
-From the aforementioned results, we can see that Breath-first Search can be used efficiently to generate attack graphs for an increasing number of services and denser connectivity in microservices architectures.
+
+In summary, we found out  that our algorithm generates  attack graphs efficiently, it handles a system with a \textit{thousand} container in 13 minutes.
+Considering the strongly connected system in the experiment, and the high number of vulnerabilities in it, we think that the results of this experiment show a practical solution that can be used as part of the continuous delivery process of real-world systems.

### 2018-09-24 paper_own_docker/chapters/introduction.tex
reductions
fixes

@@
 As a result, the systems are deployed as networks of communicating microservices.
-For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative of hypervisors \cite{kratzke2017microservices}.
+For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high-performance  alternative to hypervisors \cite{kratzke2017microservices}.
 The second often-used concept in the domain of microservices development is \textit{DevOps} \cite{cerny2018contextual}.
@@
 In the course of this, end-to-end automated packaging and deployment is a vital part of microservices development.
-In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements} arise.
-These concerns are motivated by the increasing communication end-points among the microservices, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley,bui2015analysis}.
+In addition to the agility and optimization brought by the two concepts, significant concerns around their impact on security \cite{ahmadvand2016requirements} arise.
+These concerns are motivated by the increasing communication end-points among the microservices, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by Docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{bottomely, bui2015analysis}.
 In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordy2014dag}.
@@
 In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.
-Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
+Tools that scan the vulnerabilities of a particular host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
 
@@
 We present an approach, based on methods from computer networks, to automatically generate attack graphs for microservice-based architectures that are deployed as containers.
-	\item We present the technical details of an extensible tool that implements our approach. The tool is available for use at\footnote{}.
+	\item We present the technical details of an extensible tool that implements our approach. The tool is available online \footnote{The link is omitted for anonymization  purpose}.
 	\item An empirical evaluation of the efficiency of our tool in generating attack graphs of real-world systems.

### 2018-09-24 paper_own_docker/chapters/method.tex
fixes

@@
 Now, we look at how the existing components of attack graph generation for a computer network map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}.
-Then, in Subsection \ref{chap:technical}, we present the tools that we use to achieve this mapping and present an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Generator Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
+Then, in Subsection \ref{chap:technical}, we present the tools that we use to achieve this mapping and give an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Generator Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
 
@@
 In our work, we adapt already existing attack graph generation methods from computer networks to the microservices ecosystem.
-In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture.
+In order to do this, we identify the corresponding components and find an equivalent replacement that can be used in a microservice architecture.
 In this subsection, we start first by introducing the Docker framework and its terminology.
@@
 Docker is one of the most popular and used containerization frameworks currently available.
-In Docker, a distinction is being made between the terms \textit{image}, \textit{container} and \textit{service}.
+In Docker, a distinction is being made between the terms \textit{image}, \textit{container}, and \textit{service}.
 An \textit{image} is an executable package that includes everything needed to run an application, a \textit{container} is a runtime instance of an image, and a \textit{service} represents a container in production.
 A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}.
-In our work, we construct attack graphs by statically analyzing the topology of the containers, hence, we treat these terms equally.
+In our work, we construct attack graphs by statically analyzing the topology of the containers.
+Hence, we treat these terms equally.
 
@@
 Traditionally, the privileges are modeled as a hierarchy that varies in the access level (\textit{User, Admin}), and the access scope (virtual machine VOS, host machine OS).
-The exhaustive list of privileges, that are used in this paper, are: \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}.
+The exhaustive list of privileges, that are used in this paper are \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}.
 VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
 However in our case, unlike hosts in a network, these privileges refer to images and not virtual machines.
-On the other side, the keyword \textit{OS} means that the  host machine can be controlled by a user who has this privilege.
+On the other side, the keyword \textit{OS} means that a user who has this privilege  can control the  host machine.
 Since \textit{VOS} are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of the hierarchy \cite{aksu2018automated}.
@@
 As mentioned earlier, the \textit{nodes} and the \textit{edges} are the basic building blocks of an attack graph.
-A \textit{node} represents  a combination of a docker image and its respective compromise levels (expressed as privileges obtained by the attacker).
-A directed \textit{edge} between two nodes represents an attack step from one node (a compromised image with a certain privilege gained by the attacker) to another node (adjacent exploitable image with the gained privileges).
+A \textit{node} represents  a combination of a compromised Docker image and a certain privilege gained by the attacker after exploiting a vulnerability.
+A directed \textit{edge} between two nodes represents an attack step from one node  to another node (adjacent exploitable image with the gained privileges).
 Each edge is typed with the vulnerability (CVE) that could be exploited in the end node.
 
-In order for attackers to exploit a given vulnerability, they need to have certain \textit{preconditions}, i.e, the minimum privileges needed to exploit \cite{aksu2018automated}.
-Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a \textit{postcondition} and a directed edge is added between them.
+For attackers to exploit a given vulnerability, they need to have certain \textit{preconditions}, i.e., the minimum required privileges to exploit \cite{aksu2018automated}.
+Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a \textit{postcondition}, and a directed edge is added between them.
 Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
@@
 Netflix OSS example is a Spring Cloud-based microservices architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon).
-Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge is a connection between two containers, if one calls the other.
+Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge is a connection between two containers if one calls the other.
 The topology consists of an "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
-According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resiliency, and security functionalities.
+According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resilience, and security functionalities.
 Eureka is a REST (Representational State Transfer) based service that is primarily used in the cloud for locating services for the purpose of load balancing and fail-over of middle-tier servers.
@@
 Parts of both graphs have been intentionally omitted to reduce complexity.
-An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gain USER privilege.
+An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gains USER privilege.
 With this USER privilege, an attacker can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain ADMIN privilege.
@@
 It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to exploit the CVE-2018-1124 vulnerability via creating entries in procfs by starting processes, which could result in crashes or arbitrary code execution\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2018-1124}}.
-This vulnerability can be exploited by having only USER privilege on Zuul to gain directly ADMIN privileges of the Eureka container.
-Our attack graph generator shows both paths since it is of an interest to see every possible route in which a container can be compromised.
+Another path would be to exploit the CVE-2018-1124 vulnerability via creating entries in the file-system (procfs) by starting processes, which could result in crashes or arbitrary code execution\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2018-1124}}.
+This vulnerability can be exploited by having only USER privilege on Zuul to gain ADMIN privileges of the Eureka container directly.
+Our attack graph generator shows both paths since it is of  interest to see every possible route in which a container can be compromised.
 
@@
 In the figure, the rectangles denote the main components of the system, while the arrows describe the flow of the system and the files are the intermediate products.
-Our attack graph generator is composed of three main components: \textit{Topology Parser, Vulnerability Parser and Attack Graph Generator}.
+Our attack graph generator is composed of three main components: \textit{Topology Parser, Vulnerability Parser, and Attack Graph Generator}.
 The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Generator, the Vulnerability Parser scans the vulnerabilities for each of the images and the Attack Graph Generator generates the attack graph from the topology and vulnerabilities files.
@@
 
-The generator is developed and tested for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
-Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of a multi-container applications.
+The generator is developed and tested for Docker 17.12.1-ce, and Docker Compose 1.19.0 \cite{merkel2014docker}.
+Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of  multi-container applications.
 It provides a static configuration file that specifies the system containers, networks, and ports.
@@
 
-In order to generate an attack graph of a given system, we require an arrangement of its components and connections described as a system topology.
+To generate an attack graph of a given system, we require an arrangement of its components and connections described as a system topology.
 The topology of Docker containers can be described either at  runtime or at design time by using Docker Compose.
 In our case, since we are doing static attack graph analysis, we use Docker Compose to extract the topology.
-Docker Compose provides a  file (docker-compose.yml) which is used for describes the orchestration of the services.
+Docker Compose provides a  file (docker-compose.yml) which is used to describe the orchestration of the services.
+That is to say, the file exists anyway; no further input from the security analyst is required.
 However different versions of docker-compose.yml, use different syntax.
 For example, older versions use the deprecated keyword "\textit{link}", while newer ones use exclusively "\textit{networks}", to denote a connection between two images.
-In this work, we use the keyword "\textit{networks}" as an indicator that a connection between two images exists.
+We use the keyword "\textit{networks}" as an indicator that a connection between two images exists.
 
-In the majority of cases, for an application to be useful, it communicates with the outside world, i.e, it has end points that can be used by the outer network.
+In the majority of cases, for an application to be useful, it communicates with the outside world, i.e., it has endpoints that can be used by the outer network.
 In Docker, this is usually done by using publishing ports.
@@
 Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}}.
-Some containers obtain certain privileges that grant them control over the docker daemon in order to function properly.
+Some containers obtain certain privileges that grant them control over the Docker daemon in order to function properly.
 For example, a user may want to run some hardware (e.g., web-cam) or some applications that demand higher privilege levels  from Docker.
 In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
-An attacker with access to these containers has also access to the Docker daemon.
+An attacker with access to these containers  also has  access to the Docker daemon.
 Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
@@
 An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-We collect the fields in the attack vector which are,  as described by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
-Unfortunately, Clair does not provide a command line interface to analyze a docker image.
-We use another tool, i.e.,  Clairctl  to analyze a complete docker image.
+We collect the fields in the attack vector which are,  as defined by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
+Unfortunately, Clair does not provide a command line interface to analyze a Docker image.
+We use another tool, i.e.,  Clairctl  to analyze a complete Docker image.
 
@@
 		neighbours = topology[curr\_cont] \\
-		\For{neigh in neighbours}{ \label{alg:neigh}
+		\For{nb in neighbours}{ \label{alg:neigh}
 			\If{curr\_cont == docker\_host}
 			{
-				end = neigh + "ADMIN" \\
+				end = nb + "ADMIN" \\
 				create\_edge(curr\_node, end) \\ \label{alg:daemonEdge}
 			}
-			\If{neigh == docker\_host and priv\_acc[curr\_cont]}
+			\If{nb == docker\_host and priv\_acc[curr\_cont]}
 			{     
-				end = neigh + "ADMIN" \\
+				end = nb + "ADMIN" \\
 				create\_edge(curr\_node, end) \\ \label{alg:privEdge}
@@
 			}
-			\If{neigh != outside and neigh != docker\_host}{
-				precond = cont\_expl[neigh][precond] \\
-				postcond = cont\_expl[neigh][postcond] \\
+			\If{nb != outside and nb != docker\_host}{
+				precond = cont\_expl[nb][precond] \\
+				postcond = cont\_expl[nb][postcond] \\
 				\For{vul in vuls}{
-					\If{$curr_priv > precond[vul]$}{    
-						end = neigh + post\_cond[vul]\\
+					\If{curr\_priv > precond[vul]}{    
+						end = nb + post\_cond[vul]\\
 						create\_edge(curr\_node, end\_node)\\ \label{alg:addEdge}
@@
 Breadth-first Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before diving deeper into the graph.
-A pseudo-code of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
+Pseudo-code of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
 The algorithm requires a topology, a dictionary of the exploitable vulnerabilities and a list of nodes with privileged access as an input and the output is made up of nodes and edges that make the attack graph.
-Topology (Subsection \ref{chap:topology_p}) contains the information about the connectivity between the containers, cont\_expl (Subsections \ref{chap:vulnerability_p} and \ref{chap:attack_graph_p}) contains information regarding which vulnerabilities can be attacked (with their pre- and postconditions) and priv\_acc (Subsection \ref{chap:topology_p}) is the array of nodes that have high (ADMIN) permissions to the docker daemon.
+Topology (Subsection \ref{chap:topology_p}) provides the information about the connectivity between the containers, cont\_expl (Subsections \ref{chap:vulnerability_p} and \ref{chap:attack_graph_p}) contains information regarding which vulnerabilities can be attacked (with their pre- and postconditions), and priv\_acc (Subsection \ref{chap:topology_p}) is the array of nodes that have high (ADMIN) permissions to the Docker daemon.
 The algorithm first initializes the nodes, edges, queue and the passed nodes (Lines \ref{alg:init_1}, \ref{alg:init_2}).
@@
 \begin{itemize}
-	\item Completeness: Breadth-first Search is complete i.e. if there is a solution, Breadth-first search will find it regardless of the kind of graph.
+	\item Completeness: Breadth-first Search is complete, i.e., if there is a solution, Breadth-first search will find it regardless of the kind of graph.
 	\item Termination: This follows from the monotonicity property.

### 2018-09-24 paper_own_docker/chapters/related_work.tex
fixes

@@
 A collection of these counterexamples form an attack graph.
-They state that model checkers satisfy a monotonicity property in order to ensure termination.
+They state that model checkers satisfy a monotonicity property  to ensure termination.
 However, model checkers have a computational disadvantage.
-In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges \cite{sheyner2002automated}.
+%In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges .
 As a result of this, more scalable approach was needed.
@@
 Ou et al.
-use logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al.
-use Breadth-first search algorithm in order to tackle the scalability issue.
+use a logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al.
+use a Breadth-first search algorithm in order to tackle the scalability issue.
 Ingols et al.
-discuss the redundancy Full and Predictive graphs and model an attack graph as an MP graph with contentless edges and 3 types of nodes.
+discuss the redundancy Full and Predictive graphs and model an attack graph as an MP graph with content-less edges and 3 types of nodes.
 They use Breath-first search technique for generating the attack graph.
@@
 
-Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and a lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}.
-To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for Docker containers.
+Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their  need of connectivity and a lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}.
+To the best of our knowledge, no previous work that has been done  in the area of attack graph generation for Docker containers.
 Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
-Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.
-Therefore we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction to Clair OS  to generate attack graphs for microservice architectures.
+Containers in our model correspond to hosts, and a connection between hosts translates to communication between containers.
+
+In summary, our contribution is proposing attack graph generation as part of the DevOps practices, and providing a tool-support for this idea.
+To that end, we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction with Clair OS to generate attack graphs for microservice architectures.

### 2018-09-24 paper_own_docker/chapters/conclusion.tex
last round of fixes

@@
 Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services.
-The manual constriction of attack graphs is an error-prone, resource consuming activity, hence, automating this construction does not only guarantee efficient construction but also complies with the spirit of DevOps practices.
+The manual construction of attack graphs is an error-prone, resource consuming activity.
+Hence, automating this process does not only guarantee efficient construction but also complies with the spirit of DevOps practices.
 We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.

### 2018-09-24 paper_own_docker/chapters/method.tex
last round of fixes

@@
 The generator is written in Python 3.6.
-Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing.
+Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners, and microservice architectures.
 
@@
 In the majority of cases, for an application to be useful, it communicates with the outside world, i.e., it has endpoints that can be used by the outer network.
-In Docker, this is usually done by using publishing ports.
+In Docker, this is usually done by  publishing ports.
 This is the case in both computer networks, as well as in microservice architectures.
@@
 We collect the fields in the attack vector which are,  as defined by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
-Unfortunately, Clair does not provide a command line interface to analyze a Docker image.
-We use another tool, i.e.,  Clairctl  to analyze a complete Docker image.
+Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl  to analyze a complete Docker image.
 
@@
 When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-An example precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the Impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}.
+An example of a precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}.
 If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.

### 2018-10-21 paper_own_docker/chapters/background.tex
Background updated based on proof-reading feedback

@@
 
-We start by introducing the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
+We introduce the concept of microservices, their benefits and security implications in Subsection \ref{chap:microservices}.
 In Subsection \ref{chap:vulnerability_scanners}, we look into vulnerability scanners as tools to scan a single host for vulnerabilities.
-In Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose security weaknesses of a given system composed of multiple hosts.
+In Subsection \ref{chap:attack_graphs}, we introduce and formally describe attack graphs as methods to diagnose the security weaknesses of a given system comprising multiple hosts.
 

### 2018-10-21 paper_own_docker/chapters/background_attack_graphs.tex
Background updated based on proof-reading feedback

@@
 
-Attack graphs \cite{sheyner2002automated} are a popular way of examining network security weaknesses.
-They help analysts to analyze a given system and detect its vulnerable parts carefully.
-The definition of attack graphs may vary, but it is essentially a directed graph that consists of nodes and edges with various representations.
+Attack graphs \cite{sheyner2002automated} are a popular way to examine network security weaknesses.
+They facilitate careful analysis of a given system and detection its vulnerable components.
+The definition of an attack graph may vary, however, it is essentially a directed graph comprising nodes and edges with various representations.
 
 Seyner et al.
-define an attack graph as a tuple of states, transitions between the states, initial state and success states.
-An initial state represents the state from where the attacker starts the attack and through a chain of atomic attacks tries to reach one of the success states \cite{sheyner2002automated}.
+defined an attack graph as a tuple of states, transitions between the states, an initial state and success states.
+An initial state represents the state from which the attacker begins an attack and through a chain of atomic attacks attempts to reach one of the success states \cite{sheyner2002automated}.
 Ou et al.
-introduce the notion of a logical attack graph.
-A logical attack graph is a bipartite directed graph that consists of two kinds of nodes: fact nodes and derivation nodes.
-Each fact node is labeled with a logical statement in the form of a predicate applied to its arguments, while each derivation node is labeled with an interaction rule that is used for the derivation step.
-The edges in the graph represent a "depends on" relation \cite{ou2006scalable}.
+introduced the notion of a logical attack graph, which is a bipartite directed graph comprising fact and derivation nodes.
+Each fact node is labeled with a logical statement in the form of a predicate applied to its arguments, while each derivation node is labeled with an interaction rule used in the derivation step.
+The edges in a logical attack graph represent a "depends on" relation \cite{ou2006scalable}.
 Ingols et al.
-make a distinction between full, predictive and multiple-prerequisite (MP) attack graphs.
-Full graph is a directed acyclic graph that consists of nodes that represent hosts and edges that represent vulnerability instances.
+made a distinction between full, predictive and multiple-prerequisite (MP) attack graphs.
+A full graph is a directed acyclic graph comprising of nodes that represent hosts and edges that represent vulnerability instances.
 Predictive attack graphs use the same representation as full attack graphs with the only difference lying in the constraint of when the edges are added to the attack graph.
-These graphs are generally smaller than full graphs.
-MP attack is an attack graph with as contentless edges and three node type: state nodes, vulnerability instance nodes and prerequisite nodes \cite{ingols2006practical}.
+Note that predictive graphs are generally smaller than full graphs.
+An MP attack is an attack graph with contentless edges, state nodes, vulnerability instance nodes and prerequisite nodes \cite{ingols2006practical}.
 
-In this paper, we define an attack graph to be a directed acyclic graph with a set of nodes and edges similar to the full graph representation of Ingols et al.
+In this paper, we define an attack graph as a directed acyclic graph with a set of nodes and edges similar to the full graph representation proposed by Ingols et al.
 \cite{ingols2006practical}.
-As an expansion to this model, a node represents a state of a host with its current privilege.
-An edge represents a successful transition between two such hosts.
-We can think of an edge as a successful vulnerability exploitation which is initiated from a host with a required privilege to another or the same host with the newly gained privilege as a result of the vulnerability exploitation.
-To the best of our knowledge, attack graphs are used for networks but not microservices, potentially because there is no tool support.
+As an expansion to this model, a node represents the state of a host with its current privilege, and an edge represents a successful transition between two such hosts.
+We can consider an edge as a successful vulnerability exploitation initiated from a host with a required privilege to another or the same host with a newly gained privilege as a result of the vulnerability exploitation.
+To the best of our knowledge, attack graphs have been used for networks but not microservices, potentially because there is currently no existing tool support.

### 2018-10-21 paper_own_docker/chapters/background_microservices.tex
Background updated based on proof-reading feedback

@@
 
-As real-world software grows in size, there is an ever-increasing need to decompose it into an organized structure to promote scaling, reuse, and readability.
-A software application whose modules cannot be executed independently is called a monolith.
+As real-world software increases in size, there is an increasing need to decompose software into an organized structure to promote scalability, reusability, and readability.
+A software application with modules that cannot be executed independently is referred to as a monolith.
 Monolithic systems  are characterized by tight coupling, vertical scaling and strong dependence \cite{microservicesfrowler}.
-Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services which are used by other entities through a networking protocol \cite{papazoglou2003service}.
-However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices  to provide an even more fine-grained task separation \cite{ahmadvand2016requirements}.
-The novel term "microservices" was first introduced in 2011 at an architectural workshop to propose a common term for the explorations of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
-In the microservices paradigm, multiple services are split into very basic units which are task oriented.
-According to Dragoni et al.
-a microservice is a cohesive, independent process interacting via messages.
+The Service Oriented Architecture (SOA) addresses these issues by restructuring its elements into components that provide services that are used by other entities via a networking protocol \cite{papazoglou2003service}.
+However, in a typical SOA, the services are monolithic which gives rise to the concept of microservices  to provide even more fine-grained task separation \cite{ahmadvand2016requirements}.
+The term "microservices" was first introduced in 2011 at an architectural workshop as a common term to describe the work of multiple researchers \cite{dragoni2017microservices, microservicesfrowler}.
+In the microservices paradigm, multiple services are split into very basic task-oriented units.
+According to Dragoni et al., a microservice is a cohesive, independent process interacting via messages.
 These microservices constitute a distributed architecture called a microservice architecture \cite{dragoni2017microservices}.
-Microservice architectures benefit us with the advantage of having more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability \cite{newman2015building}.
+Microservice architectures have more heterogeneous technologies, cheaper scaling, resilience, organizational alignment, and composability \cite{newman2015building}.
 However, they add additional complexity and have a wider attack surface as the need for many services to communicate with each other and third-party software increases \cite{combe2016docker, dragoni2017microservices}.
 While microservices are an architectural principle, container technology has emerged in cloud computing to provide a lightweight virtualization mechanism.
-This technology enables microservices to be packaged and orchestrated through the Cloud \cite{pahl2016microservices}.
+Container technology enables microservices to be packaged and orchestrated through the Cloud \cite{pahl2016microservices}.

### 2018-10-21 paper_own_docker/chapters/method.tex
Method updated based on proof-reading feedback

@@
 \label{chap:method}
-We already defined an attack graph.
-Now, we look at how the existing components of attack graph generation for a computer network map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}.
-Then, in Subsection \ref{chap:technical}, we present the tools that we use to achieve this mapping and give an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Generator Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.
+In Subsection \ref{chap:mapping}, we discuss how the existing components of attack graph generation for a computer network are mapped to a microservice environment, and the concepts are illustrated using a small example.
+Then, in Subsection \ref{chap:technical}, we present the tools we use to achieve this mapping and provide an overview of the proposed system and its components, i.e., the Topology Parser (Subsection \ref{chap:topology_p}), the Vulnerability Parser (Subsection \ref{chap:vulnerability_p}) and the Attack Graph Generator (Subsection \ref{chap:attack_graph_p}).
+In addition, the Breath-first Search (BFS) graph traversal algorithm is discussed in Subsection \ref{chap:bfs}.
 
@@
 % abit reptative 
-In our work, we adapt already existing attack graph generation methods from computer networks to the microservices ecosystem.
-In order to do this, we identify the corresponding components and find an equivalent replacement that can be used in a microservice architecture.
-In this subsection, we start first by introducing the Docker framework and its terminology.
-We then discuss the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}:  that fit our use-case.
-We illustrate the whole idea  by demonstrating a small example.
+In this study, we adapt existing attack graph generation methods from the computer networks field to the microservices ecosystem.
+To accomplish this, we identify the corresponding components and identify an equivalent replacement that can be used in a microservice architecture.
+In this subsection, we begin by introducing the Docker framework and its terminology.
+We then discuss the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs} that fit our use case.
+We illustrate the overall concept by demonstrating a small example.
 
 Docker is one of the most popular and used containerization frameworks currently available.
-In Docker, a distinction is being made between the terms \textit{image}, \textit{container}, and \textit{service}.
-An \textit{image} is an executable package that includes everything needed to run an application, a \textit{container} is a runtime instance of an image, and a \textit{service} represents a container in production.
-A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}.
-In our work, we construct attack graphs by statically analyzing the topology of the containers.
-Hence, we treat these terms equally.
+In Docker, a distinction is made between the terms \textit{image}, \textit{container}, and \textit{service}.
+Here, an \textit{image} is an executable package that includes everything required to run an application, a \textit{container} is a runtime instance of an image, and a \textit{service} represents a container in production.
+A service only runs a single image, however, it codifies the way that image runs, what ports it should use, and how many replicas of the container should run so the service has the capacity it requires \cite{merkel2014docker}.
+We construct attack graphs by statically analyzing the topology of the containers; therefore, we treat these terms equally.
 
 Privileges play a central role in the generation of attack graphs.
-Traditionally, the privileges are modeled as a hierarchy that varies in the access level (\textit{User, Admin}), and the access scope (virtual machine VOS, host machine OS).
-The exhaustive list of privileges, that are used in this paper are \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}.
-VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine.
+Traditionally, the privileges are modeled as a hierarchy that varies in the access level (\textit{User, Admin}), and access scope (virtual machine VOS, host machine OS).
+The privileges used in this paper are \textit{None, VOS(User), VOS(Admin), OS(User), and OS(Admin)}.
+VOS means that the privilege is exclusive to a virtual machine while not affecting the host machine.
 However in our case, unlike hosts in a network, these privileges refer to images and not virtual machines.
-On the other side, the keyword \textit{OS} means that a user who has this privilege  can control the  host machine.
-Since \textit{VOS} are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of the hierarchy \cite{aksu2018automated}.
-\textit{None} means that no privilege is obtained, \textit{User} means only a subset of user level privileges are granted, and \textit{Admin} grants control over the whole system.
+The \textit{OS} keyword means that a user who has this privilege can control the host machine.
+Since \textit{VOSs} are isolated from host machines and their exploitation does not imply exploitation of the host machine, they are at the lower level of the hierarchy \cite{aksu2018automated}.
+\textit{None} means that no privilege is obtained, \textit{User} means that only a subset of user level privileges is granted, and \textit{Admin} grants control over the whole system.
 
-As mentioned earlier, the \textit{nodes} and the \textit{edges} are the basic building blocks of an attack graph.
+As mentioned previously, \textit{nodes} and \textit{edges} are the basic building blocks of an attack graph.
 A \textit{node} represents a combination of a compromised Docker image and a certain privilege gained by the attacker after exploiting a vulnerability.
-A directed \textit{edge} between two nodes represents an attack step from one node  to another node (adjacent exploitable image with the gained privileges).
+A directed \textit{edge} between two nodes represents an attack step from one node to another (adjacent exploitable image with the gained privileges).
 Each edge is typed with the vulnerability (CVE) that could be exploited in the end node.
 
-For attackers to exploit a given vulnerability, they need to have certain \textit{preconditions}, i.e., the minimum required privileges to exploit \cite{aksu2018automated}.
-Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a \textit{postcondition}, and a directed edge is added between them.
-Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}.
-The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.
+For attackers to exploit a given vulnerability, they must have certain \textit{preconditions}, i.e., the minimum privileges required to exploit \cite{aksu2018automated}.
+Once an attacker meets these preconditions and exploits the vulnerability, he gains the privilege of the end node as a \textit{postcondition}, and a directed edge is added between the two nodes.
+Both the preconditions and postconditions in this study are transformed from precondition and postcondition rules manually selected and evaluated by experts \cite{aksu2018automated}.
+The precondition and postcondition rules use the fields defined by the NVD, as well as an occurrence of specific keywords from CVE descriptions \cite{booth2013national}.
 
@@
 
-	\caption[Two numerical solutions]{Reduced Netflix OSS example (a) Example topology graph  (b) Example resulting attack graph}
+	\caption[Two numerical solutions]{Reduced Netflix OSS example: (a) example topology graph  and (b) example resulting attack graph}
 \end{figure*}
 
-In order to show how the attack graph generation works in practice, we present a small example.
-The example is taken from the Netflix OSS Github repository.
-Netflix OSS example is a Spring Cloud-based microservices architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul) and Client Side Load Balancing (Ribbon).
-Displayed in Figure \ref{TopologyGraph} is a subset of the example topology where each node denotes a container and each edge is a connection between two containers if one calls the other.
-The topology consists of an "Outside" node, "Docker daemon" node, Zuul, Eureka and other nodes.
+Here, we present a small example to demonstrate how attack graph generation works in practice.
+The example is taken from the Netflix OSS GitHub repository.
+The Netflix OSS example is a Spring Cloud-based microservice architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul), and Client Side Load Balancing (Ribbon).
+Figure \ref{TopologyGraph} shows a subset of the example topology where each node denotes a container and each edge is a connection between two containers if one calls the other.
+The topology comprises an "Outside" node and a "Docker daemon" node, as well as Zuul, Eureka and other nodes.
 According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resilience, and security functionalities.
-Eureka is a REST (Representational State Transfer) based service that is primarily used in the cloud for locating services for the purpose of load balancing and fail-over of middle-tier servers.
-In Figure \ref{AttackGraph} we can see a part of the corresponding attack graph, where a node is a pair of the image and its privilege, while an edge represents an atomic attack.
-Parts of both graphs have been intentionally omitted to reduce complexity.
-An example path that an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gains USER privilege.
-With this USER privilege, an attacker can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain ADMIN privilege.
-Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container by exploiting CVE-2017-7600 via another crafted image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2017-7600}} and gain ADMIN privilege.
-It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka.
-Another path would be to exploit the CVE-2018-1124 vulnerability via creating entries in the file-system (procfs) by starting processes, which could result in crashes or arbitrary code execution\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2018-1124}}.
-This vulnerability can be exploited by having only USER privilege on Zuul to gain ADMIN privileges of the Eureka container directly.
-Our attack graph generator shows both paths since it is of  interest to see every possible route in which a container can be compromised.
+Eureka is a Representational State Transfer (REST) based service primarily used in the cloud for locating services for load balancing and fail-over of middle-tier servers.
+Figure \ref{AttackGraph} shows a part of the corresponding attack graph, where a node is a pair of the image and its privilege, while an edge represents an atomic attack.
+Parts of both graphs have been omitted intentionally for simplicity.
+An example path an attacker would take could be to first attack the Zuul container by exploiting the CVE-2016-10249 vulnerability by crafting an image file, which triggers a heap-based buffer overflow\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2016-10249}} and gains the USER privilege.
+With this USER privilege, an attacker can exploit the CVE-2015-7554 vulnerability on the same container via crafted field data in an extension tag in a TIFF image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2015-7554}} to gain the ADMIN privilege.
+Once the ADMIN privilege has been obtained on the Zuul container, the attacker can attack the Eureka container by exploiting CVE-2017-7600 via another crafted image\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2017-7600}} and gain the ADMIN privilege.
+Note that this is not the only path the attacker can take to obtain ADMIN privileges on the Eureka container.
+Another path would be to exploit the CVE-2018-1124 vulnerability by creating entries in the file system (procfs) by starting processes, which could result in crashes or arbitrary code execution\footnote{\url{https://nvd.nist.gov/vuln/detail/CVE-2018-1124}}.
+This vulnerability can be exploited by having only the USER privilege on Zuul to gain the ADMIN privileges of the Eureka container directly.
+Our attack graph generator shows both paths because it is of interest to identify all possible routes through which a container can be compromised.
 
@@
 
- Figure \ref{AttackGraphSystem} gives an overview of the attack graph generator.
-In the figure, the rectangles denote the main components of the system, while the arrows describe the flow of the system and the files are the intermediate products.
-Our attack graph generator is composed of three main components: \textit{Topology Parser, Vulnerability Parser, and Attack Graph Generator}.
-The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Generator, the Vulnerability Parser scans the vulnerabilities for each of the images and the Attack Graph Generator generates the attack graph from the topology and vulnerabilities files.
-In the following subsections, we first have a look into the system requirements, then describe each component in more details.
+ Figure \ref{AttackGraphSystem} shows an overview of our attack graph generator, where the rectangles denote the main system components, the arrows indicate the flow of the system and the files are intermediate products.
+The proposed attack graph generator comprises three primary components, i.e., the \textit{Topology Parser}, the \textit{Vulnerability Parser}, and the \textit{Attack Graph Generator}.
+The Topology Parser reads the underlying topology of the system and converts it to a format required by the Attack Graph Generator.
+The Vulnerability Parser scans the vulnerabilities for each image, and the Attack Graph Generator generates the attack graph from the topology and vulnerabilities files.
+In the following, we first examine the system requirements, and then describe each component in greater detail.
 
-The generator is developed and tested for Docker 17.12.1-ce, and Docker Compose 1.19.0 \cite{merkel2014docker}.
+The proposed generator was developed and tested for Docker 17.12.1-ce and Docker Compose 1.19.0 \cite{merkel2014docker}.
 Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of  multi-container applications.
-It provides a static configuration file that specifies the system containers, networks, and ports.
-Clair and ClairCtl \footnote{\url{https://github.com/coreos/clair}}  are used for vulnerabilities scanning.
-The generator is written in Python 3.6.
-Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners, and microservice architectures.
+Docker Compose provides a static configuration file that specifies the system containers, networks, and ports.
+Note that Clair and ClairCtl \footnote{\url{https://github.com/coreos/clair}} were used for vulnerability scanning.
+The generator was written in Python 3.6.
+Although we used specific versions of these tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners, and microservice architectures.
 
@@
 	\includegraphics[scale=0.9]{./images/AttackGraphSystem}
-	\caption{Overview of the Attack Graph Generator System}
+	\caption{Overview of the proposed attach graph generator system}
 	\label{AttackGraphSystem}
@@
 
-To generate an attack graph of a given system, we require an arrangement of its components and connections described as a system topology.
-The topology of Docker containers can be described either at  runtime or at design time by using Docker Compose.
-In our case, since we are doing static attack graph analysis, we use Docker Compose to extract the topology.
-Docker Compose provides a  file (docker-compose.yml) which is used to describe the orchestration of the services.
-That is to say, the file exists anyway; no further input from the security analyst is required.
-However different versions of docker-compose.yml, use different syntax.
-For example, older versions use the deprecated keyword "\textit{link}", while newer ones use exclusively "\textit{networks}", to denote a connection between two images.
-We use the keyword "\textit{networks}" as an indicator that a connection between two images exists.
+To generate an attack graph for a given system, we must arrange its components and connections as a system topology.
+The topology of Docker containers can be described at runtime or design time using Docker Compose.
+In our case, we are performing a static attack graph analysis; thus, we used Docker Compose to extract the topology.
+Docker Compose provides a file (docker-compose.yml) that is used to describe the orchestration of the services.
+In other words, this file already exists; therefore, no further input is required from a security analyst.
+However, different versions of the docker-compose.yml file use different syntax.
+For example, older versions use the deprecated keyword "\textit{link}," while newer versions exclusively use "\textit{networks}" to denote a connection between two images.
+Here, we use the keyword "\textit{networks}" to indicate a connection between two images.
 
-In the majority of cases, for an application to be useful, it communicates with the outside world, i.e., it has endpoints that can be used by the outer network.
-In Docker, this is usually done by  publishing ports.
-This is the case in both computer networks, as well as in microservice architectures.
+For an application to be useful in most cases, it communicates with the outside world, i.e., it has endpoints that can be used by an outer network.
+In Docker, this is typically accomplished by publishing ports.
+This is the case for both computer networks and microservice architectures.
 
-Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}}.
-Some containers obtain certain privileges that grant them control over the Docker daemon in order to function properly.
-For example, a user may want to run some hardware (e.g., web-cam) or some applications that demand higher privilege levels  from Docker.
-In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file.
-An attacker with access to these containers  also has  access to the Docker daemon.
-Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.
+Another consideration is \textit{privileged access}\footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}}.
+In order to function properly, some containers obtain certain privileges that grant them control over the Docker daemon.
+For example, a user may want to run hardware (e.g., a webcam) or applications that demand higher privilege levels from Docker.
+In Docker, this is typically achieved either by mounting the Docker socket or specifying the "privileged" keyword in the docker-compose.yml file.
+Here, an attacker with access to these containers also has access to the Docker daemon.
+Once the attacker has access to the Docker daemon, he has potential access to the entire microservice system because each container is controlled and hosted by the daemon.
 
@@
 
-In the preprocessing step, we use Clair to generate the vulnerabilities of a given image.
-Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing \textit{CVE-ID}, a description and attack vector for each vulnerability.
-An attack vector is an entity that describes which conditions and effects are connected to this vulnerability.
-We collect the fields in the attack vector which are,  as defined by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete).
+In the preprocessing step, we use Clair to generate the vulnerabilities for a given image.
+Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing a \textit{CVE-ID}, a description and an attack vector for each vulnerability.
+An attack vector is an entity that describes which conditions and effects are connected to the given vulnerability.
+We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}, i.e.,Access Vector (Local, Adjacent Network, Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete), and Availability Impact (None, Partial, Complete).
 Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl to analyze a complete Docker image.
@@
 
-After the topology  is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation.
-Here, we first pre-process the vulnerabilities and convert them into sets of pre- and postconditions.
-In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
-When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule.
-An example of a precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}.
-If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions.
-If no rule matches, we take None as a precondition and ADMIN(OS) as a postcondition.
+After the topology is extracted and the vulnerabilities for each container are generated, we proceed to attack graph generation.
+Here, we first preprocess the vulnerabilities and convert them to sets of preconditions and postconditions.
+To achieve this, we match the previously acquired attack vectors from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules.
+When a subset of attack vector fields and description keywords matches a given rule, we use the precondition or postcondition of that rule.
+An example precondition attack rule would be for a vulnerability to have "gain root," "gain unrestricted, root shell access" or "obtain root" in its description and the impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" to obtain the OS(ADMIN) precondition \cite{aksu2018automated}.
+If more than one rule matches, we take the rule with the highest privilege level for preconditions and the lowest privilege level for postconditions.
+If no rule matches, we take None as the precondition and ADMIN(OS) as the postcondition.
 This results in a list of container vulnerabilities with their preconditions and postconditions.
@@
 
-After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted.
-Together with the topology, they are feed into a Breadth-first Search algorithm (BFS).
-Breadth-first Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before diving deeper into the graph.
-Pseudo-code of our modified Breadth-first Search is given in Algorithm \ref{BFSalgorithm}.
-The algorithm requires a topology, a dictionary of the exploitable vulnerabilities and a list of nodes with privileged access as an input and the output is made up of nodes and edges that make the attack graph.
-Topology (Subsection \ref{chap:topology_p}) provides the information about the connectivity between the containers, cont\_expl (Subsections \ref{chap:vulnerability_p} and \ref{chap:attack_graph_p}) contains information regarding which vulnerabilities can be attacked (with their pre- and postconditions), and priv\_acc (Subsection \ref{chap:topology_p}) is the array of nodes that have high (ADMIN) permissions to the Docker daemon.
-The algorithm first initializes the nodes, edges, queue and the passed nodes (Lines \ref{alg:init_1}, \ref{alg:init_2}).
-Afterward, it generates the attacker node (line \ref{alg:attackNodeInit}) from where the attack starts.
-The attacker node is a combination of the image name ("Outside") and the privilege level (ADMIN).
-Then into a while loop (Line \ref{alg:while}), it iterates through every node (Line \ref{alg:get_node}), checks its neighbors (Line \ref{alg:neigh}) and adds the edges if the conditions are satisfied (Lines \ref{alg:daemonEdge}, \ref{alg:privEdge}, \ref{alg:addEdge}).
-If the neighbor was not passed, then it is added to the queue (Line \ref{alg:putQueue}).
-The algorithm terminates when the queue is empty (Line \ref{alg:while}).
+After preprocessing, the vulnerabilities are parsed and their preconditions and postconditions are extracted.
+Together with the topology, they are fed into a BFS algorithm.
+BFS is a popular search algorithm that traverses a graph by first looking at the neighbors of a given node before diving deeper into the graph.
+The pseudocode for our modified BFS algorithm is given in Algorithm \ref{BFSalgorithm}.
+This algorithm requires a topology, a dictionary of the exploitable vulnerabilities and a list of nodes with privileged access as input.
+The output comprises nodes and edges that form the attack graph.
+In Algorithm \ref{BFSalgorithm}, "topology" (Subsection \ref{chap:topology_p}) provides information about the connectivity between containers, "cont\_expl" (Subsections \ref{chap:vulnerability_p} and \ref{chap:attack_graph_p}) contains information about which vulnerabilities can be attacked (with their preconditions and postconditions), and "priv\_acc" (Subsection \ref{chap:topology_p}) is an array of nodes with high (i.e., ADMIN) permissions to the Docker daemon.
+First, the algorithm initializes the nodes, edges, queue, and passed nodes (lines \ref{alg:init_1} and \ref{alg:init_2}).
+Then, it generates the attacker node (line \ref{alg:attackNodeInit}) as the node where the attack begins.
+The attacker node is a combination of the image name ("outside") and the privilege level (ADMIN).
+Then, in a while loop (line \ref{alg:while}), the algorithm iterates through each node (line \ref{alg:get_node}), checks the given node's neighbors (line \ref{alg:neigh}), and adds the edges if the conditions are satisfied (lines \ref{alg:daemonEdge}, \ref{alg:privEdge} and \ref{alg:addEdge}).
+If a neighbor was not passed, then it is added to the queue (line \ref{alg:putQueue}).
+The algorithm terminates when the queue is empty (line \ref{alg:while}).
 Furthermore, BFS is characterized by the following properties.
@@
 \begin{itemize}
-	\item Completeness: Breadth-first Search is complete, i.e., if there is a solution, Breadth-first search will find it regardless of the kind of graph.
+	\item Completeness: BFS is complete, i.e., if there is a solution, BFS will find it regardless of the graph type.
 	\item Termination: This follows from the monotonicity property.
 Monotonicity is ensured if it is assumed that an attacker will never need to relinquish a state \cite{ingols2006practical, ou2006scalable, ammann2002scalable}.
-In this implementation, each edge is traversed only once, making sure that monotonicity is preserved.
-	\item  Complexity: is $O(|N| + |E|)$ where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
+In this implementation, each edge is traversed only once, which ensures that monotonicity is preserved.
+	\item  Complexity: The algorithm's complexity is $O(|N| + |E|)$, where $|N|$ is the number of nodes and $|E|$ is the number of edges in the attack graph.
 \end{itemize}

### 2018-10-21 paper_own_docker/chapters/evaluation.tex
last round of fixes
Evaluation updated based on proof-reading feedback

@@
 
-Real-world microservice systems are composed of many containers that run different technologies with various degrees of connectivity among each other.
-This raises the need for a robust and scalable attack graph generator.
-In Subsection \ref{chap:heterogenious_systems}, we first our use-cases.
-We then have a look at how others evaluate their systems.
-Finally, in Subsection \ref{chap:scalability_eval}, we conduct experiments to test the scalability of our system with a different number of containers and connectivity.
-All of the experiments were performed on an Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.
-
 \subsection{Use Cases}
 \label{chap:heterogenious_systems}
-\begin{table*}[t]
+\begin{table*}[!htb]
 	\begin{center}
@@
 			\hline
-			Name & Description & Technology Stack & No. Containers & No. vuln. & Github link \\\hline
+			Name & Description & Technology Stack & No. Containers & No. vuln. & GitHub link \\\hline
 
@@
 
-	\caption{Microservice architecture examples analyzed by the attack graph generator}
+	\caption{Microservice architecture examples analyzed by proposed attack graph generator}
 	\label{table_technologies}
@@
 
-Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity, and number of vulnerabilities.
-Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios.
-To do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}.
-We intended to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains.
-We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging.
-The resulting examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo.
-NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses many tools like Spring Cloud, Netflix Ribbon, and Netflix Eureka.
-Atsea Sample Shop App is an e-commerce sample web application consisting  of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL.
-JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE.
-We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al.
+Real-world microservice systems comprise many containers that run different technologies with various degrees of connectivity among each other.
+This raises the need for a robust and scalable attack graph generator.
+First, we demonstrate use cases in Subsection \ref{chap:heterogenious_systems}.
+We then examine how others have evaluated their systems.
+In Subsection \ref{chap:scalability_eval}, we discuss experiments conducted to test the scalability of the proposed system with different numbers of containers and varying degrees of connectivity.
+Note that all experiments were performed on an Intel(R) Core(TM) i5-7200U CPU (2.50GHz) with 8 GB of RAM running Ubuntu 16.04.3 LTS.
+
+Modern microservice architectures use many different technologies,  different numbers of containers, various degrees of connectivity, and have different numbers of vulnerabilities.
+Therefore it is critically important to demonstrate that an attack graph generator works well in such heterogeneous scenarios.
+Here, we tested the proposed system on real and slightly modified GitHub examples (Table \ref{table_technologies}).
+We employed test examples that are publicly available to facilitate potential future comparison characterized by different system properties (e.g., topologies, technologies and vulnerabilities) and different usage domains.
+We also had to consider the fact that an overwhelming majority of publicly-available examples are small, i.e., only one or a few containers, which made finding appropriate test examples challenging.
+The resulting examples are as follows: NetflixOSS, the Atsea Sample Shop App, and the JavaEE demo.
+NetflixOSS is a microservice system provided by Netflix comprising of 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
+The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX and PostgreSQL.
+The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React and Tomcat EE.
+We ran the attack graph generator and manually verified the resulting attack graphs for the small examples based on domain knowledge under the assumption that the output from Clair, the NVD attack vectors \cite{booth2013national}, and the preconditions and postconditions from Aksu et al.
 \cite{aksu2018automated} are \textit{correct}.
-After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges.
-The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks.
-This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation.
-Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps to reach the target container.
-All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property.
-Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed.
-The Phpmailer and Samba  system is an artificial example that we use and extend in the following subsection to perform these scalability tests.
+After running the proposed attack graph generator, the attack graphs for the Atsea Sample Shop App and JavaEE demo were small as expected, containing only a few nodes and edges.
+The structure of the NetflixOSS attack graph demonstrated a nearly linear structure in which each node was connected to a small number of other nodes to form a chain of attacks.
+This linearity is due to the fact that each container is connected to only a few other containers to reduce unnecessary communication and increase encapsulation.
+Therefore, based on this degree of connectivity an attacker needs to perform multiple intermediate steps to reach the target container.
+Note that all examples terminated, there were no directed edges from containers with higher privileges to lower privileges, no duplication of nodes, and no reflexive edges were observed, which is in line with the monotonicity property.
+In addition, the run time of the proposed system with each example was short, however, additional scalability tests were required.
+Therefore, the Phpmailer and Samba system was extended and employed as an artificial example to perform scalability tests.
+This is discussed in the following subsection.
 
@@
 
-			Breadth-First Search time & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
+			BFS time & 0.2763 & 1.6524 & 6.5527 & 165.3634 & 767.5539 \\
 
@@
 
-	\caption{Scalability results with the graph characteristics and execution times in seconds.}
+	\caption{Scalability results with graph characteristics and execution times (s)}
 
@@
 \end{table*}
-Extensive scalability study of attack graph generators is rare in current literature, and many parameters contribute to the complexity of a comprehensive analysis.
-Parameters that usually vary in this sort of evaluation are the number of nodes, their connectivity and the number of vulnerabilities per container.
-All of these components contribute to the execution time of a given algorithm.
-Even though the definitions of an attack graph differ, we hope to reach a comprehensive comparison with current methods.
-In this case, we compare our system to existing work in computer networks by treating every container as a host machine, and any physical connection between two machines as a connection between two containers.
-In the following, we first look at three works and their scalability evaluation results.
-After this comparison, we present the scalability results of our system.
+Extensive study of the scalability of attack graph generators is rare in the current literature, and many parameters contribute to the complexity of comprehensive analyses.
+Parameters that typically vary in this sort of evaluation include the number of nodes, their connectivity and the number of vulnerabilities per container, all of which contribute to the execution time of a given algorithm.
+Even though the definitions of an attack graph differ, we hope to achieve a comprehensive comparison with current methods.
+Here, we compared the proposed system to existing work in computer networks by treating each container as a host machine and any physical connection between two machines as a connection between two containers.
+In the following, we first examine three methods and their scalability evaluation results.
+We then present the scalability results of the proposed system.
 
 Sheyner et al.
-\cite{sheyner2002automated} test their system in both small and extended examples.
+\cite{sheyner2002automated} tested their system (NuSMV) using both small and extended examples.
 The attack graph in the larger example has 5948 nodes and 68364 edges.
-The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes.
-The authors claim that the performance bottleneck is inside the graph generation procedure.
+The time required for NuSMV to execute this configuration was two hours; however, the model checking component took four minutes.
+The authors claim that the performance bottleneck resides in the graph generation procedure.
 Ingols et al.
 \cite{ingols2006practical} tested their system on a network of 250 hosts.
-They afterward continued the study on a simulated network of 50000 hosts in under 4 minutes.
-Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple-Prerequisite graph, which is different from ours.
-In addition to this, missing an explanation of how the hosts are connected, does not make it directly comparable to our method.
+They continued the study on a simulated network with 50000 hosts in under four minutes.
+Although their method yields better performance than NuSMV, their evaluation was based on a MP graph, which differs from our target graph.
 Ou et al.
-\cite{ou2006scalable} provide some more extended study where they test their system (MulVAL) on more examples.
-They mention that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
-The performance of the system for 1000 fully connected nodes takes more than 1000 seconds to execute.
+\cite{ou2006scalable} provided a more extensive study wherein they tested their system (MulVAL) using more examples.
+They state that the asymptotic CPU time was between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
+With 1000 fully-connected nodes, their system required more than 1000 seconds to execute.
 % The authors also provide an evaluation where he MulVAL clearly outperforms the Sheyner's system.
 
-In our scalability experiments, we use Samba \cite{samba} and Phpmailer \cite{phpmailer} containers.
-We extended this example and artificially created fully connected topologies of \textit{20, 50, 100, 500 and 1000} Samba containers to test the scalability of the system.
-The Phpmailer container has \textit{181} vulnerabilities, while the Samba container has \textit{367} vulnerabilities reported by Clair.
-In our tests, we measure the total execution time as well as partial times: Topology parsing time, Vulnerability preprocessing time and Breath-first Search time.
-The total time contains the topology parsing, the attack graph generation and some minor utility processes.
-The Topology parsing time is the time required to generate the graph topology.
-The Vulnerability preprocessing time is the time needed to convert the vulnerabilities into sets of pre- and postconditions.
-The Breath-first Search time is the time needed for Breadth-first Search to traverse the topology and generate the attack graph after the previous steps are done.
-All of the components are executed five times for each of the examples and their final time is averaged.
-The times are given in seconds.
-However, the total time does not include the vulnerability analysis by Clair.
-Evaluation of Clair is not in the scope of this analysis.
+We used Samba \cite{samba} and Phpmailer \cite{phpmailer} containers in our scalability experiments.
+We extended this example and artificially created fully-connected topologies of \textit{20, 50, 100, 500, and 1000} Samba containers to test the scalability of the proposed system.
+As reported by Clair, the Phpmailer container has \textit{181} vulnerabilities and the Samba container has \textit{367} vulnerabilities.
+In our tests, we measured the total execution time and partial times, i.e., topology parsing time, vulnerability preprocessing time, and BFS time.
+The total time contains topology parsing, attack graph generation, and other utility processes.
+Here, the topology parsing time is the time required to generate the graph topology, the vulnerability preprocessing time is the time required to convert vulnerabilities into sets of preconditions and postconditions, and the BFS time is the time required for the BFS algorithm to traverse the topology and generate the attack graph after the previous steps are complete.
+All components were executed five times for each example and their final time was averaged.
+Note that the measured times are given in seconds.
+However, the total time does not include the Clair vulnerability analysis, because this evaluation is beyond the scope of this analysis.
 
-Table \ref{table_scalability} shows the results of our experiments.
-In each of these experiments, the number of Phpmailer containers stays constant, while the number of Samba containers is increasing.
-This increase is done in a fully connected fashion, where a node of each container is connected to every other container.
-In addition, there are also two additional artificial containers: "outside" that represents the environment from where the attacker can attack and the "docker host", i.e., the Docker daemon where the containers are hosted.
-Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers.
-The number of edges of the topology graph is a combination of one edge ("outside"-"Phpmailer"), n edges ("docker host" to all of the containers) and n*(n+1)/2 edges of between Phpmailer and Samba containers.
-For example\_20, the number of containers is 23 (one Phpmailer, one "outside", one "docker host" and 20 Samba containers) the number of edges in the topology graph would be 253: one outside edge, 21 Docker host edges (one toward Phpmailer and 20 toward the Samba containers) and 231 between-container edges (21*22/2=231).
+Table \ref{table_scalability} shows the experimental results.
+In each experiment, the number of Phpmailer containers was constant.
+In contrast, the number of Samba containers increased in a fully-connected manner, where a node of each container was connected to all other containers.
+In addition, there were also two additional artificial containers, i.e., "outside," which represents the environment from where the attacker can attack, and the "docker host," i.e., the Docker daemon where containers are hosted.
+Thus, the total number of nodes in the topology graph is the sum of "outside," "docker host," the number of Phpmailer containers, and the number of Samba containers.
+The number of edges in the topology graph is a combination of one edge ("outside"-"Phpmailer"), n edges ("docker host" to all containers) and n*(n+1)/2 edges between the Phpmailer and Samba containers.
+For example\_20, the number of containers is 23 (one Phpmailer container, one "outside" container, one "docker host" container, and 20 Samba containers).
+Thus, the number of edges in this topology graph is 253, i.e., one outside edge, 21 Docker host edges (one toward Phpmailer and 20 toward the Samba containers), and 231 between-container edges (i.e., 21*22/2=231).
 
-Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step.
-However, this step increases linearly because the container files are analyzed only once by Clair.
-The attack graph generation for the smaller examples is considerably less than the preprocessing time.
-Starting from example\_500, we can notice a sharp increase in execution time to 165 seconds.
-For the previous example with example\_100, the attack graph was generated in  6.5 seconds.
+Throughout the experiments, the greatest time bottleneck was the preprocessing step for the smaller configurations.
+However, this time increased linearly because the container files are analyzed only once by Clair.
+Note that the attack graph generation time for the smaller examples was considerably less than the preprocessing time.
+For example\_500, we note a sharp increase in execution time (165 seconds) compared to the previous example (i.e., example\_100), where the attack graph was generated in 6.5 seconds.
 
-The total time of the attack graph generation procedure for 1000 fully connected hosts (784 seconds) outperforms results from OurOu et al.
+The total time of the attack graph generation procedure for 1000 fully-connected hosts (784 seconds) was better than the results of Ou et al.
 \cite{ou2006scalable}, i.e., 1000 seconds.
-In the Sheyners's extended example(4 hosts, 8 atomic attacks and multiple vulnerabilities) the attack graph took 2 hours to create.
-Our attack graph procedure even for the bigger number of hosts(1000) shows faster attack graph generation time.
-It, however, performs worse than the generator from Ingols et al., but that is attributed to the usage of MP attack graph which is different from ours.
+In Sheyners's extended example (four hosts, eight atomic attacks and multiple vulnerabilities), the attack graph took two hours to create.
+In contrast, even for a greater number of hosts (1000), the proposed attack graph procedure demonstrates faster attack graph generation time.
+However, the proposed system performs worse than the generator proposed by Ingols et al., but that is attributed to the usage of the MP attack graph, which differs from our target graph.
 
-In summary, we found out  that our algorithm generates  attack graphs efficiently, it handles a system with a \textit{thousand} container in 13 minutes.
-Considering the strongly connected system in the experiment, and the high number of vulnerabilities in it, we think that the results of this experiment show a practical solution that can be used as part of the continuous delivery process of real-world systems.
+In summary, we found that the proposed algorithm generates attack graphs efficiently, i.e., it handles a system with 1000 containers in 13 minutes.
+Considering the strongly-connected system employed in the experiment and the high number of vulnerabilities in it, we consider that the results demonstrate that the proposed system is a practical solution that can be used as part of the continuous delivery processes of real-world systems.

### 2018-10-21 paper_own_docker/chapters/conclusion.tex
Related work and conclusion updated based on proof-reading feedback

@@
 
-Microservices are a promising architectural style that advocate practitioners to build systems as a group of small connected  services.
-Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns.
-In this paper, we proposed to use automated attack graph generation as part of the practices of developing microservice-based architectures.
-Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services.
-The manual construction of attack graphs is an error-prone, resource consuming activity.
-Hence, automating this process does not only guarantee efficient construction but also complies with the spirit of DevOps practices.
-We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.
+Microservices are a promising architectural style that encourage practitioners to build systems as a group of small connected  services.
+Although such architectures can realize better scalability and faster deployment, full container-based automation raises many security concerns.
+In this paper, we have proposed the use of automated attack graph generation relative to the development of microservice-based architectures.
+Attack graphs help developers identify attack paths that comprise exploitable vulnerabilities in deployed services.
+Manual construction of attack graphs is an error-prone, resource consuming activity; therefore, automating this process guarantees efficient construction and complies with the spirit of DevOps practices.
+By extending previous work in field of computer networks, we have demonstrated that such automation is efficient and scales to large and complex microservice-based systems.
 
-As a future work, we plan to extend this work to support more frameworks that are used in microservices systems.
-We also plan to study the possible analysis of the resulting attack graphs for purposes of attack detection, and post-postmortem forensics investigations.
+In future work, we plan to extend this work to support more frameworks used in microservice systems.
+We also plan to study possible analysis of the resulting attack graphs for use in attack detection and post-postmortem forensics investigations.

### 2018-10-21 paper_own_docker/chapters/related_work.tex
last round of fixes
Related work and conclusion updated based on proof-reading feedback

@@
 
-Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.
+Previous studies have examined attack graph generation, primarily relative to computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet.
 %In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host.
@@
 Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
-One of the earlier works in attack graph generation was done by Sheyner et al.
-by using model checkers with goal property \cite{sheyner2002automated}.
-Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counterexample.
+One early study of attack graph generation was conducted by Sheyner et al.
+using model checkers with a goal property \cite{sheyner2002automated}.
+Model checkers use computational logic to determine if a model is correct; otherwise, if the model is incorrect, the model checkers provide a counterexample.
 A collection of these counterexamples form an attack graph.
-They state that model checkers satisfy a monotonicity property  to ensure termination.
+Sheyner et al.
+stated that model checkers satisfy the monotonicity property to ensure termination.
 However, model checkers have a computational disadvantage.
@@
  Amman et al.
-extend this work with some simplifications and more efficient storage \cite{ritchey2000using}.
+extended this work with some simplifications and more efficient storage \cite{ritchey2000using}.
 Ou et al.
-use a logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al.
-use a Breadth-first search algorithm in order to tackle the scalability issue.
+used a logical attack graph \cite{ou2006scalable} and Ingols et al.
+\cite{ingols2006practical} used BFS algorithm to tackle the scalability issue.
 Ingols et al.
-discuss the redundancy Full and Predictive graphs and model an attack graph as an MP graph with content-less edges and 3 types of nodes.
-They use Breath-first search technique for generating the attack graph.
-This approach provides faster results in comparison to using model checkers.
-An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.
+discussed the redundancy of full and predictive graphs and modeled an attack graph as an MP graph with contentless edges and three node types.
+They used BFS technique to generate the attack graph.
+This approach provides faster results compared to using model checkers.
+For example, with this method, an MP graph with 8901 nodes and 23315 edges was constructed in 0.5 seconds.
 Aksu et al.
-build on top of Ingols's system and evaluate a set of rule pre- and postconditions in generating attacks.
-They define a specific test of pre- and postcondition rules and test their correctness.
-In their evaluation, they use a machine learning approach \cite{aksu2018automated}.
+conveyed a study on top of Ingols's system.
+They defined a specific set of precondition and postcondition rules and tested their correctness.
+Note that they used a machine learning approach in their evaluation \cite{aksu2018automated}.
 
-Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their  need of connectivity and a lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}.
-To the best of our knowledge, no previous work that has been done  in the area of attack graph generation for Docker containers.
-Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers.
+Despite their increasing popularity, containers and microservice architectures have demonstrated serious security risks, primarily due to their connectivity requirements and lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}.
+To the best of our knowledge, no previous study has been conducted relative to attack graph generation for Docker containers.
+Similar to computer networks, microservice architectures have a container topology and tools for container analysis.
 Containers in our model correspond to hosts, and a connection between hosts translates to communication between containers.
 
-In summary, our contribution is proposing attack graph generation as part of the DevOps practices, and providing a tool-support for this idea.
-To that end, we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction with Clair OS to generate attack graphs for microservice architectures.
+In summary, our contribution is using attack graph generation as part of DevOps practices and providing tool support for this concept.
+To that end, we have extended the work of Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction with the Clair OS to generate attack graphs for microservice architectures.

### 2018-10-21 paper_own_docker/chapters/abstract.tex
Abstract and introduction updated based on proof-reading feedback

--- 2018-09-14 paper_own_docker/chapters/abstract.tex
@@
-Microservices are increasingly dominating the field of service systems, among their many characterstics, practices are technology heterogeneity and reuse and network interfaces.
-Therefore, with the increase of utilizing third-party components, the potential vulanrabilities existing in a microservice-based system increase.
-Based on components dependency, these vulnerabilities lead to exposing critical assets of such systems.
-Similar problems have been tackled in computer networks communities.
-In this paper, we propose the utilization of attack graphs as a part of the automated development infrastructure used in microservices-based systems.
-To that end, we relate microservices to network nodes, and automatically generate attack graphs that help practitioners to identify, analyze, and prevent plausible attack paths on their microservice-based container networks.
-We present a complete solution that can be easily embeded into the continuous delivery systems, and show with real-world use cases its efficiency and scalability.
+Microservices, which are typically technologically heterogenous and can be deployed automatically, are increasingly dominating service systems.
+However, with increased utilization of third-party components distributed as images, the potential vulnerabilities in microservice-based systems increase.
+Based on component dependency, such vulnerabilities can lead to exposing a system's critical assets.
+Similar problems have been addressed by the computer networks community.
+In this paper, we propose utilizing attack graphs in the continuous delivery infrastructure of microservices-based systems.
+To that end, we relate microservices to network nodes and automatically generate attack graphs that help practitioners identify, analyze, and prevent plausible attack paths in their microservice-based container networks.
+We present a complete solution that can be easily embedded in continuous delivery systems and demonstrate its efficiency and scalability based on real-world use cases.
 %Breath-first Search (BFS) based method for attack graph generation and security analysis of microservice architectures using Docker

### 2018-10-21 paper_own_docker/chapters/introduction.tex
Abstract and introduction updated based on proof-reading feedback

--- 2018-09-23 paper_own_docker/chapters/introduction.tex
@@
 %intro about the new paradiagm of mirocservices its benefits and new oppurnties, maybe its utilization in secuirty/ safety critical systems
-Microservices, a recent approach to manage the complexity of modern applications, are increasingly adopted in real-world systems.
-The new architectural style follows the foundational principle of Unix that decomposes systems into small programs \cite{wolff2016microservices}, each fulfills only one cohesive task and can work together using universal interfaces.
-Each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{microservicesfrowler}.
-The smaller decoupled services have a positive impact on some system qualities like scalability, fault isolation, and technology heterogeneity \cite{newman2015building}.
-However, other qualities like the network utilization and the security can be negatively affected \cite{ahmadvand2016requirements}.
-Balancing the trade-off among these factors derive the decision of using microservices in industry.
-That said, a none-exhaustive list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} shows a significant shift by many enterprises across different domains towards using microservice-based architecture.
-This shift is motivated mainly by the demanding requirements of scalability, time to market, and better optimization of development efforts.
-We see microservice-based systems in domains of video streaming, social networks, logistics, Internet of things \cite{butzin2016microservices}, smart cities \cite{krylovskiy2015designing}, and security-critical systems \cite{fetzer2016building}.
+Microservices, a recent approach to managing the complexity of modern applications, are increasingly being adopted in real-world systems.
+Microservice architectures follow the fundamental principle of Unix, i.e., systems are decomposed into small programs \cite{wolff2016microservices}, each performing a single cohesive task.
+However, such programs can work together via universal interfaces, where each program is a microservice that is designed, developed, tested,  deployed, and scaled independently \cite{microservicesfrowler}.
+Smaller decoupled services have a positive impact on some system qualities, such as scalability, fault isolation, and technology heterogeneity \cite{newman2015building}; however, other qualities, such as network utilization and security, can be affected negatively \cite{ahmadvand2016requirements}.
+The decision to use microservices in industrial applications must consider the tradeoffs among these factors.
+That said, a list \footnote{\url{https://microservices.io/articles/whoisusingmicroservices.html}} of companies from different domains that use microservice-based architecture indicates a significant shift towards their use.
+This shift is primarily motivated by the demanding requirements of scalability, time to market, and improving development optimization.
+Microservice-based systems can be seen in various domains, such as video streaming, social networks, logistics, the Internet of Things \cite{butzin2016microservices}, smart cities \cite{krylovskiy2015designing}, and security-critical systems \cite{fetzer2016building}.
 
@@
 The utilization of microservices has popularized two main concepts in the software engineering community.
-The first is the \textit{container-based deployment}, in which the new small services are shipped and deployed in containers \cite{jaramillo2016leveraging}.
-As a result, the systems are deployed as networks of communicating microservices.
-For their lightweight and operating-system level virtualization \cite{bottomely}, the containerization frameworks like \textit{Docker} \cite{cerny2018contextual}, are a high performance alternative of hypervisors \cite{kratzke2017microservices}.
-The second often-used concept in the domain of microservices development is \textit{DevOps} \cite{cerny2018contextual}.
-\textit{DevOps} enable practices in which full automation of the deployment process is achieved.
-In the course of this, end-to-end automated packaging and deployment is a vital part of microservices development.
-In addition to the agility and optimization brought by the two concepts, major concerns around their impact on security \cite{ahmadvand2016requirements} arise.
-These concerns are motivated by the increasing communication end-points among the microservices, the potentially growing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by docker hub \cite{shu2017study,gummaraju2015over}, and the weaker isolation (than hypervisor-based virtualization) between the host and the container since all containers share the same kernel \cite{Bottomley,bui2015analysis}.
-In this paper, we tackle the problem of analyzing the security of the container networks using threat models \cite{kordy2014dag}.
+The first is \textit{container-based deployment}, where new small services are shipped and deployed in containers \cite{jaramillo2016leveraging}.
+As a result, such systems are deployed as networks of communicating microservices.
+Due to their lightweight and operating-system level virtualization \cite{bottomely}, containerization frameworks, such as \textit{Docker} \cite{cerny2018contextual}, have become a high-performance alternative to hypervisors \cite{kratzke2017microservices}.
+The second concept in microservices development is \textit{DevOps} \cite{cerny2018contextual}, which enable practices that can fully automate the deployment process.
+Here, end-to-end automated packaging and deployment is a vital component of microservice development.
+In addition to the agility and optimization realized by these two concepts, significant concerns have been raised about their security \cite{ahmadvand2016requirements}.
+These concerns are motivated by the increasing number of communication endpoints among microservices, the potentially increasing number of vulnerabilities emerging from open-source DevOps tools and third-party frameworks distributed by Docker hub \cite{shu2017study,gummaraju2015over}, and weaker isolation (compared to hypervisor-based virtualization) between hosts and containers because all containers share the same kernel \cite{bottomely, bui2015analysis}.
+In this paper, we address the problem of analyzing the security of container networks using threat models \cite{kordy2014dag}.
 Following the DevOps mentality, we propose an automated method that can be integrated into continuous delivery systems to generate attack graphs.
@@
 
-Security threat models are widely used to assess threats facing a system \cite{kordy2014dag}.
-Not only are they appealing to the practitioners as they provide a visual presentation of possible attack paths on a system, but also to scientists, since they are well formalized (syntax and semantics \cite{mauw2005foundations,jha2002two}).
-Such formalism enables quantitative and qualitative analysis of the risk, cost, and likelihood of the attacks, which affect the defense strategy.
-In computer networks, attack graphs \cite{sheyner2002automated,ou2006scalable} are the dominant threat model to inspect the security aspects of a network.
-They help analysts to carefully analyze system connections and detect the most vulnerable parts of the system.
-An attack graph depicts the actions that an attacker may use to reach their goal.
-Typically, experts (e.g., red teams) manually construct attack graphs.
-The manual process is time-consuming, error-prone and does not address the complexity of modern infrastructure.
+Security threat models are widely used to assess threats to a system \cite{kordy2014dag}.
+They appeal to practitioners because they provide visual presentations of possible attack paths in a system.
+They also appeal to scientists, because they are well formalized (syntax and semantics) \cite{mauw2005foundations,jha2002two}.
+Such formalism enables quantitative and qualitative analysis of the risk, cost, and likelihood of attacks, which affect defense strategies.
+In computer networks, attack graphs \cite{sheyner2002automated,ou2006scalable} are the dominant threat model used to inspect the security aspects of a network.
+They help analysts carefully analyze system connections and detect the most vulnerable parts of a system.
+An attack graph depicts the actions an attacker may use to reach their goal.
+Typically, experts (e.g., red teams) construct attack graphs manually; however, this manual process is time-consuming, error-prone, and does not address the complexity of modern infrastructures.
 %Within the last 15 years, there have been some proposals of approaches [e.g., 5-9] to automate the generation of attack graphs and attack trees in the domain of network security.
@@
 % contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
-Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated, ou2006scalable}.
-In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host.
-Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
+Previous studies have dealt with automatic attack graph generation for computer networks \cite{ingols2006practical, sheyner2002automated, ou2006scalable}.
+In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining the privileges of a specific host.
+Tools that scan the vulnerabilities of a particular host are available \cite{farmer1990cops}; however, they are insufficient to analyze the security of an entire network and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.
 
-To the best of our knowledge, an automated attack graph generation for microservice architectures was not tackled by any previous work.
-To that end, in this paper, we extend the advancement made in the computer networks field to the domain of microservices.
-Therefore the contribution of this paper is as follows.
+To the best of our knowledge, automated attack graph generation for microservice architectures has not been examined by previous studies.
+To that end, we extend advancements made in the computer networks field to the microservice domain.
+The primary contributions of this paper are summarized as follows.
 \begin{itemize}
-	\item We propose attack graphs as a new artifact of the continuous delivery systems.
-We present an approach, based on methods from computer networks, to automatically generate attack graphs for microservice-based architectures that are deployed as containers.
-	\item We present the technical details of an extensible tool that implements our approach. The tool is available for use at\footnote{}.
-	\item An empirical evaluation of the efficiency of our tool in generating attack graphs of real-world systems.
+	\item We propose attack graphs as a new artifact for continuous delivery systems.
+We present an approach based on methods from computer networks to automatically generate attack graphs for microservice-based architectures deployed as containers.
+	\item We present the technical details of an extensible tool that implements the proposed approach. Note that this tool is available online \footnote{The link is omitted for anonymization  purpose}.
+	\item We provide an empirical evaluation of the efficiency of the proposed approach relative to generating attack graphs for real-world systems.
 \end{itemize}
@@
 
-The structure of this paper is as follows.
-We introduce the preliminaries needed for this paper in Section \ref{chap:background}.
-We, then, present our approach in Section \ref{chap:method}, and its evaluation in Section \ref{chap:eval}.
+The remainder of this paper is organized as follows.
+We introduce preliminaries in Section \ref{chap:background}.
+Then, we present the proposed approach in Section \ref{chap:method}.
+An evaluation of the proposed approach is given in Section \ref{chap:eval}.
 We discuss related work in Section \ref{chap:related_work}.
-Lastly, conclusions and future work are discussed in Section \ref{chap:conclusion}.
+Conclusions and suggestions for future work are discussed in Section \ref{chap:conclusion}.

### 2018-10-31 paper_own_docker/chapters/background_attack_graphs.tex
Feedback annotated with uncorrected corrections in yellow, notes with description are added and uploaded. Some very small corrections are undertaken in the paper as well.

@@
 Ingols et al.
-made a distinction between full, predictive and multiple-prerequisite (MP) attack graphs.
-A full graph is a directed acyclic graph comprising of nodes that represent hosts and edges that represent vulnerability instances.
-Predictive attack graphs use the same representation as full attack graphs with the only difference lying in the constraint of when the edges are added to the attack graph.
+made a distinction between full, predictive, and multiple-prerequisite (MP) attack graphs.
+A full graph is a directed acyclic graph comprising nodes that represent hosts and edges that represent vulnerability instances.
+Predictive attack graphs use the same representation as full attack graphs, with the only difference lying in the constraint of when the edges are added to the attack graph.
 Note that predictive graphs are generally smaller than full graphs.
-An MP attack is an attack graph with contentless edges, state nodes, vulnerability instance nodes and prerequisite nodes \cite{ingols2006practical}.
+An MP attack is an attack graph with contentless edges, state nodes, vulnerability instance nodes, and prerequisite nodes \cite{ingols2006practical}.
 

### 2018-10-31 paper_own_docker/chapters/evaluation.tex
Feedback annotated with uncorrected corrections in yellow, notes with description are added and uploaded. Some very small corrections are undertaken in the paper as well.

@@
 \label{chap:eval}
+
+Real-world microservice systems comprise many containers that run different technologies with various degrees of connectivity among each other.
+This raises the need for a robust and scalable attack graph generator.
+We demonstrate use cases in Subsection \ref{chap:heterogenious_systems}.
+We then examine how others have evaluated their systems.
+In Subsection \ref{chap:scalability_eval}, we discuss experiments conducted to test the scalability of the proposed system with different numbers of containers and varying degrees of connectivity.
+Note that all experiments were performed on an Intel(R) Core(TM) i5-7200U CPU (2.50GHz) with 8 GB of RAM running Ubuntu 16.04.3 LTS.
 
@@
 
-Real-world microservice systems comprise many containers that run different technologies with various degrees of connectivity among each other.
-This raises the need for a robust and scalable attack graph generator.
-First, we demonstrate use cases in Subsection \ref{chap:heterogenious_systems}.
-We then examine how others have evaluated their systems.
-In Subsection \ref{chap:scalability_eval}, we discuss experiments conducted to test the scalability of the proposed system with different numbers of containers and varying degrees of connectivity.
-Note that all experiments were performed on an Intel(R) Core(TM) i5-7200U CPU (2.50GHz) with 8 GB of RAM running Ubuntu 16.04.3 LTS.
-
 Modern microservice architectures use many different technologies,  different numbers of containers, various degrees of connectivity, and have different numbers of vulnerabilities.
-Therefore it is critically important to demonstrate that an attack graph generator works well in such heterogeneous scenarios.
+Therefore, it is critically important to demonstrate that an attack graph generator works well in such heterogeneous scenarios.
 Here, we tested the proposed system on real and slightly modified GitHub examples (Table \ref{table_technologies}).
@@
 The resulting examples are as follows: NetflixOSS, the Atsea Sample Shop App, and the JavaEE demo.
-NetflixOSS is a microservice system provided by Netflix comprising of 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
-The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX and PostgreSQL.
-The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React and Tomcat EE.
+NetflixOSS is a microservice system provided by Netflix comprising 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
+The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX, and PostgreSQL.
+The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React, and Tomcat EE.
 We ran the attack graph generator and manually verified the resulting attack graphs for the small examples based on domain knowledge under the assumption that the output from Clair, the NVD attack vectors \cite{booth2013national}, and the preconditions and postconditions from Aksu et al.
@@
 This linearity is due to the fact that each container is connected to only a few other containers to reduce unnecessary communication and increase encapsulation.
-Therefore, based on this degree of connectivity an attacker needs to perform multiple intermediate steps to reach the target container.
+Therefore, based on this degree of connectivity, an attacker needs to perform multiple intermediate steps to reach the target container.
 Note that all examples terminated, there were no directed edges from containers with higher privileges to lower privileges, no duplication of nodes, and no reflexive edges were observed, which is in line with the monotonicity property.
@@
 Ou et al.
-\cite{ou2006scalable} provided a more extensive study wherein they tested their system (MulVAL) using more examples.
+\cite{ou2006scalable} provided a more extensive study, wherein they tested their system (MulVAL) using more examples.
 They state that the asymptotic CPU time was between $O(n^2)$ and $O(n^3)$, where n is the number of nodes (hosts).
@@
 In summary, we found that the proposed algorithm generates attack graphs efficiently, i.e., it handles a system with 1000 containers in 13 minutes.
-Considering the strongly-connected system employed in the experiment and the high number of vulnerabilities in it, we consider that the results demonstrate that the proposed system is a practical solution that can be used as part of the continuous delivery processes of real-world systems.
+Considering the strongly-connected system employed in the experiment and the high number of vulnerabilities in this system, we consider that the results demonstrate that the proposed system is a practical solution that can be used as part of the continuous delivery processes of real-world systems.

### 2018-10-31 paper_own_docker/chapters/method.tex
Feedback annotated with uncorrected corrections in yellow, notes with description are added and uploaded. Some very small corrections are undertaken in the paper as well.

@@
 In Subsection \ref{chap:mapping}, we discuss how the existing components of attack graph generation for a computer network are mapped to a microservice environment, and the concepts are illustrated using a small example.
-Then, in Subsection \ref{chap:technical}, we present the tools we use to achieve this mapping and provide an overview of the proposed system and its components, i.e., the Topology Parser (Subsection \ref{chap:topology_p}), the Vulnerability Parser (Subsection \ref{chap:vulnerability_p}) and the Attack Graph Generator (Subsection \ref{chap:attack_graph_p}).
+Then, in Subsection \ref{chap:technical}, we present the tools we use to achieve this mapping and provide an overview of the proposed system and its components, i.e., the Topology Parser (Subsection \ref{chap:topology_p}), the Vulnerability Parser (Subsection \ref{chap:vulnerability_p}), and the Attack Graph Generator (Subsection \ref{chap:attack_graph_p}).
 In addition, the Breath-first Search (BFS) graph traversal algorithm is discussed in Subsection \ref{chap:bfs}.
@@
 The Netflix OSS example is a Spring Cloud-based microservice architecture that uses the following microservices: Service Discovery (Eureka), Circuit Breaker (Hystrix), Intelligent Routing (Zuul), and Client Side Load Balancing (Ribbon).
-Figure \ref{TopologyGraph} shows a subset of the example topology where each node denotes a container and each edge is a connection between two containers if one calls the other.
-The topology comprises an "Outside" node and a "Docker daemon" node, as well as Zuul, Eureka and other nodes.
+Figure \ref{TopologyGraph} shows a subset of the example topology, where each node denotes a container and each edge is a connection between two containers if one calls the other.
+The topology comprises an "Outside" node and a "Docker daemon" node, as well as Zuul, Eureka, and other nodes.
 According to Netflix, Zuul is an edge service that provides dynamic routing, monitoring, resilience, and security functionalities.
@@
 An attack vector is an entity that describes which conditions and effects are connected to the given vulnerability.
-We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}, i.e.,Access Vector (Local, Adjacent Network, Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete), and Availability Impact (None, Partial, Complete).
+We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}, i.e., Access Vector (Local, Adjacent Network, Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete), and Availability Impact (None, Partial, Complete).
 Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl to analyze a complete Docker image.
@@
 The pseudocode for our modified BFS algorithm is given in Algorithm \ref{BFSalgorithm}.
-This algorithm requires a topology, a dictionary of the exploitable vulnerabilities and a list of nodes with privileged access as input.
+This algorithm requires a topology, a dictionary of the exploitable vulnerabilities, and a list of nodes with privileged access as input.
 The output comprises nodes and edges that form the attack graph.

### 2018-11-27 paper_own_docker/chapters/evaluation.tex
Minor comments from reviewer 2 fixed

@@
 We also had to consider the fact that an overwhelming majority of publicly-available examples are small, i.e., only one or a few containers, which made finding appropriate test examples challenging.
-The resulting examples are as follows: NetflixOSS, the Atsea Sample Shop App, and the JavaEE demo.
-NetflixOSS is a microservice system provided by Netflix comprising 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
-The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX, and PostgreSQL.
-The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React, and Tomcat EE.
+The resulting examples are as follows:
+
+\begin{itemize}
+	\item NetflixOSS is a microservice system provided by Netflix comprising 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
+	\item The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX, and PostgreSQL.
+	\item The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React, and Tomcat EE.
+\end{itemize}
+
    We ran the attack graph generator and manually verified the resulting attack graphs for the small examples based on domain knowledge under the assumption that the output from Clair, the NVD attack vectors \cite{booth2013national}, and the preconditions and postconditions from Aksu et al.

### 2018-11-27 paper_own_docker/chapters/method.tex
Minor comments from reviewer 2 fixed

@@
 An attack vector is an entity that describes which conditions and effects are connected to the given vulnerability.
-We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}, i.e., Access Vector (Local, Adjacent Network, Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete), and Availability Impact (None, Partial, Complete).
+We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}:
+
+\begin{itemize}
+	\item Access Vector (Local, Adjacent Network, Network)
+	\item Access Complexity (Low, Medium, High)
+	\item Authentication (None, Single, Multiple)
+	\item Confidentiality Impact (None, Partial, Complete)
+	\item Integrity Impact (None, Partial, Complete)
+	\item Availability Impact (None, Partial, Complete)
+\end{itemize}
+
 Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl to analyze a complete Docker image.
